### 2015-02-14 doc/StockPrices/stock.prices.Rmd
Initial commit

---
output:
  pdf_document:
    fig_height: 5.5
    fig_width: 8
    highlight: espresso
  html_document:
    fig_height: 5.5
    fig_width: 8
  word_document: default
---

Problem of extreme values in stock prices
=====

```{r,echo=FALSE,warning=FALSE,message=FALSE}
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(data.table)
library(ggplot2)
library(zoo)
library(scales)
source('lib/BL-functions.R')

af.data.collect<- function(data.id,n)
{
  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
    id=strsplit(i,split = '\\.');
    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='',skip=2)[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
}
stock.ref <- setkey(unique(rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/names/',pattern='name.ds.*.csv'),function(i){fread(paste('~/Dropbox/Datastream/AllStocks/names/',i,sep=''),header=T,na.strings = '')})),by='DSCD')[,Stock:=WC05601],DSCD,Stock)

load('data/ref.matrix.RData')
#make DT of it
ref.dt <- setkey(data.table(Stock=ref.matrix[,1],DSCD=rownames(ref.matrix)),DSCD)
sp.id <- setkey(setnames(fread('data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
miss.dt <- data.table(Stock=miss.tkt,DSCD=ref.dt[sp.id][which(is.na(Stock))][,DSCD])
ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],DSCD,Stock)
full.stock.ref <- setkey(unique(merge(stock.ref,ref.dt,all=T),by=c('DSCD','Stock')),DSCD,Stock)
s.id <- setkey(full.stock.ref[ref.dt][,list(DSCD,NAME,Stock)],DSCD)

ds.af <- setkey(unique(af.data.collect('af',1),by=c('Date','DSCD'))[,':='(year=format(Date,'%Y'),af=as.numeric(af),Time=Date)][,Date:=NULL],DSCD)[s.id]
load('doc/StockPrices/pt.prices.RData')
```
## New development

I did another round of iteration in downloading the data from the `DataStream`. This time, I notice inconsistency from my previous downloads.

My set of stocks in PriceTarget folder all labeled with their respective ticker IDs (e.g., for Apple is AAPL). However, when I downloaded the SP500 constituent list, I got odd results: the data for list was complete (i.e, there were 500 rows: each for one stock) but the ticker IDs for some stock were missing. Instead, `DataStream` output the `DSCD` - a `DataStream` unique code for a stock. My further research revealed, that when a company gets delisted from the Exchanges, its ticker can be either dropped from the `DataStream` or assigned to another stock. So, here is a problem: my PT (and EPS) files all ID'ed by the tickers but the SP500 stocks by `DSCD`. In total there were `r stock.ref[sp.id][is.na(Stock)][,list(DSCD,Stock)][,.N]` stocks with missing tickers which I had to manually fill the tickers (luckily, `DataStream` provides a complete company name):

```{r,echo=FALSE,warning=FALSE,comment=""}
stock.ref[sp.id][is.na(Stock)][,list(DSCD,NAME,Stock)][1]
```

After I created a new prices set based on `DSCD` stock identification, I followed Ana Paula's suggestion to check PTs for the adjustment factor (AF). It turns out, that stocks that got adjustment after 2009 (the latest year in my dataset), do not have their PTs adjusted. For example, in June AAPL had a 7:1 stock split (AF=`r 1/7`) and the all history of price information got adjusted by this factor. I had to do the same for price targets (notice the `old.PT` and `PT`):
``` {r,echo=FALSE,warning=FALSE,message=FALSE,comment=""}
pt.prices[Stock=='AAPL'][137,list(Date,old.PT,Stock,PT,priceAdj,priceClose)]
```
There were `r unique(ds.af[year>2010&af!=1],by='DSCD')[,.N]` stocks that had splits since 2010 and I have corrected their PT information.

Here is a new set of plots that are based on the new price dataset and post 2010 PT adjustments.
```{r,echo=FALSE,warning=FALSE,message=FALSE}
ggplot(melt(pt.prices,id.vars = 'q.id',measure.vars = c('tper','trunc.tper')),aes(x=as.Date(q.id),y=value,group=as.Date(q.id)))+geom_boxplot() + facet_wrap(~variable,scale='free_y',ncol=3)+scale_y_continuous(labels = percent)+ylab('Expected return, in percent')+theme_bw()+xlab('Quarters')+ggtitle('Brokers\'s Expected returns: full sample and truncated')

ggplot(melt(pt.prices[,descriptive.f(.SD),by=q.id,.SDcols=c('tper','trunc.tper')][V1=='mean'],id.vars = c('q.id','V1')),aes(x=as.Date(q.id),y=value))+geom_bar(stat='identity')+facet_wrap(~variable,scale='free_y',ncol=3)+scale_y_continuous(labels = percent)+ylab('Average expected return, in percent')+theme_bw()+ggtitle('Average TPER per quarter')+xlab('Quarters')
```

Some descriptive statistics:
```{r,echo=FALSE,warning=FALSE,message=FALSE,results='asis'}
library(pastecs)
library(xtable)
options(xtable.comment = FALSE)
xtable(setnames(pt.prices[,descriptive.f(.SD),.SDcols=c('tper','trunc.tper')],'V1', 'Statistics'))
```
As we see, the situation with `TPER` improved especially in truncated sample. We see that the average trimmed `tper` is `r pt.prices[,mean(trunc.tper,na.rm=T)]*100`\%. That is, on average, brokers expect to rise of a stock price by fifth of the current value.

The full sample continues to show some extreme values. I can continue adjusting price targets  before 2009 but I don't think it is a good idea because we don't know for sure if a stock had been already adjusted in `IBES`. I think, trimming the `tper` is the only solution to avoid the extreme values. 
``` {r,echo=FALSE,warning=FALSE,message=FALSE,comment=""}
head(unique(pt.prices[order(tper,decreasing=T),list(Stock,priceAdj,tper,PT,NAME)],by='Stock'))
```
In case of `DAL`, it seems to be that the stock got delisted but the information stayed with `$0.02` price. 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
ggplot(pt.prices[Stock=='DAL',],aes(x=Date,y=tper))+geom_point()+geom_line()+scale_y_continuous(labels = percent)+ylab('Expected return, in percent')+theme_bw()+ggtitle('The expected return of \'DAL\'')+xlab('Quarters')
```

-------------

# Previous report
As we know, the stock prices in `DataStream` produce very extreme values for the Target Price Expected Return(TPER) when we divide an analyst target price over the stock price: $TPER = TP/P-1$

``` {r, echo=FALSE, message=FALSE,warning=FALSE,cache.vars='pt.prices'} 
#library('ProjectTemplate')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')

load('data/adj.prices.v5.RData')
load('doc/StockPrices/pt.dt.old.RData')
load('doc/StockPrices/all.prices.old.RData')
yahoo.p <- setkey(melt(data.table(Date=index(p),coredata(p)),id.vars = 'Date',variable.name = 'Stock',value.name = 'yahoo')[,yahooPT:=yahoo[c(rep(NA,3),1:(.N-3))],by=Stock][,Stock:=as.character(Stock)],Date,Stock)[Stock=='AAPL',':='(yahoo=yahoo*7,yahooPT=yahooPT*7)]

setkey(pt.dt,Date,Stock)
setkey(all.prices[,Stock:=as.character(Stock)],Date,Stock)
pt.prices <- na.omit(unique(pt.dt)[all.prices[yahoo.p]])[,meanPT:=mean(PT),by=list(Broker,Stock,q.id)]
```

```{r, echo=FALSE,warning=FALSE,cache.vars='analysis.p'}
analysis.p <- pt.prices[,fix.p:=ifelse(priceAdj==0.02,yahoo,priceAdj)][,':='(tperDS=PT/pricePT-1,tperYH=PT/yahooPT-1,tperFix=PT/fix.p-1)][,':='(trunk.yh=truncate.f(tperYH,c(0.01,0.99)),trunk.ds=truncate.f(tperDS,c(0.01,0.99)),trunk.fix=truncate.f(tperFix,c(0.01,0.99))) ][,year:=format(q.id,'%Y')]
```

The following stocks have adjusted price of 2 cents which seems to be a database anomaly as I downloaded various times and got the same result:
```{r, echo=FALSE,comment=""}
unique(pt.prices[priceAdj==0.02],by='Stock')[,list(Date,Stock,priceAdj)]
```
I, then,  turn to another stock price database from `finance.yahoo.com`. Surprisingly, this source has different prices for the same stocks:
```{r,echo=FALSE,warning=FALSE,comment=""}
unique(pt.prices[priceAdj==0.02],by='Stock')[,list(Date,Stock,priceAdj,yahoo,meanPT)]
```
Notice, that average price target (`meanPT`) for the sames stock is very close to the values of the `yahoo` prices.  Giving the fact that `yahoo` seems to have a better stock prices information, I have created three stock prices sets. One is the `DataStream (DS)`, for the second, I completely substitute all prices in my analysis by the  `yahoo (YH)` prices, and third is replaced prices only for anomalous stocks with the `yahoo (Fix)` prices. Here are plots of `TPER` for each of the sets:
```{r, echo=FALSE,warning=FALSE,cache.vars='analysis.p'}
analysis.p <- pt.prices[,fix.p:=ifelse(priceAdj==0.02,yahoo,priceAdj)][,':='(tperDS=PT/pricePT-1,tperYH=PT/yahooPT-1,tperFix=PT/fix.p-1)][,':='(trunk.yh=truncate.f(tperYH,c(0.01,0.99)),trunk.ds=truncate.f(tperDS,c(0.01,0.99)),trunk.fix=truncate.f(tperFix,c(0.01,0.99))) ][,year:=format(q.id,'%Y')]
```

```{r,echo=FALSE,warning=FALSE,message=FALSE}

ggplot(melt(analysis.p,id.vars = 'q.id',measure.vars = c('tperDS','tperYH','tperFix','trunk.ds','trunk.yh','trunk.fix')),aes(x=as.Date(q.id),y=value,group=as.Date(q.id)))+geom_boxplot()+facet_wrap(~variable,scale='free_y',ncol=3)+scale_y_continuous(labels = percent)+ylab('Expected return, in percent')+theme_bw()+ggtitle('Comparison of TPER values for each of the stock prices \n for the full set (top row) and trunkated (bottom row)')+xlab('Years')
```

```{r,echo=FALSE,warning=FALSE}
ggplot(melt(analysis.p[,lapply(.SD,mean,na.rm=T),.SDcols=c('tperDS','tperYH','tperFix','trunk.ds','trunk.yh','trunk.fix'),by=year],id.vars = 'year'),aes(x=as.Date(year,format='%Y'),y=value,color=variable))+geom_bar(stat='identity',fill='white')+facet_wrap(~variable,scale='free_y',ncol=3)+scale_y_continuous(labels = percent)+ylab('Average expected return, in percent')+theme_bw()+ggtitle('Average per year per stock TPER values \n for each of the stock prices databases \n for the full set (top row) and trunkated (bottom row)')+xlab('Years')+theme(legend.position='none')
```

Looking at average per year plot, observe that the `Fix` dataset seems cured the anomaly in the `DataStream` sets as values mostly uniformly distributed. Now we have two options whether to switch completely to the `yahoo` prices or to use `yhaoo` prices for the selected  stocks and keep all others from the `DataStream`.

The table below shows some descriptive statistics for each of the resulted price sets.

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='asis'}
library(pastecs)
library(xtable)
options(xtable.comment = FALSE)
xtable(analysis.p[,descriptive.f(.SD),.SDcols=c('tperDS','tperYH','tperFix','trunk.ds','trunk.yh','trunk.fix')])
```

### 2015-02-14 doc/meeting.Rmd
Initial commit

---
output:
  pdf_document: default
---
Meeting at INESC, on 2014-06-14
=====
Price data
----
- pick some stocks and check 
- get price form data stream ( iterate )

Black-Litterman
--
## Strategy
- create true from non ranking (at t+1)
- same omega, different views

## Story: paper structure
build on top of ssrn paper

### 1. use paper and reproduce strategy

- {views: meanTPER from t-1; conf: coef of variation}

### 2. _Rank matters_
- {views: baseline rankings t-1 (ranking on PT); conf=coef. of variation}

- {views: true ranking(PT), meanTPER from t; conf: 1}

### 3. Last part
- {views: true ranking (EPS), meanTPER from t; conf: 1, coef of variation}

## result assumptions:
- ranking god
- average god
- naive
- default

## Constrains
Run the code with no short-sale

-----

Meeting with Ana Paula 2014-07-28
====
## More research DS PT vs. our PT
1. Check the min and max of $PT/DS.PT$ ratio
2. Contact Thompson/DataStream for help
3. Check AMZN price targets over the net and compare.

### 2015-02-14 doc/paper/chapter-1.Rnw
Initial commit

% \documentclass{article}
% \usepackage{fancyhdr}
% \usepackage{time}
% \usepackage{authblk}
% \usepackage{amsmath, amssymb}
% \usepackage{caption}
% \captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
% \captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
% %\usepackage{fullpage}
% %\usepackage{rotating}
% %\usepackage{xcolor}
% \usepackage[hyphens]{url}
% \usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
% %\usepackage{breakurl}
% \usepackage{times}
% \usepackage{setspace}
% \usepackage{graphicx}
% \usepackage{array}
% \usepackage{tabularx}
% \usepackage{booktabs}
% \usepackage{multirow}
% %\onehalfspacing
% \doublespace
% \usepackage[longnamesfirst]{natbib}
% %\usepackage[natbibapa,longnamesfist]{apacite}
% 
% \DeclareMathOperator*{\argmax}{arg\,max}
% %\newcommand{\r}{\Sexpr{}}
% \DeclareMathOperator{\rank}{rank}
% \DeclareMathOperator*{\median}{median}
% %\newcommand{\theHalgorithm}{\arabic{algorithm}}
% \newcommand{\tr}{\textit{true}}
% \newcommand{\naive}{\textit{recent}}
% \newcommand{\default}{\textit{all-time}}
% \newcommand{\market}{\textit{market}}
% \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
% %\newcommand{\raw}{\textit{raw}}
% %\newcommand{\diff}{\textit{diff}}
% %\newcommand{\random}{\textit{random}}
% %\newcommand{\rollsd}{\textit{roll.sd}}
% 
% 
% \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
% 
% %-------------------------------------------------------------------------
% % take the % away on next line to produce the final camera-ready version
% % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
% %\pagestyle{empty}
% \pagestyle{fancy}
%  
% \newcommand\myTime{\now}
% \fancyhead{}
% \fancyhead[CO, CE]{\texttt{-Draft-}}
% \fancyhead[RO, RE]{\texttt{\today, \myTime}}
% \setlength{\headheight}{2\baselineskip}
% \renewcommand{\headrulewidth}{0pt}
% %-------------------------------------------------------------------------
% 
% 
% \begin{document}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

%<<set-parent, echo=FALSE, cache=FALSE>>=
%set_parent('~/Dropbox/workspace/Projects/Thesis/thesis.Rnw')
%@

<<chp1-load-data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(descr)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
library("PerformanceAnalytics")
load('cache/q.data.RData')
load('cache/final.bl.RData')
load('cache/market.set.RData')
load('cache/example.dt.RData')
source('lib/BL-functions.R')
#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
trunk.percent <- 0.05
stocks <- unique(market.set[,Stock])
#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)

q.data <- na.omit(q.data.full[stocks])
q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
#stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])

### General stat of TP/P-1
#stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')

core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]

#pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])

load('cache/ranked.pt.dt.RData')
n <- 3
n.b <- 3

#options(descr.na.replacement = "noRank")
pt.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.pt.dt,i,n.b)})

###Statistics for views:
###non rank base data
load('cache/nr.views.RData')
load('cache/pt.rank.views.RData')
load('cache/eps.rank.views.RData')
load('cache/ranked.eps.dt.RData')
load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')

complete.dt <- setkey(complete.dt,calQ)[quarters]
eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'calQ','q.id')

eps.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.eps.dt,i,n.b)})

brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))

#Views stat

stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']

stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']

stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']

stat.full <- rbind(stat.nr,stat.pt.view,stat.eps.view)

test <- melt(stat.full,id.vars = c('year','Method','Strategy'))
test.a <- acast(test,year~Method~Strategy~variable,value.var = 'value')

brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))

load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')

final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]

final.bl$Method <- factor(final.bl$Method,levels=strategies)
final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views')),Views~Method~variable,value.var = 'value')

quarters <- unique(final.bl[,Quarters])
periods.id <- c(paste(gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,first,by=4)),gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,last,by=4)),sep='/'),'All period')

periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat)][,sr:=ann.ret/ann.sd]

periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat')),period~Views~Method~strat~variable,value.var = 'value')

start.year <- format(as.Date(final.bl[,head(Quarters,1)]),'%Y')
end.year <- format(as.Date(final.bl[,tail(Quarters,1)]),'%Y')
@

<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
require(gridExtra)
example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
test <- rbind(example.dt[,.(s.Date,PT,Series=Broker)][,Broker:='Broker'],example.dt[,.(s.Date,PT=priceAdj)][,Broker:='AMZN'][,Series:='AMZN'])
test$Series <- factor(test$Series,levels=c('AMZN',as.character(unique(example.dt$Broker))))

ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
@

<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
library(scales)
#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))

colourCount = length(unique(final.bl$Views))
getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))

#p.cum.ret <-
ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)

@

% \title{Are rankings of financial analysts useful to investors?}
%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
% 
% \affil[1]{FEP \& CEF.UP, University of Porto}
% \affil[2]{INESC TEC}
% \affil[4]{FEUP, University of Porto}
% 
% 
% \maketitle
% % You need this here, or else the first page won't have a header.
% \thispagestyle{fancy}
% 
% \begin{abstract}
% Some institutions issue rankings of financial analysts. Given that these rankings are \textit{ex-post} they may not be able useful to investors. In this paper  we show that trading strategies based on past rankings outperform a passive strategy.  In addition, we report that analysts issuing accurate price targets are more favorable to the investors  to follow rather than analysts issuing accurate EPS forecasts. In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
% %Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
% \end{abstract}

\chapter{Are rankings of financial analysts useful to investors?}
\section{Introduction}
\label{sec:intro}

% citations  full for aurtors
The idea that financial analysts play an important role in financial markets is rather consensual \citep{cowles1933csm,obrien1990}. Yet there is some debate on whether following the advice of analysts brings value to investors after transaction costs \citep{womack1996,mikhail2004sae,li2005persistence}. Related to this is the difficulty in identifying the analysts with superior stock picking skills. In this paper, we show that the rankings of financial analysts are useful to investors because strategies based upon these rankings yield positive abnormal returns.

In recent years, some institutions have been very active in publishing and  selling  rankings of financial analysts. Some rankings  are based on privately held surveys of  buy-side analysts (e.g., the Institutional Investor's rankings of the All-America Research Teams\footnote{\url{http://www.institutionalinvestor.com/Research/4560/First-Team.html}} and Bloomberg's America's Best Stock Analysts\footnote{\sloppy \url{http://www.bloomberg.com/news/2013-08-14/jpmorgan-top-stock-picker-with-equities-out-of-lockstep.html}}); others are based on the performance of sell-side analysts (ThomsonReuters' top StarMine analysts\footnote{\url{http://excellence.thomsonreuters.com/award/starmine}}). In any of these cases, the rankings aim at identifying the top analysts. However, aside from personal acknowledgment among peers, it is still arguable whether these are useful \citep{desai2000ass} or are merely ``popularity contests" \citep{emery2009}. %In this paper, we support the argument that the top-ranked analysts, indeed, have stock picking skills.

We show that the top ranked analysts have stock picking skills. The contributions of our research is fourfold. First, we develop a trading strategy that transforms the rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}. Second, we show that annualized cumulative returns generated by some trading strategies  based upon analysts' rankings outperform the passive strategy (e.g., buy-and-hold the general stock market index). Third, we show that the strategy based upon the perfect foresight of rankings yields the highest cumulative annualized return. Fourth, we find that investors  are better off following analysts that issue the most accurate target prices, rather than those that issue the most accurate EPS forecasts.

The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines our proposed  trading strategies; section \ref{sec:rankings} describes the sample and presents some preliminary results; section \ref{sec:results} presents and discusses the results; and section \ref{sec:conclusion} concludes.

\section{Industry Rankings of Financial Analysts}
\label{sec:ranking}

In the financial literature there has been a long debate on whether financial analysts produce valuable  advice. Some argue that following the advice of financial analysts,  translated as recommendations of buying, holding, or selling a particular stock, does not yield  abnormal returns, i.e.,  returns that are above the required return to compensate for risk. The Efficient Market Hypothesis \citep{fama1970ecm} states that financial markets are efficient and that any public available information  regarding a stock would be immediately reflected in prices; hence, it would be  impossible to generate abnormal returns based upon past information.

Yet, several authors have since stressed that  there are information-gathering costs and information is not immediately reflected on prices  \citep{grossman1980iie}. As such, prices may not  reflect all the available information at all time because if this were the case, those who spent resources to collect and analyze   information would not have an incentive to do it because there would not get any compensation for it.

%Many trading strategies try to forecast the price movements relying on the historical prices or estimate the intrinsic value of a company. Obviously, this type of research is associated with significant amount of up-front costs to acquire databases, software, etc. On the other hand, financial analysts have these tools and, presumably, skills to identify  stocks that worth be invested. Thus, for an investor, it is cheaper to follow the recommendations of financial analysts rather than perform a proper stock market analysis.

Some authors show that that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts. \cite{barber2001} finds that over the period of 1986-1996 a portfolio of stocks with the most (least) favorable consensus analyst recommendations yields an average abnormal return of 4.13 (-4.91)\%.}. Assuming that some analysts produce valuable advice it make sense to rank analysts based on the accuracy of their recommendations.

StarMine rankings are based on financial analysts accuracy either on price target or EPS forecasts. To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES). This score measures ``... [a] relative accuracy; that is, analysts are compared against their peers. An analyst's SES can range from 0 to 100, with 50 representing the average analyst. To get a score higher than 50, an analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates"\footnote{\url{http://excellence.thomsonreuters.com/award/starmine?award=Analyst+Awards&award_group=Overall+Analyst+Awards}}.

As for target price ranking, StarMine's methodology compares the portfolios based on analysts recommendations. Portfolios are constructed as follows. For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark. ``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark. ``Hold'' invests one unit in the benchmark (i.e., an excess return of zero). ``Sell" recommendations work in the reverse way. StarMine re-balances its calculations at the end of each month to adjust for analysts revisions (adding, dropping or altering a rating), and when a stock enters or exits an industry grouping.

Recent evidence suggests that top ranked financial analyst affect market participants: prices seem to react more to the recommendations issued by the top-ranked analysts \citep{emery2009}. As such, StarMine ranking based models can be used to identify such analysts and generate superior estimates (e.g., SmartEstimates\footnote{\url{http://www.starmine.com/index.phtml?page_set=sm_products&sub_page_set=sm_professional&topic=analytical&section=accurate_estimates}}).
%Evidence shows that market response to analysts' recommendations is stronger when analysts issue them with a good forecasting tracking record \citep{park2000analyst,loh2006aef}. Thus, it seems to be the case that only a subset of analysts influences the stock prices and, as such, only that subset of analysts deserves to be followed \citep{loh2011}.

The goal of our study is to evaluate if and how rankings  add value to investors.  With this purpose, we develop several sets of active trading strategies, selecting the stocks most favored by analysts. The first strategy is based on the consensus estimate (giving equal weights to analysts' recommendations). The second set of strategies takes in consideration the analysts' target price and EPS accuracy ranks to form ``smart estimates". For the latter set of strategies, we analyse different time information sets of the accuracy of the analysts.

We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy). By doing this, we address the ongoing debate in the literature on whether analysts, when issue the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}). For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices. Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.

A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period’s EPS invested at the cost of equity.}. In short, this model justifies a price earnings ratio for companies where next period’s earnings are expected to grow over and above the normal rate.

% and it is, in a sense, an upper bound of all trading strategies.

%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \tr{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.

%We claim that the ranking strategies outperform the consensus ones as well as the passive strategy.

%we investigate the problem with two ranking  methods that are used further as the inputs for the trading strategy. The first is the \naive{} rankings and this is simply the last known analysts' actual rankings. The second method is taken from the Machine Learning literature \citep{aiguzhinov2010} and it is so-called the \default{} ranking. It is the average rank of an analyst since the beginning of the sample period and it encompasses the average analyst's relative performance. We formalize these methods in the appropriate section of the paper.

\section{Trading Strategies}
%- BL model
%- Information sets
\label{sec:trading}
Our trading strategy use the framework for  active portfolio management proposed by \cite{black1992}.  The model incorporates ``views" in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting. ``Views" are expectations on individual stocks future performance by investors/analysts.

While in the CAPM model expected returns are a function of systematic risk, in the BL model some stocks can be over- or under-priced and, therefore, their alphas are non-zero. The model blends the subjective views of investors about future performance of a stock with the market implicit returns given by CAPM.

\cite{da2011bl} apply the BL model and use the consensus expected returns as a proxy for views. They report that the resulting strategy outperforms a passive buy-and-hold strategy. Our approach is similar to theirs but we define views not only based on consensus estimates but also on smart estimates that account for previous analysts' TP and EPS accuracy.

Here below we kept the notation in \cite{black1992}.  $Q$ is the vector of  expected returns for the eligible stocks; $\Omega$ matrix is the confidence of $Q$. Altogether these two reflect the views of a particular analyst or a set of analysts.

To proxy expected returns we compare the analysts' 12-month target prices (TP) with today's stock price. Confidence $\Omega$ for stock is based on variation  across analysts which is similar to the measure of dispersion in analysts' opinions outlined in \cite{diether2002}.

We define a trading strategy as follows (figure \ref{fig:bl}):
\begin{enumerate}
\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);

\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix across stocks;

\item We apply the BL model to get  optimal portfolio weights on the basis of combining views and implicit returns. We  buy or sell stocks accordingly. At the beginning of $t+1$, based on the new views, we set the new portfolio weights following  steps 1--3.
\end{enumerate}

\subsection{Defining $Q$}
\label{def-q}

For the consensus strategy, we use median of expected returns for a particular stock $s$:
\begin{equation}
\label{consq}
Q_{cons,s}= \median \left\{r_{j,s}\right\}
%\frac{1}{N} \sum_{j=1}^{N} r_{j,s}
\end{equation}
%$N$ is the number of analysts with a valid TP report and
where $r_{j,s}=TP_{j,s}/P_{s}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,s}$ and stock price $P_{s}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement. This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.

For the strategies that weight the analysts' estimates of expected return, we use analysts' rankings and the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.

\begin{equation}
\label{eq:weight}
w_{j,s}=1-\frac{rank_{j,s}-\min{ \{rank \} }}{\max{\{rank \}}}
\end{equation}

The expected rank-weighted return is thus:
\begin{equation}
\label{rankq}
Q_{rank,s}=\frac{\sum_{j=1}^{N} (w_{j,s} \times r_{j,s})}{\sum_{j=1}^{N} w_{j,s}}
\end{equation}
$N$ is the number of analysts.

As described above, we use target price and EPS rankings.

\subsubsection{Target Price ranking}

Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}. First,  we define the forecast daily error  $FE_{i,j}$ as the absolute value of the difference between analysts' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:

\begin{equation}
\label{dfe}
FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
\end{equation}
The PMAFE is given as:
\begin{equation}
\label{tp:pmafe}
PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
\end{equation}
where $\overline{{FE}_{t,s}^{TP}}$ is the average over quarter forecasting error. The target price is fixed over the quarter unless it gets revised.

The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
\begin{equation}
\overline{PMAFE_{j,s}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,s}^{TP}
\end{equation}

\begin{equation}
\label{tp:rank}
rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
\end{equation}
where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.

\subsubsection{EPS ranking} 
To compute the EPS rankings, we apply the same procedure as above:
\begin{equation}
FE_{j,s}^{EPS}=|{ACT_{s}-PRED_{j,s}}|
\end{equation}
\begin{equation}
PMAFE_{j,s}^{EPS}= \frac{FE_{j,s}^{EPS}}{\overline{FE_{s}^{EPS}}}
\end{equation}
\begin{equation}
\label{eps:rank}
rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\} 
\end{equation}
where $ACT_{s}$ and $PRED_{j,s}$ are the actual and  analyst $j$ forecast EPS respectively for each stock $s$.

\subsection{Defining the confidence of expected returns $\Omega$}
\label{def-omega}
The confidence of $Q$ are given by the coefficient of variation of forecasting errors:

\begin{equation}
CV = \frac{\sigma (FE)}{\overline{FE}}
\end{equation}
where $\sigma$ and $\overline{FE}$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS. A low value of $CV$ reflects consensual estimates of either future prices or EPS.

\subsection{Information sets to define the views}

To proceed with the trading strategy, we need to establish which information we going to use to build the rankings that will be used to compute the weighted return estimates. Different analysts' ranks are obtained  if we select different time horizons. If use only recent information, we focus on recent performance of the analysts. This, of course, is more sensitive to unique episodes (e.g., a quarter, which has been surprisingly good or bad). If, alternatively, we opt to incorporate all analyst performance, the ranking is less affected by such events, yet, it may not reflect the current abilities of the analyst. In this paper, we use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst. We call the former the \naive{} set and the latter the \default{} set.

In addition to these sets,  we also create a hypothetical scenario that assumes we know the future information about the analyst' accuracy performance which would only be available at the end of $t$. In this setting, we are assuming that we could  perfectly predict the true analysts' ranking in advance. This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies. We call this approach as the \tr{} set.

We formalize these sets as follows. 
\begin{itemize}
\item  the \tr{} %-- a perfect foresight information:
\begin{equation}
\label{q:true}
\widehat{Q_{.,t}}=Q_{.,t}
\end{equation}

\item  the \naive{} % -- $t-$ information:
\begin{equation}
\label{q:naive}
\widehat{Q_{.,t}}=Q_{.,t-1}
\end{equation}

\item  the \default{} %-- the entire history of analysts performance:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{q:default}
\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
%\end{equation}
%\end{itemize}
\end{itemize}
where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).

\section{Data and preliminary results}
\label{sec:rankings}

\subsection{Database and sample}
We focus on the  S\&P500 stocks. We extract the target price information and the EPS forecasts from ThomsonReuters  I/B/E/S detailed history database. The  S\&P500 constituents' list and the stock daily prices are from ThomsonReuters DataStream.

The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks. Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised. After one year we assume that TP recommendation expires.

Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}). This is done due to occurrence of the extreme values. Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases. In some cases the stock-splits and the dividends were not properly adjusted.}. After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the EPS ranking, we require that a stock had at least three brokers per quarter. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.

Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data. Panel A shows the number of quarterly target prices per stock. For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations. Each stock had on average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} quarterly target price reports. Panel B  presents similar statistics of the number of EPS forecasts. In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations. The average number of quarterly forecasts is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.

We apply the ranking procedure outline in section \ref{def-q} on two datasets. For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq. \ref{tp:pmafe}).

Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}. Four analysts had valid target price for Amazon for second quarter of 1999. We plot the daily Amazon price against the brokers' target prices. Table \ref{tab:example} shows the resulting TP and EPS ranking. On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate. For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.

%The daily frequency allows us to capture the analysts' performance with better precision. Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices. As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock. At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts. Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices. The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4). In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
\subsection{Ranking contingency results}
We consider  three terciles (\textit{top}, \textit{medium}, \textit{bottom}). In one particular quarter ($t$), we place  analysts at one of these bins which corresponds to a tercile. We, then,  check analysts position at the immediate next quarter ($t+1$) and after one year ($t+4$).

We convert the rankings into scores as follows:
\begin{equation}
\label{eq:score}
score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
\end{equation}

To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,s}$
\begin{equation}
\label{eq:mean-score}
score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
\end{equation}
where $k$ is number of stocks for which an analyst $j$ had rank.

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on the accuracy in target prices. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter and even after one year. The case of EPS ranking shows similar results (panel B). This analysis confirms recent finding of \cite{hilary2013} on analyst forecast consistency.

%the next quarter  $top_{t+1}$ group is as follows: \Sexpr{round(pt.cont.tab[[1]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][3,1],3)*100}\% from the $bottom_{t-1}$. It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank. %Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[1]][4,4],3)*100}\%). This suggests that analysts are not frequent in issuing target price reports.

%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
%An interesting observation is for the \emph{noRank} category: \Sexpr{ round(cont.tab[[2]][4,1],3)*100}\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.

%Panel B depicts the similar analysis for the EPS forecast rankings. For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$. %However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[1]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[1]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[1]][4,3],3)*100}\%. This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.

\subsection{$Q$ descriptive statistics}

Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets. The expected returns  are computed comparing TP estimates with actual price. To inform the strategies we obtain rank-weighted estimates where weights are given either by the TP or the EPS ranks.

\cite{bradshaw2002} reports that analysts' average expected returns for the period of 2000--2009 of 206 brokers 24\%, in \cite{da2011} these average expected return post 40\% for the period of 1996--2004, \cite{zhou2013} find on average  96\% for the sample period of 2000--2009 reports. The figures suggest that analyst overly optimistic.
%these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns. \cite{bodie2009} show that arithimatic average rate of return for the U.S. large stocks (S\&P 500) for the period of 1926--2005 is 10.17\% and the average rate of excess return is 8.39\% with the risk premium estimated 6--8\%. While it is not the best idea to extrapolate the historical values, still, we can say that the expected stocks return should be around 14--16\%. Clearly, the values presented in the literature shows that analysts are very optimistic in issuing target price reports.

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{ round(stat.pt.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.pt.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.pt.view[year=='Total'&Method=='default',mean],3)*100}\%). Panel C shows the EPS based weighted expected returns averages (\Sexpr{ round(stat.eps.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.eps.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.eps.view[year=='Total'&Method=='default',mean],3)*100}\%).

Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns considering that it includes the whole history of analysts' performance.

%obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

%put in to the different section

\section{Empirical Results}
\label{sec:results}

We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.

\subsection{Passive strategy}
Panel A shows  the performance of the passive strategy \textit{Market}. The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results[4,1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results[4,1,'ann.sr'],3)}. The average number of stocks used per quarter is \Sexpr{ round(bl.results[4,1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results[4,1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results[1,1,1],2)}\%, \Sexpr{round(bl.results[2,1,1],2)}\%, \Sexpr{round(bl.results[3,1,1],2)}\%. All the strategies outperform the benchmark (\Sexpr{round(bl.results[4,1,1],2)}\%). The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy. In any case, the results suggest that the advice of analysts are valuable. 
%Yet, the top analyst

%The result confirms that these strategies set an upper bound for the cumulative return yield. It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.

The \textit{TP} rankings strategy dominates also in the risk-adjusted setting. Its Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies. In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. Panel A of the table corresponds to the perfect foresight information set. The TP strategy wins over the others in every period.

While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking. One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied. For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.

\subsection{Feasible strategies}
Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets. As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.

As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy. The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively). The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.

The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively). The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

The feasible information sets demonstrate interesting results. It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus. Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}. Thus, rankings are useful for investors.

%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports. Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.

%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}. In addition, the results show that keeping all available information about analysts' performance does not create any value. As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.

Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable. Yet, it is not the case for EPS ranking.  This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts). EPS are not good predictors of future returns, at least for short-term horizon.

Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets. The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}. Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.

\section{Conclusions}
\label{sec:conclusion}

Some institutions, such as StarMine, rank financial analysts based on their accuracy. These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors. Therefore, there is a growing interest in understanding the relative performance of analysts.

We show that rankings do bring value to investors as they identify the top analysts. By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets. We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve. The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets. %The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.

For the future work we would like to develop the new methods to be able to get closer to the upper bound.

% 
% \bibliographystyle{ecta}
% %\bibliographystyle{newapa}
% \bibliography{rank}
% \appendix

%\section{Tables and Figures}

%Descriptive  table
\begin{table}[hp]
  \caption{Sample Statistics}
  \label{tab:ret-stat}
\ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
Year & Min& Mean & Median &Max& Std.dev\\
\midrule
%Panel A: TP&&&&&\\
\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
\midrule
%Year & Min& Mean & Median &Max& Std.dev\\
<<desc-pt,echo=F,results='asis'>>=

#data.to.display <- c('min','mean', 'median','max','std.dev')
#results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])

options(xtable.comment = FALSE)
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
@
\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
\midrule
<<desc-eps,echo=F,results='asis'>>=
print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
@
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Example of ranking}
  \label{tab:example}
\ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999. We apply (\ref{tp:rank}) to obtain the ranks of the brokers. \emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error. For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts. 
\begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
    \multicolumn{4}{c}{\textbf{Panel A: TP}} \\
<<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
print(xtable(setnames(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'\\emph{TP}'=PT,'$\\overline{PMAFE}^{TP}$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],4,'$rank^{TP}$'),display=c('s','d','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
    \multicolumn{4}{c}{\textbf{Panel B: EPS}} \\
<<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
print(xtable(setnames(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'$PRED$'=Est,'$PMAFE^{EPS}$'=eps.pmafe,rank)][order(rank)],4,'$rank^{EPS}$'),display=c('s','d','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

% Descritive rankings
 \begin{table}[hp]
  \caption{Analysts' accuracy consistency}
  \label{tab:rank-stat}

\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins. Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\

<<desc-rank-pt-t1,echo=F,results='asis'>>=
tab=1
tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)

tab=2
tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
<<desc-rank-eps-t1,echo=F,results='asis'>>=
tab=1
tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
tab=2
tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
  \label{tab:view-stat}
  \small\addtolength{\tabcolsep}{-2pt}

\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).

\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \toprule
Year &Stocks& Mean & Median &Std.dev\\
\midrule
<<desc-nr.views,echo=F,results='asis'>>=

print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
@
  \midrule
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-r.views,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-eps.views,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
@
\bottomrule
  \end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
  \label{tab:view-stat-naive}
  \small\addtolength{\tabcolsep}{-2pt}

\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.

\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \toprule
Year &Stocks& Mean & Median &Std.dev\\
\midrule
<<desc-nr.views-naive,echo=F,results='asis'>>=

print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
@
  \midrule
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-r.views-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-eps.views-naive,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
@
\bottomrule
  \end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
  \label{tab:view-stat-default}
  \small\addtolength{\tabcolsep}{-2pt}

\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.

\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \toprule
Year &Stocks& Mean & Median &Std.dev\\
\midrule
<<desc-nr.views-default,echo=F,results='asis'>>=

print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
@
  \midrule
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-r.views-default,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{5}{Y}}
  \midrule
<<desc-eps.views-default,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
@
\bottomrule
  \end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Trading strategy performance}
  \label{tab:strategy}
  \ This table shows the performance statistics of the different trading strategies. Panel A presents the results for the passive strategy. Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}). Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average. The trading period spreads from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
<<bl-market,echo=F,results='asis'>>=
bl.results.tab <- bl.results
dimnames(bl.results.tab)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
results.final <- bl.results.tab[4,1,]
cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
cat('\\midrule \n')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
<<bl-nr,echo=F,results='asis'>>=
print(xtable(bl.results.tab[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
print(xtable(bl.results.tab[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
print(xtable(bl.results.tab[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[hp]
  \caption{Trading strategy performance: Sharpe ratio}
  \label{tab:substrategy}
  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods. Panel A represents the perfect foresight information set; panels B and C show, respectively, the recent and the all history analysts' performance. 
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
<<sr-true,echo=F,results='asis'>>=

#results.final <- bl.results['Market',1,]
cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
cat('\\midrule \n')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
<<sr-naive,echo=F,results='asis'>>=
print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
cat('\\midrule \n')
@
%\midrule
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
<<sr-default,echo=F,results='asis'>>=
print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
@
\bottomrule
\end{tabularx}
\end{table}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\linewidth]{figure/Black-litterman}
\end{center}
\caption{Trading strategy timeline}
\label{fig:bl}
\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\linewidth]{figure/example-fig-1}
\end{center}
\caption{Daily stock price Amazon and brokers target prices}
\label{fig:example}
\ Target price and actual prices for Amazon  the second quarter of 1999.
\end{figure}

\begin{figure}[hp]
\begin{center}
\includegraphics[width=\linewidth]{figure/bl-results-fig-1}
\end{center}
\caption{Performance of the BL model}
\label{fig:bl-results}
\ Quarterly performance of the cumulative portfolio wealth for all strategies. Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$. \textit{TP} is the strategy with rankings based on the accuracy in target prices, \textit{CONS} is the strategy based on the consensus among the analysts regarding a stock's expected return. \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts. The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}
\end{figure}

%\end{document}

### 2015-02-14 doc/paper/chapter-1.tex
Initial commit

--- 2015-02-14 doc/paper/chapter-1.Rnw
@@
+\documentclass{book}
+\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
+\newcommand{\SweaveOpts}[1]{}  % do not interfere with LaTeX
+\newcommand{\SweaveInput}[1]{} % because they are not real TeX commands
+\newcommand{\Sexpr}[1]{}       % will only be parsed by R
+
+\usepackage{fancyhdr}
+\usepackage{time}
+\usepackage{authblk}
+\usepackage{amsmath, amssymb}
+\usepackage{caption}
+\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
+\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
+%\usepackage{fullpage}
+\usepackage{rotating}
+%\usepackage{xcolor}
+\usepackage[hyphens]{url}
+\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
+%\usepackage{breakurl}
+\usepackage{times}
+\usepackage{setspace}
+\usepackage{graphicx}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{booktabs}
+\usepackage{multirow}
+%\onehalfspacing
+\doublespace
+\usepackage[longnamesfirst]{natbib}
+%\usepackage[natbibapa,longnamesfist]{apacite}
+
+\DeclareMathOperator*{\argmax}{arg\,max}
+%\newcommand{\r}{\Sexpr{}}
+\DeclareMathOperator{\rank}{rank}
+\DeclareMathOperator*{\median}{median}
+%\newcommand{\theHalgorithm}{\arabic{algorithm}}
+\newcommand{\tr}{\textit{true}}
+\newcommand{\naive}{\textit{recent}}
+\newcommand{\default}{\textit{all-time}}
+\newcommand{\market}{\textit{market}}
+\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
+\newcommand{\raw}{\textit{raw}}
+\newcommand{\diff}{\textit{diff}}
+\newcommand{\random}{\textit{random}}
+\newcommand{\rollsd}{\textit{roll.sd}}
+
+\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
+
+%-------------------------------------------------------------------------
+% take the % away on next line to produce the final camera-ready version
+% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
+%\pagestyle{empty}
+\pagestyle{fancy}
+
+\newcommand\myTime{\now}
+\fancyhead{}
+\fancyhead[CO, CE]{\texttt{-Draft-}}
+\fancyhead[RO, RE]{\texttt{\today, \myTime}}
+\setlength{\headheight}{2\baselineskip}
+\renewcommand{\headrulewidth}{0pt}
+%-------------------------------------------------------------------------
+
+\begin{document}
 % \documentclass{article}
@@
 
-<<include=FALSE>>=
-library(knitr)
-opts_chunk$set(concordance=TRUE)
-@
-
-%<<set-parent, echo=FALSE, cache=FALSE>>=
-%set_parent('~/Dropbox/workspace/Projects/Thesis/thesis.Rnw')
-%@
-
-<<chp1-load-data,echo=F,warning=FALSE,message=FALSE>>=
-strategies <- c('true','recent','all-time')
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
-library(reshape2)
-library(descr)
-library(data.table)
-library(ggplot2)
-library(stringr)
-library(zoo)
-library(xtable)
-library("PerformanceAnalytics")
-load('cache/q.data.RData')
-load('cache/final.bl.RData')
-load('cache/market.set.RData')
-load('cache/example.dt.RData')
-source('lib/BL-functions.R')
-#library(ProjectTemplate)
-#load.project()
-###ADD NAs for the case of no ranking ( if NA, no raking)
-trunk.percent <- 0.05
-stocks <- unique(market.set[,Stock])
-#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
-q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)
-
-q.data <- na.omit(q.data.full[stocks])
-q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
-#stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])
-
-### General stat of TP/P-1
-#stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')
-
-core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
-
-#pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
-quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])
-
-load('cache/ranked.pt.dt.RData')
-n <- 3
-n.b <- 3
-
-#options(descr.na.replacement = "noRank")
-pt.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.pt.dt,i,n.b)})
-
-###Statistics for views:
-###non rank base data
-load('cache/nr.views.RData')
-load('cache/pt.rank.views.RData')
-load('cache/eps.rank.views.RData')
-load('cache/ranked.eps.dt.RData')
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
-
-complete.dt <- setkey(complete.dt,calQ)[quarters]
-eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'calQ','q.id')
-
-eps.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.eps.dt,i,n.b)})
-
-brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
-
-#Views stat
-
-stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']
-
-stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']
-
-stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']
-
-stat.full <- rbind(stat.nr,stat.pt.view,stat.eps.view)
-
-test <- melt(stat.full,id.vars = c('year','Method','Strategy'))
-test.a <- acast(test,year~Method~Strategy~variable,value.var = 'value')
-
-brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
-
-load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
-
-final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]
-
-final.bl$Method <- factor(final.bl$Method,levels=strategies)
-final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
-final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
-bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views')),Views~Method~variable,value.var = 'value')
-
-quarters <- unique(final.bl[,Quarters])
-periods.id <- c(paste(gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,first,by=4)),gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,last,by=4)),sep='/'),'All period')
-
-periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat)][,sr:=ann.ret/ann.sd]
-
-periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat')),period~Views~Method~strat~variable,value.var = 'value')
-
-start.year <- format(as.Date(final.bl[,head(Quarters,1)]),'%Y')
-end.year <- format(as.Date(final.bl[,tail(Quarters,1)]),'%Y')
-@
-
-<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-require(gridExtra)
-example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
-test <- rbind(example.dt[,.(s.Date,PT,Series=Broker)][,Broker:='Broker'],example.dt[,.(s.Date,PT=priceAdj)][,Broker:='AMZN'][,Series:='AMZN'])
-test$Series <- factor(test$Series,levels=c('AMZN',as.character(unique(example.dt$Broker))))
-
-ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
-@
-
-<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-library(scales)
-#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))
-
-colourCount = length(unique(final.bl$Views))
-getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-
-#p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
-
-@
-
 % \title{Are rankings of financial analysts useful to investors?}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{figure/Black-litterman}
+\end{center}
+\caption{Trading strategy timeline}
+\label{fig:bl}
+\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
+\end{figure}
+
 We define a trading strategy as follows (figure \ref{fig:bl}):
@@
 
-The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
+The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 361, covering 504 S\&P500 stocks.
 Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
@@
 
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and at the 95\textsuperscript{th} percentile (values above 0.791).
 This is done due to occurrence of the extreme values.
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
-
-The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
+After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 145 630 to 131 068.
+
+The initial file of quarterly EPS forecast consists of  571 brokers covering 3655 stocks.
 To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+Our final sample of EPS forecasts consist of  169 brokers covering 449 stocks.
+The total number of observation is 106 609.
+
+\begin{table}
+  \caption{Sample Statistics}
+  \label{tab:ret-stat}
+\ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+    \toprule
+Year & Min& Mean & Median &Max& Std.dev\\
+\midrule
+%Panel A: TP&&&&&\\
+\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
+\midrule
+%Year & Min& Mean & Median &Max& Std.dev\\
+ 1999 & 3.00 & 4.25 & 4 &  10 & 1.59 \\ 
+  2000 & 3.00 & 4.76 & 4 &  14 & 1.88 \\ 
+  2001 & 3.00 & 5.25 & 5 &  15 & 2.32 \\ 
+  2002 & 3.00 & 6.04 & 5 &  19 & 2.95 \\ 
+  2003 & 3.00 & 6.67 & 6 &  21 & 3.43 \\ 
+  2004 & 3.00 & 7.12 & 6 &  21 & 3.62 \\ 
+  2005 & 3.00 & 7.35 & 7 &  21 & 3.59 \\ 
+  2006 & 3.00 & 7.41 & 7 &  20 & 3.42 \\ 
+  2007 & 3.00 & 7.05 & 6 &  20 & 3.33 \\ 
+  2008 & 3.00 & 6.37 & 6 &  18 & 2.88 \\ 
+  2009 & 3.00 & 5.15 & 5 &  18 & 2.19 \\ 
+  Total & 3.00 & 6.42 & 6 &  21 & 3.21 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\midrule
+\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
+\midrule
+ 1999 & 3.00 & 6.26 & 5 &  20 & 3.40 \\ 
+  2000 & 3.00 & 6.22 & 5 &  40 & 3.45 \\ 
+  2001 & 3.00 & 6.59 & 6 &  24 & 3.36 \\ 
+  2002 & 3.00 & 7.15 & 6 &  48 & 4.02 \\ 
+  2003 & 3.00 & 7.43 & 6 &  26 & 3.91 \\ 
+  2004 & 3.00 & 8.02 & 7 &  32 & 4.35 \\ 
+  2005 & 3.00 & 8.28 & 7 &  30 & 4.30 \\ 
+  2006 & 3.00 & 8.80 & 8 &  54 & 4.88 \\ 
+  2007 & 3.00 & 8.29 & 7 &  40 & 4.42 \\ 
+  2008 & 3.00 & 7.17 & 6 &  34 & 3.67 \\ 
+  2009 & 3.00 & 6.39 & 6 &  30 & 3.29 \\ 
+  Total & 3.00 & 7.48 & 6 &  54 & 4.11 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
 
@@
 Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-Each stock had on average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} quarterly target price reports.
+For the sample period (1999-2009), we report 13 672 stock-quarter observations.
+Each stock had on average of 6.42 quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-The average number of quarterly forecasts is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.
+In total, the EPS forecast sample has 14 231 stock-quarter observations.
+The average number of quarterly forecasts is 7.49.
 
@@
 \ref{tp:pmafe}).
+
+\begin{table}
+  \caption{Example of ranking}
+  \label{tab:example}
+\ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999.
+We apply (\ref{tp:rank}) to obtain the ranks of the brokers.
+\emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error.
+For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts.
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+    \toprule
+    \multicolumn{4}{c}{\textbf{Panel A: TP}} \\
+Broker/Analyst & \emph{TP} & $\overline{PMAFE}^{TP}$ & $rank^{TP}$ \\ 
+  \midrule 
+LEGG & 58.50 & 0.05 &   1 \\ 
+  MONTSEC & 87.50 & 0.46 &   2 \\ 
+  KAUFBRO & 125.00 & 1.65 &   3 \\ 
+  DLJ & 140.00 & 1.97 &   4 \\ 
+   \midrule
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+    \multicolumn{4}{c}{\textbf{Panel B: EPS}} \\
+Broker/Analyst & $PRED$ & $PMAFE^{EPS}$ & $rank^{EPS}$ \\ 
+  \midrule 
+PACCREST & -0.130 & 0.066 &    1 \\ 
+  BACHE & -0.135 & 0.088 &    2 \\ 
+  MONTSEC & -0.082 & 0.146 &    3 \\ 
+  HAMQUIST & -0.075 & 0.176 &    4 \\ 
+  BEAR & -0.073 & 0.183 &    5 \\ 
+  FBOSTON & -0.065 & 0.219 &    6 \\ 
+  RBRTSON & -0.011 & 0.457 &    7 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
 
@@
 For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{figure/example-fig-1}
+\end{center}
+\caption{Daily stock price Amazon and brokers target prices}
+\label{fig:example}
+\ Target price and actual prices for Amazon  the second quarter of 1999.
+\end{figure}
 
@@
 
+% Descritive rankings
+ \begin{table}
+  \caption{Analysts' accuracy consistency}
+  \label{tab:rank-stat}
+
+\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins.
+Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+    \toprule
+\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+
+ &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
+  &$middle$ & 30.5 & 47.8 & 21.7 & 100.0 \\ 
+  &$bottom$ & 13.7 & 16.9 & 69.4 & 100.0 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 46.6 & 27.9 & 25.6 & 100.0 \\ 
+  &$middle$ & 39.0 & 29.1 & 31.9 & 100.0 \\ 
+  &$bottom$ & 32.7 & 26.4 & 40.9 & 100.0 \\
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\midrule
+\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+ &$top$ & 51.8 & 26.5 & 22.0 & 100.3 \\ 
+  &$middle$ & 40.0 & 35.2 & 24.9 & 100.1 \\ 
+  &$bottom$ & 31.7 & 21.7 & 46.5 & 100.0 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 42.0 & 29.5 & 29.5 & 101.0 \\ 
+  &$middle$ & 38.9 & 28.9 & 32.7 & 100.4 \\ 
+  &$bottom$ & 35.0 & 25.9 & 40.0 & 100.9 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
 Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
@@
 
-%the next quarter  $top_{t+1}$ group is as follows: \Sexpr{round(pt.cont.tab[[1]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][3,1],3)*100}\% from the $bottom_{t-1}$.
+%the next quarter  $top_{t+1}$ group is as follows: round(pt.cont.tab[[1]][1,1],3)*100\%  of analysts stay at the same ranking category from the $top_{t-1}$; round(pt.cont.tab[[1]][2,1],3)*100\% move from the $middle_{t-1}$; round(pt.cont.tab[[1]][3,1],3)*100\% from the $bottom_{t-1}$.
 It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank.
-%Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[1]][4,4],3)*100}\%).
+%Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (round(cont.tab[[1]][4,4],3)*100\%).
 This suggests that analysts are not frequent in issuing target price reports.
@@
 %This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
-%An interesting observation is for the \emph{noRank} category: \Sexpr{ round(cont.tab[[2]][4,1],3)*100}\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.
+%An interesting observation is for the \emph{noRank} category:  round(cont.tab[[2]][4,1],3)*100\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.
 
@@
 For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$.
-%However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[1]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[1]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[1]][4,3],3)*100}\%.
+%However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes round(eps.cont.tab[[1]][4,1],3)*100\%, for the \emph{middle} --- round(eps.cont.tab[[1]][4,2],3)*100\%, and for the \emph{bottom} --- round(eps.cont.tab[[1]][4,3],3)*100\%.
 This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.
@@
 \subsection{$Q$ descriptive statistics}
+
+ \begin{table}
+  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
+  \label{tab:view-stat}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 & 219 & 0.28 & 0.27 & 0.12 \\ 
+  2000 & 295 & 0.28 & 0.27 & 0.12 \\ 
+  2001 & 341 & 0.25 & 0.24 & 0.13 \\ 
+  2002 & 375 & 0.22 & 0.20 & 0.12 \\ 
+  2003 & 393 & 0.19 & 0.18 & 0.12 \\ 
+  2004 & 402 & 0.15 & 0.14 & 0.09 \\ 
+  2005 & 418 & 0.14 & 0.14 & 0.10 \\ 
+  2006 & 424 & 0.15 & 0.14 & 0.10 \\ 
+  2007 & 427 & 0.14 & 0.13 & 0.09 \\ 
+  2008 & 419 & 0.16 & 0.15 & 0.10 \\ 
+  2009 & 365 & 0.22 & 0.20 & 0.13 \\ 
+  Total & 448 & 0.19 & 0.17 & 0.12 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 219 & 0.24 & 0.24 & 0.10 \\ 
+  2000 & 295 & 0.24 & 0.23 & 0.10 \\ 
+  2001 & 341 & 0.21 & 0.21 & 0.10 \\ 
+  2002 & 375 & 0.18 & 0.17 & 0.10 \\ 
+  2003 & 393 & 0.16 & 0.15 & 0.09 \\ 
+  2004 & 402 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 418 & 0.12 & 0.12 & 0.08 \\ 
+  2006 & 424 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 427 & 0.12 & 0.12 & 0.08 \\ 
+  2008 & 419 & 0.13 & 0.12 & 0.09 \\ 
+  2009 & 365 & 0.18 & 0.17 & 0.10 \\ 
+  Total & 448 & 0.16 & 0.14 & 0.10 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 166 & 0.17 & 0.14 & 0.12 \\ 
+  2000 & 248 & 0.19 & 0.17 & 0.12 \\ 
+  2001 & 292 & 0.17 & 0.16 & 0.11 \\ 
+  2002 & 330 & 0.18 & 0.16 & 0.11 \\ 
+  2003 & 349 & 0.16 & 0.14 & 0.10 \\ 
+  2004 & 363 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 372 & 0.12 & 0.12 & 0.08 \\ 
+  2006 & 383 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 391 & 0.12 & 0.11 & 0.08 \\ 
+  2008 & 379 & 0.14 & 0.13 & 0.10 \\ 
+  2009 & 304 & 0.18 & 0.17 & 0.11 \\ 
+  Total & 417 & 0.15 & 0.13 & 0.10 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
+
+\begin{table}
+  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
+  \label{tab:view-stat-naive}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 &  71 & 0.26 & 0.26 & 0.13 \\ 
+  2000 & 257 & 0.28 & 0.27 & 0.12 \\ 
+  2001 & 310 & 0.26 & 0.25 & 0.13 \\ 
+  2002 & 360 & 0.22 & 0.20 & 0.13 \\ 
+  2003 & 376 & 0.21 & 0.20 & 0.12 \\ 
+  2004 & 388 & 0.15 & 0.14 & 0.10 \\ 
+  2005 & 403 & 0.14 & 0.14 & 0.09 \\ 
+  2006 & 419 & 0.15 & 0.14 & 0.10 \\ 
+  2007 & 423 & 0.14 & 0.13 & 0.10 \\ 
+  2008 & 422 & 0.14 & 0.14 & 0.09 \\ 
+  2009 & 405 & 0.23 & 0.21 & 0.14 \\ 
+  Total & 448 & 0.19 & 0.17 & 0.12 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  71 & 0.24 & 0.23 & 0.11 \\ 
+  2000 & 257 & 0.24 & 0.24 & 0.10 \\ 
+  2001 & 310 & 0.22 & 0.22 & 0.10 \\ 
+  2002 & 360 & 0.19 & 0.17 & 0.10 \\ 
+  2003 & 376 & 0.17 & 0.17 & 0.09 \\ 
+  2004 & 388 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 403 & 0.12 & 0.11 & 0.08 \\ 
+  2006 & 419 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 423 & 0.12 & 0.11 & 0.08 \\ 
+  2008 & 422 & 0.12 & 0.11 & 0.08 \\ 
+  2009 & 405 & 0.19 & 0.18 & 0.11 \\ 
+  Total & 448 & 0.16 & 0.14 & 0.10 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  54 & 0.14 & 0.12 & 0.10 \\ 
+  2000 & 212 & 0.18 & 0.16 & 0.12 \\ 
+  2001 & 273 & 0.18 & 0.16 & 0.11 \\ 
+  2002 & 316 & 0.17 & 0.16 & 0.11 \\ 
+  2003 & 337 & 0.17 & 0.16 & 0.10 \\ 
+  2004 & 350 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 364 & 0.12 & 0.12 & 0.08 \\ 
+  2006 & 380 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 389 & 0.12 & 0.11 & 0.09 \\ 
+  2008 & 385 & 0.13 & 0.12 & 0.09 \\ 
+  2009 & 351 & 0.18 & 0.18 & 0.12 \\ 
+  Total & 417 & 0.15 & 0.13 & 0.10 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
+
+\begin{table}
+  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
+  \label{tab:view-stat-default}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 & 219 & 0.28 & 0.27 & 0.12 \\ 
+  2000 & 295 & 0.28 & 0.27 & 0.11 \\ 
+  2001 & 346 & 0.27 & 0.26 & 0.11 \\ 
+  2002 & 380 & 0.25 & 0.24 & 0.11 \\ 
+  2003 & 399 & 0.24 & 0.23 & 0.10 \\ 
+  2004 & 415 & 0.22 & 0.21 & 0.10 \\ 
+  2005 & 432 & 0.20 & 0.20 & 0.09 \\ 
+  2006 & 444 & 0.19 & 0.19 & 0.09 \\ 
+  2007 & 445 & 0.18 & 0.18 & 0.09 \\ 
+  2008 & 448 & 0.18 & 0.18 & 0.08 \\ 
+  2009 & 448 & 0.19 & 0.18 & 0.08 \\ 
+  Total & 448 & 0.22 & 0.20 & 0.10 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 219 & 0.24 & 0.24 & 0.10 \\ 
+  2000 & 295 & 0.24 & 0.24 & 0.10 \\ 
+  2001 & 346 & 0.23 & 0.23 & 0.09 \\ 
+  2002 & 380 & 0.22 & 0.21 & 0.09 \\ 
+  2003 & 399 & 0.20 & 0.20 & 0.09 \\ 
+  2004 & 415 & 0.19 & 0.18 & 0.08 \\ 
+  2005 & 432 & 0.17 & 0.16 & 0.08 \\ 
+  2006 & 444 & 0.17 & 0.16 & 0.08 \\ 
+  2007 & 445 & 0.16 & 0.16 & 0.07 \\ 
+  2008 & 448 & 0.16 & 0.15 & 0.07 \\ 
+  2009 & 448 & 0.16 & 0.16 & 0.07 \\ 
+  Total & 448 & 0.19 & 0.18 & 0.09 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 185 & 0.17 & 0.15 & 0.11 \\ 
+  2000 & 259 & 0.19 & 0.17 & 0.11 \\ 
+  2001 & 315 & 0.21 & 0.20 & 0.10 \\ 
+  2002 & 351 & 0.22 & 0.21 & 0.10 \\ 
+  2003 & 369 & 0.21 & 0.21 & 0.10 \\ 
+  2004 & 385 & 0.20 & 0.19 & 0.09 \\ 
+  2005 & 397 & 0.18 & 0.18 & 0.08 \\ 
+  2006 & 411 & 0.18 & 0.17 & 0.08 \\ 
+  2007 & 417 & 0.18 & 0.17 & 0.08 \\ 
+  2008 & 420 & 0.18 & 0.17 & 0.08 \\ 
+  2009 & 421 & 0.18 & 0.18 & 0.07 \\ 
+  Total & 421 & 0.19 & 0.18 & 0.09 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
 
@@
 (\ref{consq}).
-The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{ round(stat.pt.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.pt.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.pt.view[year=='Total'&Method=='default',mean],3)*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{ round(stat.eps.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.eps.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.eps.view[year=='Total'&Method=='default',mean],3)*100}\%).
+The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are 18.6\%, 18.6\%, and 21.5\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (15.7\%, 15.7\%, and 18.7\%).
+Panel C shows the EPS based weighted expected returns averages (14.7\%, 14.7\%, and 19\%).
 
@@
 %obtained from the rankings based on the target price accuracy.
-We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%.
-The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%.
+We observe a reduction in average per stock expected return with the mean of  round(rank.views.full.period['true','mean'],3)*100\%.
+The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of  round(pt.eps.rank.views.full.period['true','mean'],3)*100\%.
 Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.
@@
 
-We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
-
-\subsection{Passive strategy}
-Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results[4,1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results[4,1,'ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results[4,1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results[4,1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
-
-\subsection{Perfect foresight strategy}
-\label{sec:perfect}
-Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results[1,1,1],2)}\%, \Sexpr{round(bl.results[2,1,1],2)}\%, \Sexpr{round(bl.results[3,1,1],2)}\%.
-All the strategies outperform the benchmark (\Sexpr{round(bl.results[4,1,1],2)}\%).
-The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
-In any case, the results suggest that the advice of analysts are valuable.
-%Yet, the top analyst
-
-%The result confirms that these strategies set an upper bound for the cumulative return yield.
-It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.
-
-The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
-Its Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
-In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
-Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-Panel A of the table corresponds to the perfect foresight information set.
-The TP strategy wins over the others in every period.
-
-While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
-One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
-For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
-
-\subsection{Feasible strategies}
-Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
-As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
-
-As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
-The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
-The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
-
-The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively).
-The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
-
-The feasible information sets demonstrate interesting results.
-It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus.
-Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-Thus, rankings are useful for investors.
-
-%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
-Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.
-
-%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-In addition, the results show that keeping all available information about analysts' performance does not create any value.
-As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.
-
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
-Yet, it is not the case for EPS ranking.
-This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
-EPS are not good predictors of future returns, at least for short-term horizon.
-
-Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
-Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-Some institutions, such as StarMine, rank financial analysts based on their accuracy.
-These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
-Therefore, there is a growing interest in understanding the relative performance of analysts.
-
-We show that rankings do bring value to investors as they identify the top analysts.
-By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
-We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
-The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
-%The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.
-
-For the future work we would like to develop the new methods to be able to get closer to the upper bound.
-
-% 
-% \bibliographystyle{ecta}
-% %\bibliographystyle{newapa}
-% \bibliography{rank}
-% \appendix
-
-%\section{Tables and Figures}
-
-%Descriptive  table
-\begin{table}[hp]
-  \caption{Sample Statistics}
-  \label{tab:ret-stat}
-\ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-    \toprule
-Year & Min& Mean & Median &Max& Std.dev\\
-\midrule
-%Panel A: TP&&&&&\\
-\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
-\midrule
-%Year & Min& Mean & Median &Max& Std.dev\\
-<<desc-pt,echo=F,results='asis'>>=
-
-#data.to.display <- c('min','mean', 'median','max','std.dev')
-#results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])
-
-options(xtable.comment = FALSE)
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\midrule
-\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
-\midrule
-<<desc-eps,echo=F,results='asis'>>=
-print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Example of ranking}
-  \label{tab:example}
-\ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999.
-We apply (\ref{tp:rank}) to obtain the ranks of the brokers.
-\emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error.
-For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts.
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-    \toprule
-    \multicolumn{4}{c}{\textbf{Panel A: TP}} \\
-<<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'\\emph{TP}'=PT,'$\\overline{PMAFE}^{TP}$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],4,'$rank^{TP}$'),display=c('s','d','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-    \multicolumn{4}{c}{\textbf{Panel B: EPS}} \\
-<<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'$PRED$'=Est,'$PMAFE^{EPS}$'=eps.pmafe,rank)][order(rank)],4,'$rank^{EPS}$'),display=c('s','d','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-% Descritive rankings
- \begin{table}[hp]
-  \caption{Analysts' accuracy consistency}
-  \label{tab:rank-stat}
-
-\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins.
-Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-    \toprule
-\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
-
-<<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-
-tab=2
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\midrule
-\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
-<<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab=2
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
-  \label{tab:view-stat}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views,echo=F,results='asis'>>=
-
-print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
-  \label{tab:view-stat-naive}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-naive,echo=F,results='asis'>>=
-
-print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
-  \label{tab:view-stat-default}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-default,echo=F,results='asis'>>=
-
-print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-\begin{table}[hp]
+\begin{table}
   \caption{Trading strategy performance}
@@
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average.
-The trading period spreads from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
+The trading period spreads from 2000Q1 until 2009Q4.
 
@@
   %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-<<bl-market,echo=F,results='asis'>>=
-bl.results.tab <- bl.results
-dimnames(bl.results.tab)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results.tab[4,1,]
-cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
-#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
-cat('\\midrule \n')
-@
+Strategy&Annualized cum. return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
+\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
+  \midrule
+
 \end{tabularx}
@@
   \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
-<<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
+ \textit{CONS} & 1.891 & 15.134 & 0.125 &  291 & 0.291 \\ 
+  \textit{TP} & 5.125 & 14.608 & 0.351 &  291 & 0.314 \\ 
+  \textit{EPS} & 1.498 & 14.611 & 0.103 &  237 & 0.453 \\ 
+   \midrule
+
 \end{tabularx}
@@
   \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
-<<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
+ \textit{CONS} & 0.115 & 15.948 & 0.007 &  284 & 0.256 \\ 
+  \textit{TP} & 0.280 & 15.663 & 0.018 &  284 & 0.264 \\ 
+  \textit{EPS} & 0.117 & 15.342 & 0.008 &  235 & 0.370 \\ 
+   \midrule
+
 \end{tabularx}
@@
   \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
-<<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
-@
+ \textit{CONS} & -0.113 & 15.837 & -0.007 &  290 & 0.188 \\ 
+  \textit{TP} & 0.074 & 15.693 & 0.005 &  290 & 0.191 \\ 
+  \textit{EPS} & -0.178 & 15.540 & -0.011 &  273 & 0.197 \\
+
 \bottomrule
@@
 \end{table}
+
+We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
+
+\subsection{Passive strategy}
+Panel A shows  the performance of the passive strategy \textit{Market}.
+The strategy resulted in an annualized cumulative return of \ensuremath{-3.03}\% and the Sharpe Ratio  of \ensuremath{-0.182}.
+The average number of stocks used per quarter is 499.98 and the turnover ratio of strategy is 0.053, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+
+\subsection{Perfect foresight strategy}
+\label{sec:perfect}
+Panel B presents the results for the case of \tr{} information set.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.89\%, 5.12\%, 1.5\%.
+All the strategies outperform the benchmark (\ensuremath{-3.03}\%).
+The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
+In any case, the results suggest that the advice of analysts are valuable.
+%Yet, the top analyst
+
+%The result confirms that these strategies set an upper bound for the cumulative return yield.
+It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.
 
@@
   %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-<<sr-true,echo=F,results='asis'>>=
-
-#results.final <- bl.results['Market',1,]
-cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
-#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
-cat('\\midrule \n')
-@
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-<<sr-naive,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
-cat('\\midrule \n')
-@
+Period&\textit{Market}&\textit{CONS}&\textit{TP}&\textit{EPS} \\  \multicolumn{5}{l}{\textbf{Panel A: \tr{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.286 & 0.446 & 0.222 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.261 & 0.475 & 0.269 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.486 & 0.792 & 0.528 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.201 & 1.846 & 1.225 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.233 & 0.138 & -0.193 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.041 & 0.244 & -0.025 \\ 
+  All period & -0.182 & 0.125 & 0.351 & 0.103 \\ 
+  \midrule
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel B: \naive{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.167 & 0.168 & 0.167 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.170 & 0.214 & 0.259 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.447 & 0.490 & 0.493 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.106 & 1.248 & 1.187 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.343 & -0.306 & -0.327 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.146 & -0.125 & -0.134 \\ 
+  All period & -0.182 & 0.007 & 0.018 & 0.008 \\ 
+  \midrule
+
 %\midrule
@@
 \begin{tabularx}{\linewidth}{r*{5}{Y}}
-<<sr-default,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
-@
+  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.244 & 0.239 & 0.227 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.233 & 0.263 & 0.296 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.430 & 0.480 & 0.471 \\ 
+  2003Q1/2007Q4 & 0.925 & 0.878 & 0.979 & 0.931 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.440 & -0.407 & -0.432 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.237 & -0.206 & -0.226 \\ 
+  All period & -0.182 & -0.007 & 0.005 & -0.011 \\
+
 \bottomrule
@@
 
-\begin{figure}[hp]
-\begin{center}
-\includegraphics[width=\linewidth]{figure/Black-litterman}
-\end{center}
-\caption{Trading strategy timeline}
-\label{fig:bl}
-\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
-\end{figure}
-
-\begin{figure}[hp]
-\begin{center}
-\includegraphics[width=\linewidth]{figure/example-fig-1}
-\end{center}
-\caption{Daily stock price Amazon and brokers target prices}
-\label{fig:example}
-\ Target price and actual prices for Amazon  the second quarter of 1999.
-\end{figure}
-
-\begin{figure}[hp]
+The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
+Its Sharpe Ratio is 0.351 against 0.125, 0.103, and \ensuremath{-0.182}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
+In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
+Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
+Panel A of the table corresponds to the perfect foresight information set.
+The TP strategy wins over the others in every period.
+
+While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
+One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
+For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
+
+\subsection{Feasible strategies}
+Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
+As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\ensuremath{-3.03}\%)  and gain positive cumulative annualized returns: 0.28\%,  0.12\%, 0.12\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
+
+As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
+The Sharpe Ratio for this strategy is 0.018 which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (0.007 and 0.008 respectively).
+The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
+
+The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (0.07\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\ensuremath{-0.11}\% and \ensuremath{-0.18}\% respectively).
+The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+
+The feasible information sets demonstrate interesting results.
+It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus.
+Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
+Thus, rankings are useful for investors.
+
+%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
+Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.
+
+%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
+In addition, the results show that keeping all available information about analysts' performance does not create any value.
+As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.
+
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
+Yet, it is not the case for EPS ranking.
+This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
+EPS are not good predictors of future returns, at least for short-term horizon.
+
+\begin{figure}
 \begin{center}
@@
 \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
-The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}
+The trading period ranges from 2000Q1 until 2009Q4
 \end{figure}
 
+Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
+The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at January of 2000 and ending at December of 2009.
+Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+
+\section{Conclusions}
+\label{sec:conclusion}
+
+Some institutions, such as StarMine, rank financial analysts based on their accuracy.
+These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
+Therefore, there is a growing interest in understanding the relative performance of analysts.
+
+We show that rankings do bring value to investors as they identify the top analysts.
+By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
+We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
+The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
+%The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.
+
+For the future work we would like to develop the new methods to be able to get closer to the upper bound.
+
+% 
+% \bibliographystyle{ecta}
+% %\bibliographystyle{newapa}
+% \bibliography{rank}
+% \appendix
+
+%\section{Tables and Figures}
+
+%Descriptive  table
+
 %\end{document}
+\bibliographystyle{ecta}
+\bibliography{thesis}
+\end{document}

### 2015-02-14 doc/paper/paper-knitr-APS.Rnw
Initial commit

--- 2015-02-14 doc/paper/chapter-1.Rnw
@@
-% \documentclass{article}
-% \usepackage{fancyhdr}
-% \usepackage{time}
-% \usepackage{authblk}
-% \usepackage{amsmath, amssymb}
-% \usepackage{caption}
-% \captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
-% \captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
-% %\usepackage{fullpage}
-% %\usepackage{rotating}
-% %\usepackage{xcolor}
-% \usepackage[hyphens]{url}
-% \usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
-% %\usepackage{breakurl}
-% \usepackage{times}
-% \usepackage{setspace}
-% \usepackage{graphicx}
-% \usepackage{array}
-% \usepackage{tabularx}
-% \usepackage{booktabs}
-% \usepackage{multirow}
-% %\onehalfspacing
-% \doublespace
-% \usepackage[longnamesfirst]{natbib}
-% %\usepackage[natbibapa,longnamesfist]{apacite}
-% 
-% \DeclareMathOperator*{\argmax}{arg\,max}
-% %\newcommand{\r}{\Sexpr{}}
-% \DeclareMathOperator{\rank}{rank}
-% \DeclareMathOperator*{\median}{median}
-% %\newcommand{\theHalgorithm}{\arabic{algorithm}}
-% \newcommand{\tr}{\textit{true}}
-% \newcommand{\naive}{\textit{recent}}
-% \newcommand{\default}{\textit{all-time}}
-% \newcommand{\market}{\textit{market}}
-% \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
-% %\newcommand{\raw}{\textit{raw}}
-% %\newcommand{\diff}{\textit{diff}}
-% %\newcommand{\random}{\textit{random}}
-% %\newcommand{\rollsd}{\textit{roll.sd}}
-% 
-% 
-% \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-% 
-% %-------------------------------------------------------------------------
-% % take the % away on next line to produce the final camera-ready version
-% % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
-% %\pagestyle{empty}
-% \pagestyle{fancy}
-%  
-% \newcommand\myTime{\now}
-% \fancyhead{}
-% \fancyhead[CO, CE]{\texttt{-Draft-}}
-% \fancyhead[RO, RE]{\texttt{\today, \myTime}}
-% \setlength{\headheight}{2\baselineskip}
-% \renewcommand{\headrulewidth}{0pt}
-% %-------------------------------------------------------------------------
-% 
-% 
-% \begin{document}
+\documentclass{article}
+\usepackage{fancyhdr}
+\usepackage{time}
+\usepackage{authblk}
+\usepackage{amsmath, amssymb}
+\usepackage{caption}
+\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
+\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
+%\usepackage{fullpage}
+%\usepackage{rotating}
+%\usepackage{xcolor}
+\usepackage[hyphens]{url}
+\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
+%\usepackage{breakurl}
+\usepackage{times}
+\usepackage{setspace}
+\usepackage{graphicx}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{booktabs}
+\usepackage{multirow}
+%\onehalfspacing
+\doublespace
+\usepackage[longnamesfirst]{natbib}
+%\usepackage[natbibapa,longnamesfist]{apacite}
+
+\DeclareMathOperator*{\argmax}{arg\,max}
+%\newcommand{\r}{\Sexpr{}}
+\DeclareMathOperator{\rank}{rank}
+\DeclareMathOperator*{\median}{median}
+%\newcommand{\theHalgorithm}{\arabic{algorithm}}
+\newcommand{\tr}{\textit{true}}
+\newcommand{\naive}{\textit{recent}}
+\newcommand{\default}{\textit{all-time}}
+\newcommand{\market}{\textit{market}}
+\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
+%\newcommand{\raw}{\textit{raw}}
+%\newcommand{\diff}{\textit{diff}}
+%\newcommand{\random}{\textit{random}}
+%\newcommand{\rollsd}{\textit{roll.sd}}
+
+\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
+
+%-------------------------------------------------------------------------
+% take the % away on next line to produce the final camera-ready version
+% Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
+%\pagestyle{empty}
+\pagestyle{fancy}
+
+\newcommand\myTime{\now}
+\fancyhead{}
+\fancyhead[CO, CE]{\texttt{-Draft-}}
+\fancyhead[RO, RE]{\texttt{\today, \myTime}}
+\setlength{\headheight}{2\baselineskip}
+\renewcommand{\headrulewidth}{0pt}
+%-------------------------------------------------------------------------
+
+\begin{document}
 
@@
 
-%<<set-parent, echo=FALSE, cache=FALSE>>=
-%set_parent('~/Dropbox/workspace/Projects/Thesis/thesis.Rnw')
-%@
-
-<<chp1-load-data,echo=F,warning=FALSE,message=FALSE>>=
+<<load.data,echo=F,warning=FALSE,message=FALSE>>=
 strategies <- c('true','recent','all-time')
@@
 load('cache/example.dt.RData')
-source('lib/BL-functions.R')
+source('lib/aux.functions.R')
 #library(ProjectTemplate)
@@
 
-complete.dt <- setkey(complete.dt,calQ)[quarters]
+complete.dt <- setkey(complete.dt,fis.q)[quarters]
 eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'calQ','q.id')
+complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')
 
@@
 
-<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-require(gridExtra)
-example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
-test <- rbind(example.dt[,.(s.Date,PT,Series=Broker)][,Broker:='Broker'],example.dt[,.(s.Date,PT=priceAdj)][,Broker:='AMZN'][,Series:='AMZN'])
-test$Series <- factor(test$Series,levels=c('AMZN',as.character(unique(example.dt$Broker))))
-
-ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
-@
-
-<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-library(scales)
-#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))
-
-colourCount = length(unique(final.bl$Views))
-getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-
-#p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
-
-@
-
-% \title{Are rankings of financial analysts useful to investors?}
-%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
-%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
-%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-% 
-% \affil[1]{FEP \& CEF.UP, University of Porto}
-% \affil[2]{INESC TEC}
-% \affil[4]{FEUP, University of Porto}
-% 
-% 
-% \maketitle
-% % You need this here, or else the first page won't have a header.
-% \thispagestyle{fancy}
-% 
-% \begin{abstract}
-% Some institutions issue rankings of financial analysts.
+\title{Are rankings of financial analysts useful to investors?}
+ \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
+ \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
+ \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+
+\affil[1]{FEP \& CEF.UP, University of Porto}
+\affil[2]{INESC TEC}
+\affil[4]{FEUP, University of Porto}
+
+\maketitle
+% You need this here, or else the first page won't have a header.
+\thispagestyle{fancy}
+
+\begin{abstract}
+Some institutions issue rankings of financial analysts.
 Given that these rankings are \textit{ex-post} they may not be able useful to investors.
@@
 In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
-% %Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
-% \end{abstract}
-
-\chapter{Are rankings of financial analysts useful to investors?}
+%Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
+\end{abstract}
+
 \section{Introduction}
@@
 Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results[4,1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results[4,1,'ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results[4,1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results[4,1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}.
+The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
 
@@
 Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results[1,1,1],2)}\%, \Sexpr{round(bl.results[2,1,1],2)}\%, \Sexpr{round(bl.results[3,1,1],2)}\%.
-All the strategies outperform the benchmark (\Sexpr{round(bl.results[4,1,1],2)}\%).
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results['CONS',1,1],2)}\%, \Sexpr{round(bl.results['TP',1,1],2)}\%, \Sexpr{round(bl.results['EPS',1,1],2)}\%.
+All the strategies outperform the benchmark (\Sexpr{round(bl.results['Market',1,1],2)}\%).
 The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
@@
 
-% 
-% \bibliographystyle{ecta}
-% %\bibliographystyle{newapa}
-% \bibliography{rank}
-% \appendix
+\bibliographystyle{ecta}
+%\bibliographystyle{newapa}
+\bibliography{rank}
+\appendix
 
@@
 \end{table}
+
+<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
+require(gridExtra)
+example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
+test <- rbind(example.dt[,.(s.Date,PT,Series=Broker)][,Broker:='Broker'],example.dt[,.(s.Date,PT=priceAdj)][,Broker:='AMZN'][,Series:='AMZN'])
+test$Series <- factor(test$Series,levels=c('AMZN',as.character(unique(example.dt$Broker))))
+
+#ggplot(setnames(rbind(example.dt[,.(s.Date,PT,Broker)],setnames(example.dt[,.(s.Date,priceAdj)][,Broker:='AMZN'],2,'PT')),'Broker','Stock Price'),aes(x=s.Date,y=PT,group=`Stock Price`,color=`Stock Price`,shape=`Stock Price`))+geom_line(size=1)+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
+
+#ggplot(example.dt,aes(x=s.Date,y=PT,group=Broker,color=Broker,shape=Broker))+geom_line(size=1)+geom_line(aes(y=priceAdj),color='black')+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
+
+ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
+
+#+geom_line(aes(y=priceAdj),color='black')+theme(plot.title = element_text(colour = "Black"),legend.position='top')
+#grid.draw(grobTree(arrangeGrob(p,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
+@
 
@@
 
+<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
+library(scales)
+#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))
+
+colourCount = length(unique(final.bl$Views))
+getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
+
+#p.cum.ret <-
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
+
+#+scale_color_manual(values=getPalette(colourCount))+
+
+#+scale_x_date(breaks='year',labels=date_format('%Y'))
+
+#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
+
+#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))
+
+require(gridExtra)
+#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
+#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
+@
+
 \begin{table}[hp]
@@
 <<bl-market,echo=F,results='asis'>>=
-bl.results.tab <- bl.results
-dimnames(bl.results.tab)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results.tab[4,1,]
+
+dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
+results.final <- bl.results[4,1,]
 cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
@@
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
@@
 print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
-cat('\\midrule \n')
-@
+@
+\midrule
 \end{tabularx}
@@
 print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
-cat('\\midrule \n')
-@
-%\midrule
+@
+\midrule
 \end{tabularx}
@@
 
-%\end{document}
+\end{document}

### 2015-02-14 doc/paper/paper-knitr-APS.tex
Initial commit

--- 2015-02-14 doc/paper/paper-knitr-APS.Rnw
@@
 
-<<include=FALSE>>=
-library(knitr)
-opts_chunk$set(concordance=TRUE)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
 
-<<load.data,echo=F,warning=FALSE,message=FALSE>>=
-strategies <- c('true','recent','all-time')
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
-library(reshape2)
-library(descr)
-library(data.table)
-library(ggplot2)
-library(stringr)
-library(zoo)
-library(xtable)
-library("PerformanceAnalytics")
-load('cache/q.data.RData')
-load('cache/final.bl.RData')
-load('cache/market.set.RData')
-load('cache/example.dt.RData')
-source('lib/aux.functions.R')
-#library(ProjectTemplate)
-#load.project()
-###ADD NAs for the case of no ranking ( if NA, no raking)
-trunk.percent <- 0.05
-stocks <- unique(market.set[,Stock])
-#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
-q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
 
-q.data <- na.omit(q.data.full[stocks])
-q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
-#stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(eps.rank.views[View != 0, list(mean = mean(View), median = median(View), : object 'eps.rank.views' not found}}
 
-### General stat of TP/P-1
-#stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(stat.nr, stat.pt.view, stat.eps.view): object 'stat.eps.view' not found}}
 
-core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in melt(stat.full, id.vars = c("{}year"{}, "{}Method"{}, "{}Strategy"{})): object 'stat.full' not found}}
 
-#pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
-quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])
-
-load('cache/ranked.pt.dt.RData')
-n <- 3
-n.b <- 3
-
-#options(descr.na.replacement = "noRank")
-pt.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.pt.dt,i,n.b)})
-
-###Statistics for views:
-###non rank base data
-load('cache/nr.views.RData')
-load('cache/pt.rank.views.RData')
-load('cache/eps.rank.views.RData')
-load('cache/ranked.eps.dt.RData')
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
-
-complete.dt <- setkey(complete.dt,fis.q)[quarters]
-eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')
-
-eps.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.eps.dt,i,n.b)})
-
-brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
-
-#Views stat
-
-stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']
-
-stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']
-
-stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']
-
-stat.full <- rbind(stat.nr,stat.pt.view,stat.eps.view)
-
-test <- melt(stat.full,id.vars = c('year','Method','Strategy'))
-test.a <- acast(test,year~Method~Strategy~variable,value.var = 'value')
-
-brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
-
-load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
-
-final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]
-
-final.bl$Method <- factor(final.bl$Method,levels=strategies)
-final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
-final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
-bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views')),Views~Method~variable,value.var = 'value')
-
-quarters <- unique(final.bl[,Quarters])
-periods.id <- c(paste(gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,first,by=4)),gsub('[[:space:]]','',rollapplyr(as.character(quarters),20,last,by=4)),sep='/'),'All period')
-
-periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat)][,sr:=ann.ret/ann.sd]
-
-periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat')),period~Views~Method~strat~variable,value.var = 'value')
-
-start.year <- format(as.Date(final.bl[,head(Quarters,1)]),'%Y')
-end.year <- format(as.Date(final.bl[,tail(Quarters,1)]),'%Y')
-@
-
-\title{Are rankings of financial analysts useful to investors?}
- \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
- \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
- \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-
-\affil[1]{FEP \& CEF.UP, University of Porto}
-\affil[2]{INESC TEC}
-\affil[4]{FEUP, University of Porto}
-
-\maketitle
-% You need this here, or else the first page won't have a header.
-\thispagestyle{fancy}
-
-\begin{abstract}
-Some institutions issue rankings of financial analysts.
-Given that these rankings are \textit{ex-post} they may not be able useful to investors.
-In this paper  we show that trading strategies based on past rankings outperform a passive strategy.
-In addition, we report that analysts issuing accurate price targets are more favorable to the investors  to follow rather than analysts issuing accurate EPS forecasts.
-In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
-%Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
-\end{abstract}
-
-\section{Introduction}
-\label{sec:intro}
-
-% citations  full for aurtors
-The idea that financial analysts play an important role in financial markets is rather consensual \citep{cowles1933csm,obrien1990}.
-Yet there is some debate on whether following the advice of analysts brings value to investors after transaction costs \citep{womack1996,mikhail2004sae,li2005persistence}.
-Related to this is the difficulty in identifying the analysts with superior stock picking skills.
-In this paper, we show that the rankings of financial analysts are useful to investors because strategies based upon these rankings yield positive abnormal returns.
-
-In recent years, some institutions have been very active in publishing and  selling  rankings of financial analysts.
-Some rankings  are based on privately held surveys of  buy-side analysts (e.g., the Institutional Investor's rankings of the All-America Research Teams\footnote{\url{http://www.institutionalinvestor.com/Research/4560/First-Team.html}} and Bloomberg's America's Best Stock Analysts\footnote{\sloppy \url{http://www.bloomberg.com/news/2013-08-14/jpmorgan-top-stock-picker-with-equities-out-of-lockstep.html}}); others are based on the performance of sell-side analysts (ThomsonReuters' top StarMine analysts\footnote{\url{http://excellence.thomsonreuters.com/award/starmine}}).
-In any of these cases, the rankings aim at identifying the top analysts.
-However, aside from personal acknowledgment among peers, it is still arguable whether these are useful \citep{desai2000ass} or are merely ``popularity contests" \citep{emery2009}.
-%In this paper, we support the argument that the top-ranked analysts, indeed, have stock picking skills.
-
-We show that the top ranked analysts have stock picking skills.
-The contributions of our research is fourfold.
-First, we develop a trading strategy that transforms the rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}.
-Second, we show that annualized cumulative returns generated by some trading strategies  based upon analysts' rankings outperform the passive strategy (e.g., buy-and-hold the general stock market index).
-Third, we show that the strategy based upon the perfect foresight of rankings yields the highest cumulative annualized return.
-Fourth, we find that investors  are better off following analysts that issue the most accurate target prices, rather than those that issue the most accurate EPS forecasts.
-
-The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines our proposed  trading strategies; section \ref{sec:rankings} describes the sample and presents some preliminary results; section \ref{sec:results} presents and discusses the results; and section \ref{sec:conclusion} concludes.
-
-\section{Industry Rankings of Financial Analysts}
-\label{sec:ranking}
-
-In the financial literature there has been a long debate on whether financial analysts produce valuable  advice.
-Some argue that following the advice of financial analysts,  translated as recommendations of buying, holding, or selling a particular stock, does not yield  abnormal returns, i.e.,  returns that are above the required return to compensate for risk.
-The Efficient Market Hypothesis \citep{fama1970ecm} states that financial markets are efficient and that any public available information  regarding a stock would be immediately reflected in prices; hence, it would be  impossible to generate abnormal returns based upon past information.
-
-Yet, several authors have since stressed that  there are information-gathering costs and information is not immediately reflected on prices  \citep{grossman1980iie}.
-As such, prices may not  reflect all the available information at all time because if this were the case, those who spent resources to collect and analyze   information would not have an incentive to do it because there would not get any compensation for it.
-
-%Many trading strategies try to forecast the price movements relying on the historical prices or estimate the intrinsic value of a company.
-Obviously, this type of research is associated with significant amount of up-front costs to acquire databases, software, etc.
-On the other hand, financial analysts have these tools and, presumably, skills to identify  stocks that worth be invested.
-Thus, for an investor, it is cheaper to follow the recommendations of financial analysts rather than perform a proper stock market analysis.
-
-Some authors show that that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
-\cite{barber2001} finds that over the period of 1986-1996 a portfolio of stocks with the most (least) favorable consensus analyst recommendations yields an average abnormal return of 4.13 (-4.91)\%.}.
-Assuming that some analysts produce valuable advice it make sense to rank analysts based on the accuracy of their recommendations.
-
-StarMine rankings are based on financial analysts accuracy either on price target or EPS forecasts.
-To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES).
-This score measures ``...
-[a] relative accuracy; that is, analysts are compared against their peers.
-An analyst's SES can range from 0 to 100, with 50 representing the average analyst.
-To get a score higher than 50, an analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates"\footnote{\url{http://excellence.thomsonreuters.com/award/starmine?award=Analyst+Awards&award_group=Overall+Analyst+Awards}}.
-
-As for target price ranking, StarMine's methodology compares the portfolios based on analysts recommendations.
-Portfolios are constructed as follows.
-For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark.
-``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark.
-``Hold'' invests one unit in the benchmark (i.e., an excess return of zero).
-``Sell" recommendations work in the reverse way.
-StarMine re-balances its calculations at the end of each month to adjust for analysts revisions (adding, dropping or altering a rating), and when a stock enters or exits an industry grouping.
-
-Recent evidence suggests that top ranked financial analyst affect market participants: prices seem to react more to the recommendations issued by the top-ranked analysts \citep{emery2009}.
-As such, StarMine ranking based models can be used to identify such analysts and generate superior estimates (e.g., SmartEstimates\footnote{\url{http://www.starmine.com/index.phtml?page_set=sm_products&sub_page_set=sm_professional&topic=analytical&section=accurate_estimates}}).
-%Evidence shows that market response to analysts' recommendations is stronger when analysts issue them with a good forecasting tracking record \citep{park2000analyst,loh2006aef}.
-Thus, it seems to be the case that only a subset of analysts influences the stock prices and, as such, only that subset of analysts deserves to be followed \citep{loh2011}.
-
-The goal of our study is to evaluate if and how rankings  add value to investors.
-With this purpose, we develop several sets of active trading strategies, selecting the stocks most favored by analysts.
-The first strategy is based on the consensus estimate (giving equal weights to analysts' recommendations).
-The second set of strategies takes in consideration the analysts' target price and EPS accuracy ranks to form ``smart estimates".
-For the latter set of strategies, we analyse different time information sets of the accuracy of the analysts.
-
-We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy).
-By doing this, we address the ongoing debate in the literature on whether analysts, when issue the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
-For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices.
-Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.
-
-A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period’s EPS invested at the cost of equity.}.
-In short, this model justifies a price earnings ratio for companies where next period’s earnings are expected to grow over and above the normal rate.
-
-% and it is, in a sense, an upper bound of all trading strategies.
-
-%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \tr{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.
-
-%We claim that the ranking strategies outperform the consensus ones as well as the passive strategy.
-
-%we investigate the problem with two ranking  methods that are used further as the inputs for the trading strategy.
-The first is the \naive{} rankings and this is simply the last known analysts' actual rankings.
-The second method is taken from the Machine Learning literature \citep{aiguzhinov2010} and it is so-called the \default{} ranking.
-It is the average rank of an analyst since the beginning of the sample period and it encompasses the average analyst's relative performance.
-We formalize these methods in the appropriate section of the paper.
-
-\section{Trading Strategies}
-%- BL model
-%- Information sets
-\label{sec:trading}
-Our trading strategy use the framework for  active portfolio management proposed by \cite{black1992}.
-The model incorporates ``views" in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting.
-``Views" are expectations on individual stocks future performance by investors/analysts.
-
-While in the CAPM model expected returns are a function of systematic risk, in the BL model some stocks can be over- or under-priced and, therefore, their alphas are non-zero.
-The model blends the subjective views of investors about future performance of a stock with the market implicit returns given by CAPM.
-
-\cite{da2011bl} apply the BL model and use the consensus expected returns as a proxy for views.
-They report that the resulting strategy outperforms a passive buy-and-hold strategy.
-Our approach is similar to theirs but we define views not only based on consensus estimates but also on smart estimates that account for previous analysts' TP and EPS accuracy.
-
-Here below we kept the notation in \cite{black1992}.
-$Q$ is the vector of  expected returns for the eligible stocks; $\Omega$ matrix is the confidence of $Q$.
-Altogether these two reflect the views of a particular analyst or a set of analysts.
-
-To proxy expected returns we compare the analysts' 12-month target prices (TP) with today's stock price.
-Confidence $\Omega$ for stock is based on variation  across analysts which is similar to the measure of dispersion in analysts' opinions outlined in \cite{diether2002}.
-
-We define a trading strategy as follows (figure \ref{fig:bl}):
-\begin{enumerate}
-\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
-
-\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix across stocks;
-
-\item We apply the BL model to get  optimal portfolio weights on the basis of combining views and implicit returns.
-We  buy or sell stocks accordingly.
-At the beginning of $t+1$, based on the new views, we set the new portfolio weights following  steps 1--3.
-\end{enumerate}
-
-\subsection{Defining $Q$}
-\label{def-q}
-
-For the consensus strategy, we use median of expected returns for a particular stock $s$:
-\begin{equation}
-\label{consq}
-Q_{cons,s}= \median \left\{r_{j,s}\right\}
-%\frac{1}{N} \sum_{j=1}^{N} r_{j,s}
-\end{equation}
-%$N$ is the number of analysts with a valid TP report and
-where $r_{j,s}=TP_{j,s}/P_{s}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,s}$ and stock price $P_{s}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
-This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
-
-For the strategies that weight the analysts' estimates of expected return, we use analysts' rankings and the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
-
-\begin{equation}
-\label{eq:weight}
-w_{j,s}=1-\frac{rank_{j,s}-\min{ \{rank \} }}{\max{\{rank \}}}
-\end{equation}
-
-The expected rank-weighted return is thus:
-\begin{equation}
-\label{rankq}
-Q_{rank,s}=\frac{\sum_{j=1}^{N} (w_{j,s} \times r_{j,s})}{\sum_{j=1}^{N} w_{j,s}}
-\end{equation}
-$N$ is the number of analysts.
-
-As described above, we use target price and EPS rankings.
-
-\subsubsection{Target Price ranking}
-
-Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}.
-First,  we define the forecast daily error  $FE_{i,j}$ as the absolute value of the difference between analysts' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
-
-\begin{equation}
-\label{dfe}
-FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
-\end{equation}
-The PMAFE is given as:
-\begin{equation}
-\label{tp:pmafe}
-PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
-\end{equation}
-where $\overline{{FE}_{t,s}^{TP}}$ is the average over quarter forecasting error. The target price is fixed over the quarter unless it gets revised.
-
-The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
-\begin{equation}
-\overline{PMAFE_{j,s}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,s}^{TP}
-\end{equation}
-
-\begin{equation}
-\label{tp:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
-\end{equation}
-where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.
-
-\subsubsection{EPS ranking} 
-To compute the EPS rankings, we apply the same procedure as above:
-\begin{equation}
-FE_{j,s}^{EPS}=|{ACT_{s}-PRED_{j,s}}|
-\end{equation}
-\begin{equation}
-PMAFE_{j,s}^{EPS}= \frac{FE_{j,s}^{EPS}}{\overline{FE_{s}^{EPS}}}
-\end{equation}
-\begin{equation}
-\label{eps:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\} 
-\end{equation}
-where $ACT_{s}$ and $PRED_{j,s}$ are the actual and  analyst $j$ forecast EPS respectively for each stock $s$.
-
-\subsection{Defining the confidence of expected returns $\Omega$}
-\label{def-omega}
-The confidence of $Q$ are given by the coefficient of variation of forecasting errors:
-
-\begin{equation}
-CV = \frac{\sigma (FE)}{\overline{FE}}
-\end{equation}
-where $\sigma$ and $\overline{FE}$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS.
-A low value of $CV$ reflects consensual estimates of either future prices or EPS.
-
-\subsection{Information sets to define the views}
-
-To proceed with the trading strategy, we need to establish which information we going to use to build the rankings that will be used to compute the weighted return estimates.
-Different analysts' ranks are obtained  if we select different time horizons.
-If use only recent information, we focus on recent performance of the analysts.
-This, of course, is more sensitive to unique episodes (e.g., a quarter, which has been surprisingly good or bad).
-If, alternatively, we opt to incorporate all analyst performance, the ranking is less affected by such events, yet, it may not reflect the current abilities of the analyst.
-In this paper, we use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
-We call the former the \naive{} set and the latter the \default{} set.
-
-In addition to these sets,  we also create a hypothetical scenario that assumes we know the future information about the analyst' accuracy performance which would only be available at the end of $t$.
-In this setting, we are assuming that we could  perfectly predict the true analysts' ranking in advance.
-This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies.
-We call this approach as the \tr{} set.
-
-We formalize these sets as follows. 
-\begin{itemize}
-\item  the \tr{} %-- a perfect foresight information:
-\begin{equation}
-\label{q:true}
-\widehat{Q_{.,t}}=Q_{.,t}
-\end{equation}
-
-\item  the \naive{} % -- $t-$ information:
-\begin{equation}
-\label{q:naive}
-\widehat{Q_{.,t}}=Q_{.,t-1}
-\end{equation}
-
-\item  the \default{} %-- the entire history of analysts performance:
-%\begin{itemize}
-%\item ranking based views:
-\begin{equation}
-\label{q:default}
-\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
-\end{equation}
-%\item consensus based views:
-%\begin{equation}
-%\label{default.cons}
-%\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
-%\end{equation}
-%\end{itemize}
-\end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).
-
-\section{Data and preliminary results}
-\label{sec:rankings}
-
-\subsection{Database and sample}
-We focus on the  S\&P500 stocks.
-We extract the target price information and the EPS forecasts from ThomsonReuters  I/B/E/S detailed history database.
-The  S\&P500 constituents' list and the stock daily prices are from ThomsonReuters DataStream.
-
-The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
-After one year we assume that TP recommendation expires.
-
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
-This is done due to occurrence of the extreme values.
-Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases.
-In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
-
-The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
-To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
-In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
-
-Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data.
-Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-Each stock had on average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} quarterly target price reports.
-Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-The average number of quarterly forecasts is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.
-
-We apply the ranking procedure outline in section \ref{def-q} on two datasets.
-For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq.
-\ref{tp:pmafe}).
-
-Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
-Four analysts had valid target price for Amazon for second quarter of 1999.
-We plot the daily Amazon price against the brokers' target prices.
-Table \ref{tab:example} shows the resulting TP and EPS ranking.
-On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate.
-For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.
-
-%The daily frequency allows us to capture the analysts' performance with better precision.
-Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices.
-As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock.
-At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts.
-Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices.
-The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4).
-In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
-\subsection{Ranking contingency results}
-We consider  three terciles (\textit{top}, \textit{medium}, \textit{bottom}).
-In one particular quarter ($t$), we place  analysts at one of these bins which corresponds to a tercile.
-We, then,  check analysts position at the immediate next quarter ($t+1$) and after one year ($t+4$).
-
-We convert the rankings into scores as follows:
-\begin{equation}
-\label{eq:score}
-score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
-\end{equation}
-
-To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,s}$
-\begin{equation}
-\label{eq:mean-score}
-score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
-\end{equation}
-where $k$ is number of stocks for which an analyst $j$ had rank.
-
-Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
-%Chi square statistics include/ expected frequiency test
-%Journ. of Fin economics 
-Panel A shows the dynamics of each tercile for rankings based on the accuracy in target prices.
-We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter and even after one year.
-The case of EPS ranking shows similar results (panel B).
-This analysis confirms recent finding of \cite{hilary2013} on analyst forecast consistency.
-
-%the next quarter  $top_{t+1}$ group is as follows: \Sexpr{round(pt.cont.tab[[1]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(pt.cont.tab[[1]][3,1],3)*100}\% from the $bottom_{t-1}$.
-It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank.
-%Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[1]][4,4],3)*100}\%).
-This suggests that analysts are not frequent in issuing target price reports.
-
-%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
-%An interesting observation is for the \emph{noRank} category: \Sexpr{ round(cont.tab[[2]][4,1],3)*100}\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.
-
-%Panel B depicts the similar analysis for the EPS forecast rankings.
-For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$.
-%However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[1]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[1]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[1]][4,3],3)*100}\%.
-This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.
-
-\subsection{$Q$ descriptive statistics}
-
-Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
-The expected returns  are computed comparing TP estimates with actual price.
-To inform the strategies we obtain rank-weighted estimates where weights are given either by the TP or the EPS ranks.
-
-\cite{bradshaw2002} reports that analysts' average expected returns for the period of 2000--2009 of 206 brokers 24\%, in \cite{da2011} these average expected return post 40\% for the period of 1996--2004, \cite{zhou2013} find on average  96\% for the sample period of 2000--2009 reports.
-The figures suggest that analyst overly optimistic.
-%these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns.
-\cite{bodie2009} show that arithimatic average rate of return for the U.S.
-large stocks (S\&P 500) for the period of 1926--2005 is 10.17\% and the average rate of excess return is 8.39\% with the risk premium estimated 6--8\%.
-While it is not the best idea to extrapolate the historical values, still, we can say that the expected stocks return should be around 14--16\%.
-Clearly, the values presented in the literature shows that analysts are very optimistic in issuing target price reports.
-
-Panel A show the statistics for the consensus expectations as defined in eq.
-(\ref{consq}).
-The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{ round(stat.pt.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.pt.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.pt.view[year=='Total'&Method=='default',mean],3)*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{ round(stat.eps.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.eps.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.eps.view[year=='Total'&Method=='default',mean],3)*100}\%).
-
-Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic.
-The \default{} information set shows higher values of expected returns considering that it includes the whole history of analysts' performance.
-
-%obtained from the rankings based on the target price accuracy.
-We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%.
-The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%.
-Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.
-
-%put in to the different section
-
-\section{Empirical Results}
-\label{sec:results}
-
-We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
-
-\subsection{Passive strategy}
-Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
-
-\subsection{Perfect foresight strategy}
-\label{sec:perfect}
-Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results['CONS',1,1],2)}\%, \Sexpr{round(bl.results['TP',1,1],2)}\%, \Sexpr{round(bl.results['EPS',1,1],2)}\%.
-All the strategies outperform the benchmark (\Sexpr{round(bl.results['Market',1,1],2)}\%).
-The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
-In any case, the results suggest that the advice of analysts are valuable.
-%Yet, the top analyst
-
-%The result confirms that these strategies set an upper bound for the cumulative return yield.
-It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.
-
-The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
-Its Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
-In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
-Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-Panel A of the table corresponds to the perfect foresight information set.
-The TP strategy wins over the others in every period.
-
-While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
-One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
-For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
-
-\subsection{Feasible strategies}
-Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
-As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
-
-As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
-The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
-The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
-
-The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively).
-The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
-
-The feasible information sets demonstrate interesting results.
-It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus.
-Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-Thus, rankings are useful for investors.
-
-%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
-Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.
-
-%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-In addition, the results show that keeping all available information about analysts' performance does not create any value.
-As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.
-
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
-Yet, it is not the case for EPS ranking.
-This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
-EPS are not good predictors of future returns, at least for short-term horizon.
-
-Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
-Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-Some institutions, such as StarMine, rank financial analysts based on their accuracy.
-These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
-Therefore, there is a growing interest in understanding the relative performance of analysts.
-
-We show that rankings do bring value to investors as they identify the top analysts.
-By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
-We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
-The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
-%The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.
-
-For the future work we would like to develop the new methods to be able to get closer to the upper bound.
-
-\bibliographystyle{ecta}
-%\bibliographystyle{newapa}
-\bibliography{rank}
-\appendix
-
-%\section{Tables and Figures}
-
-%Descriptive  table
-\begin{table}[hp]
-  \caption{Sample Statistics}
-  \label{tab:ret-stat}
-\ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-    \toprule
-Year & Min& Mean & Median &Max& Std.dev\\
-\midrule
-%Panel A: TP&&&&&\\
-\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
-\midrule
-%Year & Min& Mean & Median &Max& Std.dev\\
-<<desc-pt,echo=F,results='asis'>>=
-
-#data.to.display <- c('min','mean', 'median','max','std.dev')
-#results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])
-
-options(xtable.comment = FALSE)
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\midrule
-\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
-\midrule
-<<desc-eps,echo=F,results='asis'>>=
-print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Example of ranking}
-  \label{tab:example}
-\ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999.
-We apply (\ref{tp:rank}) to obtain the ranks of the brokers.
-\emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error.
-For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts.
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-    \toprule
-    \multicolumn{4}{c}{\textbf{Panel A: TP}} \\
-<<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'\\emph{TP}'=PT,'$\\overline{PMAFE}^{TP}$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],4,'$rank^{TP}$'),display=c('s','d','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-    \multicolumn{4}{c}{\textbf{Panel B: EPS}} \\
-<<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'$PRED$'=Est,'$PMAFE^{EPS}$'=eps.pmafe,rank)][order(rank)],4,'$rank^{EPS}$'),display=c('s','d','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-require(gridExtra)
-example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
-test <- rbind(example.dt[,.(s.Date,PT,Series=Broker)][,Broker:='Broker'],example.dt[,.(s.Date,PT=priceAdj)][,Broker:='AMZN'][,Series:='AMZN'])
-test$Series <- factor(test$Series,levels=c('AMZN',as.character(unique(example.dt$Broker))))
-
-#ggplot(setnames(rbind(example.dt[,.(s.Date,PT,Broker)],setnames(example.dt[,.(s.Date,priceAdj)][,Broker:='AMZN'],2,'PT')),'Broker','Stock Price'),aes(x=s.Date,y=PT,group=`Stock Price`,color=`Stock Price`,shape=`Stock Price`))+geom_line(size=1)+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
-
-#ggplot(example.dt,aes(x=s.Date,y=PT,group=Broker,color=Broker,shape=Broker))+geom_line(size=1)+geom_line(aes(y=priceAdj),color='black')+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
-
-ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
-
-#+geom_line(aes(y=priceAdj),color='black')+theme(plot.title = element_text(colour = "Black"),legend.position='top')
-#grid.draw(grobTree(arrangeGrob(p,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
-@
-
- % Descritive rankings
- \begin{table}[hp]
-  \caption{Analysts' accuracy consistency}
-  \label{tab:rank-stat}
-
-\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins.
-Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-    \toprule
-\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
-
-<<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-
-tab=2
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\midrule
-\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
-<<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab=2
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
-rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
-#colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
-  \label{tab:view-stat}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views,echo=F,results='asis'>>=
-
-print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
-  \label{tab:view-stat-naive}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-naive,echo=F,results='asis'>>=
-
-print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
-  \label{tab:view-stat-default}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-default,echo=F,results='asis'>>=
-
-print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
-
-<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-library(scales)
-#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))
-
-colourCount = length(unique(final.bl$Views))
-getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-
-#p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
-#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
-
-#+scale_color_manual(values=getPalette(colourCount))+
-
-#+scale_x_date(breaks='year',labels=date_format('%Y'))
-
-#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
-
-#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))
-
-require(gridExtra)
-#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
-#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
-@
-
-\begin{table}[hp]
-  \caption{Trading strategy performance}
-  \label{tab:strategy}
-  \ This table shows the performance statistics of the different trading strategies.
-Panel A presents the results for the passive strategy.
-Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}).
-Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average.
-The trading period spreads from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \toprule
-  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-<<bl-market,echo=F,results='asis'>>=
-
-dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results[4,1,]
-cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
-#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
-cat('\\midrule \n')
-@
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
-<<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
-<<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
-<<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{table}[hp]
-  \caption{Trading strategy performance: Sharpe ratio}
-  \label{tab:substrategy}
-  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
-Panel A represents the perfect foresight information set; panels B and C show, respectively, the recent and the all history analysts' performance.
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-\toprule
-  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-<<sr-true,echo=F,results='asis'>>=
-
-#results.final <- bl.results['Market',1,]
-cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
-#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
-@
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-<<sr-naive,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
-@
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-<<sr-default,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
-@
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\begin{figure}[hp]
-\begin{center}
-\includegraphics[width=\linewidth]{figure/Black-litterman}
-\end{center}
-\caption{Trading strategy timeline}
-\label{fig:bl}
-\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
-\end{figure}
-
-\begin{figure}[hp]
-\begin{center}
-\includegraphics[width=\linewidth]{figure/example-fig-1}
-\end{center}
-\caption{Daily stock price Amazon and brokers target prices}
-\label{fig:example}
-\ Target price and actual prices for Amazon  the second quarter of 1999.
-\end{figure}
-
-\begin{figure}[hp]
-\begin{center}
-\includegraphics[width=\linewidth]{figure/bl-results-fig-1}
-\end{center}
-\caption{Performance of the BL model}
-\label{fig:bl-results}
-\ Quarterly performance of the cumulative portfolio wealth for all strategies.
-Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$.
-\textit{TP} is the strategy with rankings based on the accuracy in target prices, \textit{CONS} is the strategy based on the consensus among the analysts regarding a stock's expected return.
-\textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
-The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}
-\end{figure}
-
-\end{document}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in match(x, table, nomatch = 0L): object 'test' not found}}\end{kframe}
+\end{knitrout}

### 2015-02-14 doc/paper/paper-knitr.Rnw
Initial commit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\usepackage{natbib}
\usepackage[natbibapa]{apacite}

\DeclareMathOperator*{\argmax}{arg\,max}
%\newcommand{\r}{\Sexpr{}}
\DeclareMathOperator{\rank}{rank}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\tr}{\textit{true}}
\newcommand{\naive}{\textit{recent}}
\newcommand{\default}{\textit{all-time}}
\newcommand{\market}{\textit{market}}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
%\newcommand{\raw}{\textit{raw}}
%\newcommand{\diff}{\textit{diff}}
%\newcommand{\random}{\textit{random}}
%\newcommand{\rollsd}{\textit{roll.sd}}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\begin{document}

<<include=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
load('cache/q.data.RData')
load('cache/final.bl.RData')
load('cache/market.set.RData')
load('cache/example.dt.RData')
source('lib/BL-functions.R')
#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
split.rank <- function(r,n){
if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}        
        t <- head(r,n)
        b <- tail(r,n)
        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
}

summary.stat <- function(dt){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
}

summary.mean.stat <- function(dt,value){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
}

trunk.percent <- 0.05
stocks <- unique(market.set[,Stock])
#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)

q.data <- na.omit(q.data.full[stocks])
q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])

### General stat of TP/P-1
stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')

core.dt <- unique(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],by=c('q.id','Broker','Stock'))
quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])

n <- 3
ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

#core.dt[Stock=='AAPL'&Broker=='PIPER'][,list(q.id,rank)][,NextPeriod:=split.rank(rank,5),by=q.id][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))]][]

require(descr)
ranked.pt.dt$CurrentPeriod <- factor(ranked.pt.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
ranked.pt.dt$NextPeriod <- factor(ranked.pt.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
cont.tab <- ranked.pt.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.c=T,prop.t=T,prop.chisq = F,plot=F)]

###Statistics for views:
###non rank base data
load('cache/nr.views.RData')
load('cache/pt.rank.views.RData')
load('cache/eps.rank.views.RData')

load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')

complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')

quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])

ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))

eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))

brok.full.stat.pt <- acast(setnames(na.omit(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
pt.full.period <- setnames(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))
#Views stat
stat.rank.views <- acast(setnames(pt.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')
rank.views.full.period <- acast(setnames(pt.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

pt.eps.stat.rank.views <- acast(setnames(eps.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')

pt.eps.rank.views.full.period <- acast(setnames(eps.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

stat.nr.views <- acast(setnames(nr.views[Method=='true',descriptive.f(View),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
nr.full.period <- acast(setnames(nr.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')

#setkey(pt.rank.views,Stock,q.id,year)
#setkey(nr.views,Stock,q.id,year)

brok.full.stat.eps <- acast(setnames(na.omit(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
eps.full.period <- setnames(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))

#join.dt <- na.omit(setkey(core.dt,q.id,Broker,Stock,Sector)[setkey(complete.dt,q.id,Broker,Stock,Sector)])

load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
#num.b <- apply(estimates[,working.s,working.b,2],c(1,3),function(i){length(i[!is.na(i)])})
#num.s <- apply(estimates[,working.s,working.b,2],c(1,2),function(i){length(i[!is.na(i)])})
#final.bl <- setkey(all.final.bl,Method)[methods]
#methods <- as.character(unique(final.bl$Method)[c(1:7,11:13)])
final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]

final.bl$Method <- factor(final.bl$Method,levels=strategies)
final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
final.bl <- final.bl[,ann.ret:=ann.ret*100]
bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Aggregation','Views'),measure.vars  = c('ann.ret','ann.sd','ann.sr','meanViews','Ave.TO')),by=c('Method','Aggregation','variable','Views')),Views~Method~Aggregation~variable,value.var = 'value')
@

\title{Are rankings of financial analysts useful for investors?}
 \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
 \author[1,3]{ Ana Paula Serra (\href{mailto:aserra@pbs.up.pt}{aserra@pbs.up.pt})}
 \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}

\affil[1]{FEP \& CEF.UP, University of Porto}
\affil[2]{INESC TEC}
\affil[4]{FEUP, University of Porto}
\affil[3]{CEF.UP \& Porto Business School, University of Porto}

\maketitle
\begin{abstract}
Some institutions issue rankings of the financial analysts. Given that these rankings are \textit{ex-post}, it is arguable if they are useful for investors. In this paper we show that a relative performance by a set of financial analysts seems to be valuable. We show that the rankings can identify the top analysts and a trading strategy based on these rankings outperforms the passive strategy -- ``buy and hold'' a general index. Moreover, the strategy based on the average analysts' performance fails to attain abnormal returns. In addition, we report that analysts issuing accurate price targets are more favorable for the investors  to follow rather than analysts issuing accurate EPS forecasts. %Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
\end{abstract}

\section{Introduction}
\label{sec:intro}

Financial analysts play an important role, as they are the experts in interpreting financial information. In the literature, there is still a debate if following the  advice of analysts bring value to investors after transaction costs \citep{womack1996,mikhail2004sae,li2005persistence}. The essence of this debate lies in the problem of identifying the analysts with good stock picking skills. In this paper we show that rankings of financial analysts can identify such analysts and an investor, by leveraging these rankings, can gain positive abnormal returns.

In recent years, some institutions were very active in publishing and  selling  rankings of financial analysts. Some rankings  are based on privately held surveys of  buy-side analysts (e.g., the Institutional Investor's rankings of the All-America Research Teams\footnote{\url{http://www.institutionalinvestor.com/Research/4560/First-Team.html}} and Bloomberg's America's Best Stock Analysts\footnote{\url{http://www.bloomberg.com/news/2013-08-14/jpmorgan-top-stock-picker-with-equities-out-of-lockstep.html}}); others are based on the performance of sell-side analysts (ThomsonReuters' top StarMine analysts\footnote{\url{http://excellence.thomsonreuters.com/award/starmine}}). In any of the cases, these rankings serve as one way to identify the best analysts. However, aside from personal acknowledgment among the peers, it is still arguable whether these rankings can truly identify the best specialists \citep{desai2000ass} or they are just  ``popularity contests" \citep{emery2009}. %In this paper, we support the argument that the top-ranked analysts, indeed, have stock picking skills.

Our approach in forming the rankings is purely academic and is based on  accuracy of reports that financial analysts supply. We show that the top-ranked analysts, indeed, have stock picking skills. The contributions of our research are the following. First, we develop a trading strategy that transforms rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}. Second, we show that annualized cumulative returns form trading strategies that are  based on analysts' rankings achieve outperform the passive strategy: buy-and-hold the general index. Third, we show that a strategy with a perfect foresight of rankings yields the highest potential cumulative annualized return. Finally, we find that, for investors, it is favorable to follow analysts who issue the most accurate target price reports as opposed to the ones who issue the most accurate EPS forecasts.

The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines the trading strategy; section \ref{sec:rankings} summarizes the methodology of building the rankings and provides the database description used in the paper; section \ref{sec:results} analyzes the results; and section \ref{sec:conclusion} concludes.

\section{Rankings of Financial  Analysts}
\label{sec:ranking}

In the finance literature there has been a long debate on whether financial analysts produce valuable  advice. Some argue that following the advice of financial analysts,  translated as recommendations of buying, holding, or selling a particular stock, does not yield  abnormal returns, i.e.,  returns that are above the required return to compensate for risk \citep{fama1970ecm}. The Efficient Market Hypothesis (EMH) states that financial markets are efficient and any past information  regarding a stock would  be reflected in its current price; hence, it would be  impossible to generate abnormal returns based upon publicly available information.

Yet there are information-gathering costs and the information is not immediately reflected on prices  \citep{grossman1980iie}. As such, prices might not  reflect all the available information because if this were the case, those who spent resources to collect and analyze   information would not receive a compensation for it.

Many trading strategies try to forecast the price movements relying on the historical prices or estimate the intrinsic value of a company. Obviously, this type of research is associated with significant amount of up-front costs to acquire databases, software, etc. On the other hand, financial analysts have these tools and, presumably, skills to identify  stocks that worth be invested. Thus, for an investor, it is cheaper to follow the recommendations of financial analysts rather than perform a proper stock market analysis.

Assuming that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}, it is possible to rank analysts based on the accuracy of their reports. In fact, StarMine does exactly this: it ranks analysts according to their performance in forecasting earnings (the EPS forecast accuracy) and in predicting stock prices (the price targets accuracy).

To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES). It measures ``... [a] relative accuracy; that is, analysts are compared against their peers. An analyst's SES can range from 0 to 100, with 50 representing the average analyst. To get a score higher than 50, an analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates".\footnote{\url{http://excellence.thomsonreuters.com/award/starmine?award=Analyst+Awards&award_group=Overall+Analyst+Awards}}

For target price ranking, StarMine's methodology compares the non-leveraged portfolio for each analyst based on his/her recommendations. The portfolio is constructed as follows. For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark (Comparable index). ``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark. ``Holds'' invest one unit in the benchmark (i.e., for an excess return of zero). Sell are reverse. StarMine re-balances its calculations at the end of each month to adjust for when an analyst changes his or her mind (by adding, dropping or altering a rating) or when a stock enters or exits an industry grouping.

The rankings that StarMine obtains are not only used for the broad media coverage and a ``red carpet" ceremony to praise the best analysts, but also to develop and sell ranking based models to monitor stock market (e.g., SmartEstimates\footnote{\url{http://www.starmine.com/index.phtml?page_set=sm_products&sub_page_set=sm_professional&topic=analytical&section=accurate_estimates}}). In addition, the top-ranked financial analysts affect the market participants: the market  reacts more to the recommendations issued by the top-ranked analysts \citep{emery2009}.
%Evidence shows that market response to analysts' recommendations is stronger when analysts issue them with a good forecasting tracking record \citep{park2000analyst,loh2006aef}. Thus, it seems to be the case that only a subset of analysts influences the stock prices and, as such, only that subset of analysts deserves to be followed \citep{loh2011}.

The goal of this study is to evaluate if rankings indeed add value to the investors; that is, if following advice of the top analysts truly yields positive abnormal returns compared to following the advice of analysts' consensus. For this purpose, we develop two types of  active trading strategies. The first, the ranking strategy,  leverages the analysts' rankings as the main component in obtaining the information about future performance of a stock. The second, the consensus strategy, relies on the consensus among the analysts regarding future stock performance.

Each of these strategies uses information about analysts' past performance. Different analysts' profiles can be obtained by looking at different horizons in the past. If only recent information is used, then it better reflects the recent performance of the analysts. However, it is more sensitive to spurious events (e.g., a quarter, which has been surprisingly good or bad). As we incorporate older information, the analysts' historical performance become less affected by these spurious events but it may not reflect the current abilities of the analysts. Based on this, we define two information availability sets representing the two scenarios: 1) only use information about analysts' performance  from the period $t-1$ and 2) use information from the beginning of the trading period up to $t-1$. We call the former the \naive{} set and the latter --- the \default{}.

In addition to feasible approaches, we also create the one that uses future information about analysts' performance that only would be available at the end of $t$. In case of rankings, this would mean that we would know the true rankings of the analysts. Naturally, this scenario is not feasible; however, it is still important to consider it as it represents a perfect foresight strategy. Therefore, it serves as a reference point to the feasible trading strategies. We call this approach as the \tr{}.

There seems to be a debate in the literature on whether the analysts in issuing the target price reports rely on growth-based models (e.g., PEG ratio) or on more rigorous models (such as the residual income model of \cite{ohlson1995}). On one hand, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to evaluate stocks' target prices. On the other hand, \cite{simon2011} argues the most accurate analysts rely more on the rigorous models in setting their price targets. As we create two types of rankings that are based on accuracy of analysts' target price reports and  EPS forecasts, we can evaluate if the most accurate analysts' use growth heuristics or rigorous models in setting their target prices.
% and it is, in a sense, an upper bound of all trading strategies.

%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \tr{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.

%We claim that the ranking strategies outperform the consensus ones as well as the passive strategy.

%we investigate the problem with two ranking  methods that are used further as the inputs for the trading strategy. The first is the \naive{} rankings and this is simply the last known analysts' actual rankings. The second method is taken from the Machine Learning literature \citep{aiguzhinov2010} and it is so-called the \default{} ranking. It is the average rank of an analyst since the beginning of the sample period and it encompasses the average analyst's relative performance. We formalize these methods in the appropriate section of the paper.

\section{Trading Strategy}
\label{sec:trading}
The Black-Litterman (BL) model is a tool for  active portfolio management\citep{black1992}. The model incorporates views in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting. Compared to CAPM model, where expected return is a function of systematic risk, expected market risk premium and the risk-free assets, in the BL model investors have views regarding individual stocks. As such, the model blends the subjective views of an investor about future performance of a stock with the market implicit returns. Hence, it is important to have the views that the BL model transforms into a portfolio, which should outperform the general market.

Previous research in applying the BL model that relates to this paper includes a work of \cite{da2011bl}. In this study, the authors combine the consensus expected returns with the market implicit returns. They report that the resulted strategy outperformed the market. Our consensus strategy is based upon the strategy outlined in \cite{da2011bl}.

The literature on the BL model has established a notation. The views are formalized as: $Q$ - the expected returns for stock $s$; $\Omega$ - the confidence of $Q$. In this paper, we use analysts' 12-month target price (TP) reports as proxy for stock expected return \citep{da2011bl}. Confidence $\Omega$ for stock $s$ is based on the coefficient of variation  among the analysts which is similar to the measure of dispersion in analysts' options outlined in \cite{diether2002}.

Operationally, the trading strategy applies as follows (fig. \ref{fig:bl}):
\begin{enumerate}
\item For each stock $s$, at the beginning of quarter $t$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);

\item Using market information available at the last day of quarter $t-1$, we obtain the market inputs: vector of implicit returns and variance/co-variance matrix);

\item Apply BL model to get  optimized portfolio weights and buy/sell stocks accordingly;

\end{enumerate}

\subsection{Defining analysts' expected returns}
\label{def-q}

For the consensus strategy, we follow \cite{da2011bl} to obtain analysts' expected returns as follows:
\begin{equation}
\label{consq}
consQ_{s,t}= \frac{1}{N_a} \sum_1^{N_a} r_{a,s}
\end{equation}
where $N_a$ is the number of analysts with valid TP report and $r_{a,s}=TP_{a,s}/P_{s}-1$  is the analysts' expected return for a stock $s$ based on the analyst's price target $TP_{a,s}$ and $P_{s}$ is a stock price three days before the $TP$ announcement.

In the ranking strategy, we convert the rankings into expected returns as follows:

\begin{enumerate}
\item We calculate the weights for each of the analysts $a$ based on the analyst's rank, such that rank 1 receives the weight of 1 and then the weights diminish as the ranks increase:
\begin{equation}
\label{eq:weight}
w_{a,s}=1-\frac{rank_{a,s}-\min{ \{rank \} }}{\max{\{rank \}}}
\end{equation}

\item The expected rank-weighted return is:
\begin{equation}
\label{rankq}
rankQ_{s,t}=\frac{\sum_{i=1}^{N_a} (w_{i,s} \times r_{i,s})}{\sum_{i=1}^{N_a} w_{i,s}}
\end{equation}
\end{enumerate}

\paragraph{Target Price ranking.} In these strategy, we rank analysts based on the Proportional  Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}. First,  we define the forecast daily error  $FE_{d,a,s}$ as an absolute value of the difference between analysts' $TP_{a,s}$ and daily stock price $P_{s}$:
\begin{equation}
\label{dfe}
FE_{d,a,s}=|{P_{s}-TP_{a,s}}|
\end{equation}
The daily PMAFE is given as:
\begin{equation}
\label{tp:pmafe}
PMAFE_{d,a,s}=\frac{FE_{d,a,s}}{\mu(FE_{t,s})}
\end{equation}
where $\mu({FE}_{t,s})$ is the average per quarter forecasting error.
The rank of an analyst that goes into equation (\ref{eq:weight}) is the ranked average analyst's $PMAFE$ per quarter:
\begin{eqnarray}
\label{tp:rank}
\mu(PMAFE)=&\frac{1}{N_d} \sum_{i=1}^{N_d} PMAFE_{i,a,s} \\
rank_{a,s}=&\rank_{i=1}^{N_a} \{ \mu(PMAFE_{i,s}) \}
\end{eqnarray}
where $N_d$ is the number of trading days in a quarter.

\paragraph{EPS ranking.} For the EPS rankings, we apply the same procedure as for the TP rankings that the equations (\ref{dfe}) through (\ref{tp:rank}) for the case of EPS ranking are as follows:
\begin{eqnarray}
\label{eps:rank}
FE_{a,s}=&|{ACT_{s}-PRED_{a,s}}| \nonumber \\
PMAFE_{a,s}=& \frac{FE_{a,s}}{\mu(FE_{s})} \nonumber \\
rank_{a,s}=&\rank_{i=1}^{N_a} \{ PMAFE_{i,s} \}  \nonumber
\end{eqnarray}
where $ACT_{s}$ and $PRED_{a,s}$ are actual quarterly and forecasted EPS respectively.

\subsection{Defining the confidence of expected returns}
\label{def-omega}
We base the confidence of BL views on coefficient of variation of forecasting error:

\begin{equation}
CV = \frac{\sigma (FE)}{\mu (FE)}
\end{equation}
where $\sigma$ and $\mu$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS. The low value of $CV$ means a general agreement among analysts about stocks' performance.

\section{Data and experimental setup}
\label{sec:rankings}

\subsection{Database and data sample}
To implement the trading strategy, we focus on the  S\&P500 stocks. We get both the target price information and the EPS forecasts from ThomsonReuters  I/B/E/S detailed history database. The  S\&P500 constituents list and stock daily prices are from DataStream.

The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in TP dataset is \Sexpr{q.data[!is.na(trunk.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(trunk.view),.N,by=Stock][,.N]} S\&P500 stocks. Given the fact that financial analyst mostly issue TP annually,\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have 12-month horizon \citep{glushkov2009}} we assume that an analyst keeps her TP forecast valid for one calendar year until it gets revised or expires after one year.

Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}). This is done due to the extreme values cause by misalignment errors found on I/B/E/S data.\footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.} The final sample size of $TP/P-1$ observations is reduced from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.

The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks. To implement the ranking, we require that a stock had at least three brokers per quarter that issue EPS forecasts. In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters). Finally, we consider only S\&P500 stocks. All these requirements reduce our sample of EPS forecasts to \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks. The total number of EPS-Stock-Broker observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
Panel A shows the composition of each category for rankings based on the accuracy in target prices. We observe that the distribution of the $top_{t}$ group is as follows: \Sexpr{round(cont.tab[[3]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(cont.tab[[3]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(cont.tab[[3]][3,1],3)*100}\% from the $bottom_{t-1}$; and \Sexpr{round(cont.tab[[3]][4,1],3)*100}\%  from the $noRank_{t-1}$. It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank. Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[3]][4,4],3)*100}\%). This suggests that analysts are not frequent in issuing target price reports.

Table (\ref{tab:ret-stat}) provides descriptive statistics of target price and EPS data. Panel A shows the number of target prices per stock per quarter. For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations with average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} target price reports per quarter per stock. Panel B of the table presents the statistics of the number of EPS forecasts. In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} forecast-quarter observations. The average number of forecasts per stock per quarter is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.

We applied the ranking procedure outline in section \ref{def-q} on both datasets. For target price rankings, we use the average per quarter daily errors as the measure of analysts' forecasting ability (\ref{tp:pmafe}). The daily frequency allows us to capture the analysts' performance with better precision. Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices. As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock. At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts. Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices. The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4). In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
\subsection{Ranking contingency analysis}
The rankings allows us to perform a contingency analysis of analysts' ranks and their intetemporal changes. Table (\ref{tab:rank-stat}) demonstrates the results. For this table, we split rankings into four categories: the analysts fall into \emph{top} category if they have ranks below or equal to \Sexpr{n},\footnote{The choice comes from the restriction of a stock having at least \Sexpr{n} brokers of coverage in a quarter.} the \emph{bottom} category includes analysts whose ranks fall into the last \Sexpr{n} ranks, the \emph{middle} category is for analysts who neither \emph{top} nor \emph{bottom}, and if analysts do not issue any report they fall into the \emph{noRank} category.  We, then, calculate a distribution of analysts for each of the category for the period $t$,i.e., for a given ranking group, we would like to know how it was composed.

%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
%An interesting observation is for the \emph{noRank} category: \Sexpr{ round(cont.tab[[2]][4,1],3)*100}\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.

Panel B depicts the similar analysis for the EPS forecast rankings. For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$. However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[3]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[3]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[3]][4,3],3)*100}\%. This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.

\subsection{Stocks' expected returns}
With analysts' rankings and corresponding analysts' expected returns, we obtain rank-weighted stocks' expected returns (eq. \ref{rankq}). The literature on target price analysis reports different values: \cite{bradshaw2002} reports 24\% for the period of 2000--2009, \cite{da2011} post 40\% for the period of 1996--2004, \cite{zhou2013} for the sample period of 2000--2009 reports 96\%. None of these studies discuss these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns. \cite{bodie2009} show that geometric average rate of return for the U.S. large stocks (S\&P 500) for the period of 1926--2005 is 10.17\% and the average rate of excess return is 8.39\% with the risk premium estimated 6--8\%. While it is not the best idea to extrapolate the historical values, still, we can say that the expected stocks return should be around 14--16\%. Clearly, the values presented in the literature shows that analysts are very optimistic in issuing target price reports.

We present descriptive statistics of the expected stock returns in table (\ref{tab:view-stat}). Panel A show the statistics for $consQ$ defined in eq. (\ref{consq}). The consensus among the analysts about stock expected return is \Sexpr{round(nr.views[,mean(View,na.rm=T),by=Method][Method=='true',V1],3)*100 }\%.  Panel B of the table shows the statistics for $rankQ$ obtained from the rankings based on the target price accuracy. We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%. The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%. Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.

\subsection{Feasible strategies}
To proceed with the trading strategy, we formalize the two feasibility sets mentioned at the end of section (\ref{sec:ranking}). We use the \naive{} views for case when the analysts' information known only at $t-1$, and we use the \default{} views when the analysts' information known from the beginning of the period for up to the period $t-1$. Formally, we define:
\begin{itemize}

\item  the \naive{} views information:
\begin{equation}
\label{naive:ranking}
\widehat{Q_{t}}=Q_{t-1}
\end{equation}

\item  the \default{} views information:
%\begin{itemize}
%\item ranking based views:
\begin{equation}
\label{default.rank}
\widehat{Q_{t}} = \frac{1}{N_{t-1}} \sum_{i=1}^{N_{t-1}} Q_{i}
\end{equation}
%\item consensus based views:
%\begin{equation}
%\label{default.cons}
%\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
%\end{equation}
%\end{itemize}
\end{itemize}

\section{Empirical Results}
\label{sec:results}

We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.

\subsection{Passive strategy}
Panel A shows  the performance of the passive strategy \textit{Market}. The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,'ma',1],2)}\% and an annualized Sharpe ratio (SR) of \Sexpr{ round(bl.results['Market',1,'ma','ann.sr'],3)}. The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'ma','meanViews'])} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'ma','Ave.TO'],3)}, which demonstrates the ins/outs of the S\&P 500 constituents list.

\subsection{Results of the perfect ranking foresight strategy}
Panel B presents the result for the case of \tr{} information availability set. The annualized cumulative returns for each of the active strategies (CONS,TP,and EPS) are: CONS =\Sexpr{round(bl.results['CONS',1,'ma',1],2)}\%, TP = \Sexpr{round(bl.results['TP',1,'ma',1],2)}\%, and EPS = \Sexpr{round(bl.results['EPS',1,'ma',1],2)}\%. All the strategies outperform the benchmark. The result confirms that these strategies set an upper bound for the cumulative return yield. It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.

In addition, the result from the perfect foresight strategy implies that knowing the information in advance is beneficial. Namely, knowing in advance the rankings of the analysts who issue accurate target price reports would result in positive trading strategy. At fist sight this seems to be an impossible task; however, one of the possibilities is to apply methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}) where this type of problem (referred as a label ranking problem) has been broadly studied. For example, in \cite{aiguzhinov2010} a label ranking algorithm takes the Bayesian approach in predicting the rankings --- the same Bayesian approach that is in the core of the Black-Litterman model.

\subsection{Results of feasible strategies}
Panels C and D of the table (\ref{tab:strategy}) show the trading results of the feasible information availability sets. In the case of the \naive{}, the strategy that outperforms all the others (including the \emph{Market}) is the TP strategy which yields an annualized cumulative return of \Sexpr{round(bl.results['TP',2,'ma',1],2)}\%. The other two strategies (CONS and EPS) resulted in below-the-market performance (annualized cumulative return of \Sexpr{round(bl.results['CONS',2,'ma',1],2)}\% and \Sexpr{round(bl.results['EPS',2,'ma',1],2)}\% respectively). The case of the \default{}, demonstrates the worse results as none of the active strategies is able to outperform the \emph{Market} (TP = \Sexpr{round(bl.results['TP',3,'ma',1],2)}\%, CONS = \Sexpr{round(bl.results['CONS',3,'ma',1],2)}\%, EPS = \Sexpr{round(bl.results['EPS',3,'ma',1],2)}\%)

The feasible information sets demonstrate interesting results. It seems to be the case that the information about stock's expected return based on rankings create more value than the same information but based on analysts' consensus. Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}. In addition, the results show that keeping all available information about analysts' performance does not create any value. As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.

Finally, the trading results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets create more value than that of following analysts issuing accurate EPS forecasts. This result contradicts with findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are less correlated with the growth-based heuristics (such as EPS forecasts) as these are optimistic and not good predictors of future returns.

Figure (\ref{fig:bl-results}) shows the graphical representation of the cumulative portfolio wealth for all of the information sets. The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at October of  2000 and ending at December 2009. Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.

\section{Conclusions}
\label{sec:conclusion}

Some institutions, such as StarMine, rank financial analysts based on their accuracy. These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors. Therefore, there is a growing interest in understanding the relative performance of analysts.

We show that rankings do bring value to investors as they identify the top analysts. By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets. We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve. The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets. The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.

For the future work we would like to develop the new methods to be able to get closer to the upper bound.

\bibliographystyle{apalike}
\bibliography{rank}
\appendix

\section{Tables and Figures}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\linewidth]{figure/Black-litterman}
\end{center}
\caption{Trading strategy schematics}
\label{fig:bl}
\ Schematics of the implementation of the Black-Litterman model. We gather all necessary inputs at the end of  $t-1$. At the beginning of $t$ we apply the BL model and form the portfolio of stocks based on the optimal weights. At the end of $t$, we evaluate the portfolio.
\end{figure}

%Descriptive  table
\begin{table}[htb]
  \caption{Descriptive statistics of data}
  \label{tab:ret-stat}
\ Descriptive statistics of target price reports (panel A) and EPS forecasts (panel B) per stock per quarter.

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
   \multicolumn{6}{l}{\textbf{Panel A: TP}} \\
<<desc-pt,echo=F,results='asis'>>=

data.to.display <- c('nbr.val','min','mean', 'median','max','std.dev')
results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])

options(xtable.comment = FALSE)
cat("Years & Observ & Min& Mean & Median &Max& std.dev\\\\\n")
cat('\\midrule \n')
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
   \multicolumn{6}{l}{\textbf{Panel B: EPS}} \\
<<desc-eps,echo=F,results='asis'>>=

results.final <- rbind(brok.full.stat.eps[,data.to.display],'Total period'=setkey(setnames(setkey(complete.dt[,.N,by=list(Stock,q.id,year)],year)[,descriptive.f(N)],c('Statistics','value')),Statistics)[data.to.display][,value])

print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[htb]
  \caption{Example of ranking}
  \label{tab:example}
\ An example of rankings for target price (panel A) and EPS forecasts (panel B). The brokers cover the stock of Amazon (AMZN) during the second quarter of 1999. We apply (\ref{tp:rank}) to obtain ranks of the brokers. \emph{TP} is a valid target price; $\mu(P)$ is the average stock price in quarter; $\mu(PMAFE)$ is the average proportional mean adjusted error. In EPS case, $PRED$ is the EPS forecast issued by the brokers; $ACT$ is the actual earnings reported by a company.
\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \toprule
    \multicolumn{5}{l}{\textbf{Panel A: TP}} \\
<<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
print(xtable(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list(Broker,TP=PT,'$\\mu(P)$'=round(meanQprice,3),'$\\mu(PMAFE)$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],display=c('s','d','f','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \multicolumn{5}{l}{\textbf{Panel B: EPS}} \\
<<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
print(xtable(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list(Broker,'$PRED$'=Est,'ACT'=act.eps,'$PMAFE$'=eps.pmafe,rank)][order(rank)],display=c('s','d','f','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
require(gridExtra)
example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
ggplot(example.dt,aes(x=s.Date,y=PT,group=Broker,color=Broker,shape=Broker))+geom_line(size=1)+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Example of daily stock price (AMZN), compared to broker\'s TP (ranked by daily forecast error)')+scale_color_grey()+geom_line(aes(y=priceAdj),color='black')+theme(plot.title = element_text(colour = "Black"),legend.position='top')
#grid.draw(grobTree(arrangeGrob(p,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\linewidth]{figure/example-fig-1}
\end{center}
\caption{Example of ranking the analysts}
\label{fig:example}
\ An example of ranking of the analysts for the second quarter of 1999 for Amazon. Broker are ordered by their daily forecasting error.
\end{figure}

 % Descritive rankings
 \begin{table}[htb]
  \caption{Descriptive analysts' rankings}
  \label{tab:rank-stat}

\ Changes in analysts' \emph{top}, \emph{middle}, \emph{bottom} and \emph{noRank} ranking categories when moving from $t-1$ (rows) to $t$ (columns). Each cell informs a percent of total that compose the ranking category at $t$. Panel A depicts the breakdown of rankings  based on the accuracy in target prices. Panel B shows the rankings that are based on the EPS forecasts.
\begin{tabularx}{\linewidth}{r*{5}{Y}}
    \toprule
\multicolumn{5}{l}{\textbf{Panel A: Target Price ranking}} \\
<<desc-rank-pt,echo=F,results='asis'>>=
tab.r <- round(rbind(cont.tab[[3]],Total=apply(cont.tab[[3]],2,sum)),3)*100
rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=T,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)

@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
\midrule
   \multicolumn{5}{l}{\textbf{Panel B: EPS ranking}} \\
<<desc-rank-eps,echo=F,results='asis'>>=
tab.r <- round(rbind(eps.cont.tab[[3]],Total=apply(eps.cont.tab[[3]],2,sum)),3)*100
rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{table}

\begin{table}[htb]
  \caption{Descriptive statistics of views}
  \label{tab:view-stat}
  \small\addtolength{\tabcolsep}{-2pt}
  \ Descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
\begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
%    \multicolumn{4}{l}{\textbf{Panel A: Consensus views}} \\
<<desc-nr.views,echo=F,results='asis'>>=
cat("Years & Observ & Mean & Median &std.dev\\\\\n")
cat('\\midrule \n')
data.to.display <- c('nbr.val','mean', 'median','std.dev')
results.final <- rbind(stat.nr.views[,data.to.display],'Total period'=nr.full.period['true',data.to.display])

print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1,0),command=c('\\midrule \n','\\multicolumn{4}{l}{\\textbf{Panel A: Consensus views}} \\\\')))
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \midrule
    \multicolumn{4}{l}{\textbf{Panel B: TP Ranking views}} \\
<<desc-r.views,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

results.final <- rbind(stat.rank.views[,'true',data.to.display],'Total period'=rank.views.full.period['true',data.to.display])

options(xtable.comment = FALSE)

#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \midrule
    \multicolumn{4}{l}{\textbf{Panel C: EPS Ranking views}} \\
<<desc-eps.views,echo=F,results='asis'>>=
#data.to.display <- c('nbr.val','mean', 'median','std.dev')

results.final <- rbind(pt.eps.stat.rank.views[,'true',data.to.display],'Total period'=pt.eps.rank.views.full.period['true',data.to.display])
print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))

@
\bottomrule
  \end{tabularx}
\end{table}

<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
library(scales)
#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))

colourCount = length(unique(final.bl$Views))
getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))

#p.cum.ret <-
ggplot(final.bl[Aggregation=='ma'],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+geom_hline(yintercept=100)+facet_grid(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top')+scale_color_grey()+geom_point()

#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))

#+scale_color_manual(values=getPalette(colourCount))+

#+scale_x_date(breaks='year',labels=date_format('%Y'))

#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))

#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))

require(gridExtra)
#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
@

\begin{table}[ht]
  \caption{Trading strategy performance}
  \label{tab:strategy}
  \ Annualized cumulative statistics of trading based of rankings. Panel A presents the results from the passive strategy and is serve as the benchmark. Panel B shows the results of the trading where we, at the end of $t-1$, know the true analysts' rankings for the end of $t$. Panel C summarizes the results of the strategy in which rankings are recent and known at time $t-1$. Finally, panel D demonstrates the results of strategies for the case where we use all known rankings from the beginning of the period for up to $t-1$. TP is the strategy with rankings based on the accuracy in target prices, CONS is the strategy based on the consensus among the analysts regarding a stock's expected return. EPS is the strategy with rankings based on the accuracy of EPS forecasts. The trading period ranges from 2000Q4 until 2009Q4.

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
<<bl-market,echo=F,results='asis'>>=

results.final <- bl.results['Market',1,'ma',]
cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized std. dev','Annualized Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
print(xtable(t(data.table(Market=results.final)),display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\')))
cat('\\midrule \n')
@

\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
<<bl-nr,echo=F,results='asis'>>=
results.final <- bl.results[1:3,1,'ma',]
print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)),command=c('\\midrule \n')))
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
<<bl-pt,echo=F,results='asis'>>=
results.final <- bl.results[1:3,2,'ma',]
print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(results.final)),command=c('\\midrule \n')))
@
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
<<bl-eps,echo=F,results='asis'>>=
results.final <- bl.results[1:3,3,'ma',]
print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
@
\bottomrule
\end{tabularx}
\end{table}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\linewidth]{figure/bl-results-fig-1}
\end{center}
\caption{Performance of the BL model}
\label{fig:bl-results}
\ Quarterly performance of the cumulative portfolio wealth for all strategies. Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$. TP is the strategy with rankings based on the accuracy in target prices, CONS is the strategy based on the consensus among the analysts regarding a stock's expected return. EPS is the strategy with rankings based on the accuracy of EPS forecasts. The trading period ranges from 2000Q4 until 2009Q4.
\end{figure}

\end{document}

### 2015-02-14 doc/paper/paper-knitr.tex
Initial commit

--- 2015-02-14 doc/paper/paper-knitr.Rnw
@@
-\documentclass{article}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{authblk}
@@
 \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
-
-<<include=FALSE>>=
-library(knitr)
-opts_chunk$set(concordance=TRUE)
-@
-
-<<load.data,echo=F,warning=FALSE,message=FALSE>>=
-strategies <- c('true','recent','all-time')
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
-library(reshape2)
-library(data.table)
-library(ggplot2)
-library(stringr)
-library(zoo)
-library(xtable)
-load('cache/q.data.RData')
-load('cache/final.bl.RData')
-load('cache/market.set.RData')
-load('cache/example.dt.RData')
-source('lib/BL-functions.R')
-#library(ProjectTemplate)
-#load.project()
-###ADD NAs for the case of no ranking ( if NA, no raking)
-split.rank <- function(r,n){
-if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}
-        t <- head(r,n)
-        b <- tail(r,n)
-        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
-}
-
-summary.stat <- function(dt){
-  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
-}
-
-summary.mean.stat <- function(dt,value){
-  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
-}
-
-trunk.percent <- 0.05
-stocks <- unique(market.set[,Stock])
-#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
-q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)
-
-q.data <- na.omit(q.data.full[stocks])
-q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
-stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])
-
-### General stat of TP/P-1
-stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(trunk.view,na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')
-
-core.dt <- unique(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],by=c('q.id','Broker','Stock'))
-quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])
-
-n <- 3
-ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
-#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]
-
-#core.dt[Stock=='AAPL'&Broker=='PIPER'][,list(q.id,rank)][,NextPeriod:=split.rank(rank,5),by=q.id][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))]][]
-
-require(descr)
-ranked.pt.dt$CurrentPeriod <- factor(ranked.pt.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
-ranked.pt.dt$NextPeriod <- factor(ranked.pt.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
-cont.tab <- ranked.pt.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.c=T,prop.t=T,prop.chisq = F,plot=F)]
-
-###Statistics for views:
-###non rank base data
-load('cache/nr.views.RData')
-load('cache/pt.rank.views.RData')
-load('cache/eps.rank.views.RData')
-
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
-
-complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
-eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')
-
-quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])
-
-ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
-#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]
-
-ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
-ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
-
-eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
-#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
-#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))
-
-brok.full.stat.pt <- acast(setnames(na.omit(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
-pt.full.period <- setnames(setkey(core.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))
-#Views stat
-stat.rank.views <- acast(setnames(pt.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')
-rank.views.full.period <- acast(setnames(pt.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')
-
-pt.eps.stat.rank.views <- acast(setnames(eps.rank.views[,descriptive.f(View),by=list(year,Method)],c('Year','Method','Statistics','value')),Year~Method~Statistics,value.var='value')
-
-pt.eps.rank.views.full.period <- acast(setnames(eps.rank.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')
-
-stat.nr.views <- acast(setnames(nr.views[Method=='true',descriptive.f(View),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
-nr.full.period <- acast(setnames(nr.views[,descriptive.f(View),by=Method],c('Method','Statistics','value')),Method~Statistics,value.var = 'value')
-
-#setkey(pt.rank.views,Stock,q.id,year)
-#setkey(nr.views,Stock,q.id,year)
-
-brok.full.stat.eps <- acast(setnames(na.omit(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)])[,descriptive.f(N),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
-eps.full.period <- setnames(setkey(complete.dt,Stock)[,.N,by=list(Stock,q.id,year)][,descriptive.f(N)],c('Statistics','value'))
-
-#join.dt <- na.omit(setkey(core.dt,q.id,Broker,Stock,Sector)[setkey(complete.dt,q.id,Broker,Stock,Sector)])
-
-load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
-#num.b <- apply(estimates[,working.s,working.b,2],c(1,3),function(i){length(i[!is.na(i)])})
-#num.s <- apply(estimates[,working.s,working.b,2],c(1,2),function(i){length(i[!is.na(i)])})
-#final.bl <- setkey(all.final.bl,Method)[methods]
-#methods <- as.character(unique(final.bl$Method)[c(1:7,11:13)])
-final.bl <- final.bl[,Method:=ifelse(Method=='true',strategies[1],ifelse(Method=='naive',strategies[2],strategies[3]))]
-
-final.bl$Method <- factor(final.bl$Method,levels=strategies)
-final.bl$Views <- factor(final.bl$Views,levels=c('CONS','TP','EPS','Market'))
-final.bl <- final.bl[,ann.ret:=ann.ret*100]
-bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Aggregation','Views'),measure.vars  = c('ann.ret','ann.sd','ann.sr','meanViews','Ave.TO')),by=c('Method','Aggregation','variable','Views')),Views~Method~Aggregation~variable,value.var = 'value')
-@
 
@@
 
-The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in TP dataset is \Sexpr{q.data[!is.na(trunk.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(trunk.view),.N,by=Stock][,.N]} S\&P500 stocks.
+The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in TP dataset is 351, covering 497 S\&P500 stocks.
 Given the fact that financial analyst mostly issue TP annually,\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have 12-month horizon \citep{glushkov2009}} we assume that an analyst keeps her TP forecast valid for one calendar year until it gets revised or expires after one year.
 
-Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
-This is done due to the extreme values cause by misalignment errors found on I/B/E/S data.\footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.} The final sample size of $TP/P-1$ observations is reduced from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
+Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and the 95\textsuperscript{th} percentile (values above 0.791).
+This is done due to the extreme values cause by misalignment errors found on I/B/E/S data.\footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.} The final sample size of $TP/P-1$ observations is reduced from 145 628 to 131 066.
 
-The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
+The initial file of quarterly EPS forecast consists of  571 brokers covering 3655 stocks.
 To implement the ranking, we require that a stock had at least three brokers per quarter that issue EPS forecasts.
@@
 Finally, we consider only S\&P500 stocks.
-All these requirements reduce our sample of EPS forecasts to \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of EPS-Stock-Broker observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+All these requirements reduce our sample of EPS forecasts to 172 brokers covering 449 stocks.
+The total number of EPS-Stock-Broker observation is 107 626.
 Panel A shows the composition of each category for rankings based on the accuracy in target prices.
-We observe that the distribution of the $top_{t}$ group is as follows: \Sexpr{round(cont.tab[[3]][1,1],3)*100}\%  of analysts stay at the same ranking category from the $top_{t-1}$; \Sexpr{round(cont.tab[[3]][2,1],3)*100}\% move from the $middle_{t-1}$; \Sexpr{round(cont.tab[[3]][3,1],3)*100}\% from the $bottom_{t-1}$; and \Sexpr{round(cont.tab[[3]][4,1],3)*100}\%  from the $noRank_{t-1}$.
+We observe that the distribution of the $top_{t}$ group is as follows: 14.5\%  of analysts stay at the same ranking category from the $top_{t-1}$; 53.6\% move from the $middle_{t-1}$; 13.1\% from the $bottom_{t-1}$; and 18.8\%  from the $noRank_{t-1}$.
 It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank.
-Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (\Sexpr{round(cont.tab[[3]][4,4],3)*100}\%).
+Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (78.4\%).
 This suggests that analysts are not frequent in issuing target price reports.
@@
 Panel A shows the number of target prices per stock per quarter.
-For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations with average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} target price reports per quarter per stock.
+For the sample period (1999-2009), we report 15 079 stock-quarter observations with average of 6.7 target price reports per quarter per stock.
 Panel B of the table presents the statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} forecast-quarter observations.
-The average number of forecasts per stock per quarter is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.
+In total, the EPS forecast sample has 14 354 forecast-quarter observations.
+The average number of forecasts per stock per quarter is 7.5.
 
@@
 Table (\ref{tab:rank-stat}) demonstrates the results.
-For this table, we split rankings into four categories: the analysts fall into \emph{top} category if they have ranks below or equal to \Sexpr{n},\footnote{The choice comes from the restriction of a stock having at least \Sexpr{n} brokers of coverage in a quarter.} the \emph{bottom} category includes analysts whose ranks fall into the last \Sexpr{n} ranks, the \emph{middle} category is for analysts who neither \emph{top} nor \emph{bottom}, and if analysts do not issue any report they fall into the \emph{noRank} category.
+For this table, we split rankings into four categories: the analysts fall into \emph{top} category if they have ranks below or equal to 3,\footnote{The choice comes from the restriction of a stock having at least 3 brokers of coverage in a quarter.} the \emph{bottom} category includes analysts whose ranks fall into the last 3 ranks, the \emph{middle} category is for analysts who neither \emph{top} nor \emph{bottom}, and if analysts do not issue any report they fall into the \emph{noRank} category.
 We, then, calculate a distribution of analysts for each of the category for the period $t$,i.e., for a given ranking group, we would like to know how it was composed.
@@
 For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$.
-However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes \Sexpr{round(eps.cont.tab[[3]][4,1],3)*100}\%, for the \emph{middle} --- \Sexpr{round(eps.cont.tab[[3]][4,2],3)*100}\%, and for the \emph{bottom} --- \Sexpr{round(eps.cont.tab[[3]][4,3],3)*100}\%.
+However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes 34.3\%, for the \emph{middle} --- 43.9\%, and for the \emph{bottom} --- 48.7\%.
 This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.
@@
 (\ref{consq}).
-The consensus among the analysts about stock expected return is \Sexpr{round(nr.views[,mean(View,na.rm=T),by=Method][Method=='true',V1],3)*100 }\%.
+The consensus among the analysts about stock expected return is 20.1\%.
 Panel B of the table shows the statistics for $rankQ$ obtained from the rankings based on the target price accuracy.
-We observe a reduction in average per stock expected return with the mean of \Sexpr{ round(rank.views.full.period['true','mean'],3)*100}\%.
-The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of \Sexpr{ round(pt.eps.rank.views.full.period['true','mean'],3)*100}\%.
+We observe a reduction in average per stock expected return with the mean of 15.4\%.
+The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of 11.2\%.
 Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.
@@
 Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,'ma',1],2)}\% and an annualized Sharpe ratio (SR) of \Sexpr{ round(bl.results['Market',1,'ma','ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'ma','meanViews'])} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'ma','Ave.TO'],3)}, which demonstrates the ins/outs of the S\&P 500 constituents list.
+The strategy resulted in an annualized cumulative return of 4.49\% and an annualized Sharpe ratio (SR) of 0.278.
+The average number of stocks used per quarter is 499 and the turnover ratio of strategy is 0.003, which demonstrates the ins/outs of the S\&P 500 constituents list.
 
@@
 Panel B presents the result for the case of \tr{} information availability set.
-The annualized cumulative returns for each of the active strategies (CONS,TP,and EPS) are: CONS =\Sexpr{round(bl.results['CONS',1,'ma',1],2)}\%, TP = \Sexpr{round(bl.results['TP',1,'ma',1],2)}\%, and EPS = \Sexpr{round(bl.results['EPS',1,'ma',1],2)}\%.
+The annualized cumulative returns for each of the active strategies (CONS,TP,and EPS) are: CONS =5.61\%, TP = 8.2\%, and EPS = 4.93\%.
 All the strategies outperform the benchmark.
@@
 Panels C and D of the table (\ref{tab:strategy}) show the trading results of the feasible information availability sets.
-In the case of the \naive{}, the strategy that outperforms all the others (including the \emph{Market}) is the TP strategy which yields an annualized cumulative return of \Sexpr{round(bl.results['TP',2,'ma',1],2)}\%.
-The other two strategies (CONS and EPS) resulted in below-the-market performance (annualized cumulative return of \Sexpr{round(bl.results['CONS',2,'ma',1],2)}\% and \Sexpr{round(bl.results['EPS',2,'ma',1],2)}\% respectively).
-The case of the \default{}, demonstrates the worse results as none of the active strategies is able to outperform the \emph{Market} (TP = \Sexpr{round(bl.results['TP',3,'ma',1],2)}\%, CONS = \Sexpr{round(bl.results['CONS',3,'ma',1],2)}\%, EPS = \Sexpr{round(bl.results['EPS',3,'ma',1],2)}\%)
+In the case of the \naive{}, the strategy that outperforms all the others (including the \emph{Market}) is the TP strategy which yields an annualized cumulative return of 5.46\%.
+The other two strategies (CONS and EPS) resulted in below-the-market performance (annualized cumulative return of 4.36\% and 2.04\% respectively).
+The case of the \default{}, demonstrates the worse results as none of the active strategies is able to outperform the \emph{Market} (TP = 4.08\%, CONS = 4.4\%, EPS = 2.32\%)
 
@@
    \multicolumn{6}{l}{\textbf{Panel A: TP}} \\
-<<desc-pt,echo=F,results='asis'>>=
+Years & Observ & Min& Mean & Median &Max& std.dev\\
+\midrule 
+ 1999 & 304 & 3.00 & 4.29 & 4.00 & 11.00 & 1.66 \\ 
+  2000 & 1 021 & 3.00 & 4.87 & 4.00 & 14.00 & 2.01 \\ 
+  2001 & 1 202 & 3.00 & 5.54 & 5.00 & 16.00 & 2.45 \\ 
+  2002 & 1 426 & 3.00 & 6.41 & 6.00 & 19.00 & 3.11 \\ 
+  2003 & 1 509 & 3.00 & 7.00 & 6.00 & 21.00 & 3.53 \\ 
+  2004 & 1 559 & 3.00 & 7.46 & 7.00 & 22.00 & 3.67 \\ 
+  2005 & 1 643 & 3.00 & 7.65 & 7.00 & 24.00 & 3.74 \\ 
+  2006 & 1 663 & 3.00 & 7.73 & 7.00 & 22.00 & 3.57 \\ 
+  2007 & 1 710 & 3.00 & 7.39 & 7.00 & 22.00 & 3.50 \\ 
+  2008 & 1 653 & 3.00 & 6.71 & 6.00 & 18.00 & 3.02 \\ 
+  2009 & 1 389 & 3.00 & 5.51 & 5.00 & 19.00 & 2.41 \\ 
+   \midrule 
+Total period & 15 079 & 3.00 & 6.70 & 6.00 & 24.00 & 3.34 \\
 
-data.to.display <- c('nbr.val','min','mean', 'median','max','std.dev')
-results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])
-
-options(xtable.comment = FALSE)
-cat("Years & Observ & Min& Mean & Median &Max& std.dev\\\\\n")
-cat('\\midrule \n')
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
-@
 \end{tabularx}
@@
    \multicolumn{6}{l}{\textbf{Panel B: EPS}} \\
-<<desc-eps,echo=F,results='asis'>>=
+ 1999 & 768 & 3.00 & 6.36 & 5.00 & 24.00 & 3.46 \\ 
+  2000 & 932 & 3.00 & 6.28 & 5.00 & 40.00 & 3.55 \\ 
+  2001 & 1 101 & 3.00 & 6.59 & 6.00 & 24.00 & 3.36 \\ 
+  2002 & 1 244 & 3.00 & 7.15 & 6.00 & 48.00 & 4.02 \\ 
+  2003 & 1 318 & 3.00 & 7.43 & 6.00 & 26.00 & 3.90 \\ 
+  2004 & 1 435 & 3.00 & 8.03 & 7.00 & 32.00 & 4.36 \\ 
+  2005 & 1 518 & 3.00 & 8.40 & 8.00 & 30.00 & 4.33 \\ 
+  2006 & 1 558 & 3.00 & 8.85 & 8.00 & 54.00 & 4.91 \\ 
+  2007 & 1 605 & 3.00 & 8.29 & 7.00 & 40.00 & 4.42 \\ 
+  2008 & 1 512 & 3.00 & 7.17 & 6.00 & 34.00 & 3.67 \\ 
+  2009 & 1 363 & 3.00 & 6.39 & 6.00 & 30.00 & 3.29 \\ 
+   \midrule 
+Total period & 14 354 & 3.00 & 7.50 & 6.00 & 54.00 & 4.12 \\
 
-results.final <- rbind(brok.full.stat.eps[,data.to.display],'Total period'=setkey(setnames(setkey(complete.dt[,.N,by=list(Stock,q.id,year)],year)[,descriptive.f(N)],c('Statistics','value')),Statistics)[data.to.display][,value])
-
-print(xtable(results.final,display=c('s','d','f','f','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
-@
 \bottomrule
@@
     \multicolumn{5}{l}{\textbf{Panel A: TP}} \\
-<<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list(Broker,TP=PT,'$\\mu(P)$'=round(meanQprice,3),'$\\mu(PMAFE)$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],display=c('s','d','f','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
+Broker & TP & $\mu(P)$ & $\mu(PMAFE)$ & rank \\ 
+  \midrule 
+LEGG & 58.50 & 71.09 & 0.05 &   1 \\ 
+  MONTSEC & 87.50 & 71.09 & 0.46 &   2 \\ 
+  KAUFBRO & 125.00 & 71.09 & 1.65 &   3 \\ 
+  DLJ & 140.00 & 71.09 & 1.97 &   4 \\ 
+   \midrule
+
 \end{tabularx}
@@
     \multicolumn{5}{l}{\textbf{Panel B: EPS}} \\
-<<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list(Broker,'$PRED$'=Est,'ACT'=act.eps,'$PMAFE$'=eps.pmafe,rank)][order(rank)],display=c('s','d','f','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
+Broker & $PRED$ & ACT & $PMAFE$ & rank \\ 
+  \midrule 
+PACCREST & -0.130 & -0.115 & 0.066 &    1 \\ 
+  BACHE & -0.135 & -0.115 & 0.088 &    2 \\ 
+  MONTSEC & -0.082 & -0.115 & 0.147 &    3 \\ 
+  HAMQUIST & -0.075 & -0.115 & 0.176 &    4 \\ 
+  BEAR & -0.073 & -0.115 & 0.184 &    5 \\ 
+  FBOSTON & -0.065 & -0.115 & 0.220 &    6 \\ 
+  RBRTSON & -0.011 & -0.115 & 0.459 &    7 \\
+
 \bottomrule
@@
 \end{table}
-
-<<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-require(gridExtra)
-example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
-ggplot(example.dt,aes(x=s.Date,y=PT,group=Broker,color=Broker,shape=Broker))+geom_line(size=1)+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Example of daily stock price (AMZN), compared to broker\'s TP (ranked by daily forecast error)')+scale_color_grey()+geom_line(aes(y=priceAdj),color='black')+theme(plot.title = element_text(colour = "Black"),legend.position='top')
-#grid.draw(grobTree(arrangeGrob(p,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
-@
 
@@
 \multicolumn{5}{l}{\textbf{Panel A: Target Price ranking}} \\
-<<desc-rank-pt,echo=F,results='asis'>>=
-tab.r <- round(rbind(cont.tab[[3]],Total=apply(cont.tab[[3]],2,sum)),3)*100
-rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
-colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=T,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
+ & $top_{t}$ & $middle_{t}$ & $bottom_{t}$ & $noRank_{t}$ \\ 
+ $top_{t-1}$ & 14.5 & 21.6 & 20.5 & 4.9 \\ 
+  $middle_{t-1}$ & 53.6 & 43.3 & 35.9 & 13.1 \\ 
+  $bottom_{t-1}$ & 13.1 & 8.8 & 12.6 & 3.5 \\ 
+  $noRank_{t-1}$ & 18.8 & 26.3 & 31.0 & 78.4 \\ 
+  Sum & 100.0 & 100.0 & 100.0 & 100.0 \\
 
-@
 \end{tabularx}
@@
    \multicolumn{5}{l}{\textbf{Panel B: EPS ranking}} \\
-<<desc-rank-eps,echo=F,results='asis'>>=
-tab.r <- round(rbind(eps.cont.tab[[3]],Total=apply(eps.cont.tab[[3]],2,sum)),3)*100
-rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
-colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-@
+ $top_{t-1}$ & 11.8 & 13.6 & 13.7 & 3.0 \\ 
+  $middle_{t-1}$ & 43.7 & 36.4 & 28.0 & 8.7 \\ 
+  $bottom_{t-1}$ & 10.1 & 6.1 & 9.6 & 2.5 \\ 
+  $noRank_{t-1}$ & 34.3 & 43.9 & 48.7 & 85.8 \\ 
+  Sum & 100.0 & 100.0 & 100.0 & 100.0 \\
+
 \bottomrule
@@
 %    \multicolumn{4}{l}{\textbf{Panel A: Consensus views}} \\
-<<desc-nr.views,echo=F,results='asis'>>=
-cat("Years & Observ & Mean & Median &std.dev\\\\\n")
-cat('\\midrule \n')
-data.to.display <- c('nbr.val','mean', 'median','std.dev')
-results.final <- rbind(stat.nr.views[,data.to.display],'Total period'=nr.full.period['true',data.to.display])
+Years & Observ & Mean & Median &std.dev\\
+\midrule 
+  \multicolumn{4}{l}{\textbf{Panel A: Consensus views}} \\1999 & 302 & 0.27 & 0.26 & 0.14 \\ 
+  2000 & 1 479 & 0.30 & 0.28 & 0.14 \\ 
+  2001 & 1 482 & 0.28 & 0.26 & 0.15 \\ 
+  2002 & 1 562 & 0.23 & 0.21 & 0.13 \\ 
+  2003 & 1 552 & 0.22 & 0.20 & 0.12 \\ 
+  2004 & 1 551 & 0.15 & 0.14 & 0.10 \\ 
+  2005 & 1 573 & 0.14 & 0.13 & 0.09 \\ 
+  2006 & 1 619 & 0.15 & 0.14 & 0.09 \\ 
+  2007 & 1 622 & 0.15 & 0.13 & 0.09 \\ 
+  2008 & 1 687 & 0.15 & 0.14 & 0.08 \\ 
+  2009 & 1 207 & 0.26 & 0.24 & 0.15 \\ 
+   \midrule 
+Total period & 15 636 & 0.20 & 0.17 & 0.13 \\
 
-print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1,0),command=c('\\midrule \n','\\multicolumn{4}{l}{\\textbf{Panel A: Consensus views}} \\\\')))
-@
   \end{tabularx}
@@
     \multicolumn{4}{l}{\textbf{Panel B: TP Ranking views}} \\
-<<desc-r.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
+ 1999 & 461 & 0.23 & 0.24 & 0.11 \\ 
+  2000 & 1 076 & 0.23 & 0.23 & 0.11 \\ 
+  2001 & 1 255 & 0.20 & 0.19 & 0.11 \\ 
+  2002 & 1 463 & 0.17 & 0.17 & 0.10 \\ 
+  2003 & 1 521 & 0.15 & 0.14 & 0.10 \\ 
+  2004 & 1 580 & 0.12 & 0.11 & 0.08 \\ 
+  2005 & 1 652 & 0.12 & 0.11 & 0.08 \\ 
+  2006 & 1 675 & 0.12 & 0.11 & 0.08 \\ 
+  2007 & 1 705 & 0.12 & 0.11 & 0.08 \\ 
+  2008 & 1 576 & 0.15 & 0.13 & 0.10 \\ 
+  2009 & 683 & 0.20 & 0.20 & 0.11 \\ 
+   \midrule 
+Total period & 14 647 & 0.15 & 0.14 & 0.10 \\
 
-results.final <- rbind(stat.rank.views[,'true',data.to.display],'Total period'=rank.views.full.period['true',data.to.display])
-
-options(xtable.comment = FALSE)
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
-@
   \end{tabularx}
@@
     \multicolumn{4}{l}{\textbf{Panel C: EPS Ranking views}} \\
-<<desc-eps.views,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
+ 1999 & 443 & 0.12 & 0.11 & 0.10 \\ 
+  2000 & 951 & 0.14 & 0.12 & 0.11 \\ 
+  2001 & 1 151 & 0.14 & 0.12 & 0.10 \\ 
+  2002 & 1 244 & 0.14 & 0.13 & 0.09 \\ 
+  2003 & 1 336 & 0.11 & 0.10 & 0.09 \\ 
+  2004 & 1 433 & 0.09 & 0.08 & 0.07 \\ 
+  2005 & 1 515 & 0.09 & 0.08 & 0.07 \\ 
+  2006 & 1 557 & 0.09 & 0.08 & 0.07 \\ 
+  2007 & 1 569 & 0.09 & 0.09 & 0.07 \\ 
+  2008 & 1 483 & 0.12 & 0.10 & 0.09 \\ 
+  2009 & 715 & 0.14 & 0.13 & 0.10 \\ 
+   \midrule 
+Total period & 13 397 & 0.11 & 0.10 & 0.09 \\
 
-results.final <- rbind(pt.eps.stat.rank.views[,'true',data.to.display],'Total period'=pt.eps.rank.views.full.period['true',data.to.display])
-print(xtable(results.final,display=c('s','d','f','f','f'),align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)-1),command=c('\\midrule \n')))
-
-@
 \bottomrule
@@
 \end{table}
-
-<<bl-results-fig,echo=FALSE, include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-library(scales)
-#final.bl$Method <- factor(final.bl$Method,levels=sort(unique(final.bl$Method)))
-
-colourCount = length(unique(final.bl$Views))
-getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-
-#p.cum.ret <-
-ggplot(final.bl[Aggregation=='ma'],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+geom_hline(yintercept=100)+facet_grid(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top')+scale_color_grey()+geom_point()
-
-#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
-
-#+scale_color_manual(values=getPalette(colourCount))+
-
-#+scale_x_date(breaks='year',labels=date_format('%Y'))
-
-#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
-
-#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))
-
-require(gridExtra)
-#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
-#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
-@
 
@@
   %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-<<bl-market,echo=F,results='asis'>>=
-
-results.final <- bl.results['Market',1,'ma',]
-cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized std. dev','Annualized Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
-#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table(Market=results.final)),display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\')))
-cat('\\midrule \n')
-@
+Strategy&Annualized cum.
+return (in \%)&Annualized std.
+dev&Annualized Sharpe ratio&Average num.
+stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\Market & 4.49 & 0.16 & 0.28 & 499 & 0.00 \\
+  \midrule
 
@@
   \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
-<<bl-nr,echo=F,results='asis'>>=
-results.final <- bl.results[1:3,1,'ma',]
-print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(results.final)),command=c('\\midrule \n')))
-@
+ CONS & 5.61 & 0.18 & 0.31 & 278 & 0.01 \\ 
+  TP & 8.20 & 0.18 & 0.46 & 264 & 0.02 \\ 
+  EPS & 4.93 & 0.18 & 0.27 & 237 & 0.03 \\ 
+   \midrule
+
 \end{tabularx}
@@
   \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
-<<bl-pt,echo=F,results='asis'>>=
-results.final <- bl.results[1:3,2,'ma',]
-print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(results.final)),command=c('\\midrule \n')))
-@
+ CONS & 4.36 & 0.18 & 0.24 & 278 & 0.01 \\ 
+  TP & 5.46 & 0.18 & 0.31 & 265 & 0.01 \\ 
+  EPS & 2.04 & 0.17 & 0.12 & 237 & 0.02 \\ 
+   \midrule
+
 \end{tabularx}
@@
   \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
-<<bl-eps,echo=F,results='asis'>>=
-results.final <- bl.results[1:3,3,'ma',]
-print(xtable(results.final,display=c('s','f','f','f','d','f'),digits=2,align=c('r',rep('c',ncol(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
+ CONS & 4.40 & 0.18 & 0.24 & 294 & 0.01 \\ 
+  TP & 4.08 & 0.18 & 0.23 & 283 & 0.01 \\ 
+  EPS & 2.32 & 0.18 & 0.13 & 274 & 0.02 \\
+
 \bottomrule

### 2015-02-14 doc/paper/paper-test.Rmd
Initial commit

---
title: "Paper outline"
output:
  pdf_document: default
  word_document: default
---
## Possible title
"Are rankings of financial analysts useful for investors?"

### 1. Introduction:
  + Rankings are important;
  + Who also ranks analysts;
  + Paper objectives:
    + operationalize BL;
    + ranking based strategy outperforms baselines;
  + Paper structure;

### 2. Rankings of FA:
  + Efficient Market Hypothesis and advice of FA;
  + Can we make money if EMH holds?
  + FA do have skills;
  + Rankings of FA by StarMine:
    + based on recommendations (target prices);
    + based on EPS forecast accuracy (SES metrics);
  + FA rankings signal who to follow;
  + Our FA rankings methods:
    + naive;
    + default;
    + non ranking benchmark;

### 3. Trading strategy:
  + Why BL and not CAMP?;
  + BL notations;
  + BL strategy outline;
  + Defining expected returns:
    + rank-based;
    + non-rank based (mean);
  + Defining the confidence (coefficient of variation);

### 4. Data and experiment setup:
  + Data description (sources, total observations);
  + TPER is truncated;
  + Descriptive stats of filtered data;
  + How we rank analysts?
  + How we create:
    + naive ranking;
    + default ranking;

### 5. Results
  + BL strategies outperform market;
  + _true_ of rank based outperforms non-rank;
  + Foreknowledge of rankings leads to highest cumulative return;
  + FA Rankings are important, goal is to forecast them correctly;

### 6. Conclusion
  + Ranking of FA are important and produce the highest possible cumulative return;
  + BL strategy takes rankings as inputs to build views;
  + Future research: predict rankings of FA;

### References

### Tables and Plots

### 2015-02-14 doc/paper/paper.Rnw
Initial commit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt} 
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt} 
\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}

%\onehalfspacing
\doublespace
%\usepackage{natbib}
\usepackage[natbibapa]{apacite}

\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\tr}{\textit{true}}
\newcommand{\naive}{\textit{naive}}
\newcommand{\default}{\textit{default}}
\newcommand{\market}{\textit{market}}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
%\newcommand{\raw}{\textit{raw}}
%\newcommand{\diff}{\textit{diff}}
%\newcommand{\random}{\textit{random}}
%\newcommand{\rollsd}{\textit{roll.sd}}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\begin{document}
\SweaveOpts{concordance=TRUE}
<<load.data,echo=F>>=
source('/Users/aiguzhinov/Documents/Dropbox/workspace/MetaRanks/my.paths.R')
source(analysts.dir('Functions/main.functions.R'))
source(analysts.dir('updated.functions.R'))
#lapply(list('Hmisc','pastecs','abind','xts','xtable','parallel','PerformanceAnalytics','MASS'), function(X) {do.call("require", list(X)) })
library('pastecs')
library('abind')
library('xts')
library('xtable')
library('PerformanceAnalytics')
#library('texreg')

#load(file=project.dir('/RankPriceTarget/pt.eps.accuracy.short.RData'))
load(project.dir('/RankPriceTarget/working.brok.s.upd.RData' ))
#load(project.dir('Predict Analysts/eps.info.array.RData'))
load(project.dir('EPS/brokers.estimates.number.RData'))
load(project.dir('EPS/brokers.estimates.RData'))
load(project.dir('Price Targets/ext.exp.ret.RData'))
old.tp.info <- extendent.exp.ret
total.obs <- length(old.tp.info[!is.na(old.tp.info)])
range.old <- range((old.tp.info[!is.infinite(old.tp.info)]),na.rm=T)
years<-seq(1989,2009,1)
methods<-c('raw','1diff','random','roll.sd')
#methods <- methods[1]
baselines<-c('true','naive','default',methods)

###Desriptive stat of EPS data
#descr.stat.eps <- annual.desc.stat(estimates[,working.s,working.b,3],seq(40,84,4))
descr.stat.eps <- annual.desc.stat(estimates.num[,working.s,working.b],seq(40,84,4))
#total.stat.eps <- stat.desc(estimates[,working.s,working.b,3][!is.infinite(estimates[,working.s,working.b,3])])

total.stat.eps <- stat.desc(estimates.num[,working.s,working.b][!is.infinite(estimates.num[,working.s,working.b])])

#num.b <- apply(estimates[,working.s,working.b,2],c(1,3),function(i){length(i[!is.na(i)])})
#num.s <- apply(estimates[,working.s,working.b,2],c(1,2),function(i){length(i[!is.na(i)])})

eps.brok.stat <- broker.stats.f(estimates.num[,working.s,working.b])

#plot.perform(eps.brok.stat[c(1,2),],name.y='Mean',name.x='quarters',name.plot='Average stat',x.labels=1:84,legnd.size=0.4,'topleft','b')

q.num.b <- eps.brok.stat[1,]
q.num.s <- eps.brok.stat[2,]
eps.num.s.per.b <- eps.brok.stat[6,]
# eps.b <- apply(apply(estimates.num[,working.s,working.b],c(1,3),function(i){length(show.no.na(i))}),1,function(j){length(j[j!=0])})
# 
# eps.a <- apply(apply(estimates.num[,working.s,working.b],c(1,2),function(i){length(show.no.na(i))}),1,function(j){length(j[j!=0])})

#num.f.b <- apply(estimates[,,,3],c(1,3),function(i){sum(i[!is.na(i)])})
#num.f.s <- apply(estimates[,,,3],c(1,2),function(i){sum(i[!is.na(i)])})

#q.num.f.b <- apply(num.f.b,1,function(i){sum(i[i!=0],na.rm=T)})
#q.num.f.s <- apply(num.f.s,1,function(i){sum(i[i!=0],na.rm=T)})

#descr.eps <- rbind(descr.stat.eps[,2:15],total.stat.eps)
#rownames(descr.eps) <- c(years[11:21],'Total periods')
#lat.tab<- xtable(descr.eps[,c(1,8,9,10,11,13)],digits=3,align=rep('c',7),caption='Descriptive statistics of EPS dataset')
#digits(lat.tab)[c(2)] <- 0
#print(lat.tab,caption.placement='top',sanitize.text.function = function(x){x})

####Descr stat of TP/P-1
#descr.stat.pt <- annual.desc.stat(extendent.exp.ret[,working.b,working.s],seq(40,84,4))

#total.sp.summary.12m <- stat.desc(extendent.exp.ret[,working.b,working.s][!is.infinite(extendent.exp.ret[,working.b,working.s])])

percentile <- c(0.01,0.99)

descr.stat.pt <- annual.desc.stat.tunk(extendent.exp.ret[,working.b,working.s],seq(40,84,4),percentile)
data <- extendent.exp.ret[,working.b,working.s]
trunk.tp<- quantile(data[!is.infinite(data)],percentile,na.rm=T)
data[data<trunk.tp[[1]]] <- NA
data[data>trunk.tp[[2]]] <- NA
trunk.data <- data
total.sp.summary.12m <- stat.desc(trunk.data[!is.infinite(trunk.data)])
rm(data)

q.pt.per.b <- apply(apply(trunk.data,c(1,2),function(i){length(show.no.na(i))}),1,function(j){mean(j[j!=0])})

q.pt.per.s <- apply(apply(trunk.data,c(1,3),function(i){length(show.no.na(i))}),1,function(j){mean(j[j!=0])})

b <- apply(apply(trunk.data,c(1,2),function(i){length(show.no.na(i))}),1,function(j){length(j[j!=0])})

a <- apply(apply(trunk.data,c(1,3),function(i){length(show.no.na(i))}),1,function(j){length(j[j!=0])})

pt.num.s.per.b <- a/b

#descr.pt <- rbind(descr.stat.pt[,2:15],total.sp.summary.12m)
#rownames(descr.pt) <- c(years[11:21],'Total periods')
#lat.tab<- xtable(descr.pt[,c(1,8,9,10,11,13)],digits=3,align=rep('c',7),caption='Descriptive statistics of TP dataset')
#digits(lat.tab)[c(2)] <- 0
#print(lat.tab,caption.placement='top',sanitize.text.function = function(x){x})

source(project.dir('Black-Litterman/BL-functions.R'))

load(file=project.dir('/Black-Litterman/market.inputs.upd.RData'))
load(file=analysts.dir('Sectors/All Sectors/xts.sp.q.ret.RData'))
load(file=analysts.dir('/Sectors/Market/market.weights.upd.RData'))

sel.period <- 6:44
full.period<-index(sel.period)
pre.crisis<-seq(1,(length(full.period)-4),1)
post.crisis<-full.period[(length(full.period)-3):(length(full.period))]
periods <- list('full.period','pre.crisis','post.crisis')

#load(project.dir('/Black-Litterman/pt-trunk.RData'))
load(project.dir('Black-Litterman/Weights/pt-ma.work.sam.RData'))
results.pt<- abind(lapply(periods,function(p){final.results.f(p,baselines[1:3],weights,market.inputs[sel.period],mw[sel.period],xts.sp.q.ret[sel.period])}),along=3,new.names=list(NULL,NULL,periods))
sel.data.pt <- xts.ret.full.full.period

#load(project.dir('/Black-Litterman/eps-working-s-trunk-slide.RData'))
load(project.dir('/Black-Litterman/Weights/eps-ma.work.sam.RData'))
results.eps<- abind(lapply(periods,function(p){final.results.f(p,baselines[1:3],weights,market.inputs[sel.period],mw[sel.period],xts.sp.q.ret[sel.period])}),along=3,new.names=list(NULL,NULL,periods))

#dimnames(xts.ret.full.full.period)[[2]][1:3] <- c("$\\tr{}$","$\\naive{}$","$\\default{}$")
sel.data.eps <- xts.ret.full.full.period

results <- abind(results.eps[1:3,,1],results.pt[1:3,,1],along=3)
dimnames(results)[[2]] <- c("Annualized cum. return","Annualized std. dev.","Annualized Sharpe ratio", "Average num. stock","Average turnover rate")

load(file=project.dir('/RankPriceTarget/pmafe.RData'))
mean.pmafe <- apply(pmafe,c(1,2,4),mean,na.rm=T)
d.pmafe.eps <- annual.desc.stat(t(mean.pmafe[,,'eps']) ,seq(0,40,4))
d.pmafe.pt <- annual.desc.stat(t(mean.pmafe[,,'pt']) ,seq(0,40,4))
total.pmafe.eps <- stat.desc(mean.pmafe[,,'eps'][!is.infinite(mean.pmafe[,,'eps'])])
total.pmafe.pt <- stat.desc(mean.pmafe[,,'pt'][!is.infinite(mean.pmafe[,,'pt'])])
load(file=project.dir('/RankPriceTarget/rel.rank.RData'))
mean.rel.rank <- apply(rel.rank,c(1,2,4),mean,na.rm=T)

eps.pmafe <- apply(mean.pmafe[,,'eps'],1,mean,na.rm=T)
pt.pmafe <- apply(mean.pmafe[,,'pt'],1,mean,na.rm=T)

#eps.pmafe[is.na(eps.pmafe)] <- 0
#pt.pmafe[is.na(pt.pmafe)] <- 0
#model.pmafe <- lm(eps.pmafe ~ pt.pmafe)
#cancor(mean.pmafe[,,'eps'],mean.pmafe[,,'pt'])$cor
#cor(eps.pmafe,pt.pmafe)
@

\title{Are rankings of financial analysts useful for investors?}
 \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
 \author[1,3]{ Ana Paula Serra (\href{mailto:aserra@pbs.up.pt}{aserra@pbs.up.pt})}
 \author[2,4]{Carlos Soares (\href{mailto:csoares@feup.up.pt}{csoares@feup.up.pt})}

\affil[1]{FEP \& CEF.UP, University of Porto}
\affil[2]{INESC TEC}
\affil[4]{FEUP, University of Porto}
\affil[3]{CEF.UP \& Porto Business School, University of Porto}

%We address the following question: does an investment strategy that follows the advice of the top analysts in a period produce superior returns?

\maketitle
\begin{abstract}
Some institutions issue rankings of the financial analysts. Given that these rankings are \textit{ex-post}, it is arguable if they are useful for investors. In this paper we show that relative performance by a set of financial analysts seem to be valuable. Namely, we show that simple methods of building the expected rankings of financial analysts based on the  accuracy of both EPS forecasts and price targets generate a significant gain over the passive strategy -- ``buy and hold'' a general index. In addition, we report that analysts issuing the accurate price targets are more favorable for the investors  to follow rather than analysts issuing the accurate EPS forecasts. We operationalize the Black-Litterman model to be able to use rankings as the inputs for the model and facilitate the trading experiment.
\end{abstract}

\section{Introduction}
\label{sec:intro}
%Artur,
%
%The idea is that if we are able to forecast rankings well (as god), this is important for an investment strategy based on rankings of TP and not EPS accuracy. Thus, you should mention both. Let's say Thomson Reuters sells (good) forecasts of the TP an EPS accuracy rankings. For the horizon we analyzed an investor should only buy the TP ranking.
%

%and if they do, which advice of the analysts either on EPS or on price target bring more value.

Financial analysts play an important role, as they are the experts in interpreting the financial information. In the literature, there is still conflicting debate if following the  advice of analysts brings value to investors after transaction costs \citep{womack1996,mikhail2004sae,li2005persistence}. The essence of this debate lies in the problem of identifying the analysts with good stock picking skills. Evidence shows that market response to analysts' recommendations is stronger when analysts issue them with good forecasting tracking record \citep{park2000analyst,loh2006aef}. Thus, it seems to be the case that only a subset of analysts influences the stock prices and, as such, only that subset of analysts deserves to be followed \citep{loh2011}.

In recent years, some institutions were very active in publishing and  selling the rankings of financial analysts based on their relative performance. Some of them are based on the privately held surveys of the buy-side analysts (e.g., the Institutional Investor's rankings of the All-America Research Teams\footnote{\url{http://www.institutionalinvestor.com/Research/4560/First-Team.html}} and Bloomberg's America's Best Stock Analysts\footnote{\url{http://www.bloomberg.com/news/2013-08-14/jpmorgan-top-stock-picker-with-equities-out-of-lockstep.html}}); others are based on the performance of the sell-side analysts (ThomsonReuters' the top StarMine analysts\footnote{\url{http://excellence.thomsonreuters.com/award/starmine}}). In any of the cases, these rankings serve as one way to identify the best analysts. However, aside from personal acknowledgment among the peers, it is still arguable whether these rankings truly identify the best specialists \citep{desai2000ass} or they are just  ``popularity contests" \citep{emery2009}. In this paper, we show that top-ranked analysts are the ones who do have stock picking skills and a trading strategy  based on these rankings outperforms the market. %We support the argument of \cite{desai2000ass} in that recommendations issued by the top ranked analysts have been reported to outperform the others implying that top analysts do have stock picking skills \citep{desai2000ass}.

%Hence, following the recommendations of the top analysts should result in yielding abnormal returns.

%Moreover, changes in recommendation of these analysts have a greater impact on market  \citep{stickel1995}  and  these changes are profitable for the investors \citep{fang2008aso}.

As part of their job, financial analysts produce EPS forecasts, price targets, and recommendations. The literature has been mixed in whether accuracy in EPS forecasts \citep{brown2001,hall2010} and in price targets \citep{da2011,bradshaw2012,zhou2013} correlates with the ability of the analysts to identify the mispriced stocks. In this study we empirically show that accuracy in price targets has greater underlying potential to the investors as opposed to the accuracy in EPS forecasts. We show that a trading strategy based on rankings with the accuracy in price targets is more profitable compared to a strategy based on the accuracy in EPS forecasts.

%Applying the Black-Litterman model \citep{black1992}, we develop a trading strategy based on the rankings of financial analysts. We base these rankings on forecast accuracy of both:  EPS forecasts and target prices (TP). The choice of TP has to do with the fact that EPS forecasts do not subsume the value of a company and its growth prospects (and risks) in the long run.

%For  market participants, rankings could be useful because they signal the top analysts. et, the value of these rankings for investors is arguable as they are ex-post and a good analyst in one year does not necessarily make equally good recommendations in the following year \citep{emery2009}. However, if we know the ranking of analysts ahead of time  then it would be possible to create a successful trading strategy based upon that information.

%That is, analysts who provide information about future of a stock has more value to the investor than information about the past (EPS-based rankings). This conclusion is important both for market participants to buy rankings of the analyst based on the price target information and for the researches to better analyze the effects of the price target and EPS forecasts on the market.

% Building the rankings based on the analyst' past performance outperforms the market in terms of CAR, and finally, the historical average rankings of the analysts show insignificant statistical CAR.

The contributions of our research are the following. First, we develop a trading strategy that transforms rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}. %Second, we find an empirical evidence that most errors in rankings were done at the bottom ranks; hence, we confirm that there is a  consistency at the top analysts \citep{bonini2010,hilary2013}. 
Second, we show that by implementing simple methods to construct expected rankings of financial analysts, we achieve annualized cumulative returns that outperform the passive strategy: buy-and-hold the general index. Third, we show that an active investment strategy that weights more heavily the stocks that are recommended by financial analysts with more accurate price targets yield the maximum potential cumulative annualized return. %In other words, strategies that follow the rankings with base of TP are more  profitable compared to the ones with base of EPS forecasts.

%Ranking the analyst and use this rankings as one of the inputs to the BL model shows in backtesting that we can achieve a significant cumulative returns had we known the true rankings in advance. Despite this hypothetical scenario, using the past period rankings still shows the considerable market outperformance in terms of cumulative returns.

The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines the trading strategy; section \ref{sec:rankings} summarizes the methodology of building the rankings and provides the database description used in the paper; section \ref{sec:results} analyzes the results; and section \ref{sec:conclusion} concludes.

\section{Rankings of Financial  Analysts}
\label{sec:ranking}

In the finance literature there has been a long debate on whether financial analysts produce valuable  advice. Some argue that following the advice of financial analysts,  translated as recommendations of buying, holding, or selling a particular stock, does not yield  abnormal returns, i.e.,  returns that are above the required return to compensate for risk \citep{fama1970ecm}. The Efficient Market Hypothesis (EMH) states that financial markets are efficient and any past information  regarding a stock would  be reflected in its current price; hence, it would be  impossible to generate abnormal returns based upon publicly available information.

%In general, the EMH holds and studies show that markets  are efficient \citep{fama1991ecm}. 
Yet there are information-gathering costs and the information is not immediately reflected on prices  \citep{grossman1980iie}. As such, prices might not  reflect all the available information because if this were the case, those who spent resources to collect and analyze   information would not receive a compensation for it.

%The possibility of obtaining   abnormal returns is an incentive to  numerous different trading strategies of portfolio management \footnote{e.g. \url{www.asiapacfinance.com/trading-strategies}} such as mean-reversion \citep{li2012} or trend-following trading strategy \citep{szakmary2010}.

Many trading strategies try to forecast the price movements relying on the historical prices or estimate the intrinsic value of a company. Obviously, this type of research is associated with significant amount of up-front costs to acquire databases, software, etc. On the other hand, financial analysts have these tools and skills to identify stocks worth to be invested. Thus, for an investor, it is cheaper to follow the recommendations of financial analysts rather than perform a self-based market analysis.

Assuming that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}, it is possible to rank the analysts based on their forecasting accuracy (EPS forecasts) or predictive power of future returns (price targets). In fact, Thomson Reuters' StarMine ranking does exactly this: it ranks analysts based on the earnings forecasts.
%The StarMine ranking methodology is based on the analysts performance. This performance is measured by comparing the non-leveraged portfolio for each analysts based on his/her recommendations. The portfolio is constructed as follows. For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark \footnote{Comparable index}. ``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark. ``Holds'' invest one unit in the benchmark (i.e., for an excess return of zero). Sell are the reverse. StarMine re-balances its calculations at the end of each month to adjust for when an analyst changes his or her mind (by adding, dropping or altering a rating) or when a stock enters or exits an industry grouping. 
For that, they developed a proprietary metric called a Single-stock Estimating Score (SES). It measures ``... [a] relative accuracy; that is, analysts are compared against their peers. An analyst's SES can range from 0 to 100, with 50 representing the average analyst. To get a score higher than 50, an analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates"\footnote{\url{http://excellence.thomsonreuters.com/award/starmine?award=Analyst+Awards&award_group=Overall+Analyst+Awards}}. %StarMine attributes the Excellence Award to the best analysts at an annual ceremony with broad media coverage.

Rankings of financial analysts play an important role in the industry. The benefits of top-ranked analysts are more engraved in the areas of analysts' personal reputation, their prestige among fellow peers, and their compensation at the employed brokerage house. However, top-ranked financial analysts also affect the market participants: the market  reacts more to the recommendations issued by the top-ranked analysts than to the ones who ranked lower \citep{emery2009}.

%In this study, we propose to measure the value of rankings of financial analysts. 
%The value of rankings such as StarMine for investors is arguable given that these are \textit{ex-post} and a good analyst on one year does not necessarily make equally good recommendations in the following year.

%The value of rankings such as StarMine Ratings for investors is arguable given that these are \textit{ex-post} and a good analyst on one year does not necessarily make equally good recommendations in the following year. However, if one could predict the ranking of analysts ahead of time (even if with some estimation error) then it would be possible to create a successful trading strategy. For this reason, we create our method of rankings of the analysts based on the \textit{ex-ante} price target information. %Recent research suggests that analysts' price target forecasts do affect the opinion of the market participants \citep{bradshaw2012}.\cite{brown2003} show that foreknowledge of analyst forecast accuracy is indeed valuable.
Our goal of this study is to evaluate if rankings add value to the investors. For this purpose, we investigate the problem with two ranking  methods that are used to calculate the necessary inputs for the trading strategy. The first is the \naive{} rankings and they are based on the last known analysts' actual rankings. The second method is taken from the Machine Learning literature \citep{aiguzhinov2010} and it is so-called the \default{} ranking. It is the average rank of an analyst since the beginning of the sample period and it encompasses the average analyst's relative performance. We formalize these methods in the appropriate section of the paper.
%These rankings are what StarMine actually sells: the \textit{ex-post} rankings of the analysts. 
%The question of whether the analysts' recommendations bring value to investors has been around since the mid-90s.  It is acknowledged that there is a positive benefit for investors from following the recommendations \cite{womack1996}. Assuming that these recommendations, on average, do bring value to the investors, it is possible to create rankings of the best analysts based on their performance. In fact, StarMine does exactly this: rankings of the analysts for the given fiscal year and publishes it worldwide. The rankings from StarMine serve mostly to the benefits of the analysts in the areas of personal reputation, prestige, and compensation.

%We propose to utilize the rankings of financial analyst as the tool for the trading strategy. The idea is to follow the best analysts and rely on their advanced knowledge. In fact, recent studies show that only a small group of analysts have an impact  on the market 
%For the investors these ranks cannot bring any value since the ranks are ex-post. Knowing the rankings of financial analysts ahead of time (with some estimation error) will be beneficial to the investors as it would be possible to create a trading strategy that combines the predicted rankings of financial analysts with financial investment models for active portfolio management.

%For  market participants, rankings could be useful because they signal the top analysts. Evidence shows that market response to analysts' recommendations is stronger when they are  issued by  analysts with good forecasting tracking record \citep{park2000analyst}. Yet, the value of these rankings for investors is arguable as they are ex-post and a good analyst in one year does not necessarily make equally good recommendations in the following year \citep{emery2009}. However, if we know the ranking of analysts ahead of time  then it would be possible to create a successful trading strategy based upon that information. If we can, with reasonable accuracy, predict the rankings  we can follow the recommendations of the analysts that are expected to be at the top and, in presence of contradictory recommendations, take the rank of the corresponding analysts into account. 
%The next step is to automate trading based on both the rankings and recommendations. However, this raises a challenge as there are none such methods.
%Existing label ranking algorithms cannot be directly applied to the problem of predicting the rankings of the analyst. Some adaptation is required in order to capture the timing of the rankings. We select to apply this adaption on naive Bayes label ranking algorithm.  The Bayesian statistics takes a great step in the financial literature; moreover, the Black-Litterman model is based on the Bayes theorem. For these reason, we choose the NBLR algorithm. 
%Addressing this problem requires developing methods for:
%\begin{enumerate}
%\item predicting the rankings;
%\item translating the rankings into a trading strategy.
%\end{enumerate}
%In the following we address these problems. In addition, since we already have a basic label ranking algorithm, we should address the timing in the rankings. We adapt the existing algorithm for this issue.

%This paper only introduces methodologies of how to predict the rankings of the financial analysts. The implementation of the predicted resutls into a trading strategy is out of scope of this paper.

\section{Trading Strategy}
\label{sec:trading}
The Black-Litterman (BL) model is a tool for the active portfolio management. The model incorporates views in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting.
%way that a portfolio of these stocks would have a minimum risk of losing money while maximizing the total portfolio return.   a procedure to mix personal views of analysts with market equilibrium expected returns. It is common in the financial literature to use  S\&P500 as the market. %The starting , the market equilibrium returns  of the model are calculated from 
%the historical returns of these 500 stocks. 
Compared to CAPM model, where expected return is a function of systematic risk, expected market risk premium, and the risk-free assets, in the BL model investors have views regarding individual stocks. As such, the model blends the subjective views of an investor about future performance of a stock and the market implicit returns.

%investors' views are expressed for the objective market variables such as expected market return, variances/co-variances, and the risk-free assets, the BL model allows an investor to use her own expectations for a individual stocks. In general, the model blends a subjective view of an investor about the future performance of a stock with the market implicit returns.

%According to modern portfolio theory, it is assumed that market, as a whole, is an optimal portfolio and is distributed among all investors; thus, investors require to have an interest on their holdings that must be above the interest on the risk-free asset \citep{sharpe1974}. It these implicit excess returns over the risk-free rate that model mixes with the individual views on a stock return and  outputs an updated optimal market portfolio.

Hence, it is important to have the views that the BL model transforms into a portfolio, which should outperform the general market. It is a challenging problem, as it requires a deep knowledge and skills to screen and monitor stocks in the market and find the ones that are mispriced. The financial analysts can do this job but the question is who are the best analysts? Is it those who issue more accurate EPS forecasts or those who make more accurate price targets (TP)? Instead of going for a trial-and-error approach, we rank the analysts based on their relative performance in forecasting the EPS and the price targets. We, then, transform the rankings into the views and feed them along with other inputs into the BL model.

%approach, where it is assumed that there exist equilibrium returns that clear the market. Thus,  in case of no views, the BL portfolio is the market portfolio with the market capitalization of the assets. Assuming that market is an optimal portfolio, The starting point to obtain the implicit returns is market capitalization of S\&P500 stocks which is assumed to be the optimal portfolio. Given this assumption, through reverse optimization, one  obtains implicit expected stock returns \citep{sharpe1974}.

%Figure (\ref{fig:bl}) depicts the schematics of the trading strategy. At the end of quarter $q-1$, we gather all available infromation for the BL model. At the beginning of $q$, we apply the BL model and obtain the optimal weights to form a BL-optimal portfolio. At the end of $q$ we evaluate the BL-portfolio with the market.

%There are two sources of inputs: 1) the investor's  view on a stock's return; and 2) the equilibrium implicit returns obtained from the market.

The literature on the BL model has established notations for the model. The views formalized as: $Q$ - the expected returns for stock $s$; $\Omega$ - the confidence of $Q$. The expected return $Q$  is the weighted average of the individual analysts' expected returns based on their 12-month TP \citep{da2011}. Confidence $\Omega$ for stock $s$ is based on the confidence of the accuracy of expected ranking.

Operationally, the trading strategy applies as follows (fig. \ref{fig:bl}):
\begin{enumerate}
\item For each stock $s$, at the beginning of quarter $q$, we select the expected the rankings for the end of the quarter $q$;
\item Based on these  expected rankings and analysts' TP,  we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
\item Using market information available at the last day of quarter $q-1$, we obtain the market inputs: vector of implicit returns, variance/co-variance matrix);
\item Apply BL model to get  optimized portfolio weights and buy/sell stocks accordingly;
%\item We buy and sell stocks accordingly; % using last day quarter $t-1$ stock prices;
%\item  At the end of the quarter $t$, check value of the portfolio;
%\item The return of your strategy portfolio return. % $r_{p,t}=v_t/v_{t-1}-1$
%\item Predict rankings based on updated market/stock/sector/broker information for the quarter $t+1$
%\begin{itemize}
%\item Check value of the portfolio position based on the current stock prices;
%\item Or we can forget the beginning of quarter $t$ portfolio and calculate the new portfolio with new set of weights and end-quarter prices;
%\end{itemize} 
\end{enumerate}

%To measure the  performance of our portfolio, we compare it to  the baseline which is the market portfolio (S\&P500). We compare the relative performance of our portfolio using the Sharpe ratio.
%\begin{equation}
%SR=\frac{r_p-r_f}{\sigma_p}
%\end{equation}
%where $r_p$ is the  portfolio quarterly  return and $r_f$ is the risk-free rate for the same; $\sigma_p$ is the standard deviation of the portfolio returns. \footnote{The Sharpe ratio measures the excess return per unit of risk \citep{sharpe1966}. This ratio shows how much the excess return over a risk-free asset an investor gets for holding a risky asset. Given that investors are risk-averse, they require a premium for holding risky assets.}

%This is based on the assumption that every investor holds a portion of the stocks in the market with implicit return.
%
%The model is based on the Bayes theorem that states posterior probability of the event A  given B is the function of prior probability of A and conditional probability of B given A. 
%\begin{equation}
%P(A|B)=\frac{P(A) \times P(B|A)}{P(B)}
%\end{equation}
%
%In this framework, the prior probability of A is the market equilibrium returns and the conditional probabilities are the views of the analysts conditional on the market  equilibrium returns. 
%
% Applying the Bayesian transformation \cite{idzorek2002}, the expected means of expected returns is given by:
%\begin{equation}
%\overline{E(r)}= \Pi + \tau \Sigma P^\intercal\left[\left(P\tau \Sigma P^\intercal\right)+\Omega\right]^{-1}\left[Q-P \Pi\right]
%\end{equation}
%The posterior variance is:
%\begin{equation}
%\Sigma_p=\Sigma + \left[\left(\tau \Sigma\right)^{-1} + P^\intercal \Omega^{-1} P\right]^{-1}
%\end{equation}
%where:
%\begin{itemize}
%\item $\Pi$ - a vector of market equilibrium returns;
%\item $\tau$ - a parameter of scaling the variance due to the fact that the variance of the distribution of means is less than the variance of distribution of a variable;
%\item $\Sigma$ - historical co-variance matrix of all assets; 
%\item $P$ is an identification matrix of stocks that have views;
%\item $\Omega$ is confidence of the views
%\item $Q$ is the value of the expected return given by an analysts
%\end{itemize}

%At the beginning of the quarter, we run a ranking prediction algorithm NBLR(t) to predict the position of the analysts by the end of the quarter. The accuracy of prediction compared to the true ranking is what is used as the confidence of the expected return. That is, we assume that the higher the accuracy of the prediction, the more confident we are about the values of  $Q$.

\subsection{Defining analysts' expected returns} 
\label{def-q}
We follow \cite{da2011} to obtain analysts' expected returns from TP. The literature agrees that, on average, these expectations are upward biased \citep{bradshaw2002,brav2003,da2011}.  To convert the rankings into expected returns:

\begin{enumerate}
\item We calculate the weights for each of the analysts $a$ based on the analyst's rank, such that rank 1 receives the weight of 1 and then the weights diminish as the ranks increase:
\begin{equation}
w_{q,a,s}=1-\frac{rank_{q,a,s}-\min{ \{rank_{q,a}\} }}{\max{\{rank_{q,a}\}}}
\end{equation}

\item The expected rank-weighted return is:
\begin{equation}
Q_{q,s}=\frac{\sum_1^{q,a} (w_{q,a,s} \times r_{q,a,s})}{\sum_1^a w_{q,a,s}}
\end{equation}
\end{enumerate} 
%In matrix form:
%\begin{equation}
%q_s=\frac{\mathbf{w}^\intercal\mathbf {r} }{\boldsymbol{\iota}\mathbf{w}}
%\end{equation}
where $r_{q,a,s}=TP_{q,a,s}/P_{q,s}-1$  is the analysts' expected return for a stock $s$ based on the analyst's price target $TP_{q,a,s}$ and stock price $P_{q,s}$ three days before the $TP_{q,a,s}$ announcement.

\subsection{Defining the confidence of expected returns} %The value of $Q_s$ serves as the expected return of the stock $s$ in quarter $t$. 
\label{def-omega}
To complete the view for the BL model, we need to define $\Omega$, the confidence on the views. We use the Spearman correlation to evaluate the ranking accuracy between the two rankings \citep{brazdil2003}:

\begin{equation}
\label{eq:spearman}
 \rho_{q}(rank_{act},\widehat{rank})=1-\frac{6\sum_{i=1}^a(rank_{act,i}-\widehat{rank}_i)^2}{a^3-a}
\end{equation}
where $rank_{act}$ and $\widehat{rank}$ are, respectively, the \tr{} and expected rankings; $a$ is the rank of an individual analyst in each of the rankings.

The interpretation of the coefficient is simple. Two rankings with all the analysts placed in the same position will have a Spearman correlation of $+1$. Analysts placed in reverse order will yield a correlation of $-1$. Thus, the higher the value of $\rho$ the more accurate the prediction is compared to the \tr{}.

We use the moving average of $\rho$ of past four quarters to build up more confidence in ranking forecasts as we assume that if we are able to forecast rankings for a given stock correctly, then we should weight these rankings with more confidence.

\begin{equation}
\tilde{\rho}=\frac{1}{4}\sum_{i=0}^3 \rho_{q-i}
\end{equation}

We scale $\tilde{\rho}$ from [-1,1] to [0,1] and the elements of $\Omega$ are:
\begin{equation}
\label{eq:omega}
\omega_{s}=\frac{1-\tilde{\rho_{s}}}{\tilde{\rho_{s}}}
\end{equation}
That is, if we were 100\% confident in our view, i.e., we predict the rankings with the Spearman correlation $\tilde{\rho}=1$, then the values of $\omega=0$; otherwise,  $\omega$ increases as accuracy decreases.

\section{Data and experimental setup}
\label{sec:rankings}
%NOTE: use for experiments SP500 
%We use stocks that are traded either on NYSE, NASDAQ, or AMEX. The experiment starts at the first quarter of 1999 and stops at the last quarter of 2009 (40 quarters).  First, we select stocks with at least one broker \footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person. In reality, the broker is the institution that hires the analysts.} with the minimum 12 quarters  covering a particular stock. Second, for computational purposes, we need at least 3 brokers per stock in each quarter.  We call this set of brokers as the  ``core" brokers. In total we have 244 unique core brokers covering 1785 stocks. The analysts' EPS forecast data is from the ThomsonReuters I/B/E/S database.

%ADD SP500 subset of accuracy

To implement the trading strategy, we focus on the  S\&P500 stocks. Given that we base  stock views on the analysts' price target information, the period of the strategy experiment runs from the first quarter of 2001 until the last quarter of 2009. We get price target and quarterly EPS information from ThomsonReuters  I/B/E/S  database. The list of S\&P constituents and stock daily prices data is from DataStream as well as the market capitalization data.  The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably  and we assume it is  one person.} in EPS dataset is \Sexpr{dim(estimates)[[3]]}, covering \Sexpr{dim(estimates)[[2]]} stocks. The price target dataset includes \Sexpr{dim(extendent.exp.ret)[[2]]} brokers covering \Sexpr{dim(extendent.exp.ret)[[3]]} stocks. To be consistent across the two datasets (EPS and price target), we select brokers that have made both: an EPS forecast and a price target for a given stock. Thus,  the final sample consists of \Sexpr{length(working.b)} brokers and \Sexpr{ length(working.s)} stocks.
%Contrary to other studies on analyst' price targets  \citep{bradshaw2002,brav2003,da2011}, we do not truncate our sample based on the misalignment errors found on I/B/E/S data, i.e., errors where stock prices do not adjusted for stock-splits and dividends.

Given the fact that financial analyst mostly issue TP annually\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have 12-month horizon \citep{glushkov2009}}, we assume that an analyst keeps her TP forecast open for one calendar year until it gets revised or expires after one year. %The total number of observations for a full sample is \Sexpr{format(total.obs,big.mark=' ')}. 
Consistent with other studies on analysts' expected returns based on price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at 1\textsuperscript{st} percentile (values below \Sexpr{round(trunk.tp[[1]],2)}) and 99\textsuperscript{th} percentile (values above \Sexpr{round(trunk.tp[[2]],2)}). This is done due to the extreme values cause by misalignment errors found on I/B/E/S data \footnote{We found some differences in the databases as there can the cases when one of the databases did not performed the stock-splits or dividend payment adjustment.}. The final sample size of $TP/P-1$ observations is reduced from \Sexpr{format(total.obs,big.mark=' ')} to \Sexpr{format(length(show.no.na(trunk.data)),big.mark=' ')}.
%As we mentioned, we weight the analysts' expected returns $r_{a,s}$ by the analysts' rank. This assures that very optimistic analysts' would be penalized by the lower rank and still contribute to $Q_{q,s}$

Panel A of table (\ref{tab:stat}) depicts the descriptive statistics of quarterly EPS forecasts aggregated annually. Overall, we had \Sexpr{format(total.stat.eps[1],big.mark=' ')} quarter-firm-broker  observations. On average, we report that each broker issued \Sexpr{round(total.stat.eps['mean'],2)} forecast per stock per quarter (median = \Sexpr{round(total.stat.eps['median'],2)}). Panel B shows the statistics of the expected analysts' return $r_{q,a,s}$. Consistent with the literature \citep{da2011,bradshaw2012,zhou2013}, we find the average expected annual analysts' return to be upward biased (\Sexpr{round(total.sp.summary.12m['mean'],2)}, median = \Sexpr{round(total.sp.summary.12m['median'],2)}). 
%Table ~(\ref{table:forecasts-broker}) presents the break down by sector of the forecasts issued per quarter.  Panel A shows averages form the broker perspective. As we observe, on average, for all sectors, in each quarter there were 27 forecast per broker. Each of these brokers would issue 2.75 forecasts per stock and each broker would follow a stock for 11 quarters. Panel B shows same statistics but from the stock perspective.  On average, in each quarter a stock would get 14.66 forecasts from 4.41 brokers. Per quarter, a stock would get 2.6 forecasts per broker and a stock would have a coverage life of 12 quarters.

%It does not matter what to use to build rankings EPS or TP. We select TP because we can get expected analyst' returns and have both rankings and expected returns calculated from one metric. In case of EPS, we cannot easily calculate the expected returns. Though there are models that use EPS growth forecast to valuate stocks, we selected to proceed with TP as they are widely used in the literature to measure the analyst' return expectations.

We rank analysts based on the Proportional  Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}. First,  we define the  forecast error  $FE$ as an absolute value of the difference between actual and the latest forecast made by an analyst $a$ regarding stock $s$  for quarter $q$: 
\begin{equation}
FE_{q,a,s}=|ACT_{q,s}-PRED_{q,a,s}|
\end{equation}
Then, we calculate the average error of the forecasts made by all analysts in quarter $q$ for stock $s$ as:
\begin{equation}
\overline{FE}_{q,s}=\frac{1}{a}\sum_{a=1}^a FE_{q,a,s}
\end{equation}

PMAFE is given as:%\footnote{The rankings that are commonly used by $\mathrm{FE}$ and $\mathrm{PMAFE}$ are the same. The latter is more common in the literature where OLS methods in regression analyses require normalization of the data.}
\begin{equation}
PMAFE_{q,a,s}=\frac{FE_{q,a,s}}{\overline{FE}_{q,s}}
\end{equation}

%When PMAFE equals to 1, the error of individual analyst is the same as the error of all analysts

Table (\ref{tab:stat-pmafe}) shows the descriptive statistics of PMAFE of brokers per stock. Observe that the average per stock error is greater that 1. This  means that, on average, analysts are bold in their forecasts and they do not follow the average forecast. Figure (\ref{fig:pmafe}) shows the scatter plot for both forecast error measures.  Observe that all errors are concentrated around 1 and there is no correlation between the errors.

To proceed with the trading strategy, we define the methods to obtain the expected rankings of the analysts. We define two ways to forecast the end-period rankings: the \naive{} --- the last known end-period ranking, and the \default{} --- a ranking that is build based on average broker rank starting from  the beginning of the observations and ending at last end-period. Formally, we define:
\begin{itemize}

\item  the \naive{}  rankings:
\begin{equation}
\label{naive:ranking}
\widehat{rank_{q,s}}=rank_{q-1,s}
\end{equation}

\item  the \default{}  rankings:
\begin{enumerate}
\item find the average rank of an analysts:
\begin{equation}
\label{default.rank}
\widehat{rank_{q,a,s}} = \frac{\sum_{q=1}^n rank_{q,a,s}}{n}
\end{equation}
\item rank the values of $\widehat{rank_{q,a,s}}$
\end{enumerate}
%where $y^{-1}_{a}$ is rank of analyst $a$ in the ranking $y$.
\end{itemize}

Figure (\ref{fig:tr-pmafe}) plots the relation between the \tr{} ranking and the forecast errors (PMAFE). We convert absolute rankings into relative terms by applying:
\begin{equation}
relRank_{q,a,s}=\frac{rank_{q,s,a}}{\max{rank_{q,s}}}
\label{rel-rankings}
\end{equation}

We observe that the magnitude of the errors is directly proportional to the rank. That is, most of the errors are done at the bottom of the rankings. %This conclusion confirms previous findings of consistency of the brokers.

\section{Empirical Results}
\label{sec:results}
%\subsection{Ranking accuracy: top/bottom analysis}
%We begin with the analysis of ranking accuracy. That is, how well does our methods of (\ref{naive:ranking}) and (\ref{default.rank}) fit the \tr. Table \ref{tab:accuracy} depicts the average Spearman correlation (eq.\ref{eq:spearman}) for two methods. Panel A shows the accuracy for EPS based rankings.  We observe that both forecast methods fail to accurately forecast the \tr{} rankings (then means for \naive{} and \default{} 0.05 and 0.01, respectively). Panel B depicts the same results for the rankings based on the price target. We see that the means of the both methods are higher than from the EPS case. We attribute it to the fact that price target sample is larger compared to EPS.

%Analysis of table \ref{tab:accuracy} brings us to conclusion that last period analysts, on average, do not stay at the same rank for the next period. However, this contradicts with the previous studies identifying the consistency among the analyst. We investigate further and applied a procedure to separate the top ranks from the bottom ones. This would allows us to see where the most errors in rankings were happening: at the top or at the bottom.

%First, we used relative rankings from (eq. \ref{rel-rankings}) and split the ranking set in two parts. We consider as the top rank the ones that are in the top 5\% of the ranking. That is: $top_{q,a,s}=relRank_{q,a,s}[0\ldots 0.05]$ and bottom: $bottom_{q,a,s}=relRank_{q,a,s}[0.06\ldots1]$. We sum  $top_{s,a,q}$ to get a score and we find the euclidean distance between the score of $top_{q,a,s}$ of  \tr{} and the score of $top_{q,a,s}$ for all forecast rankings. The assumption is: the less the distance, the more accurate are the rankings. Finally, we normalized the distances across all stocks to get stocks with the perfect prediction of top rankings with value of 0 and stocks where the distance is the maximum among all stocks with value of 1. For $bottom_{s,a,q} $ the analysis is the same.

%Mathematically, it looks the following:
%\begin{eqnarray}
%score_{q,s}&=&\sum_{1}^{a} top_{q,a,s} \nonumber \\
%dist_{s}&=&\sqrt{ \sum_{q=1}^{40}(score_{(\tr{}),q,s}-score_{q,s})^{2}}\nonumber \\
%norm.dist_{s}&=&\frac{dist_{s}-\min{dist_{s}}}{\max{dist_{s}}-\min{dist_{s}}}
%\end{eqnarray}
%The variable $dist_{s}$ is the distance of sum of top rankings relative to \tr{} for all stocks. %Figure (\ref{top-bottom}) shows these distances across 487 stocks. We see, indeed, that the most errors of the predicted methods were done at the bottom of the rankings. Notice, how \default{} method at 0.50 cut depicts the uniform distribution of top to bottom as it is built on averaging the ranks.

%The table (\ref{tab:top-bottom}) depicts the average per stock distance of top and bottom analysts of forecast rankings to actual ranking. Panel A demonstrates that, with EPS in rankings, the distance of top analysts of \naive{} to top analyst of \tr{} was 0.012; and for \default{} 0.027. This means, that for \naive{} top analysts in EPS rankings stays on top longer compared to \default. Panel B shows the same analysis for rankings with base in price target. In this case, top analyst for \naive{} method were very close to the top analysts of \tr{} (distance of 0.008). This indicates that \naive{} method was able to forecast top analysts more accurately compared to \default{}. %Compared between EPS and price target, we conclude that top analysts of

%\subsection{Trading strategies}
%Despite that the ranking accuracy shows (table \ref{tab:accuracy}) that it is hard to predict the rankings, the top/bottom analysis suggests that most of the errors in forecast rankings were done at the bottom part of the rankings. 
We report results from trading strategies in table (\ref{tab:strategy}). Panel A reports the performance of the passive strategy called the \textit{Market} --- a benchmark strategy. This strategy showed an annualized cumulative return of \Sexpr{results.pt['market',1,1]*100}\% and an annualized Sharpe ratio (SR) of \Sexpr{round(results.pt['market',3,1],2)}. The average number of stocks used per quarter is \Sexpr{round(results.pt['market',4,1],2)} and the turnover ratio of strategy is \Sexpr{round(results.pt['market',5,1],2)}, which demonstrates the ins/outs of the S\&P 500 constituents list. Given this table, we are able to answer the questions we pose in section (\ref{sec-intro}).

\subsection{Which one of the accurate forecasts, if followed, is more profitable for an investor?}

%The second question of this study: which analyst to follow: the one who issues accurate EPS forecasts or the one who is good at forecasting the price targets?

The panel B of table (\ref{tab:strategy}) presents the results of the trading strategy based on the accuracy in EPS forecasts. From the panel we observe that the \naive{} strategy resulted in the cumulative return of \Sexpr{results['naive',1,1]*100}\% (SR = \Sexpr{round(results['naive',3,1],2)}). The annualized cumulative return for the \default{} method is \Sexpr{results['default',1,1]*100}\% (SR = \Sexpr{round(results['default',3,1],2)}). Finally, the \tr{} strategy, the perfect foresight, achieves the cumulative return of \Sexpr{results['true',1,1]*100}\% (SR = \Sexpr{round(results['true',3,1],2)}).

%Observe that both the \naive{} and the \default{} have the same annualized cumulative returns and only the Sharpe ratio of \naive{} puts this method  ahead of \default{} in terms of the performance. As mentioned, the trading strategy with rankings in EPS forecast outperforms the benchmark strategy for all of ranking predictions.

Panel C of the table demonstrates the results of trading with rankings based on the accuracy of price targets. We report the following  results. The strategy based on the last period rankings, the \naive{},  yields the annualized cumulative return of \Sexpr{results['naive',1,2]*100}\% (SR = \Sexpr{round(results['naive',3,2],2)}). The annualized cumulative return for the \default{} method is \Sexpr{results['default',1,2]*100}\% (SR =  \Sexpr{round(results['default',3,2],2)}). Finally,  the perfect foresight achieves the annualized cumulative return of \Sexpr{results['true',1,2]*100}\% (SR = \Sexpr{round(results['true',3,2],2)}).

The analysis of the panels B and C of the table show that it is profitable for the investor to follow brokers that issue more accurate price targets and not the EPS forecasts. Moreover, we claim that the strategy based on the accuracy of EPS forecasts is not valid. The reason is that of the values of the \tr{} strategy. We assume earlier that the perfect foresight strategy should identify the best analysts and produce the maximum possible outcome in trading. We observe that the annualized cumulative return of the \tr{} strategy for the EPS case fail to pass this assumption. The \tr{} strategy resulted in the worst of the three outcomes raising question the validity of the rest of the results.

On the contrary to the EPS case, the price target strategy demonstrated the results that go in-line with the \tr{} strategy assumption. As seen from panel C, \tr{} shows the maximum possible outcomes across different portfolio performance measures. The result confirms that the top analysts are the best ones and they have skills to project the performance of the stocks. If an investor knows perfect rankings of the analysts in advance, she would get the maximum outcome from the trading. Given the fact that the \tr{} is a hypothetical condition that we introduce to check the validity of the trading model, the next best trading strategy is the one that is based on last known rankings,  the \naive{} strategy. The trading results of this strategy suggests that the top analysts stay at the top ranks; thus, we confirm the analysts' consistency argument \citep{hilary2013}.

%The result suggests that the ranking of the analysts based on their accuracy to predict the stock prices is able to identify the best ones and, if known in advance these rankings one would generate substantial annualized abnormal returns. In general,

Figure \ref{fig:bl-results} plots the graphical representation of the cumulative portfolio wealth for all of the methods of trading strategies. The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at June 2000 and ending at December 2009.

The top chart shows the evolution of wealth of portfolios obtained from the strategies based on the rankings with accuracy in EPS forecasts. We see that the wealth of each of the portfolios of all strategies is above the wealth of portfolio from the  benchmark strategy. However, the relation of wealth between the rankings-based strategies is quite mixed. As mentioned earlier, the \tr{} strategy is the worst of the three (but still beating the benchmark). We should have expected that if financial analysts have skills in making accurate EPS forecasts then the wealth of the portfolio obtained from the \tr{} rankings  should guarantee the best possible strategy outcome. We observe is the opposite: knowing in advance the best analysts resulted in the worst strategy. Financial analysts who issue accurate EPS forecasts do not ensure the best outcome from the trading strategy.

The bottom chart of the figure (\ref{fig:bl-results}) demonstrates the progress of portfolio wealth of the strategies with the rankings based on the  TP accuracy. Notice how wealth of the \tr{} strategy is on top of all the other including the benchmark strategy. Contrary to the EPS forecasts case, knowing in advance the right rankings of the financial analysts who issue accurate TP generates the maximum possible wealth in each of the trading period.

The discussion of figure (\ref{fig:bl-results}) reveals a possible  challenge for the investors. Observe the bottom chart of the figure and notice the gap between the unattainable \tr{} strategy and the next feasible strategy. The gap is quite wide suggesting it is possible to apply more sophisticated ways in predicting the \tr{} rankings and gaining more wealth.

%Similar to the EPS trading case, the \tr{} ranking produces the best results out of the other two methods. Moreover, the results of \tr{} of the price target rankings outperformed the results of \tr{} of EPS based rankings: (\Sexpr{round(results.pt['true',1,1],3)} vs. \Sexpr{round(results.eps['true',1,1],3)}). This implies that in the settings where analysts' expected returns and rankings are based on price targets, an investor can gain a maximum results from trading strategy.

%\subsection{Rankings with EPS forecast accuracy}

%The results of the trading strategy with EPS forecast based rankings are presented in Panel B of table (\ref{tab:strategy}). As observed from the table, the strategy is not valid. Notice quite high value for the annualized cumulative return for the \default{} method \Sexpr{round(results.eps['default',1,1],3)} and the Sharpe ratio of \Sexpr{round(results.eps['default',3,1],2)}. Given these values, we reject the hypothesis that rankings with base on accuracy of EPS forecast bring value to investors. We attribute this result to the inconsistency in the data: the views for individual stocks are made from TP and the confidence of the views is build from EPS forecast data.

%Figure \ref{fig:bl-results} plots the graphical representation of the cumulative portfolio wealth. The top row of the figure shows the trading for the EPS-based rankings. Notice how \default{} breaks the lines and shoots above all the other methods. Another observation is that \tr{} method is not above all. As we mentioned, the \tr{} method represents the forecasts of rankings that are the actuals. This means, that, if financial analysts have stock-picking skills and can interpreter information, this strategy should yield the maximum possible return.

%\subsection{Rankings with the base of TP}
%We apply a practical implementation of use of the rankings. For this purpose, we performed back-test trading implementing the Black-Litterman strategy outlined in section (\ref{sec:trading}). The results are presented in table (\ref{tab:strategy}).

%Panel B shows the trading strategy of rankings with the base in EPS. Observe that the \tr{} strategy demonstrated the highest values of both annualized cumulative return and annualized Sharpe ratio (\Sexpr{round(results.eps['true',1,1],3)} and \Sexpr{round(results.eps['true',3,1],2)} respectively). This suggests that if known actual rankings in advance, one could achieve the best result in trading as the rankings truly identify the top analysts and their information generate the most positive outcomes. Given the hypothetical nature of \tr{} rankings, this strategy is not feasible. However, \naive{} showed positive results, second after the \tr{}. This strategy resulted in annualized cumulative return of \Sexpr{round(results.eps['naive',1,1],3)} and annualized Sharpe ratio of \Sexpr{round(results.eps['naive',3,1],2)} and average turnover rate of \Sexpr{round(results.eps['naive',5,1],2)}.

%Since, in trading part, the analysts expected returns were calculated with the emphasis on top rankings, we can conclude that the successful trading strategy is valid. It also confirms the hypothesis that there are top analyst that exhibit a relative consistency in their forecasts.

%We stress the complete set as we show later that in splitting the rankings in top/bottom subset, we observe that most errors in accuracy were done at the bottom of the rankings. This finding suggests that even thought, on average, last period rankings cannot tell the true rankings, the analysts that stayed in top ranks continue to stay next period.

\subsection{Are rankings of financial analysts useful to investors?}

Comparing the results from trading strategies with panel A of the table, we confirm that the rankings yield cumulative returns that outperform the \textit{Market}. It follows that rankings can identify the best analysts and following the advice of these analysts can yield abnormal returns.

\section{Conclusions}
\label{sec:conclusion}

Some institutions, such as StarMine, rank financial analysts based on their accuracy. These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors. Therefore, there is a growing interest in understanding the relative performance of analysts.

%We analyzed the rankings and concluded that most errors in rankings were done at the bottom. Consistent with the literature, we confirm that there exists a subset of analysts who issue informative forecasts and this subset is consisted form one period to another.
%We perform two tasks of the label ranking problem of the financial analysts. First, we successfully perform the predicting part of the problem by adapting the existing LR algorithm. Our results were able to outperform both of the baselines: the naive rankings and the default. Based on the average ranking accuracy,  the best result of the experiment was achieved with a method in which the attributes were aggregated applying the rolling standard deviation. This finding suggests that analysts, in the  process of their interpretation of information, rely on  stability of the time series at least for 8 quarters.

By applying the Black-Litterman model, we perform the simulations of trading and report that rankings of financial analysts based either on accuracy of EPS forecasts or on accuracy of price targets yield abnormal returns. Further, we demonstrate that rankings with base in price target accuracy showed the better portfolio performance compared to the rankings with base in EPS forecast accuracy. The choice for the investors whom to follow: an analyst who makes more accurate EPS forecast or who makes more accurate price targets clearly is in favor for the latter.

%Further, we show that a strategy based on actual rankings outperforms the other ranking-based strategies only in price target case which means that analysts who issue accurate price targets have knowledge about future stock performance. We conclude that rankings can identify the best analysts and leveraging the relative performance of these analysts produces the profitable outcomes.

For the future work we would like to develop new methods in forecasting the rankings based on accuracy of price targets.

\bibliographystyle{apalike}
\bibliography{/Users/aiguzhinov/Documents/Dropbox/Documents/Bibliography/rank}
\appendix
% \section{Black-Litterman derivation}
% 
% In the BL model the prior probability of the means of expected returns: 
% \begin{equation}
% \label{eq:prior}
% P(A) \backsim N(\Pi, \tau \Sigma)
% \end{equation}
% That is, the prior probability is the normal distribution of equilibrium CAPM returns with the scaled historical variance since we estimate the means of the expected returns and not the expected returns themselves.
% 
% The conditional probability is the investors view of the expected return of $Q$ and the variance of $\Omega$:
% 
% \begin{equation}
% P(B|A) \backsim N(P^{-1}Q, [P^{\intercal} \Omega^{-1} P]^{-1})
% \end{equation}
% 
% So, the posterior probability takes from, applying the Bayes theory,:
% \begin{equation}
% P(A|B) \backsim N([(\tau \Sigma)^{-1} \Pi +  P^{\intercal} \Omega^{-1} Q][ (\tau \Sigma)^{-1}+P^{\intercal} \Omega^{-1} P]^{-1}, [(\tau \Sigma)^{-1}+P^{\intercal} \Omega^{-1} P]^{-1} )
% \end{equation}

\section{Tables and Figures}

\begin{figure}[ht]
\begin{center}
\includegraphics[scale=0.25]{Black-litterman}
\end{center}
\caption{Trading strategy schematics} 
\label{fig:bl} 
\ The figure plots the schematics of implementation of BL model. We gather all necessary inputs at the end of quarter $q-1$. At the beginning of quarter $q$ we apply the BL model and form the portfolio of stocks based on the optimal resulting weights. At the end of quarter $q$, we evaluate the portfolio.
\end{figure}

\begin{table}[htb]
  \caption{Descriptive statistics of the variables}
  \label{tab:stat}
\ The table presents a descriptive statistics of the main variables used in the paper. Panel A depicts the statistics of quarterly EPS data aggregated annually per analyst per stock. Panel B represents the statistics of analysts' expected returns defined as $TP/P-1$.

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
    \multicolumn{4}{l}{\textbf{Panel A: EPS forecasts}} \\
    \midrule
<<desc-eps,echo=F,results=tex>>=
data.to.display <- c('nbr.val','median', 'mean','std.dev')
results.final <- descr.stat.eps[,data.to.display]
rownames(results.final) <- c(years[11:21])
colnames(results.final) <- c('num.obs','median','mean','st.dev')
cat(paste('&',paste(colnames(results.final), collapse = "&"),'\\\\'))
cat(rep('&',ncol(results.final)),'\\\\')
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',format(results.final[,2],big.mark=' '),'&',apply(results.final[,c(3:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
cat('\\midrule','\n')
results.final <- total.stat.eps[data.to.display]
cat(paste('Total Period','&',format(results.final[1],big.mark=' '),'&',format(results.final[2],big.mark=' '),'&',paste(sprintf("%.3f",results.final[3:length(results.final)]), collapse = "&"),collapse="\\\\\n"),'\\\\')
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
    \multicolumn{4}{l}{\textbf{Panel B: Analysts' expected returns}} \\
    \midrule
<<desc-pt,echo=F,results=tex>>=
results.final <- descr.stat.pt[,data.to.display]
rownames(results.final) <- c(years[11:21])
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',format(results.final[,2],digits=3),'&',apply(results.final[,c(3:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
cat('\\midrule','\n')
results.final <- total.sp.summary.12m[data.to.display]
cat(paste('Total Period','&',format(results.final[1],big.mark=' '),'&',format(results.final[2],digits=3),'&',paste(sprintf("%.3f",results.final[3:length(results.final)]), collapse = "&"),collapse="\\\\\n"),'\\\\')
@
    \bottomrule
  \end{tabularx} 
\end{table}

<<eps-brok-fig,echo=FALSE,results=hide,include=false,fig=TRUE,height=10,width=12>>=
pt.time <- 43:84

g <- matrix(c(1,0,2,0,3),ncol=1,nrow=5,byrow=T)
layout(g, heights = c(2,0.05,2,0.05,2), widths = 12)

plot(q.pt.per.b[pt.time],type='b',ylim=c(pretty(range(c(q.pt.per.b[pt.time],q.num.b[pt.time]))[1])[1],pretty(range(c(q.pt.per.b[pt.time],(q.num.b)[pt.time]))[2])[2]),pch=1,main='Average number of brokers per quarter')
lines(q.num.b[pt.time],type='b',pch=2)
legend(legend=c('TP','EPS forecasts'),cex=1.2,lty=1,pch=1:2,text.col="black", bg='white', title='Datasets:', ncol=1, "topleft")
box('figure',lty='solid')

plot(q.pt.per.s[pt.time],type='b',ylim=c(pretty(range(c(q.pt.per.s[pt.time],(q.num.s)[pt.time]))[1])[1],pretty(range(c(q.pt.per.s[pt.time],(q.num.s)[pt.time]))[2])[2]),pch=1,main='Average number of stocks per quarter')
lines(q.num.s[pt.time],type='b',pch=2)
legend(legend=c('TP','EPS forecasts'),cex=1.2,lty=1,pch=1:2,text.col="black", bg='white', title='Datasets:', ncol=1, "topleft")
box('figure',lty='solid')

plot(pt.num.s.per.b[pt.time],type='b',ylim=c(pretty(range(c(pt.num.s.per.b[pt.time],eps.num.s.per.b[pt.time]))[1])[1],pretty(range(c(pt.num.s.per.b[pt.time],eps.num.s.per.b[pt.time]))[2])[2]),pch=1,main='Number of stocks per broker per quarter')
lines(eps.num.s.per.b[pt.time],type='b',pch=2)
legend(legend=c('TP','EPS'),cex=1.2,lty=1,pch=1:2,text.col="black", bg='white', title='Datasets:', ncol=1, "topleft")
box('figure',lty='solid')
@

% \begin{figure}[ht]
% \begin{center}
% \includegraphics{paper-sweave-eps-brok-fig}
% \end{center}
% \caption{Total number of brokers, stocks, and brokers per stock}
% \label{fig:brok}
% \end{figure}

\begin{table}[htb]
  \caption{Descriptive statistics of PMAFE}
  \label{tab:stat-pmafe}
\ The table presents the descriptive statistics of the two measures of analysts' forecast errors: EPS forecasts and price target. We use Proportional Mean Adjusted Forecast Error (PMAFE) defined as the absolute analysts' forecasts errors divided by the mean absolute forecast error. Panel A shows the average PMAFE of EPS forecast. Panel B depicts the same statistics for PMAFE based on the TP.
  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
    \multicolumn{4}{l}{\textbf{Panel A: EPS PMAFE}} \\
    \midrule
<<pmafe-descr-eps,echo=F,results=tex>>=
results.final <- d.pmafe.eps[,data.to.display]
rownames(results.final) <- c(years[12:21])
colnames(results.final) <- c('num.obs','median','mean','st.dev')
cat(paste('&',paste(colnames(results.final), collapse = "&"),'\\\\'))
cat(rep('&',ncol(results.final)),'\\\\')
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',format(results.final[,2],digits=3),'&',apply(results.final[,c(3:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
cat('\\midrule','\n')
results.final <- total.pmafe.eps[data.to.display]
cat(paste('Total Period','&',format(results.final[1],big.mark=' '),'&',format(results.final[2],digits=3,big.mark=' '),'&',paste(sprintf("%.3f",results.final[3:length(results.final)]), collapse = "&"),collapse="\\\\\n"),'\\\\')
@
  \end{tabularx}

  \begin{tabularx}{\linewidth}{r*{4}{Y}}
    \toprule
    \multicolumn{4}{l}{\textbf{Panel B: Analysts' expected returns PMAFE}} \\
    \midrule
<<pmafe-desc-pt,echo=F,results=tex>>=
results.final <- d.pmafe.pt[,data.to.display]
rownames(results.final) <- c(years[12:21])
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',format(results.final[,2],digits=3),'&',apply(results.final[,c(3:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
cat('\\midrule','\n')
results.final <- total.pmafe.pt[data.to.display]
cat(paste('Total Period','&',format(results.final[1],big.mark=' '),'&',format(results.final[2],digits=3),'&',paste(sprintf("%.3f",results.final[3:length(results.final)]), collapse = "&"),collapse="\\\\\n"),'\\\\')
@
    \bottomrule
  \end{tabularx}

\end{table}

<<plot-pmafe,echo=FALSE,include=false,fig=TRUE,results=hide,width=8,height=8>>=
plot(mean.pmafe[,,'eps'],mean.pmafe[,,'pt'],ylab='TP PMAFE',xlab='EPS PMAFE',main='Propotional Mean Adjusted Forecast Error')
box('figure',lty='solid')
@

\begin{figure}[htb]
\begin{center}
\includegraphics{paper-sweave-plot-pmafe}
\end{center}
\caption{The relation of TP and EPS PMAFE}
\label{fig:pmafe}
\ The plot shows the relation between the two forecast error measures: EPS and TP. PMAFE defined as an absolute forecast analyst' error divided by the mean absolute forecast error. Each circle represents an analyst in the sample of total of \Sexpr{length(working.b)} analysts.
\end{figure}

%<<stat-pmafe,echo=FALSE,results=tex>>=
%texreg(model.pmafe)
%@

<<plot-tr-pmafe,echo=FALSE,include=false,fig=TRUE,results=hide,width=8,height=4>>=
m <- matrix(c(1,0,2),1,3,byrow=T)
#pdf(file='quarterly.pdf',paper="a4r",width=0,height=0)
#matrix(c(1,0, 2,0, 3,0,4))
#layout(matrix(c(1,0,2)), heights = c(2,0.1,2), widths = c(1,1))
layout(m, heights = c(4,0.05,4), widths = c(4,0.05,4))
plot(mean.pmafe[,,'eps'],mean.rel.rank[,,'eps'],ylab='Relative true rankings',xlab='EPS PMAFE',main='EPS')
box('figure',lty='solid',xlim=c(0,6))
plot(mean.pmafe[,,'pt'],mean.rel.rank[,,'pt'],ylab='Relative true rankings',xlab='TP PMAFE',main='TP',xlim=c(0,6))
box('figure',lty='solid')
@

\begin{figure}[ht]
\begin{center}
\includegraphics{paper-sweave-plot-tr-pmafe}
\end{center}
\caption{Actual relative ranking and forecast errors}
\label{fig:tr-pmafe}
\ The figure plots the errors as a function of relative \tr{} ranking. 
\end{figure}

%<<descr.accuracy,echo=F, include=FALSE>>=

%descr.pt.accuracy <- t(sapply(baselines[1:3],function(i){stat.desc(pt.eps.accuracy[i,,,1][!is.infinite(pt.eps.accuracy[i,,,1])]) }))

%descr.eps.accuracy <- t(sapply(baselines[1:3],function(i){stat.desc(pt.eps.accuracy[i,,,2][!is.infinite(pt.eps.accuracy[i,,,2])]) }))

%rownames(descr.eps.accuracy) <- c("$\\tr{}$","$\\naive{}$","$\\default{}$")
%rownames(descr.pt.accuracy) <- c("$\\tr{}$","$\\naive{}$","$\\default{}$")
%@
%ann.pt.accuracy <- abind(lapply(baselines[1:3],function(i){annual.desc.stat(pt.eps.accuracy[i,,,1],seq(0,40,4)) }),along=3,new.names=list(NULL,NULL,baselines[1:3]))

% \begin{table}[ht]
%   \caption{Descriptive statistics of ranking accuracy}
%   \label{tab:accuracy}
%   \begin{tabularx}{\linewidth}{r*{4}{Y}}
%     \toprule
%     \multicolumn{4}{l}{\textbf{Panel A: EPS rankings}} \\
%     \midrule
% <<eps,echo=F,results=tex>>=
% results.final <- descr.eps.accuracy[,data.to.display]
% cat(paste('&',paste(colnames(results.final), collapse = "&"),'\\\\'))
% cat(rep('&',ncol(results.final)),'\\\\')
% cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',apply(results.final[,c(2:ncol(results.final))], 1, function(x) paste(sprintf("%.2f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
% @
%   \end{tabularx}
%   
%   \begin{tabularx}{\linewidth}{r*{4}{Y}}
%     \toprule
%     \multicolumn{4}{l}{\textbf{Panel B: Price Target rankings}} \\
%     \midrule
% <<pt,echo=F,results=tex>>=
% results.final <- descr.pt.accuracy[,data.to.display]
% cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',apply(results.final[,c(2:ncol(results.final))], 1, function(x) paste(sprintf("%.2f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
% @
%     \bottomrule
%   \end{tabularx}
% 
%   \ EPS-based rankings were calculated from the proportionally adjusted mean forecast error. That is, absolute forecast error of an analyst divided by the average forecast error for a given stock in a given quarter. Price target rankings were calculated similarly to that ones as for EPS but taking price target forecasting error as ranking metric. \endgraf
%   \ \tr{} is actual ranking of the analysts. \naive{} is the rankings from the last period. \default{} is the average rank of an analyst for up to the last period.
% \end{table}
% 
% 
% \begin{table}[ht]
%   \caption{Average distance of relative ranks: top/bottom }
%   \label{tab:top-bottom}
%   \begin{tabularx}{\linewidth}{r*{3}{Y}}
%     \toprule
%     \multicolumn{3}{l}{\textbf{Panel A: EPS top/bottom distance}} \\
%     \midrule
% <<rel-ranks-error,echo=F,results=tex>>=
% load(file=project.dir('/RankPriceTarget/rank.errors.RData'))
% mean.dist <- apply(rank.errors,c(2,3,4,5),mean,na.rm=T)
% results.final <- mean.dist[2:3,,2,1]
% rownames(results.final) <- c('$\\naive{}$','$\\default{}$')
% cat(paste('&',paste(colnames(results.final), collapse = "&"),'\\\\'))
% cat(rep('&',ncol(results.final)),'\\\\')
% cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' ',digits=3),'&',apply(results.final[,c(2:ncol(results.final)),drop=F], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
% @
% \end{tabularx}
%   
%   \begin{tabularx}{\linewidth}{r*{3}{Y}}
%     \toprule
%     \multicolumn{3}{l}{\textbf{Panel B: Price Target rankings}} \\
%     \midrule
% <<pt,echo=F,results=tex>>=
% results.final <- mean.dist[2:3,,1,1]
% rownames(results.final) <- c('$\\naive{}$','$\\default{}$')
% cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' ',digits=3),'&',apply(results.final[,c(2:ncol(results.final)),drop=F], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
% @
%     \bottomrule
%   \end{tabularx}
% 
%   \ The table depicts the average per stock distance of top and bottom analysts of forecast rankings to actual ranking. Panel A demonstrates that, with EPS in rankings, the distance of top analysts of \naive{} to top analyst of \tr{} was 0.012; and for \default{} 0.027. This means, that for \naive{} top analysts in EPS rankings stays on top longer compared to \default. Panel B shows the same analysis for rankings with base in price target. In this case, top analyst for \naive{} method were very close to the top analysts of \tr{} (distance of 0.008). This indicates that \naive{} method was able to forecast top analysts more accurately compared to \default{}. 
%   %\ \tr{} is actual ranking of the analysts. \naive{} is the rankings from the last period. \default{} is the average rank of an analyst for up to the last period.
% \end{table}
% 
% <<top-bottom-eps,echo=FALSE, include=false,fig=TRUE,results=hide,width=10,height=8>>=
% m <- matrix(c(1,0,2,0,0,0,3,0,4,0,0,0,5,0,6),5,3,byrow=T)
% #pdf(file='quarterly.pdf',paper="a4r",width=0,height=0)
% #matrix(c(1,0, 2,0, 3,0,4))
% #layout(matrix(c(1,0,2)), heights = c(2,0.1,2), widths = c(1,1))
% layout(m, heights = c(2,0.05,2,0.05,2), widths = c(2,0.05,2))
% sapply(1:3,function(cut)
% {
%   #par(mar = c(0, 0, 1, 0) + 0.1) 
%   #plot(0, 0, xlim = c(0, 4), ylim = c(0, 6), type="n", axes=F, xlab="", ylab="",frame.plot=F,main=paste('Plot of distance relative to true of top/bottom rankings. Relative cut is',cut,sep=' '))
%   #par(old.par)
%   sapply(dimnames(rank.errors)[[2]][c(2,3)],function(m)
%   {
%     
%     plot(rank.errors[,m,2:1,'eps',cut],main=m,ylab='Top ranks',xlab='Bottom ranks',ylim=c(0,1),xlim=c(0,1))
%     #means <- apply(rank.errors[,m,],1,mean)
%     abline(a=0,b=1)
%     #abline(lm(rank.errors[,m,2]~rank.errors[,m,1]))
%     box('figure',lty='solid')
%   })
%   #mtext(paste('Plot of distance relative to true of top/bottom rankings. Relative cut is',cut,sep=' '),outer=T)
% })
% @

%\begin{figure}[ht]
%\centering
%\includegraphics{paper-sweave-top-bottom}
%\caption{Comparison of top/bottom rankings}
%\end{figure}

<<bl-results-fig,echo=FALSE, include=false,fig=TRUE,results=hide,width=12,height=10>>=
#m <- matrix(c(1,0,2,0,0,0,3,0,4),3,3,byrow=T)
m <- matrix(c(1,0,2),3,1,byrow=T)
#pdf(file='quarterly.pdf',paper="a4r",width=0,height=0)
#matrix(c(1,0, 2,0, 3,0,4))

#layout(matrix(c(1,0,2)), heights = c(2,0.1,2), widths = c(1,1))
#layout(m, heights = c(2,0.05,2), widths = c(6,0.05,6))
layout(m, heights = c(2,0.05,2), widths = 12)

chart.CumReturns(sel.data.eps,wealth.index=T,ylab='Value of portfolio',xlab='Quarters', ylim=c(0,3),main='EPS rankings: cumulative portfolio wealth',colorset=grey(0:ncol(sel.data.eps)/ncol(sel.data.eps)),type='b',pch=1:ncol(sel.data.eps))
legend(legend=colnames(sel.data.eps),cex=1.2,lty=1,pch=1:ncol(sel.data.pt),text.col="black", bg='white', title='Strategy:', ncol=1, "topleft")
box('figure',lty='solid')

#chart.RollingPerformance(sel.data.eps,width=4,FUN='Return.cumulative',legend.loc='topleft',main='EPS rankings: cumulative return with 1 year reinvestment',colorset=grey(0:ncol(sel.data.eps)/ncol(sel.data.eps)),type='b',pch=1:ncol(sel.data.eps))
#box('figure',lty='solid')

chart.CumReturns(sel.data.pt,wealth.index=T,ylab='Value of portfolio',xlab='Quarters',ylim=c(0,3), main='TP: cumulative portfolio wealth',colorset=grey(0:ncol(sel.data.pt)/ncol(sel.data.pt)),type='b',pch=1:ncol(sel.data.pt))
legend(legend=colnames(sel.data.pt),cex=1.2,lty=1,pch=1:ncol(sel.data.pt),text.col="black", ncol=1, bg='white', title='Strategy:', "topleft")
#text_note=c(paste("Quelle: Bloomberg,", "letzter Datenpunkt:", "last(data$date)"))
#mtext(text_note ,cex=0.4,col="grey",side = 1, line = 4, outer = FALSE,padj=0,adj=1)
 #legend.loc='topleft',cex.lab=0.9

box('figure',lty='solid')

#chart.RollingPerformance(sel.data.pt,width=4,FUN='Return.cumulative',legend.loc='topleft',main='TP: cumulative return with 1 year reinvestment',colorset=grey(0:ncol(sel.data.pt)/ncol(sel.data.pt)),type='b',pch=1:ncol(sel.data.pt))
#box('figure',lty='solid')

#chart.Drawdown(sel.data,main='Drawdowns')#,colorset=grey(0:ncol(sel.data)/ncol(sel.data)),type='b',pch=1:ncol(sel.data))
#box('figure',lty='solid')

#plot(results[,1,1]~results[,3,1],xlab='Annualized Sharpe',ylab='Annualized Return',main='Return and Sharpe ratio')
#text(y = results[,1,1], x = results[,3,1], labels = names(results[,1,1]),pos=4,cex=0.8)
#box('figure',lty='solid')
@

\begin{table}[ht]
  \caption{Trading strategy performance}
  \label{tab:strategy}
  \ The table presents the annualized cumulative statistics of trading based of rankings. Panel A presents the results from the passive strategy and is serve as the benchmark. Panel B shows the results of the trading where views for the BL model were generated with the rankings based on EPS forecast errors. Panel C summarizes the results of the strategy in which views were based on TP rankings. In each of the strategies the \tr{} is the perfect ranking foresight, the \naive{} is the rankings from the last period, and the \default{} is the average rank of an analyst. The trading period ranges from 2000Q3 until 2009Q4.

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  \multicolumn{5}{l}{\textbf{Panel A: Market}} \\
  \midrule
<<bl-market,echo=F,results=tex>>=
results.final <- results.pt['market',,1]
cat(paste('&',paste(dimnames(results)[[2]], collapse = "&"),'\\\\'))
cat(rep('&',length(results.final)),'\\\\')
cat(paste('Market','&', paste(sprintf("%.3f",results.final), collapse = "&"),collapse="\\\\\n"),'\\\\')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  \multicolumn{5}{l}{\textbf{Panel B: EPS strategy}} \\
  \midrule
<<bl-eps,echo=F,results=tex>>=
results.final <- results[,,1]
rownames(results.final) <- c("$\\tr{}$","$\\naive{}$","$\\default{}$")
#cat(paste('&',paste(colnames(results.final), collapse = "&"),'\\\\'))
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',apply(results.final[,c(2:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
@
\end{tabularx}

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  \multicolumn{5}{l}{\textbf{Panel C: Price Target strategy}} \\
  \midrule
<<bl-pt,echo=F,results=tex>>=
results.final <- results[,,2]
rownames(results.final) <- c("$\\tr{}$","$\\naive{}$","$\\default{}$")
cat(paste(rownames(results.final),'&',format(results.final[,1],big.mark=' '),'&',apply(results.final[,c(2:ncol(results.final))], 1, function(x) paste(sprintf("%.3f",x), collapse = "&")),collapse="\\\\\n"),'\\\\')
@
\bottomrule
\end{tabularx}
\end{table}

\begin{figure}[ht]
\begin{center}
\includegraphics{paper-sweave-bl-results-fig}
\end{center}
\caption{Performance of the BL model}
\label{fig:bl-results}
\ In this figure we show the quarterly performance of the cumulative portfolio wealth for all strategies. The top chart demonstrates the cumulative portfolio wealth obtained from the ranking strategies based on the accuracy in EPS forecasts. The bottom charts plots the wealth accumulated with ranking strategies based on the accuracy in the price targets. The $y$-axis is the monetary value of wealth and the $x$-axis is timeline of quarters. Both plots have an equal scale.
\end{figure}

% <<test-table,echo=F,results=tex>>=
% results.final <- round(results,2)
% cat(paste("\\begin{table}\n
% \\caption{Testing table}\n 
% \\begin{center}\n
% \\begin{tabular}{ccccc}\n
% \\toprule\n",
% paste(apply(results.final, 1, function(x) paste(x, collapse = "&")),collapse="\\\\\n"),"\\\\\n",
% "\\bottomrule\n
% \\end{tabular}\n
% \\end{center}\n
% \\end{table}\n",sep=""))
% @

\end{document}

### 2015-02-14 doc/trading.Rmd
Initial commit

```{r echo=FALSE, warning=FALSE}
rm(list=ls())
setwd('~/Documents/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
library(ProjectTemplate)
library(scales)
load.project()
delta<-2.5
```

``` {r echo=FALSE, cache=TRUE, warning=FALSE}

#source('munge/01-data.pre.process.R')
###subset of core stocks/broker: min. 3 broker in quarter and min. 12 quarters of coverage 
q.data=q.data[,core.b:=.N>11,by=list(Stock,Broker)]
core.dt <- q.data[(core.b)][,rank:=rank(score),by=list(q.id,Stock)]
core.dt=core.dt[,clean.s:=.N>2,by=list(q.id,Stock)]
###core rankings
pt.new <- acast(core.dt[(clean.s)],q.id~Broker~Stock,value.var='rank')
###Ranking: making brokers view (extended TPER for 4 quarters)
brok.tper <- acast(unique(ext.pt,by=c('Stock','V2','Broker')),V2~Broker~Stock,value.var='b.view')

###an alternaive to measure accuracy: coef. of variation. To be used when compareing with non ranking methods
brok.cv <- acast(unique(q.data,by=c('Stock','q.id')),q.id~Stock~Broker,value.var='b.coefVar')

##BL inputs for non-rank strateby:meanTper and s.coefVar
meanTper <-acast(unique(q.data,by=c('Stock','q.id')),q.id~Stock,value.var='meanTper')

###Coefficient of variation: lower values means less variable,thus, more confidence. The higher the CV, the greater the dispersion in the variable [http://www.ats.ucla.edu/stat/mult_pkg/faq/general/coefficient_of_variation.htm]
conf.coef <- acast(unique(q.data,by=c('Stock','q.id')),q.id~Stock,value.var='s.coefVar')
### rescale the CV to (0,1). To be consistent with the ranking model, also scale the CV so that if CV=0, don't trust and if CV=1 trust
require(scales)
norm.conf<- rescale(1-conf.coef[1:44,])

#methods<-c('raw','1diff','random','roll.sd')
#baselines<-c('true','naive','default',methods)
#ranking <- 'pt.new'
percentile <- c(0.01,0.99)
trunk.meanTper <- truncate.f(meanTper[1:44,],percentile)
all.s <- findIntersect(pt.new,brok.tper,3)
all.b <- findIntersect(pt.new,brok.tper,2)

trunk.brok.tper <- truncate.f(brok.tper[1:dim(pt.new)[1],all.b,all.s],percentile)

true.Q <- buildQs(all.s,pt.new,trunk.brok.tper)
true.conf <- true.Q
true.conf[!is.na(true.conf)] <- 1

plot.true <- ggplot(data.table(melt(true.Q,na.rm=T)),aes(x=as.Date(as.yearqtr(Var1)),y=value,group=Var1))+geom_boxplot()+theme_bw()
plot.conf <- ggplot(data.table(melt(norm.conf,na.rm=T)),aes(x=as.Date(as.yearqtr(Var1)),y=value,group=Var1))+geom_boxplot()
```
``` {r}
plot.true
plot.conf
```

```{r samePeriod, echo=FALSE}
bl.period <- 3:(dim(trunk.meanTper)[1])
m.period <- ((length(market.list)-length(bl.period))+1) : (length(market.list))

#opt.w<- rbindlist(script.weights.env.f('meanTper',market.list[m.period],trunk.meanTper[bl.period,],norm.conf[bl.period,],0.02,2.5))

opt.w<- rbindlist(script.weights.env.f('rankTper',market.list[m.period],true.Q[bl.period,],true.conf[bl.period,],0.02,2.5))

bl.results <- unique(opt.w,by='q.id')
bl.results=bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views)][,ann.sr:=ann.ret/ann.sd]
```
# view and market in the same period: start p = 3, ann.ret=`r bl.results[1,ann.ret]`, sr=`r bl.results[1,ann.sr]`
```{r p.samePeriod,echo=FALSE}
plot(bl.results[,cum.ret],type='l')
```

```{r viewPlus, echo=FALSE}
bl.period <- 3:(dim(trunk.meanTper)[1])
m.period <- ((length(market.list)-length(bl.period))) : (length(market.list)-1)

#opt.w<- rbindlist(script.weights.env.f('meanTper',market.list[m.period],trunk.meanTper[bl.period,],norm.conf[bl.period,],0.02,2.5))

opt.w<- rbindlist(script.weights.env.f('rankTper',market.list[m.period],true.Q[bl.period,],true.conf[bl.period,],0.02,2.5))

bl.results <- unique(opt.w,by='q.id')
bl.results=bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views)][,ann.sr:=ann.ret/ann.sd]
```
# view one period ahead of market: start p = 3, ann.ret=`r bl.results[1,ann.ret]`, sr=`r bl.results[1,ann.sr]`
```{r p.viewPlus,echo=FALSE}
plot(bl.results[,cum.ret],type='l')
```

```{r viewMinus, echo=FALSE}
bl.period <- 3:(dim(trunk.meanTper)[1]-1)
m.period <- ((length(market.list)-length(bl.period))+1) : (length(market.list))

#opt.w<- rbindlist(script.weights.env.f('meanTper',market.list[m.period],trunk.meanTper[bl.period,],norm.conf[bl.period,],0.02,2.5))

opt.w<- rbindlist(script.weights.env.f('rankTper',market.list[m.period],true.Q[bl.period,],true.conf[bl.period,],0.02,2.5))

bl.results <- unique(opt.w,by='q.id')
bl.results=bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views)][,ann.sr:=ann.ret/ann.sd]
```
# view behind maket one period: ann.ret=`r bl.results[1,ann.ret]`, sr=`r bl.results[1,ann.sr]`
```{r p.viewMinus,echo=FALSE}
plot(bl.results[,cum.ret],type='l')
```

```{r ToDo,echo=FALSE}
# bl.results[,TO:=data.table(c(NA,sapply(2:42,function(b){
# beg <- setkey(opt.w[q.id==b,list(Stock,opt.w)],Stock)
# end <- setkey(opt.w[q.id==b-1,list(Stock,opt.w)],Stock)
# end[beg][,turnover.f(opt.w,opt.w.1)]})))]
# 
# 
# 
# 
# 
# all.s <- findIntersect(get(paste(ranking,'all.rankings',sep='.')),data,3)
# all.b <- findIntersect(get(paste(ranking,'all.rankings',sep='.')),data,2)
# #all.s <- intersect(intersect(intersect(dimnames(pt.all.rankings)[[3]],dimnames(eps.all.rankings)[[3]]),dimnames(data)[[3]]),dimnames(eps.all.rankings)[[3]])
# 
# #all.b <- intersect(intersect(intersect(dimnames(pt.all.rankings)[[2]],dimnames(eps.all.rankings)[[2]]),dimnames(data)[[2]]),dimnames(eps.all.rankings)[[2]])
# 
# #all.rankings <- abind(pt=pt.all.rankings[2:42,all.b,all.s,,1],eps=eps.all.rankings[,all.b,all.s,,1],along=5)
# 
# all.rankings <- abind(pt.new=get(paste(ranking,'all.rankings',sep='.'))[,all.b,all.s,,1],along=5)
# 
# accuracy <- abind(pt.new=get(paste(ranking,'accuracy',sep='.'))[,,all.s,1],along=4)
# 
# #accuracy <- abind(eps=eps.accuracy[,2:42,all.s,1],pt=pt.accuracy[,2:42,all.s,1],eps=eps.accuracy[,,all.s,1],along=4)
# 
# source('munge/bl.pre.process.R')
# source('src/bl.process.R')
```

### 2015-02-14 doc/understanding/understand-ranking.Rnw
Initial commit

\documentclass{article}
\usepackage{authblk}
\usepackage{amsmath, amssymb}
\usepackage{caption}
\captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
\captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
%\usepackage{fullpage}
\usepackage{rotating}
\usepackage{xcolor}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
\usepackage{times}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{array}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
%\onehalfspacing
\doublespace
%\geometry{a4paper}
%\usepackage[natbibapa]{apacite}
\usepackage[longnamesfirst]{natbib}

\DeclareMathOperator*{\argmax}{arg\,max}
%\newcommand{\theHalgorithm}{\arabic{algorithm}}
\DeclareMathOperator{\rank}{rank}
\newcommand{\theHalgorithm}{\arabic{algorithm}}
\newcommand{\tr}{\textit{true}}
\newcommand{\naive}{\textit{recent}}
\newcommand{\default}{\textit{all-time}}
\newcommand{\raw}{\texttt{raw}}
\newcommand{\diff}{\texttt{1diff}}
\newcommand{\random}{\texttt{random}}
\newcommand{\rollsd}{\texttt{roll.sd}}
%\newcommand{\default}{\texttt{default}}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcolumntype{Y}{>{\raggedleft\arraybackslash}X}

\begin{document}
<<include=FALSE>>=
library(knitr)
opts_chunk$set(concordance=TRUE)
@

<<load.data,echo=F,warning=FALSE,message=FALSE>>=
strategies <- c('true','recent','all-time')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
library(reshape2)
library(data.table)
library(ggplot2)
library(stringr)
library(zoo)
library(xtable)
#load('cache/q.data.RData')
#load('cache/final.bl.RData')
#load('cache/market.set.RData')
#load('cache/example.dt.RData')
load('cache/array.all.vvs.RData')
load('cache/broker.vvs.RData')
source('lib/BL-functions.R')

#library(ProjectTemplate)
#load.project()
###ADD NAs for the case of no ranking ( if NA, no raking)
split.rank <- function(r,n){
if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}        
        t <- head(r,n)
        b <- tail(r,n)
        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
}

summary.stat <- function(dt){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
}

summary.mean.stat <- function(dt,value){
  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
}

load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
# crossby = function(DT, j, by) {
#     j = substitute(j)
#     ans = rbind(
#         DT[,eval(j),by],
#         DT[,list("Total",eval(j)),by=by[1]],
#         cbind("Total",DT[,eval(j),by=by[2]]),
#         list("Total","Total",DT[,eval(j)]),
#         use.names=FALSE
#         # 'use.names' argument added in data.table v1.8.0
#     )
#     setkeyv(ans,by)
#     ans
# }
# crossby(eps.dt,length(Stock),c('Sector'))

eps.stocks <- intersect(eps.dt$Stock,dimnames(array.all.vvs)[[2]])
eps.dt <- na.omit(setkey(eps.dt[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,clean.s:=.N>=3,by=list(q.id,Stock)][(clean.s)][,q.num:=.GRP,by=q.id],Stock)[eps.stocks])
#complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
eps.stocks.rank <- intersect(complete.dt$Stock,dimnames(array.all.vvs)[[2]])

complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks.rank][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')

ind.v <- setnames(data.table(reshape2::melt(array.all.vvs[,eps.stocks,])),c('Quarter','Stock','Var','value'))

desc.ind <- acast(setnames(ind.v[,descriptive.f(value,basic=T),by=.(Var)],c('Var','Stat','value')),Var~Stat,value.var = 'value')

stat.eps <- rbind(setnames(eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),.N),by=.(Sector),.SDcols=c('Stock','Broker')],4,'Forecast'),setnames(cbind('Total',eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),Forecast=.N),.SDcols=c('Stock','Broker')]),1,'Sector'))

###per broker perspectives
# crossby = function(DT, j, by) {
#     j = substitute(j)
#     ans = rbind(
#         DT[,eval(j),by],
#         DT[,list("Total",eval(j)),by=by[1]],
#         cbind("Total",DT[,eval(j),by=by[2]]),
#         list("Total","Total",DT[,eval(j)]),
#         use.names=FALSE
#         # 'use.names' argument added in data.table v1.8.0
#     )
#     setkeyv(ans,by)
#     ans
# }

num.f.dt <- eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker,Stock)]

per.broker <- setnames(cbind(
        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N)])),
        rbind(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N)]))[,V1],
        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1)]))[,V1],
        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1)]))[,V1]),c('Sector','Forecast','Stocks','Forecast/stock','Follow time,q'))

###per stock
per.stock <- setnames(cbind(
        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N)])),
        rbind(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N)]))[,V1],
        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1)]))[,V1],
        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1)]))[,V1]),c('Sector','Forecast','Broker','Forecast/broker','Follow time,q'))

#quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])
n <- 3
#ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]

#ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
#ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
#cache('ranked.eps.dt')
load('cache/ranked.eps.dt.RData')
require(descr)
eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))

@
\title{Understanding rankings of financial analysts}
%\title{Understanding and predicting rankings of financial analysts}

 \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
 \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
 \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}

\affil[1]{FEP \& CEF.UP, University of Porto}
\affil[2]{INESC TEC}
\affil[4]{FEUP, University of Porto}

\maketitle
\begin{abstract}

Financial analysts are evaluated based on the value they create for those who follow their recommendations. Some financial institutions rank the analysts based either on the accuracy of their earnings forecasts or on the predictive power of their recommendations for future returns. Foreknowledge of rankings of analysts forecast accuracy is valuable for investors. The prediction of the most accurate analysts is typically modeled in terms of individual analyst characteristics. This approach has the disadvantage that these data are hard to collect and often unreliable. In this paper we follow a different approach in which we characterize the general behavior of rankings of analysts based upon state variables rather than individual analyst characteristics or past accuracy. We use a common learning algorithm, naive Bayes, that we adapted to address the problem of ranking the analysts.  Our results show that it is possible to model the relation between the selected variables and the rankings. To the best of our knowledge, this is the first application of label ranking to a finance problem. 
\end{abstract}

\section{Introduction}
\label{sec:introduction}

The Efficient Market Hypothesis (EHM) \citep{fama1970ecm} suggests that all public information available to investors is incorporated in prices and new information is immediately reflected in valuations. Yet, there are information gathering costs and financial analysts are better than an average investor at processing this information which reflects in issued buy/ sell recommendations.

These recommendations, like other news about the general economy as about the particular company, influence investors' perception and beliefs. Previous studies show that analyst stock recommendations have investment value. The literature suggests further that foreknowledge of analyst forecast accuracy is valuable \citep{brown2003}. In line with academic research findings, practitioners too pay attention to analyst forecast accuracy rankings. On an annual basis, firms such as The Institutional Investor and StarMine \footnote{http://www.starmine.com} publish analysts ratings according to how well they performed, based partly on past earnings forecast accuracy.

The importance of these ratings should not be ignored because the attention that the market gives to the recommendations of different analysts is expected to correlate with them. Typically, the performance of analysts is analyzed in terms of their individual characteristics (e.g., experience, background) \citep{clement1999}. The disadvantage of this approach is that the collection of the necessary data is difficult and it is not always reliable. As for practitioners, they rely mostly on past accuracy to predict future accuracy. In this paper we follow an alternative approach. We characterize the general behavior of rankings of analysts using variables that characterize the context (e.g., the company in the period of interest) rather than individual analyst characteristics or past accuracy. The model we propose uses predictor variables to distinguish between more and less accurate analyst/company forecasters in different states of the world. The latter kind of data is easier to obtain (e.g., from Thomson Reuters\footnote{http://thomsonreuters.com/}) and is quite reliable. In summary, our goal is not to understand  relative performance of the analysts  in terms of their characteristics but rather in terms of the characteristics of the context in which the analysts operate.

We address the problem as a label ranking task, which recently has been receiving an increasing attention in the Machine Learning and Data Mining literature (e.g. \citep{hullermeier,cheng2009}). In label ranking problems,  the goal is to predict an ordering of a finite set of labels \citep{vembu2009}. In our case, the labels are the analysts and the rankings reflect their relative forecasting accuracy.  We choose to use a simple algorithm, naive Bayes for ranking \citep{aiguzhinov2010}.

The paper is organized as follows: section \ref{sec:ranking} provides the motivation for ranking the analysts; section \ref{sec:labelranking} sets up the label ranking problem and introduces the algorithms for label ranking; section \ref{sec:data} describes the datasets used for the experiments, while section \ref{sec:results} presents and discusses the results; finally, section \ref{sec:conclusion} concludes this paper.

\section{Ranking the analysts}
\label{sec:ranking}

In the finance literature there has been a long debate over the possibilities that financial analysts produce valuable financial advises. Some argue that following the advises of financial analysts projected as recommendations of buy, hold, or selling a particular stock, does not yield an abnormal return. This is consistent with EMH that states financial markets are informational efficient implying that it is not possible to implement a successful trading strategy based upon analyst stock recommendations given that the underlying information would be already reflected in the current stock prices.

The study of \cite{grossman1980iie} argues that, indeed, the point of \cite{fama1970ecm} holds and that it is likely that the markets are efficient; however, there are  information costs and the reflection of the information in the current stock prices is  not immediate as theory suggests. Due to these costs, prices cannot perfectly reflect the information which is available, since if they did, those who spent resources to obtain it would receive no compensation. Later, \cite{fama1991ecm} supports this argument.

The possibility of obtaining abnormal returns spilled out to uncountable different trading strategies over the last 50 years based upon anomalies or deviations to market efficiency. Almost all these trading strategies have one goal in common: predict future returns relying on historical prices or company characteristics. Not only there is a lot of controversy on predictability results but also many of the proposed strategies are rather difficult to implement by an average investor. The obvious alternative is to follow the recommendations of the professionals in the field, such as stock analysts or asset managers. We assume that following the best analysts is the best choice for an investor

The question of whether stock analyst recommendations bring value to investors has been around since the mid-90s. \cite{womack1996} acknowledged that there is a positive benefit for investors from following recommendations of the analysts.
More recently, \cite{jegadeesh2004} suggest that only the subset of favorable recommendations has predictive power of future market returns and that the level of analyst recommendations (buy/sell) derives part of its predictive power to the fact that analysts select stocks with particular characteristics that are associated with higher returns.

Assuming that stock analyst recommendations, on average, do create value to investors \citep{womack1996,barber2001}, it is possible to create rankings of the analysts based on their forecasting accuracy or predictive power of future returns. In fact, StarMine\textsuperscript{\textregistered}
does exactly this: it ranks analysts on an annual basis and publishes the rankings worldwide. 
StarMine ratings serve to the benefits of the analysts in the areas of personal reputation, prestige, and compensation. These ratings may also affect how markets react to recommendations and a top-ranked analyst publishes a research report it is expected to have a greater effect than one who is ranked lower.

The StarMine ranking methodology is based on the analysts performance. This performance is measured by comparing the non-leveraged portfolio for each analysts based on his/her recommendations. The portfolio is constructed as follows. For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark \footnote{Comparable index}. ``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark. ``Holds'' invest one unit in the benchmark (i.e., for an excess return of zero). Sell are the reverse. StarMine re-balances its calculations at the end of each month to adjust for when an analyst changes his or her mind (by adding, dropping or altering a rating) or when a stock enters or exits an industry grouping.

StarMine also ranks the analysts based on the accuracy of the earnings forecasts. For that, StarMine developed a proprietary metric called Single-stock Estimating Score (SES). It measures the relative accuracy of each analyst's earnings when compared against their peers. 
The score from this metric ranges from 0 to 100, with 50 representing the average analyst. To get a score higher than 50, the analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates.

The value of rankings such as StarMine Ratings for investors is arguable given that these are ex-post and a good analyst on one year does not necessarily make equally good recommendations in the following year. However, if one could predict the ranking of analysts ahead of time (even if with some estimation error) then it would be possible to create a successful trading strategy. \cite{brown2003} show that foreknowledge of analyst forecast accuracy is indeed valuable.

Existing approaches to predict the future performance of the analysts are based on analysts' individual characteristics \citep{clement1999} and their past accuracy \citep{brown2001}. In this paper we follow a different approach in which we predict the rankings of the financial analysts based upon state variables.\footnote{The implementation of the predicted results into a trading strategy is out of scope of this paper.}

\section{Label ranking}
\label{sec:labelranking}

Based on \cite{vembu2009}, a label ranking problem is defined as follows. Let $\mathcal{X} \subseteq \{\mathcal{V}_1,\ldots,\mathcal{V}_m\}$ be an instance space of nominal variables, such that $\mathcal{V}_a=\{v_{a,1}, \ldots, v_{a,n_a}\}$ is the domain of nominal variable $a$, containing $n_a$ different values.  Also, let $\mathcal{L} = \{\lambda_1,\ldots,\lambda_k\}$ be a set of labels, and $\mathcal{Y} = \Pi_{\mathcal{L}}$ be the output space of all possible total orders \footnote{A total order is a complete, transitive, and asymmetric relation $\succ$ on $\mathcal{L}$, where $\lambda_i \succ \lambda_j$ indicates that $\lambda_i$ precedes $\lambda_j$. In this paper, given $\mathcal{L}=\{A,B,C\}$, we will use the notation $\{A,C,B\}$ and $\{1,3,2\}$ interchangeably to represent the order $A \succ C \succ B$.}  over $\mathcal{L}$ defined on the permutation space $\Pi$. The goal of a label ranking algorithm is to learn a mapping $h: \mathcal{X} \rightarrow \mathcal{Y}$, where $h$ is chosen from a given hypothesis space $\mathcal{H}$, such that a predefined loss function $\ell: \mathcal{H} \times \mathcal{Y} \times \mathcal{Y} \rightarrow \mathbb{R}$ is minimized. The algorithm learns $h$ from a training set $\mathcal{T}=\{x_i,y_i\}_{i \in \{1, \ldots, n\}} \subseteq \mathcal{X} \times \mathcal{Y}$ of $n$ examples, where $x_i = \{x_{i,1}, x_{i,2}, \ldots, x_{i,m} \} \in \mathcal{X}$ and $ y_i = \{y_{i,1}, y_{i,2}, \dots, y_{i,k}\} \in \Pi_{\mathcal{L}}$. Furthermore, we define $y_i^{-1} = \{y_{i,1}^{-1}, y_{i,2}^{-1}, \ldots, y_{i,k}^{-1}\}$ as the order of the labels in example $i$. Given that we are focusing on total orders, $y_i^{-1}$ is a permutation of the set $\{1, 2, \ldots, k\}$ where $y_{i,j}^{-1}$ is the rank of label $\lambda_j$ in example $i$.

To assess the accuracy of the predicted rankings relative to the corresponding target rankings, a suitable loss function is needed. In this paper we compare two rankings using the Spearman correlation coefficient \cite{brazdil2003,vembu2009}:
\begin{equation}
\label{eq00}
 \rho(\pi,\hat{\pi})=1-\frac{6\sum_{j=1}^k(\pi_j-\hat{\pi}_j)^2}{k^3-k}
\end{equation}
where $\pi$ and $\hat{\pi}$ are, respectively, the target, or ``true'', ranking that is known ex-post  and predicted rankings for a given instance.\footnote{ In the following, we will use $y_i$ and $\pi_i$ interchangeably to represent the target ranking.} Figure ~(\ref{fig: timeline}) shows the time line relation between the predicted and the target rankings. We use all information available up to time $t-2$ for training data and for the independent variables. At $t-1$, we generate a new training example given new information available at time $t-1$. We apply label ranking algorithm on this updated training example and generate a ranking model which outputs the predicted rankings for period $t$. At time $t$, we measure accuracy of the predicted rankings $\hat{\pi}$ against the true one $\pi$ by applying equation ~ (\ref{eq00}).

The interpretation of the coefficient values is simple. Two orders with all the labels placed in the same position will have a Spearman correlation of $+1$. Labels placed in reverse order will produce  correlation of $-1$. Thus, the higher the value of $\rho$ the more accurate the prediction is compared to target. The loss function is given by the mean Spearman correlation values (eq. \ref{eq00}) between the predicted and target rankings, across all examples in the dataset:

\begin{equation}
\label{loss}
 \ell=\frac{\sum_{i=1}^n \rho(\pi_i,\hat{\pi}_i)}{n}
\end{equation}
An extensive survey of label ranking algorithms is given in \cite{vembu2009}.

Here we address the problem using an adaptation of naive Bayes for label ranking \citep{aiguzhinov2010} (see Appendix).

The naive Bayes label ranking algorithm relies on the similarity  among rankings. Suppose we have  artificial data for 6 quarters and rankings of 3 brokerage firms  for each of  quarter. Also assume that we identify some independent variables $x_1 \ldots x_4$ that we think are responsible for the rankings in a given quarter. Table \ref{tab01} summarizes the example.

When looking at rankings, we observe that there are instances with the equal rankings (such as quarters $\{1,3,5\}$ and quarters $\{2,6\}$). Thus, the occurrence of $\{1,2,3\}$ is more frequent (three times) than the occurrence of $\{2,3,1\}$ (twice). Moreover, the fact that the ranking of quarter 4 is similar to the one of quarter 3 intuitively increases the similarity of the latter. For the same reason, the similarity of the ranking of quarter 4, which appears only once, is also increased by the existence of similar rankings in quarters 1, 3 and 5. Based on this reasoning, we assume that the average correlation of a ranking to a set of other rankings is a measure of its similarity and can be used in substitution of the probabilities in naive Bayes for label ranking. A similar logic can be applied in defining the conditional rankings. For example, for variables $x_1$ and its value \textit{High} we have three rankings with the most frequent occurrence of rankings $\{2,3,1\}$. Thus, this ranking has a higher similarity of appearance under condition of $(x_1|High)$. A detailed formalization of the algorithm is provided in the Appendix.

\section{State variables}

Studies by \cite{clement1999}, \cite{brown2003}, \cite{jegadeesh2004}, all try to analyze  factors that affect the performance of the analysts.  However, most these papers look at the individual characteristics of analysts such as their job experience, their sources of affiliation,  industry specializations. Despite that these variables are reasonable choices in explaining the errors in analysts forecasts, they explain the individual analysts' characteristics. We focus our research on the analysis of the analysts that work in the same informational environment and try to answer the fundamental question: given the consistency in  performance of the  analysts covering the same stock, what analysts should we follow? That is, we want to predict the relative performance of the analysts using only broker-,  firm-, industry-specific and economy-wide variables.

\subsection{Broker-based variables}
Following \cite{clement1999,clement2003,brown2001}, we select the following broker-specific variables.
\begin{itemize}
\item Consensus forecast of brokers;
\item  Revision of forecasts of brokers;
\end{itemize}
Consensus forecast can be a proxy of tendency of analysts to use forecast made by other brokers (herding). Revision of the forecasts can test the level of specialty of the brokers for the given industry/stock. The deviation from the mean revision can serve as a proxy of degree of specialty.

\subsection{Firm-based variables}

In essence, ranking means that there are differences in opinion among the analysts.  This fact implies that there is  a dispersion in the analysts' forecasts for a given stock \citep{diether2002}. Thus, we can analyze  the analysts forecasts' dispersion in terms of its origin and factors that affect it; hence, assuming the same variables affect the rankings.
The financial literature on analysts dispersion identifies two sources of its origin: uncertainty about the future of a firm  and information asymmetry between the managers of a firm and the investors \citep{barron1998,barron2009}. We propose to identify the variables affecting the dispersion of the analysts in line with these two concepts.

\subsubsection{Uncertainty}

\paragraph{Business risk.} Business risk is associated with the uncertainty in operating results, especially, in operating earnings \citep{hill1980}. An increase in business risk entails an increase in ex ante volatility of the reported earnings \citep{parkash1995}. \cite{parkash1995} propose to use two indicators to measure business risk. First, is the standard deviation of the market return on the firm's unlevereged equity. Second, is the variability of the accounting returns before interest and taxes. We think that  book-to-market ratio can serve as a proxy for the business risk measurement.

\paragraph{Financial risk.} Financial risk is also responsible for the uncertainty in the future earning of a stock. More debt implies more variability in earnings as managers would try to maximize the value of a stock using the debt; thus, having the risk of the default in the future or taking high risk investment projects.

\cite{parkash1995} suggest to use two indicators of the financial risk. One is the debt-to-equity ratio \emph{DE} and inverse of interest coverage ratio. We select \emph{DE} ratio to as measure of the financial risk.

\paragraph{Size.} The firm size can be used as a proxy for amount of information available for a firm (larger firm - more information). Thus, larger firm has more news coverage which reduces uncertainty. \cite{bhushan1989} argues that an investor is likely to find private information about larger firm more valuable than the same information about smaller firm.

Size is measured as the market value (MV) of the firm as following:
\begin{equation}
\mathrm{MV}= \log(\mathrm{PRICE} \times \mathrm{STOCKS})
\end{equation}
where \emph{PRICE}  is the stock price at the end of the quarter and \emph{STOCKS} is the number of stock outstanding. Consistent with the literature, we use log of market value.

\paragraph{Return variability.}
Return variability influence the uncertainty regarding future earnings \citep{henley2003, diether2002}. An increases in variability of the abnormal returns is positively correlated with the uncertainty about the earnings; thus, affecting the dispersion among the analysts. To calculate the return variability, we use method provided in \cite{sousa2008}, where stock return volatility is decompose into market and stock specific components as follow:
\begin{eqnarray}
Var (R_{it})&=&\sigma^2_{mkt}+\sigma^2_{i} \\
\sigma^2_{mkt}&=&\sum_{s\in t} (R_{ms}-\mu_{m})^2 \nonumber \\ 
\sigma^2_{i}&=&\sum_{s \in t} (R_{mt}-R_{it})^2 \nonumber
\end{eqnarray}
where $R_{ms}$ is the market return over sample period; $\mu_{m}$ is the daily mean of $R_{ms}$; $s$ is the number of trading days in period $t$.

\subsubsection{Information Asymmetry variables}

\paragraph{Accruals.} 
Accruals, as a part of  earnings, is one of the variables that cause the information asymmetry between managers of a firm and investors. Studies have shown that presence of asymmetry is a necessary condition for the earnings management \citep{trueman1988,richardson2000}. To be more specific, it is the discretionary part of the accruals that causes  the information inefficiency  in the earnings management \citep{richardson2000,ahmed2005}.

\paragraph{R\&D expenses.}
Another variable that contributes to the problem of information asymmetry is the R\&D expense. \cite{aboody2000} state that these R\&D activities contribute substantially to the information asymmetry between managers and investors.

Due to data constrains, we select only Accruals as  the independent variables. We calculated total accruals-to-total assets ratio defined in \cite{creamer2009}:

\begin{eqnarray}
TA=\frac{\Delta C.As._q - \Delta Cash_q - (\Delta C.Lb._q - \Delta C.Lb.D_q) - \Delta T_q - D\& A_q}{(T.As._q - T.As._{q-4})/2}
\end{eqnarray}
where $\Delta X_q=X_q-X_{q-1}$; C.As - current assets; C.Lb - current liabilities; C.Lb.D - debt in current liabilities; T - deferred taxes; D\&A - depreciation and amortization; and T.A - total assets.

\subsection{Sector-based variables}
The industry specific variables that cause the dispersion in the analysts' forecasts are connected  with the uncertainty concept. One of the variables that is suggested to capture is the variability in the industry Producer Price Index (PPI) \citep{henley2003}.

\subsection{Macroeconomics variables}
We select a set of the macroeconomic variables  to capture the state of the world. The variables are: 
%As far as the economy-wide variables is concerned, \cite{elton1984} state that these variables contribute least to the errors in analysts forecasts. They report that by decomposing the errors into firm-specific, industry-specific, and economy-wide components, the percent of errors that were related to  economy-wide information was least of all three components of errors. On average, forecasts  errors associated with misinterpreting the economy-wide information were about 2.5\%, industry-specific errors were 25\%, and firm-specific were 70\%.  Nevertheless, I will include some of the variables that are concern with the uncertainty in the economy. 
\begin{itemize}
\item Gross National Product (GNP);
\item Inflation rate;
\item Interest rate (90-days T-bill rate);
\item Market variability (CBOE VIX index)
\end{itemize}
\cite{lev1993} look at different state of the economy based on  different levels of GNP--inflation combinations. They found that when economy is booming, i.e. high GNP-low inflation state, they observed the significant increase in firms' Capital Expenditures coefficient. This implies that firms start enjoy capital investment due to the low cost of capital. This state of the economy produces less uncertainty. In the medium GNP-high inflation state of the economy  \cite{lev1993} report high R\&D expenditures, which, from the above mentioned analysis, may spur high level of information asymmetry based on the increase R\&D activities. Finally, in the low GNP-high inflation state, they observe the Doubtful Receivables coefficient is the largest implying that at this recession state many firms go bankrupt or default on the loans -- a signal of high uncertainty in the economy. All these states produce the dispersion of the analysts forecasts.

\section{Data and experimental setup}
\label{sec:data}
Independent variable data obtained from ThomsonReuters Database and Datastream. The descriptive statistics presented in tabel (\ref{tab:ind.vvs}).

We constructed rankings of analyst earnings forecast accuracy.\footnote{An alternative proxy to evaluate analyst predictive ability would be the correlation between analyst recommendations and future stock returns. To do so, we would have to assign standardized numerical ratings to recommendations (strong buy, buy, hold, sell, strong sell) in a similar way as it is done by Zacks Investment Research.}
We selected companies that are publicly traded in either NYSE, NASDAQ, or AMEX. The accounting data was obtained from the Thomson One/Reuters Fundamental database. We also obtained the data from I/B/E/S of all earnings per share forecasts ever made by an analyst\footnote{We use words ``analyst''  even-though the database is for brokerage houses.}  for each company at study.

We apply a number of requirements for our data. We select stocks with at least one broker has at minimum 12 quarters of experience in covering this stocks. In addition, for the computational purpose, we need at least 3 brokers per stock in each quarter.  We call this set of brokers as ``core" brokers: we believe they are  the ones that have specialty in a particular stock. \cite{stickel1995} finds that recommendation changes of star analysts have a greater impact and \cite{fang2008aso} also confirm that they are profitable. Thus, it seems to be the case that only a subset of analysts (not the consensus) influence prices and, as such, only that subset of brokers deserves to be followed. In total we have 244 unique brokers covering 1775 stocks during 84  quarters from 1Q1989 until 4Q2009. For calculations of market variability we use daily prices of S\&P 500.

Table ~(\ref{table:forecasts-broker}) presents the break down by sector of the forecasts issued per quarter.  Panel A shows averages form the broker perspective. As we observe, on average, for all sectors, in each quarter there were 27 forecast per broker. Each of these brokers would issue 2.75 forecasts per stock and each broker would follow a stock for 11 quarters. Panel B shows same statistics but from the stock perspective.  On average, in each quarter a stock would get 14.66 forecasts from 4.41 brokers. Per quarter, a stock would get 2.6 forecasts per broker and a stock would have a coverage life of 12 quarters.

Figures (\ref{mean-f}) depict some per quarter dynamics. %We should note that the  small mean values corresponding to the beginning of the sample period may be attributed to the absence of the corresponding data in the I/B/E/S database rather than representing the reality. Further investigation is required to clarify this issue.

%The nature of the naive Bayes algorithm requires that the independent variables should be ``converted'' from continuous flow (numerical) into discrete, or symbolic, state.  There are different ways of performing  this discretization \citep{dougherty1995}.  We chose the equal size bins method which is given in \cite{dougherty1995}. The width of the bin is computed as:
%\begin{equation}
%\label{eq:bins}
% \delta=\frac{a_{max}-a_{min}}{k}
%\end{equation}
%where $a_{max}$ and $a_{min}$ are maximum and minimum values of the variable $a$ and $k$ is the number of bins. The  value of $\delta$  used to create bins applyingis $a_{min} + \delta i$, where $i=1 \ldots k-1$.  We assign the symbolic values based on the position of the discretization interval relative to $a_{min}$ and $a_{max}$. For example, the interval of $a_{min}+ \delta$ we call ``Low''. We discretized all variables into four bins.

\subsection{Target  rankings of analysts}
Prior to address the problem of predicting the rankings of the analysts, it is important to create the target rankings $y_i$, which the approach described here will try to predict. They are the ``true'' rankings in the sense that they are calculated ex-post based on one of the analysts' performance evaluation models \citep{clement1999,brown2001,creamer2009}. In this paper, the target rankings of analysts are based on the Proportional  Mean Absolute Forecast Error (\textit{PMAFE}) that measures the forecast accuracy \citep{brown2001}. If we define the  Forecast Error  (FE) as an absolute value of the difference between I/B/E/S actual quarter earnings of a stock and the latest forecast made by an analyst for that quarter: 
\begin{equation}
\mathrm{FE_{q,a,s}}=|\mathrm{ActEPS_{q,s}}-\mathrm{EPS_{q,a,s}}|
\end{equation}
where $q$ is a quarter, $a$ and $s$ are the analysts and stocks indexes, then consensus forecast error is given by:
\begin{equation}
\mathrm{\overline{FE_{q,s}}}=\frac{1}{n}\sum_{a=1}^n \mathrm{FE_{q,a,s}}
\end{equation}
where $n$ is the number of analysts in a given quarter

PMAFE is given as:\footnote{The rankings that are commonly used by $\mathrm{FE}$ and $\mathrm{PMAFE}$ are the same. The latter is more common in the literature where OLS methods in regression analyses require normalization of the data.}
\begin{equation}
\mathrm{PMAFE_{q,a,s}}=1+\frac{\mathrm{FE_{q,a,s}}-\mathrm{\overline{FE_{q,s}}}}{\mathrm{\overline{FE_{q,s}}}}=\frac{\mathrm{FE_{q,a,s}}}{\mathrm{\overline{FE_{q,s}}}}
\end{equation}
To rank the analysts based on their PMAFE, we scaled these values by adding 1 so that those analysts who made an absolute match of EPS forecast with actuals values (PMAFE=0) would receive a higher rank. In case the analysts does not issue a forecast in the subsequent quarters, we do not roll over her previous forecasts.

An analyst that follows one stock, does not necessarily issue forecast every quarter. Therefore, the question is how to evaluate a predicted ranking in this case. For instance, when the ranking \{John, Brown, Smith\} is predicted and then Brown does not make a forecast during the corresponding quarter. In this case, we assume that the investor will simply ignore the forecast. Therefore, when evaluating the accuracy of a predicted ranking, we remove all analysts that have not made EPS forecasts during the corresponding quarter

We perform a simple analysis of the target rankings. Specifically, we compare the composition of top $n$ and last $n$ brokers on quarter-to-quarter basis. Table (\ref{tab:top}) shows the composition of top and bottom rankings at period $t$ 
compared to top and bottom rankings at period $t-1$.  We find that at period $t$, the top $n$ rankings consists of both: the  brokers that stayed in top $n$ rankings of period $t-1$  and the brokers that were in last $n$ rankings at $t-1$. That is, period $t$ top rankings have, on average, an equal proportion of the brokers that stayed in the top rankings and the ones that moved from the last rankings to top rankings.

The same analysis of the last $n$ rankings reveal somewhat different behavior. We find that period $t$ bottom rankings,  on average, consists mostly from the brokers that were in the last rankings at period $t-1$ and less from the brokers from top ranks at $t-1$. That is, top broker of period $t-1$, on average, do not move to the bottom ranks at period $t$. The outcome of this analysis reveal that there is a strong consistency of the brokers that are in the top ranks. These brokers tend to stay on top from quarter to quarter. The bottom ranks are not as consistent as the top ones as these brokers can move to the top ranks or stay in the last positions.

\section{Experimental setup}
\label{sec:exp_setup}

Given that the data are ordered in time, we estimate the accuracy of the methods using a growing window approach. When predicting the ranking for quarter $q$, the training set consists of the data for all quarters $i \in 1 \ldots q-1$. We consider timing in rankings; that is, the algorithm gives more weight to the most recent rankings and less weight to the old ones.

To test whether our approach is identifying meaningful patterns in the data, we compare it with simple baseline methods. The first baseline method is based on the mean rank of each label over all training examples \citep{brazdil2009}.

\begin{equation}
\label{default.rank}
\hat{\pi}^{-1}_{j} = \frac{\sum_{i=1}^n \pi^{-1}_{i,j}}{n}
\end{equation}
where $\pi^{-1}_{i,j}$ is the rank of label $\lambda_j$ on dataset $i$. The final ranking is obtained by ordering the mean ranks and assigning them to the labels accordingly. This ranking is usually called the \emph{default ranking}, in parallel to the default class in supervised classification \citep{mitchell1997}.

The second baseline method that we compare our predicted rankings is to simply  take  the rankings from the previous quarter. That it, use rankings from past quarter $\pi_{q-1}$ as prediction of the rankings for  the current quarter $\hat{\pi}_q$:

\begin{equation}
\label{naive:ranking}
\hat{\pi}_q=\pi_{q-1}
\end{equation}
We call this baseline method the \emph{naive ranking}. The accuracy of the methods is measured using Spearman's rank correlation coefficient (Eq.~\ref{eq00}) as is done for the naive Bayes ranking method.

The independent variables are fed into the predicting algorithm with three different methods of aggregation. As we have mentioned above, we want to capture the state of the world in which the analysts operate. For this reason, it is necessary to take into account the dynamics of independent variables from one time period to another. We call this an aggregation of the independent variables and we propose the following methods:
\singlespace
\begin{itemize}
\item \raw: no dynamics in the state of the  variables, i.e. independent variables used as they are --- $x_t$;
\item  \diff: first-differencing  of the variables,i.e., $x_{\Delta{t}}=x_t-x_{t-1}$;
\item  \random: using random part of the time series decomposition of the independent variables for the previous 8 quarters: $x_{\Delta{t}}=T(t)+S(t)+\epsilon (t)$, where $T(t)$- trend, $S(t)$ - seasonal part and $\epsilon (t)$ - the random part of time series; 
\item  \rollsd: rolling 8 quarters standard deviation of the independent variables;
\end{itemize}
\doublespace
Obviously, each of these methods produce its own predicted rankings; that is why, we will have four sets of evaluation values in addition to the two baselines.

 %We also perform a significance test using Student p-values for pairs of $\rho$ obtained using Eq.(\ref{eq00}). The first pair to test the significance in differences is $(\rho_{NBr}; \rho_{default})$ and second  is  $(\rho_{NBr}; \rho_{naive})$.

\section{Results}
\label{sec:results}

%

%\subsection{Predictive ranking accuracy of naive Bayes for  label ranking}
We start by analyzing the accuracy of the naive Bayes for ranking  $NBLR(t)$ on  the datasets tested here and discuss if it possible to predict the rankings

Applying equation of a loss function (\ref{loss}), the average ranking accuracy of  predicted rankings, measured as a correlation between predicted rankings (\raw{}, \diff{}, \random{}, \rollsd{}, \default{}, \naive{}) and \tr{} rankings,  is reported in Table (\ref{stat:acc}). We observe that, on average, the naive Bayes for label ranking consistently outperforms both of the baselines. This implies that the algorithm is able to identify the pattern in the data that produce the positive outcomes in the prediction. The result also suggests that the \naive{} prediction is not the best guess of the rankings;  moreover,  the state variables are responsible for the relative performance of the brokers.

The detailed analysis of the table (\ref{stat:acc}) shows that the \rollsd{} method has the highest average accuracy compared to other methods. This means that the dynamics of the state of the world for the previous two year can be responsible for the rankings of the brokers. Table (\ref{stat:acc:time})  and figure (\ref{fig: acc.time}) present the average annual accuracy for each of the methods on the annual basis. We observe the best performance of \rollsd{} method for the all period except for 2009. We suggest that this behavior has to do with the crisis of 2008. The downward trend of the accuracy is attributed to the ``growing window'' approach in treating the historical rankings, i.e., for training the algorithm we use all available rankings since the beginning of the dataset. An alternative will be to use the ``sliding window'' approach where old rankings are discarded from the model based on the specified period of time (window).

% At this level of aggregation, we  observe that most sectors exhibit a non-negative ranking accuracy.  
% However, given the fact that the means of two baselines methods are all close to zero,  there is plenty room for improvement by using the machine learning method. Moreover, as shown in figures (\ref{diff-ac}) and (\ref{diff-naive}), which demonstrate the differences in ranking accuracy of the NBr predicted rankings and the rankings calculated using baselines methods, there are cases where NBr was able to outperform the baselines (the circles  that are above $x=0$). This demonstrates that the NBr   is able to find patterns in the context of a company that relate the rankings of financial analysts.

%We assess the ranking accuracy of NBr relative to the default and naive rankings.  Table  \ref{table:results-default} demonstrates the summary of the results aggregated by sectors when compared to the default ranking baseline. If we define a \emph{win (loss)} as a stock in which the naive Bayes ranking method obtained higher (lower) ranking accuracy than the baseline then, the wins/loss rate is the ratio of the number of wins/losses to the total number of stock in the sample. We observed  0.40 wins rate for all stocks in the sample. Additionally, we observed that this value ranges from 0.38 to 0.46 in different sectors. This means that the method is able to outperform the default baseline in many stocks in all sectors.

%Table \ref{table:results-naive} presents the summary of the experiments compared to the second baseline which is naive rankings. We observe a decrease in the wins rate (0.37) when compared to the default ranking baseline (0.40). The number of wins with significant correlation values is also decreased dramatically for some of the sectors.  It should be noted that the two methods are not really comparable. The NBr does not take into account time (e.g., by giving more weight to the most recent rankings), unlike the naive baseline, which uses the ranking of the analysts at a given quarter as a prediction for the following quarter. We plan to adapt the NBr to take time into account in the near future.

%In summary, these results show that the method is able to find patterns in the context of a company that relate the ranking of financial analysts on a significant number of stocks. However, it is also true that there is still plenty room for improvement, which is not surprising given that this is a first attempt at this type of approach. We believe that this can be achieved by improving the predictor variables.

%\subsection{Predictive accuracy of naive Bayes for  label ranking}
%\subsection{The most discriminative values}
%
%Our model relates several state variables to the rankings of analysts. However, not all of them are expected to have the same or similar influence on those rankings. In other words, we expect that some variables explain the rankings better than others. We may say that the most discriminative variables describe the state of the market according to characteristics that affect the relative performance of analysts the most. However, this interpretation should be done carefully, as these patterns do not represent causal relations. It may be the case that they serve merely as proxies to other variables which are the ones that really affect the behavior of analysts.
%
%
%To calculated the discriminative power of the state variable, we start with the matrix of ranking similarity correlation  (see appendix) and find the average of the similarity correlations between each of the discretized bins. In total, we will have 6 averages because we have 4 bins and that produces 6 unique pairs. The intuition behind calculating the averages of  6 combinations is to see how the rankings change while the value of the state variable moves from one discretized bin to another. We, then, weight mean of each pair by the distance between bins. For example, if we have 4 discretized bins and assign letters $a$ through $d$ from the smallest to the largest intervals, the weighting factor  between bins $a$ and $b$ would be one, between $a$ and $c$ would be two, and so forth.  Averaging the averages of 6 weighted combinations will aggregate the discriminative power of the discretized bins to the level of discriminative power of the state variable. 
%
%% Table ~\ref{mdv} shows the summary of the sectors with the most discriminative power. We observe that the most discriminative variable for 3 sectors (Energy, IT, and Materials) is the \textit{Change in Consensus}. As this variable serve as control variable, we say that there is a correlation between changes in EPS consensus values and the relative analysts' accuracy in EPS forecast. In fact, this finding goes in line with the significant body of literature studying the behavior of the analysts (e.g. herding \citep{clement1999,welch2000}, social networking among analysts \citep{creamer2009}) where  consensus is one of the independent variable. The Industrial sector identifies  \textit{Accruals} as the most discriminative variable which can affect the accuracy of the earnings forecast and be responsible for variations in rankings of the analysts \citep{sloan1996,bradshaw2001} .

\section{Conclusion}
\label{sec:conclusion}
Some institutions, such as StarMine, rank financial analysts based on their accuracy and investment value performance. These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors. Therefore, there is a growing interest in understanding the relative performance of analysts. Typical approaches are based on individual characteristics of those analysts or past analyst forecasting accuracy. Here, we follow an alternative approach that links the general behavior of rankings of analysts to variables such as consensus statistics and company characteristics.

%The problem is tackled with a label ranking methodology, employing the naive Bayes ranking algorithm. The models obtained achieved better results than the default ranking and the naive ranking baselines on 40\% and 37\% of the stocks, respectively. These successful rates demonstrate that it possible to predict the rankings using the naive Bayes algorithm for label ranking.

The proposed method of predicting the rankings produced  results that outperformed simple  baselines. In addition, the algorithm identified that deviations of the independent variables are responsible in explaining the rankings of the brokers. The positive results of this study can attribute for the future research in the area of finding the relation between the state of the world and the performance of the brokers as well as  in the area of developing a trading strategy based on the predicted rankings.

\singlespace
\bibliographystyle{newapa}
\bibliography{/Users/aiguzhinov/Dropbox/Documents/Bibliography/rank}
\doublespace

%\appendix
%\appendixpage
%
%\section*{Naive Bayes for label ranking}
%\label{sec:naivebayes}
%
%In classification, each instance $x_i\in\mathcal{X}$ is binded to class $y_i\in\mathcal{L}$. The task of a learner is to create a classifier from the training set $\mathcal{T}$.The classifier takes a new, unlabelled instance and assigns it to a class (label). 
%
%The naive Bayes method classifies a new instance $x_i$ by determining the most probable target value, $c_{MAP}(x_i)$\footnote[4]{$MAP$ -- Maximum A Posteriori}, given the attribute values that describe the instance:
%\begin{equation}
%\label{eq01} 
%c_{MAP(x_i)}= \argmax_{\lambda \in \mathcal{L}} P(\lambda|x_{i,1}, x_{i,2}, \ldots, x_{i,m})
%\end{equation}
%where $x_{i,j}$ is the value of attribute $j$ for instance $i$.
%
%The algorithm is based on the  Bayes theorem that establishes the probability of $A$ given $B$ as:
%\begin{equation}
%\label{eq04}
% P(A|B)=\frac{P(B|A)P(A)}{P(B)}
%\end{equation}
%Thus, the Bayes theorem provides a way to calculate the posterior probability of a hypothesis.
%
%Using (\ref{eq04}), we can rewrite (\ref{eq01}) as 
%\begin{align}
%\label{eq02}
% c_{MAP(x_i)}= \argmax_{\lambda\in \mathcal{L}} \frac{P(x_{i,1},x_{i,2}, \ldots, x_{i,m}|\lambda)P(\lambda)}{P(x_{i,1},x_{i,2}, \ldots, x_{i,m})} \notag \\
%=\argmax_{\lambda\in \mathcal{L}} P(x_{i,1},x_{i,2} \ldots x_{i,m}|\lambda)P(\lambda)
%\end{align}
%
%Computing the likelihood $P(x_{i,1}, x_{i,2}, \ldots, x_{i,m}|\lambda)$ is very complex and requires large amounts of data, in order to produce reliable estimates. Therefore, the naive Bayes classifier makes one simple, hence, naive, assumption that the attribute values are conditionally independent from each other. This implies that the probability of observing the conjunction $x_{i,1},x_{i,2},\ldots,x_{i,m}$ is the product of the probabilities for the individual attributes: $ P(x_{i,1},x_{i,2}, \ldots, x_{i,m}|
%\lambda)=\prod_{j=1}^m P(x_{i,j}|\lambda)$. Substituting this expression into equation (\ref{eq02}), we obtain the naive Bayes classifier:
%\begin{equation}
% \label{eq03}
% c_{nb}(x_i)=\argmax_{\lambda\in \mathcal{L}} P\left(\lambda\right)\prod_{j=1}^m P\left(x_{i,j}|\lambda\right)
%\end{equation}
%
%To adapt NB for ranking we have to adapt the parts of the algorithm that depend on the target variable, namely:
%\begin{itemize}
%\item prior probability, $P(y)$
%\item conditional probability, $P(x|y)$ 
%\end{itemize}
%
%
%Similarity and probability are different concepts and, in order to adapt NB for label ranking based on the concept of similarity, it is necessary to relate them. A parallel has been established between probabilities and the general Euclidean distance measure \cite{vogt2007}. This work shows that maximizing the likelihood is equivalent to minimizing the distance (i.e., maximizing the similarity) in a Euclidean space.  Although not all assumptions required for that parallel hold when considering distance (or similarity) between rankings, given that the naive Bayes algorithm is known to be robust to violations of its assumptions, we propose a similarity-based adaptation of NB for label ranking.
%
%
%In the following description, we will retain the probabilistic terminology (e.g., prior probability) from the original algorithm, even though it does not apply for similarity functions. However, in the mathematical notation, we will use the subscript $_{LR}$ to distinguish the concepts. Despite the abuse, we believe this makes the algorithm easier to understand.
%
%We start by defining $\mathcal{S}$ as a similarity matrix between the target rankings in a training set, i.e. $\mathcal{S}_{n \times n}=\rho(\pi_i,\pi_j)$. The prior probability of a label ranking is given by:
%\begin{equation}
%P_{LR}(\pi) = \frac{\sum_{i=1}^{n} \rho(\pi,\pi_i)}{n}
%\label{eq:prior}
%\end{equation}
%
%We say that the prior probability is the mean of similarity of a given rankings to all the others. We measure similarity  using the Spearman correlation coefficient (\ref{eq00}). Equation \ref{eq:prior} shows the average similarity of one ranking relative to others. The greater the similarity between two particular rankings, the higher is the probability that the next unobserved  ranking will be similar to the known ranking. Take a look a the Table \ref{tab02} with the calculated prior probability for the unique rankings. We also added a column with prior probabilities considering the rankings as one class.
%
%
%As stated above, the ranking $\{A,C,B\}$, due to its  similarity to the other two rankings, achieves a higher probability.  Note that since we measure prior probability of label ranking as a similarity between rankings, it would not add to one as the in case of probability for classification. 
%
%The similarity of rankings based on the value $i$ of attribute $a$, ($v_{a,i}$),  or conditional probability of label rankings, is:
%\begin{equation}
%P_{LR}(v_{a,i}|\pi)= \frac{\sum_{i: x_{i,a} = v_{a,i}}\rho(\pi, \pi_i)}{\sum_i\rho(\pi,\pi_i)}%|\{i: x_{i,a} = v_{a,i}\}|}
%\label{eq:cond}
%\end{equation}
%
%
%Table \ref{tab03} demonstrates the logic behind the conditional probabilities based on similarity. Notice that there are no examples with $x_1=High$ and a target ranking of $\{A,C,B\}$; thus, $P(x_1=High|\{A,C,B\})=0$. However, in the similarity approach, the probability of $\{A,C,B\}$ depends on the probability of similar rankings, yielding $P_{LR}(x_1=High|\{A,C,B\})=0.750$.
%
%
%
%
%Applying equation (\ref{eq03}), we get the estimated posterior probability of ranking $\pi$:
%\begin{align}
%P_{LR}(\pi|x_i)&=P_{LR}(\pi)\prod_{a=1}^m P_{LR}(x_{i,a}|\pi)=\\ \notag
%& =\frac{\sum_{j=1}^{n} \rho(\pi,\pi_j)}{n}\left [ \prod_{a=1}^{m} \frac{\sum_{j: x_{j,a} = x_{i,a}}\rho(\pi, \pi_j)}{\sum_i\rho(\pi,\pi_i)}\right ]
%\end{align}
%
%The similarity-based adaptation of naive Bayes for label ranking will output the ranking with the higher $P_{LR}(\pi|x_i)$ value:
%\begin{align}
%\hat{\pi}&=\argmax_{\pi \in \Pi_{\mathcal{L}} }P_{LR}(\pi|x_i)= \\ \notag
%&=\argmax_{\pi \in \Pi_{\mathcal{L}} }P_{LR}(\pi)\prod_{a=1}^m P_{LR}(x_{i,a}|\pi) 
%\end{align}
%       
%\section*{Extensions}
%\label{nbr-ext}
%
%The naive Bayes algorithm for label ranking can be applied on data with the continuous variables. For this purpose, we apply the Gaussian distribution assumption and modify the conditional prior probability of label rankings as follows:
% 
%\begin{equation}
%\label{cont}
%P_{LR}(x_{i}|y)=\frac{1}{\sqrt{2\pi}\sigma_y}e^\frac{(x_i-\mu_y)^2}{2\sigma_y^2}
%\end{equation}
%where $\mu_y$ and $\sigma_y^2$ are weighted  mean and weighted variance and defined as follows:
%
%\begin{equation}
%\label{mu}
%\mu_y =\frac{\sum_{i=1}^n  \rho(y,y_i) x_i}{\sum_{i=1}^n \rho(y,y_i)}
%\end{equation} 
%
%
%\begin{equation}
%\label{sigma}
%\sigma_y^2=\frac{\sum_{i=1}^n \rho(y,y_i) (x_i-\mu_y)^2}{\sum_{i=1}^n \rho(y,y_i)}
%\end{equation} 
%       
%Timing in rankings
%
%In problems where rankings represent variation of labels across time, it is necessary to take the timing effect into account. That is, recent rankings have higher probability of appearing.  To capture this, we apply the weighted prior label ranking probabilities:
%
%\begin{equation}
%P_{LR}(\pi) = \mathbf{w} \frac{\sum_{i=1}^{n} \rho(\pi,\pi_i)}{n}
%\label{eq:timing}
%\end{equation}
%
%where $\mathbf{w}$ is the vector of weights calculated as:
%
%\begin{equation}
%\mathbf{w}=\alpha ^{\frac{T_{1 \ldots t}}{T}-1}   t \leqq T
%\end{equation}

 \newpage
 \begin{table}
\centering
\ra{1.2}
\small\addtolength{\tabcolsep}{-1pt}
\caption{Example of analysts rankings based on the observed variables $x_1 \ldots x_4$ }
 \begin{tabular}{cclllccc}
\toprule
Quarters&$x_1$&$x_2$&$x_3$&$x_4$&\multicolumn{3}{c}{Ranks}\\
\cline{6-8}
&&&&&Amertech& Brownbro&Cooper\\
\midrule
1&High&Low&High&Medium&1& 2& 3\\
2&High&High&High&Low& 2& 3& 1\\
3&Medium&Medium&High&Low&1 &2& 3\\
4&Low&Low&Low&High&1& 3& 2\\
5&     Medium&        High&    High& Medium& 1 &2& 3\\
6&     High&       Medium&   High& Low& 2 &3& 1\\
\bottomrule
 \end{tabular} 
\label{tab01}
\end{table}

\begin{table}
\caption{Descriptive statistics of independent variable}
\ Descriptive statists of state variables used to describe the state of the analyst.
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
\toprule
 <<desc-ind,echo=F,results='asis'>>=
data.to.display <- c('nbr.val','mean', 'median','std.dev')
results.final <- desc.ind[,data.to.display]

options(xtable.comment = FALSE)
cat("Variable & Observ & Mean & Median & std.dev\\\\\n")
cat('\\midrule \n')
#cat(rep('&',ncol(results.final)),'\\\\')
print(xtable(results.final,display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
@
\bottomrule
\end{tabularx}
\end{center}
\label{tab:ind.vvs}
\end{table}

\begin{table}
\caption{Summary of filtered data}
\ The table presents the filtered data used in building the rakings break down by sectors. The total for Brokers is the total of unique brokers.

\begin{center}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Sector & \# stocks & \# core brokers & \# forecasts \\ 
\midrule
<<desc-sector,echo=F,results='asis'>>=
print(xtable(stat.eps,display=c('s','d','d','d','d'),align=c('r',rep('c',ncol(stat.eps)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(stat.eps)-1),command=c('\\midrule \n')))
@
\bottomrule
\end{tabularx}
\label{table:filtered.summary}
\end{center}
\end{table}

\begin{table}
\caption{Averages of forecasts and stocks from broker and stock perspective}
\ The table presents the averages per quarter statistics based on the per Broker (Panel A) and per Stock (Panel B) perspective. Namely, the columns show the average number of forecast per quarter per Broker (per Stock), average number of Stocks (Brokers) per quarter, average number of forecasts per Stock (Broker) per quarter, and average number of quarters  a broker follows a stock (a stock being followed by a broker).
\begin{center}
%\begin{tabular}{rcccc}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
 \toprule
  Panel A: &\multicolumn{4}{c}{Per broker perspective}\\
  \cline{2-5}
 & Forecasts & Stocks & Forecast/stock & follow time, q \\ 
  \midrule
<<per-brok,echo=F,results='asis'>>=
print(xtable(per.broker,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.broker)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.broker)-1),command=c('\\midrule \n')))
@
\midrule
\end{tabularx}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  Panel B: &\multicolumn{4}{c}{Per stock perspective}\\
  \cline{2-5}
 & Forecasts & Brokers & Forecast/broker & follow time, q \\ 
 \midrule
<<per-stock,echo=F,results='asis'>>=
print(xtable(per.stock,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.stock)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.stock)-1),command=c('\\midrule \n')))
@
\bottomrule  
\end{tabularx}
\label{table:forecasts-broker}
\end{center}
\end{table}

<<fig-mean-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Average number of forecast per quarter',fig.lp='mean-f'>>=
ggplot(num.f.dt[,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Mean forecast')
@

<<fig-num-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of forecasts',fig.lp='num-f'>>=

ggplot(num.f.dt[,.N,by=.(q.id,Sector)],aes(x=as.Date(q.id),y=N))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

<<fig-stocks-brok,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of stocks per broker per quarter',fig.lp='num-s-b'>>=
ggplot(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

<<fig-brok-stocks,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of brokers per stock',fig.lp='num-b-s'>>=
ggplot(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
@

\begin{table}
\caption{Descriptive analysts' rankings}
\label{tab:top}
\ Changes in analysts' \emph{top}, \emph{middle}, \emph{bottom} and \emph{noRank} ranking categories when moving from $t-1$ (rows) to $t$ (columns). Each cell informs a percent of total that compose the ranking category at $t$. Panel A depicts the breakdown of rankings  based on the accuracy in target prices. Panel B shows the rankings that are based on the EPS forecasts.
%\centering
%\ra{1.2}
%\small\addtolength{\tabcolsep}{-2pt}
%Average topN-lastN changes in analyst's rank per quarter with N=3, i.e. in how many stocks, on average per quarter per analsyts, an analyst moved from top.prev to  top.current, last.prev->top.current, top.prev->last.cur, and last.prev->last.current
\begin{center}
\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  <<desc-rank-eps,echo=F,results='asis'>>=
tab.r <- round(rbind(eps.cont.tab[[3]],Total=apply(eps.cont.tab[[3]],2,sum)),3)*100
rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=T,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
@
\bottomrule
\end{tabularx}
\end{center}
\end{table}

\begin{table}[ht]

\ra{1.2}
\caption{Ranking accuracy of the naive Bayes ranking method and the two baselines.}
\label{stat:acc}
\begin{center}
\begin{tabular}{rrrrrrrrr}
  \toprule
 & Mean & .05 & .10 & .25 & .50 & .75 & .90 & .95 \\ 
\midrule
\naive{} & 0.060 & -0.004 & 0.003 & 0.033 & 0.066 & 0.085 & 0.106 & 0.134 \\ 
  \default{} & 0.037 & -0.026 & -0.007 & 0.019 & 0.040 & 0.055 & 0.074 & 0.095 \\ 
  \raw{} & 0.434 & 0.151 & 0.227 & 0.308 & 0.437 & 0.578 & 0.674 & 0.728 \\ 
  \diff{} & 0.308 & 0.045 & 0.113 & 0.208 & 0.298 & 0.417 & 0.530 & 0.591 \\ 
  \random{} & 0.319 & 0.119 & 0.162 & 0.251 & 0.321 & 0.412 & 0.480 & 0.515 \\ 
  \rollsd{} & 0.486 & 0.224 & 0.272 & 0.354 & 0.489 & 0.594 & 0.737 & 0.784 \\ 
   \bottomrule
\end{tabular}
\end{center}
\end{table}

\begin{table}
\ra{1.2}
\caption{Ranking accuracy: average correlation per year}
\label{stat:acc:time}
\begin{center}
\begin{tabular}{rrrrrrr}
  \toprule
 Year & \naive{} & \default{} & \raw{} & \diff{} & \random{} & \rollsd{} \\ 
  \midrule
1990 & 0.132 & 0.049 & 0.739 & 0.564 & 0.430 & 0.814 \\ 
  1991 & 0.062 & 0.040 & 0.665 & 0.378 & 0.371 & 0.718 \\ 
  1992 & 0.048 & 0.075 & 0.677 & 0.345 & 0.367 & 0.695 \\ 
  1993 & 0.020 & -0.002 & 0.620 & 0.482 & 0.267 & 0.702 \\ 
  1994 & 0.047 & 0.015 & 0.503 & 0.492 & 0.405 & 0.579 \\ 
  1995 & 0.061 & 0.041 & 0.489 & 0.332 & 0.413 & 0.548 \\ 
  1996 & 0.028 & 0.014 & 0.425 & 0.390 & 0.276 & 0.504 \\ 
  1997 & 0.074 & 0.050 & 0.497 & 0.292 & 0.441 & 0.539 \\ 
  1998 & 0.043 & 0.039 & 0.446 & 0.262 & 0.263 & 0.519 \\ 
  1999 & 0.086 & 0.055 & 0.464 & 0.284 & 0.352 & 0.459 \\ 
  2000 & 0.077 & 0.035 & 0.324 & 0.314 & 0.369 & 0.340 \\ 
  2001 & 0.059 & 0.024 & 0.388 & 0.330 & 0.352 & 0.401 \\ 
  2002 & 0.097 & 0.052 & 0.405 & 0.353 & 0.282 & 0.421 \\ 
  2003 & 0.066 & 0.038 & 0.468 & 0.264 & 0.141 & 0.486 \\ 
  2004 & 0.063 & 0.033 & 0.363 & 0.191 & 0.217 & 0.401 \\ 
  2005 & 0.065 & 0.045 & 0.345 & 0.231 & 0.241 & 0.404 \\ 
  2006 & 0.055 & 0.042 & 0.378 & 0.201 & 0.331 & 0.429 \\ 
  2007 & 0.054 & 0.032 & 0.167 & 0.152 & 0.199 & 0.283 \\ 
  2008 & 0.037 & 0.024 & 0.191 & 0.136 & 0.205 & 0.269 \\ 
  2009 & 0.044 & 0.032 & 0.150 & 0.178 & 0.315 & 0.117 \\ 
   \bottomrule
\end{tabular}
\end{center}
\end{table}

\clearpage

\begin{sidewaysfigure}
\includegraphics[scale=0.4]{timeline-bw}
 \caption{Timeline of ranking prediction} 
\label{fig: timeline} 
\end{sidewaysfigure}

\end{document}

### 2015-02-14 doc/understanding/understand-ranking.tex
Initial commit

--- 2015-02-14 doc/understanding/understand-ranking.Rnw
@@
 %\geometry{a4paper}
-%\usepackage[natbibapa]{apacite}
-\usepackage[longnamesfirst]{natbib}
+\usepackage[natbibapa]{apacite}
+%\usepackage{natbib}
 
@@
 \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\begin{document}
 
-\begin{document}
-<<include=FALSE>>=
-library(knitr)
-opts_chunk$set(concordance=TRUE)
-@
-
-<<load.data,echo=F,warning=FALSE,message=FALSE>>=
-strategies <- c('true','recent','all-time')
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
-library(reshape2)
-library(data.table)
-library(ggplot2)
-library(stringr)
-library(zoo)
-library(xtable)
-#load('cache/q.data.RData')
-#load('cache/final.bl.RData')
-#load('cache/market.set.RData')
-#load('cache/example.dt.RData')
-load('cache/array.all.vvs.RData')
-load('cache/broker.vvs.RData')
-source('lib/BL-functions.R')
-
-#library(ProjectTemplate)
-#load.project()
-###ADD NAs for the case of no ranking ( if NA, no raking)
-split.rank <- function(r,n){
-if(max(r,na.rm=T)==3|max(r,na.rm=T)==4){n=1}else{if(max(r,na.rm=T)==5|max(r,na.rm=T)==6){n=2}else{if(max(r,na.rm=T)==7|max(r,na.rm=T)==8){n=3}}}#else{if(max(r,na.rm=T)==9|max(r,na.rm=T)==10){n=4}}}}
-        t <- head(r,n)
-        b <- tail(r,n)
-        replace(replace(replace(replace(r,t,'top'),b,'bottom'),setdiff(r,c(t,b)),'middle'),which(is.na(r)),'noRank')
-}
-
-summary.stat <- function(dt){
-  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,.N,by=year],dt[,.N,by=list(year,Broker)][,.N,by=year][,N],dt[,.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,.N],'Brokers'=dt[,.N,by=Broker][,.N],'Observations'=prettyNum(dt[,.N],big.mark=' '))))
-}
-
-summary.mean.stat <- function(dt,value){
-  rbind(setnames(cbind(dt[,.N,by=list(year,Stock)][,descriptive.f(N),by=year][V1==value][,c(1,3),with=F],dt[,.N,by=list(year,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F],dt[,.N,by=list(year,Stock,Broker)][,descriptive.f(N),by=year][V1==value][,3,with=F]),c('Years','Firms','Brokers','Observations')),setnames(data.table(cbind(Years='All years','Firms'=dt[,.N,by=Stock][,descriptive.f(N)][V1==value][,2,with=F],'Brokers'=dt[,.N,by=Broker][,descriptive.f(N)][V1==value][,2,with=F],'Observations'=dt[,.N,by=list(Stock,Broker)][,descriptive.f(N)][V1==value][,2,with=F])),c('Years','Firms','Brokers','Observations')))
-}
-
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
-load('~/Dropbox/workspace/Projects/EPS/cache/eps.dt.RData')
-# crossby = function(DT, j, by) {
-#     j = substitute(j)
-#     ans = rbind(
-#         DT[,eval(j),by],
-#         DT[,list("Total",eval(j)),by=by[1]],
-#         cbind("Total",DT[,eval(j),by=by[2]]),
-#         list("Total","Total",DT[,eval(j)]),
-#         use.names=FALSE
-#         # 'use.names' argument added in data.table v1.8.0
-#     )
-#     setkeyv(ans,by)
-#     ans
-# }
-# crossby(eps.dt,length(Stock),c('Sector'))
-
-eps.stocks <- intersect(eps.dt$Stock,dimnames(array.all.vvs)[[2]])
-eps.dt <- na.omit(setkey(eps.dt[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,clean.s:=.N>=3,by=list(q.id,Stock)][(clean.s)][,q.num:=.GRP,by=q.id],Stock)[eps.stocks])
-#complete.dt <- rbindlist(lapply(43:85,function(q){ complete.dt[q.id==q]}))
-eps.stocks.rank <- intersect(complete.dt$Stock,dimnames(array.all.vvs)[[2]])
-
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks.rank][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')
-
-ind.v <- setnames(data.table(reshape2::melt(array.all.vvs[,eps.stocks,])),c('Quarter','Stock','Var','value'))
-
-desc.ind <- acast(setnames(ind.v[,descriptive.f(value,basic=T),by=.(Var)],c('Var','Stat','value')),Var~Stat,value.var = 'value')
-
-stat.eps <- rbind(setnames(eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),.N),by=.(Sector),.SDcols=c('Stock','Broker')],4,'Forecast'),setnames(cbind('Total',eps.dt[order(Sector),c(lapply(.SD,function(i){length(unique(i))}),Forecast=.N),.SDcols=c('Stock','Broker')]),1,'Sector'))
-
-###per broker perspectives
-# crossby = function(DT, j, by) {
-#     j = substitute(j)
-#     ans = rbind(
-#         DT[,eval(j),by],
-#         DT[,list("Total",eval(j)),by=by[1]],
-#         cbind("Total",DT[,eval(j),by=by[2]]),
-#         list("Total","Total",DT[,eval(j)]),
-#         use.names=FALSE
-#         # 'use.names' argument added in data.table v1.8.0
-#     )
-#     setkeyv(ans,by)
-#     ans
-# }
-
-num.f.dt <- eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker,Stock)]
-
-per.broker <- setnames(cbind(
-        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Broker)][,mean(N)])),
-        rbind(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N)]))[,V1],
-        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Broker)][,mean(V1)]))[,V1],
-        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Broker)][,mean(V1)]))[,V1]),c('Sector','Forecast','Stocks','Forecast/stock','Follow time,q'))
-
-###per stock
-per.stock <- setnames(cbind(
-        rbind(eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N),by=Sector],list('Total',eps.dt[order(Sector),.N,by=.(q.id,Sector,Stock)][,mean(N)])),
-        rbind(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(Sector)],list('Total',num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N)]))[,V1],
-        rbind(num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,mean(N),by=.(Sector,Stock,Broker)][,mean(V1),by=.(Sector,Stock)][,mean(V1)]))[,V1],
-        rbind(num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1),by=Sector],list('Total',num.f.dt[,.N,by=.(Sector,Broker,Stock)][,mean(N),by=.(Sector,Stock)][,mean(V1)]))[,V1]),c('Sector','Forecast','Broker','Forecast/broker','Follow time,q'))
-
-#quarters.eps <- data.table(q.id=complete.dt[order(q.id)][,unique(q.id)])
-n <- 3
-#ranked.eps.dt <- complete.dt[,merge(setkey(quarters.eps,q.id),.SD,all=T,allow.cartesian=T),by=list(Stock,Broker),.SDcols=c('q.id','Stock','Broker','rank')][,NextPeriod:=split.rank(rank,n),by=list(q.id,Stock)][,CurrentPeriod:=NextPeriod[c(NA,1:(.N-1))],by=list(q.id,Stock)]
-#[,NextPeriod:=paste(NextPeriod,'+1',sep='')]
-
-#ranked.eps.dt$CurrentPeriod <- factor(ranked.eps.dt$CurrentPeriod,levels=c('top','middle','bottom','noRank'))
-#ranked.eps.dt$NextPeriod <- factor(ranked.eps.dt$NextPeriod,levels=c('top','middle','bottom','noRank'))
-#cache('ranked.eps.dt')
-load('cache/ranked.eps.dt.RData')
-require(descr)
-eps.cont.tab <- ranked.eps.dt[,crosstab(CurrentPeriod,NextPeriod,prop.r=T,prop.t=T,prop.c=T,prop.chisq = F,plot=F)]
-#brok.full.stat.pt <- acast(setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view),by=year],c('Year','Statistics','value')),Year~Statistics,value.var='value')
-#pt.full.period <- setnames(q.data[!is.na(trunk.view),descriptive.f(trunk.view)],c('Statistics','value'))
-
-@
 \title{Understanding rankings of financial analysts}
@@
 
- \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
- \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
- \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+ \author[1,2]{ Artur Aiguzhinov (artur.aiguzhinov@inescporto.pt)}
+   \author[1]{
+   Ana Paula Serra (aserra@fep.up.pt)}
+\affil[1]{Department of Economics \& CEF.UP - University of Porto}
 
-\affil[1]{FEP \& CEF.UP, University of Porto}
-\affil[2]{INESC TEC}
-\affil[4]{FEUP, University of Porto}
+\author[2,3]{
+   Carlos Soares (csoares@fe.up.pt)}
+
+\affil[2]{INESC TEC -- Institute for Systems and Computer Engineering of Porto }
+
+\affil[3]{Department of Engineering University of Porto}
 
@@
 \singlespace
-\bibliographystyle{newapa}
+\bibliographystyle{apacite}
 \bibliography{/Users/aiguzhinov/Dropbox/Documents/Bibliography/rank}
@@
 \toprule
- <<desc-ind,echo=F,results='asis'>>=
-data.to.display <- c('nbr.val','mean', 'median','std.dev')
-results.final <- desc.ind[,data.to.display]
+Variable & Observ & Mean & Median & std.dev\\
+\midrule 
+ btm & 144 835 & 5.49 & 0.49 & 230.36 \\ 
+  size & 156 456 & 19.82 & 19.75 & 2.09 \\ 
+  debt.to.eq & 94 611 & Inf & 0.00 &  \\ 
+  accruals & 132 327 &  & -0.02 &  \\ 
+  s.vol & 169 405 & 41.86 & 0.04 & 15 195.30 \\ 
+  sec.ret & 164 538 & 0.01 & 0.03 & 0.12 \\ 
+  growth.gnp & 169 405 & 0.01 & 0.01 & 0.01 \\ 
+  inf.rate & 169 405 & 0.01 & 0.01 & 0.01 \\ 
+  ret.vix & 164 538 & 0.00 & -0.01 & 0.24 \\ 
+  t.bill & 169 405 & 0.04 & 0.04 & 0.02 \\
 
-options(xtable.comment = FALSE)
-cat("Variable & Observ & Mean & Median & std.dev\\\\\n")
-cat('\\midrule \n')
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(results.final,display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
 \bottomrule
@@
 \midrule
-<<desc-sector,echo=F,results='asis'>>=
-print(xtable(stat.eps,display=c('s','d','d','d','d'),align=c('r',rep('c',ncol(stat.eps)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(stat.eps)-1),command=c('\\midrule \n')))
-@
+ Consumer Discretionary & 436 & 225 & 270 278 \\ 
+  Consumer Staples & 103 & 120 & 47 406 \\ 
+  Energy & 195 & 133 & 188 231 \\ 
+  Financials & 484 & 147 & 206 356 \\ 
+  Health Care & 378 & 185 & 148 857 \\ 
+  IT & 532 & 255 & 363 950 \\ 
+  Industrials & 361 & 212 & 142 704 \\ 
+  Materials &  47 &  98 & 21 327 \\ 
+  Telecom Services &  12 &  47 & 3 447 \\ 
+  Utilities &  88 &  65 & 17 843 \\ 
+   \midrule 
+Total & 2 635 & 360 & 1 410 399 \\
+
 \bottomrule
@@
   \midrule
-<<per-brok,echo=F,results='asis'>>=
-print(xtable(per.broker,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.broker)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.broker)-1),command=c('\\midrule \n')))
-@
+ Consumer Discretionary & 42.64 & 12.39 & 3.14 & 10.77 \\ 
+  Consumer Staples & 15.13 & 5.14 & 2.84 & 12.19 \\ 
+  Energy & 61.19 & 13.08 & 3.73 & 11.09 \\ 
+  Financials & 52.80 & 14.08 & 3.36 & 11.35 \\ 
+  Health Care & 30.85 & 9.51 & 3.01 & 9.86 \\ 
+  IT & 53.74 & 14.14 & 3.28 & 10.16 \\ 
+  Industrials & 27.40 & 8.63 & 3.12 & 10.17 \\ 
+  Materials & 10.06 & 3.17 & 3.18 & 11.26 \\ 
+  Telecom Services & 4.84 & 1.78 & 2.78 & 10.09 \\ 
+  Utilities & 14.37 & 4.79 & 2.82 & 8.90 \\ 
+   \midrule 
+Total & 37.78 & 10.46 & 3.17 & 10.60 \\
+
 \midrule
@@
  \midrule
-<<per-stock,echo=F,results='asis'>>=
-print(xtable(per.stock,display=c('s','d','f','f','f','f'),align=c('r',rep('c',ncol(per.stock)))),only.contents=T,include.colnames=FALSE,include.rownames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(per.stock)-1),command=c('\\midrule \n')))
-@
+ Consumer Discretionary & 18.06 & 5.25 & 3.43 & 12.15 \\ 
+  Consumer Staples & 13.30 & 4.52 & 3.29 & 12.38 \\ 
+  Energy & 30.05 & 6.42 & 4.55 & 12.95 \\ 
+  Financials & 16.53 & 4.41 & 3.85 & 11.44 \\ 
+  Health Care & 14.98 & 4.62 & 3.35 & 10.19 \\ 
+  IT & 21.54 & 5.67 & 3.68 & 11.36 \\ 
+  Industrials & 12.14 & 3.82 & 3.41 & 11.66 \\ 
+  Materials & 11.89 & 3.75 & 3.44 & 12.35 \\ 
+  Telecom Services & 11.45 & 4.21 & 2.82 & 9.95 \\ 
+  Utilities & 7.79 & 2.60 & 3.05 & 10.39 \\ 
+   \midrule 
+Total & 17.57 & 4.86 & 3.60 & 11.51 \\
+
 \bottomrule  
@@
 
-<<fig-mean-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Average number of forecast per quarter',fig.lp='mean-f'>>=
-ggplot(num.f.dt[,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Mean forecast')
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/fig-mean-forecast-1} \caption[Average number of forecast per quarter]{Average number of forecast per quarter\label{mean-ffig-mean-forecast}}
+\end{figure}
 
-<<fig-num-forecast,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of forecasts',fig.lp='num-f'>>=
+\end{knitrout}
 
-ggplot(num.f.dt[,.N,by=.(q.id,Sector)],aes(x=as.Date(q.id),y=N))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/fig-num-forecast-1} \caption[Number of forecasts]{Number of forecasts\label{num-ffig-num-forecast}}
+\end{figure}
 
-<<fig-stocks-brok,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of stocks per broker per quarter',fig.lp='num-s-b'>>=
-ggplot(num.f.dt[,.N,by=.(q.id,Sector,Broker)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
-@
+\end{knitrout}
 
-<<fig-brok-stocks,echo=FALSE, include=TRUE,results='hide',fig.width=10.7,fig.height=8.3,fig.cap='Number of brokers per stock',fig.lp='num-b-s'>>=
-ggplot(num.f.dt[,.N,by=.(q.id,Sector,Stock)][,mean(N),by=.(q.id,Sector)],aes(x=as.Date(q.id),y=V1))+geom_line()+facet_wrap(~Sector,ncol=5,scale='free_x')+theme_bw()+geom_smooth(method='loess')+xlab('Years')+ylab('Forecasts')
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/fig-stocks-brok-1} \caption[Number of stocks per broker per quarter]{Number of stocks per broker per quarter\label{num-s-bfig-stocks-brok}}
+\end{figure}
+
+\end{knitrout}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{figure}
+\includegraphics[width=\maxwidth]{figure/fig-brok-stocks-1} \caption[Number of brokers per stock]{Number of brokers per stock\label{num-b-sfig-brok-stocks}}
+\end{figure}
+
+\end{knitrout}
 
@@
   \toprule
-  <<desc-rank-eps,echo=F,results='asis'>>=
-tab.r <- round(rbind(eps.cont.tab[[3]],Total=apply(eps.cont.tab[[3]],2,sum)),3)*100
-rownames(tab.r) <- c('$top_{t-1}$','$middle_{t-1}$','$bottom_{t-1}$','$noRank_{t-1}$','Sum')
-colnames(tab.r) <- c('$top_{t}$','$middle_{t}$','$bottom_{t}$','$noRank_{t}$')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=T,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-@
+ & $top_{t}$ & $middle_{t}$ & $bottom_{t}$ & $noRank_{t}$ \\ 
+ $top_{t-1}$ & 11.6 & 15.2 & 19.4 & 1.2 \\ 
+  $middle_{t-1}$ & 45.1 & 32.5 & 27.9 & 3.4 \\ 
+  $bottom_{t-1}$ & 13.7 & 7.5 & 11.7 & 0.9 \\ 
+  $noRank_{t-1}$ & 29.6 & 44.8 & 41.1 & 94.6 \\ 
+  Sum & 100.0 & 100.0 & 100.0 & 100.0 \\
+
 \bottomrule

### 2015-02-14 reports/price-target.Rmd
Initial commit

---
title: "Meeting report"
author: "Artur Aiguzhinov"
date: 'September 3rd 2014 '
output:
  pdf_document:
    highlight: espresso
    fig_caption: true
bibliography: rank.bib
---
``` {r, echo=FALSE,warning=FALSE,message=FALSE,cache.vars='pt.ratio'}
library(data.table)
#library(knitcitations)
#library(bibtex)
#biblio <- read.bib('~/Dropbox/Documents/Bibliography/rank.bib')
setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
load('cache/q.data.RData')
load('eda/ds.pt.RData')
source('lib/BL-functions.R')
q.data <- q.data[,':='(year=format(s.Date,'%Y'),trunk.view=truncate.f(b.view,0.05))]

pt.ratio <- na.omit(setkey(unique(q.data[,':='(consPT=mean(PT),mdPT=median(PT),numPT=.N),by=list(q.id,Stock)][,list(q.id,DSCD,Stock,consPT,mdPT,numPT)],by=c('q.id','Stock')),q.id,DSCD)[setkey(ds.pt,q.id,DSCD),allow.cartesian=T])[,':='(md.ratio=round(as.numeric(md.PT.DS)/mdPT,3),mn.ratio=as.numeric(mn.PT.DS)/consPT,num.ratio=as.numeric(num.PT.DS)/numPT)]
```
# High price targe values
## Introduction
The purpose of this report is to present arguments that would strengthen the hypothesis of analysts' optimism. Currently, this hypothesis is argued that there exists an inconsistency in price target database; namely, the adjusted vs. non-adjusted for stock-splits and dividends stock prices and price targets. My previous reports show that stock prices are adjusted and that price targets are mostly adjusted. In this report I show that analysts do, in fact, set a very optimistic price targets.

## Background
On my last meeting with Ana Paula, we discussed the problem of high values in price targets and, subsequently, optimistic expected returns.

Since we don't have anymore an access to the detailed history of `IBES` database, I suggested to use `Datastream` as they have the consensus history of price targets. I downloaded  mean, median, and number of price targets series. At the meeting, I had only mean price target series and I could not perform a good analysis as the values were all skewed. That is why, after the meeting, I obtained median and the number of price targets.

## Methodology
If both databases (`IBES` and `Datastream`) are in-sync, then the ratio of same metric from both databases would be close or equal to 1.

First step was to compare the total number of observations in `Datastream` and `IBES`. The total number of observations in `Datastream` is `r prettyNum(pt.ratio[,sum(as.numeric(num.PT.DS))],big.mark=' ') ` and in `IBES` it's `r prettyNum(q.data[,.N],big.mark=' ')`. `Datastream` has more price target reports than my database. I think it could be the fact that `Datastream` captures price target announcements with different time horizons.

As suggested, I calculate the following ratio for each of the metrics: median, mean, and number of observations on a  "per stock per quarter" basis.

\begin{equation}
ratio=\frac{Datastream}{IBES}
\end{equation}

The descriptive statistics is presented in table (1). The total number of observations is `r pt.ratio[,.N,by=list(Stock,q.id)][,.N]`. Observe, that mean and median of eq. (1)  are all around 1; that is, on average, the price target reports coincide in both of the databases. Visually we can see it form  figure (1) where I plot the decreasing the median of eq. (1) with the horizontal red line corresponding to 1. We see that most of the observations lie along the red line and in those cases both databases provide a similar price target information. The extreme values on both end of the red line signify an existing misalignment and, at this point, it is difficult to investigate further which database produce such extreme values.

## On-line evidence
It has been suggested to check if there are some evidences left on-line that show a very optimistic analyst's report.

[This announcement](http://www.cbsnews.com/news/280-price-seen-for-amazon/) tells that on April 16th, 1999 Amazon (AMZN) traded at $184 and one analyst (Jamie Kiggen) revised his target from $190 to $280, or, in TRER values, from `r round(190/184-1,3)` to `r round(280/184-1,3)`. In December of 2009, the analysts were not that optimistic about AMZN. [This link](http://www.benzinga.com/media/cnbc/73215/piper-jaffray-raises-amazon-s-amzn-price-target-to-172) tells that on December 29th Kaufman Bros. revised his price target to $155 with closing day stock price of 134.52 (TPER=`r round(155/134.52-1,3)`). We see, that analysts do, in fact, make a very optimistic price targets announcements.

## State-of-the-art
I looked at the literature on price targets and found a number of articles that have similar initial setup; namely, using price targets to calculate analysts' expected returns. One particular paper has even similar to my time periods: 1999 -- 2009 [@bradshaw2012]. Figure (2) reproduces the fragment of their sample descriptive statistics. I made a similar table with my values. I applied a 5th percentile filter on the top and the bottom of the observations.  The corresponding descriptive statistics is presented in  table (2). We see, that my sample has less observations (`r prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')` vs. 492 647), probably, due to the less number of firms in my sample; however, the number of Brokers is quite similar.

Next, I compare TPER of @bradshaw2012(fig. 3) and from my database (table (3)). Looking at the both tables, observe that values for TPER are quite similar: the average for all periods TPERs are 0.24 for 3619 firms (@bradshaw2012) and `r round(q.data[!is.na(trunk.view),mean(truncate.f(b.view,0.05),na.rm=T)],3)`  for `r q.data[!is.na(trunk.view),.N,by=Stock][,.N]` firms (my data). In addition, I looked in other papers with similar analysis and found that my numbers are quite low. For example, @zhou2013 reports for the period of 2000 -- 2009 an average TP/P of 1.96 for total of 2731 firms.

## Conclusion
I conclude, that values of price target in majority of cases are high because the analysts believe so. Comparing my data with different source (`Datastream`) and with similar research reveal, that, on average, my data is consistent with the state-of-the-art. The trimming of data is necessary to eliminate the extreme values.

#References

```{r,echo=FALSE,warning=FALSE,message=FALSE,results='asis'}
library(pastecs)
library(xtable)
options(xtable.comment = FALSE)
print(xtable(setnames(pt.ratio[,descriptive.f(.SD),.SDcols=c('md.ratio','mn.ratio','num.ratio')],'V1','Statistics'),caption='The descriptive statistics of ratios (full sample)'),include.rownames=F)
```

```{r,echo=FALSE,warning=FALSE,message=FALSE,fig.cap='Decreasing ratio of median'}
library(ggplot2)
library(zoo)
ggplot(pt.ratio[order(md.ratio,decreasing=T)],aes(y=md.ratio,x=index(md.ratio)))+geom_point()+geom_hline(yintercept=1,color='red')+theme_bw()+ggtitle('Decreasing median of eq.(1) (full set)')+xlab('Index')+ylab('Value')
```

![A snippet of the paper by @bradshaw2012 with their sample descriptive statistics](/Users/aiguzhinov/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/reports/bradshaw01.png)

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
#q.data[,descriptive.f(truncate.f(b.view,0.05))]
#q.data[,trunk.view:=truncate.f(b.view,0.05)]

stats.q.data <- rbind(setnames(cbind(q.data[!is.na(trunk.view),.N,by=list(year,Stock)][,.N,by=year],q.data[!is.na(trunk.view),.N,by=list(year,Broker)][,.N,by=year][,N],q.data[!is.na(trunk.view),.N,by=year][,N]),c('Years','Firms','Brokers','Observations')),data.table(cbind(Years='All years','Firms'=q.data[!is.na(trunk.view),.N,by=Stock][,.N],'Brokers'=q.data[!is.na(trunk.view),.N,by=Broker][,.N],'Observations'=prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' '))))
options(xtable.comment = FALSE)
print(xtable(stats.q.data,caption='The descriptive statistics of price target sample (truncated sample)'),include.rownames=F)

#q.data[!is.na(trunk.view),mean(truncate.f(b.view,0.05),na.rm=T),by=list(year)][,round(V1,3)]
```

![A snipped of the descriptive stat of TP/P from @bradshaw2012](/Users/aiguzhinov/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/reports/bradshaw02.png)

```{r,echo=FALSE,message=FALSE,warning=FALSE,results='asis'}
#q.data[,trunk.view:=truncate.f(b.view,0.05)]

stats.tper <- setnames(rbind(q.data[!is.na(trunk.view),mean(truncate.f(b.view,0.05),na.rm=T),by=list(year)],data.table(cbind(year='All',V1=q.data[!is.na(trunk.view),mean(truncate.f(b.view,0.05),na.rm=T)])))[,V1:=as.numeric(as.character(V1))],'V1','TP/P-1')

options(xtable.comment = FALSE)
print(xtable(stats.tper,digits=3,caption='The descriptive statistics of TP/P-1 (truncated sample)'),include.rownames=F)
```

### 2015-02-14 lib/aux.functions.R

@@ -1,0 +1,152 @@
+roll.ret.f <- function(Return){
+        cbind(ann.ret=Return.annualized(Return,scale=4),
+              ann.sd=sd(Return)*sqrt(4),
+              cum.ret=Return.cumulative(Return))
+}
+
+grow.window.f <- function(x,len,...){
+        rollapplyr(x,len,...,partial=T)
+}
+
+show.no.na <- function(data) {
+    data[!is.na(data)]
+}
+
+
+zeros2NA <- function(x){
+        x[is.infinite(x)] <- NA
+        x[x==0] <- NA
+        x
+}
+
+# ### create boxplot---
+# boxplot.f <- function(data, name) {
+#     load(analysts.dir("Sectors/Market/quarters.zoo.RData"))
+#     
+#     require(zoo)
+#     require(plyr)
+#     if (is.list(data)) {
+#         data.list <- data
+#     } else {
+#         data.list <- alply(data, 1, function(i) {
+#             i
+#         })
+#     }
+#     
+#     boxplot(data.list, xaxt = "n", main = name)
+#     abline(h = 0)
+#     axis(1, at = c(seq(1, length(data.list), 4), length(data.list)), 
+#         labels = as.yearqtr(quarters.zoo[c(seq(length(quarters.zoo) - 
+#             length(data.list) + 1, length(quarters.zoo), 4), 
+#             length(quarters.zoo))]))
+# } 
+# 
+# boxplot.gplot.f <- function(data,varnames,title,breaks="12 months"){
+#   load(analysts.dir("Sectors/Market/quarters.zoo.RData"))
+#   df <- melt(data,na.rm=T,varnames=varnames)
+#   df.dates <- data.frame(Dates=quarters.zoo[df[,1]],df)
+#   ggplot(df.dates,aes(x=Dates,y=value,group=round_any(Quarters,1,floor)))+geom_boxplot()+ scale_x_date(breaks = date_breaks(breaks),labels = date_format("%Y"))+ggtitle(title)
+# }
+
+
+findIntersect <- function(x,y,dimension){
+        intersect(dimnames(x)[[dimension]],dimnames(y)[[dimension]])
+}
+
+descriptive.f <- function(columns,...)
+{
+        require(pastecs)
[…]

### 2015-02-14 munge/01-data.pre.process.R

@@ -1,0 +1,317 @@
+###This script for data.table excercise
+# getStockData <- function(index,tmp,skip,ref.m,val.name,date.format){
+#   data <- tmp[-skip,.SD,.SDcols=c(1,index)]
+# setnames(data,c('Date',ref.m))
+# data[,Date:=as.Date(Date,format=date.format)]
+# melt(data,id.vars='Date',variable.name='Stock',value.name=val.name)
+# }
+data.collect<- function(data.id,n)
+{
+  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
+    id=strsplit(i,split = '\\.');
+    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
+      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
+    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
+}
+
+af.data.collect<- function(data.id,n)
+{
+  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
+    id=strsplit(i,split = '\\.');
+    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
+      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
[…]

### 2015-02-14 munge/01-data.q.ret.R

@@ -1,0 +1,159 @@
+###This script for data.table excercise
+# getStockData <- function(index,tmp,skip,ref.m,val.name,date.format){
+#   data <- tmp[-skip,.SD,.SDcols=c(1,index)]
+# setnames(data,c('Date',ref.m))
+# data[,Date:=as.Date(Date,format=date.format)]
+# melt(data,id.vars='Date',variable.name='Stock',value.name=val.name)
+# }
+
+#setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
+#source("lib/my.paths.R")
+
+
+#lapply(list('xts','reshape2','data.table','plyr','stringr'),function(X) {do.call("require", list(X)) })
+
+
+stock.ref <- setkey(unique(rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/names/',pattern='name.ds.*.csv'),function(i){fread(paste('~/Dropbox/Datastream/AllStocks/names/',i,sep=''),header=T,na.strings = '')})),by='DSCD')[,Stock:=WC05601],DSCD,Stock)
+
+load('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/ref.matrix.RData')
+#make DT of it
+ref.dt <- setkey(data.table(Stock=ref.matrix[,1],DSCD=rownames(ref.matrix)),DSCD)
+sp.id <- setkey(setnames(fread('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
+miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
+miss.dt <- data.table(Stock=miss.tkt,DSCD=ref.dt[sp.id][which(is.na(Stock))][,DSCD])
+ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],DSCD,Stock)
+
+full.stock.ref <- setkey(unique(merge(stock.ref,ref.dt,all=T),by=c('DSCD','Stock')),DSCD,Stock)
[…]

### 2015-02-14 munge/02-state-variables.R

@@ -1,0 +1,924 @@
+# TODO: Add comment
+#
+# Author: aiguzhinov
+##########################
+
+#####################################################
+### A new rewrite of the script with base on data.table package
+### 27/06/14
+
+### Variables:
+### btm=btm,
+### debt.to.eq=,
+### size=
+### accruals=
+### ret.vol =
+
+
+#source('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/lib/my.paths.R')
+sectors<-c('Consumer Discretionary','Consumer Staples','Energy','Financials','Health Care','Industrials','IT','Materials','Telecom Services','Utilities')
+
+vvs.data <- setkey(rbindlist(mclapply(sectors,function(sec){
+  vvs <- list.files(paste(data.stock.dir(sec),'Acc.Variables',sep='/'),pattern='*.csv')
+  dt <- do.call(cbind,lapply(vvs,function(i){
+    vvs.dt <- data.table(read.csv2(paste(data.stock.dir(sec),'Acc.Variables',i,sep='/'),sep=';',nrow=84))[,q.id:=as.yearqtr(seq.Date(as.Date('1989-04-01'),as.Date('2010-01-01'),by = '3 month')-1)]
+  setkey(melt(vvs.dt,id.vars='q.id',variable.name = 'Stock',value.name = strsplit(i,'.csv')[[1]]),q.id,Stock)
+    }))
+dt[,unique(colnames(dt)),with=F][,Sector:=sec]
+},mc.cores=4))[,':='(btm=(tot.assets-tot.liab)/as.numeric(market.cap),size=log(as.numeric(market.cap)),debt.to.eq=st.debt/(tot.assets-tot.liab),accruals=total.accruals(curr.assets,cash,curr.liab,st.debt,taxes,depr,tot.assets)),by=list(Stock,Sector)],q.id,Stock)
+
+
+###Broker specific variables load q.data from cache. To be calculated immediately before the ranking process
+# load('cache/q.data.RData')
[…]

### 2015-02-14 munge/02-variables.R

@@ -1,0 +1,946 @@
+# TODO: Add comment
+#
+# Author: aiguzhinov
+##########################
+
+#####################################################
+### A new rewrite of the script with base on data.table package
+### 27/06/14
+
+### Variables:
+### btm=btm,
+### debt.to.eq=,
+### size=
+### accruals=
+### ret.vol =
+data.collect<- function(data.id,n)
+{
+  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
+    id=strsplit(i,split = '\\.');
+    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
+      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
+    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
+}
+total.accruals<-function(cur.assets,cash,cur.liab,debt,tax,depr,tot.assets)
+{
+  variables<-cbind(
+    cur.assets,
+    cash,
+    cur.liab,
+    debt,
+    tax,
+    tot.assets)
+  variables[is.na(variables)]<-0
+  variables.diff<-diff(variables,1)
+  num<-variables.diff[,1]-variables.diff[,2]-
+    (variables.diff[,3]-variables.diff[,4])-
+    variables.diff[,5]-depr
+
+  denom<-diff(variables[,6],lag=4)/2
+  ta<-num/denom
+}
+broker.vvs.f <- function(forecasts, actual)
+{
+  sq.error <- (mean(actual) - mean(forecasts))^2
+  dispersion <- var(forecasts)
+  num.forcst <- length(forecasts)
+  sq.error[is.na(sq.error)] <- 0
+  uncertainty <- sq.error+dispersion
[…]

### 2015-02-14 munge/03-analysts.process.R

@@ -1,0 +1,73 @@
+###This script for data.table excercise
+
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
+source("lib/my.paths.R")
+
+lapply(list('xts','reshape2','data.table','plyr','stringr'),function(X) {do.call("require", list(X)) })
+
+
+stock.ref <- setkey(unique(rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/names/',pattern='name.ds.*.csv'),function(i){fread(paste('~/Dropbox/Datastream/AllStocks/names/',i,sep=''),header=T,na.strings = '')})),by='DSCD')[,Stock:=WC05601],DSCD,Stock)
+
+load('data/ref.matrix.RData')
+load(file='data/missing.brokers.RData')
+
+#make DT of it
+ref.dt <- setkey(data.table(Stock=ref.matrix[,1],DSCD=rownames(ref.matrix)),DSCD)
+sp.id <- setkey(setnames(fread('data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
+miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
+miss.dt <- data.table(Stock=miss.tkt,DSCD=ref.dt[sp.id][which(is.na(Stock))][,DSCD])
+ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],DSCD,Stock)
+
+full.stock.ref <- setkey(unique(merge(stock.ref,ref.dt,all=T),by=c('DSCD','Stock')),DSCD,Stock)
+s.id <- setkey(full.stock.ref[ref.dt][,list(DSCD,NAME,Stock)],DSCD)
+
+###all stocks to used for variables and PT
+all.stock.prices <- na.omit(setkey(setnames(unique(data.collect('p',1),by=c('Date','DSCD')),'p','priceAdj')[,pricePT:=c(rep(NA,3),head(priceAdj,-3)),by=DSCD],DSCD)[setkey(full.stock.ref,DSCD),allow.cartesian=T])[,list(Date,Stock,DSCD,NAME,priceAdj,pricePT)]
+
+### Adustment factor (AF) for all stock
[…]

### 2015-02-14 munge/03-bl.pre.process.R

@@ -1,0 +1,13 @@
+
+views.Qs <- aaply(all.rankings,5,bl.script.f,ret=data,baselines=baselines,t=dim(all.rankings)[1],.drop=F)
+###Adding Qs from tper-based method
+both.s <- intersect(findIntersect(meanTper,norm.conf,2),dimnames(views.Qs)[[3]])
+all.Qs <- abind(views.Qs[1,drop=F,,both.s,],non.rank=aperm(replicate(1,replicate(7,meanTper[1:dim(views.Qs)[2],both.s,drop=F])),c(4,1,2,3)),along=1)
+views.omegas <- aaply(accuracy,4,buildOmega,.drop=F)
+tper.all.conf <- buildOmega(aperm(replicate(1,norm.conf),c(3,1,2)))
+
+all.conf <- abind(views.omegas[,,,both.s,],aperm(replicate(7,tper.all.conf[1:dim(views.Qs)[2],,drop=F,both.s,]),c(2,1,5,3,4)),along=1)
+dimnames(all.conf)[[1]] <- dimnames(all.Qs)[[1]]
+
+bl.period <- 4:dim(all.Qs)[2]
+m.period <-(length(market.inputs)-length(bl.period)+1) : length(market.inputs)

### 2015-02-14 munge/predicting.R

@@ -1,0 +1,186 @@
+#rm(list=ls())
+#setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+#library(ProjectTemplate)
+#load.project()
+
+
+#system.time(source('munge/01-data.pre.process.R'))
+#system.time(source('munge/02-variables.R'))
+#system.time(source('munge/state-variables.R'))
+###Ranking periods:
+###true=1999 Q3 till 2010 Q1, naive: 1999 Q2 till 2009 Q4
+
+###subset of core stocks/broker: min. 3 broker in quarter and min. 12 quarters of coverage
+# setkey(market.set,q.num)
+
+###Core.dt: 1. Brokers, that follow a stock for 12 qtrs
+###2.Stocks with more than 3 brokers
+###3.Stocks with more then 8 quarters of history
+core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)]
+
+broker.vvs <- acast(melt(unique(core.dt[,broker.vvs.f(PT,priceAdj),by=list(q.id,Stock)],by=c('q.id','Stock')),id.vars = c('q.id','Stock'),measure.vars = c('uncertainty','assym','dispersion')),q.id~Stock~variable)
+
+quarters <- data.table(q.id=sort(unique(core.dt[,q.id])))
+
+#core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper','rank')]
+#ggplot(melt(core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper')],id.vars=c('q.id','V1'))[V1=='mean'],aes(x=as.Date(q.id),y=value,color=variable,fill=variable))+geom_bar(stat='identity')+facet_grid(variable~.)+theme_bw()
+
+##core rankings
+
+baselines.dt<- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
+
[…]

### 2015-02-14 munge/state-variables.R

@@ -1,0 +1,957 @@
+# TODO: Add comment
+#
+# Author: aiguzhinov
+##########################
+
+#####################################################
+### A new rewrite of the script with base on data.table package
+### 27/06/14
+
+### Variables:
+### btm=btm,
+### debt.to.eq=,
+### size=
+### accruals=
+### ret.vol =
+data.collect<- function(data.id,n)
+{
+  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
+    id=strsplit(i,split = '\\.');
+    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
+      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
+    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
+}
+total.accruals<-function(cur.assets,cash,cur.liab,debt,tax,depr,tot.assets)
+{
+  variables<-cbind(
+    cur.assets,
+    cash,
+    cur.liab,
+    debt,
+    tax,
+    tot.assets)
+  variables[is.na(variables)]<-0
+  variables.diff<-diff(variables,1)
+  num<-variables.diff[,1]-variables.diff[,2]-
+    (variables.diff[,3]-variables.diff[,4])-
+    variables.diff[,5]-depr
+
+  denom<-diff(variables[,6],lag=4)/2
+  ta<-num/denom
+}
+broker.vvs.f <- function(forecasts, actual)
+{
+  sq.error <- (mean(actual) - mean(forecasts))^2
+  dispersion <- var(forecasts)
+  num.forcst <- length(forecasts)
+  sq.error[is.na(sq.error)] <- 0
[…]

### 2015-02-14 munge/trading.R

@@ -1,0 +1,58 @@
+
+source('lib/BL-functions.R')
+stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+core.dt <- na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)]
+
+
+
+pt.trunk.brok.tper <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1))][,':='(default=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T,partial=T),raw=naive,'1diff'=naive,roll.sd=naive,random=naive),by=.(Broker,Stock)]
+
+pt.exp.ret <- setkey(melt(pt.trunk.brok.tper,id.vars = c('q.id','Stock','Broker'),measure.vars = c(baselines,methods),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
+
+
+
+
+pt.ret <-pt.exp.ret[ranked.pt.dt][,rank.exp.ret.f(rank,exp.ret),by=.(q.id,Stock,Method)][V1!=0,]
+
+pt.list.rank <- acast(pt.ret,q.id~Stock~Method,value.var='V1')
+
+#pt.list.rank <- dlply(pt.ret,'Method',acast,q.id~Stock,value.var='V1')
+
+#ggplot(pt.ret,aes(x=as.Date(q.id),y=V1,group=as.Date(q.id)))+geom_boxplot()+facet_grid(Method~.,scales='free_x')+theme_bw()
+#pt.pred.rank.views <- setnames(pt.ret[,year:=format(as.yearqtr(q.id),'%Y')],'V1','View')
+
+
+require(scales)
+
+
[…]

### 2015-02-14 src/bl.process.R

@@ -1,0 +1,110 @@
+opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
+  #list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
+  list.conf <- c(alply(case.2.non.r.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
+  #list.conf <- alply(non.r.conf[,,,agg],2,.dims=T)
+  rbindlist(lapply(names(list.views),function(type){
+    rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))[,Aggregation:=agg]
+  }))
+}))
+
+
+
+opt.w.f <- function(agg.names,rank.views,nr.views,rank.conf,nr.conf,case='1',tau,delta){
+  
+  rbindlist(lapply(agg.names,function(agg){
+    list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(nr.conf[,,,agg],2,.dims=T))
+    switch(case,
+      '1'=rbindlist(lapply(names(nr.views),function(type){
+        rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],nr.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]
+      })),
+      
+      '2'=rbind(rbindlist(lapply(names(rank.views),function(type){
+        rbindlist(script.weights.env.f(type,market.list[m.period],rank.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]})),
+        rbindlist(lapply(names(nr.views),function(type){
+          rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],nr.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]})))
+    )}))
+}
+
+
+# ####run script from here----
+# require(scales)
+# portf.perform <- abind(lapply(dimnames(all.Qs)[[1]],function(rank){ abind(lapply(baselines,function (method){
+#   sapply(dimnames(all.conf)[[5]],function(meth){
[…]

### 2015-02-14 src/bl.process.mix.R

@@ -1,0 +1,104 @@
+opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
+  list.conf <- c(alply(case.3.rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
+  
+  rbindlist(lapply(names(list.views),function(type){
+    rbindlist(
+      switch(type,
+        'true'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'naive'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'default'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'raw'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        '1diff'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'roll.sd'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'random'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'true.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'naive.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
+        'default.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))
+      )[,Aggregation:=agg]
+  }))
+}))
+
+
+
+# ####run script from here----
+# require(scales)
[…]

### 2015-02-14 src/bl.process.rank.R

@@ -1,0 +1,117 @@
+opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
+  list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
+  #list.conf <- c(alply(case.2.non.r.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
+  #list.conf <- alply(rank.conf[,,,agg],2,.dims=T)
+  rbindlist(lapply(names(list.views),function(type){
+    rbindlist(script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))[,Aggregation:=agg]
+  }))
+}))
+
+
+
+bl.results <- unique(opt.w,by=c('q.id','Method','Aggregation'))[,list(Quarters=as.yearqtr(Quarters),Method,Aggregation,port.ret,n.views,q.id)]
+  
+setkey(market.set,Quarters)
+market.info <- unique(market.set[,':='(port.ret=sum(mw*ex.ret),Method='Market',n.views=.N),by=Quarters])[m.period,list(Quarters=as.yearqtr(Quarters),Method,port.ret,n.views)][,q.id:=.I]
+
+bl.results <- rbind(bl.results,bl.results[,as.list(market.info),by=Aggregation],use.names=T)
+
+bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views),by=list(Method,Aggregation)][,ann.sr:=ann.ret/ann.sd]
+setkey(bl.results,Method,Aggregation)
+bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views),by=list(Method,Aggregation)][,ann.sr:=ann.ret/ann.sd]
+setkey(bl.results,Method,Aggregation)
+to.bl <- rbindlist(lapply(2:length(bl.period),function(b){
+  beg <- setkey(opt.w[q.id==b,list(Stock,opt.w),by=list(Method,Aggregation)],Stock,Method,Aggregation)
+  end <- setkey(opt.w[q.id==b-1,list(Stock,opt.w),by=list(Method,Aggregation)],Stock,Method,Aggregation)
[…]

### 2015-02-14 src/eda.R

@@ -1,0 +1,262 @@
+rm(list=ls())
+library('ProjectTemplate')
+load.project()
+load('data/adj.prices.v5.RData')
+yahoo.p <- setkey(melt(data.table(Date=index(p),coredata(p)),id.vars = 'Date',variable.name = 'Stock',value.name = 'yahoo',na.rm=T)[,Stock:=as.character(Stock)],Date,Stock)
+
+load('data/yahoo.close.RData')
+yahoo.close.p <- setkey(melt(data.table(Date=index(p),coredata(p)),id.vars = 'Date',variable.name = 'Stock',value.name = 'close.yahoo')[,Stock:=as.character(Stock)],Date,Stock)
+
+yahoo.set <- yahoo.p[yahoo.close.p]
+
+
+load('data/ref.matrix.RData')
+#make DT of it
+ref.dt <- setnames(setkey(data.table(Stock=ref.matrix[,1],s.id=rownames(ref.matrix)),s.id),1:2,c('Stock','s.id'))
+sp.id <- fread('data/sp.ids.new.csv',header=F)
+miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
+miss.dt <- data.table(Stock=miss.tkt,s.id=ref.dt[sp.id][which(is.na(Stock))][,s.id])
+ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],s.id)
+s.id <- ref.dt[sp.id,Stock]
+
+ds.adj.sp <- setkey(melt(setnames(data.table(read.csv2('data/prices02.csv',skip=4,sep=';'))[,Code:=as.Date(Code,format('%d-%m-%Y'))],c('Date',s.id)),id.vars = 'Date',variable.name = 'Stock',value.name = 'dsAdj')[,Stock:=as.character(Stock)],Date,Stock)[Stock=='AAPL',':='(dsAdj=dsAdj*7)]
+
+
[…]

### 2015-02-14 src/eps.trading.R

@@ -1,0 +1,135 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+
+delta<-2.5
+system.time(source('munge/01-data.pre.process.R'))
+system.time(source('munge/02-variables.R'))
+###Ranking periods:
+###true=1999 Q3 till 2010 Q1, naive: 1999 Q2 till 2009 Q4
+
+###subset of core stocks/broker: min. 3 broker in quarter and min. 12 quarters of coverage
+# setkey(market.set,q.num)
+
+core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+
+#core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper','rank')]
+#ggplot(melt(core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper')],id.vars=c('q.id','V1'))[V1=='mean'],aes(x=as.Date(q.id),y=value,color=variable,fill=variable))+geom_bar(stat='identity')+facet_grid(variable~.)+theme_bw()
+
+##core rankings
+pt.new <- acast(core.dt,q.id~Broker~Stock,value.var='rank')
+### Ranking algorithm ~ 13 min----
+rank.parameters <- c(n=10,diff.lag=1,sd.lag=8)
+methods<-c('raw','1diff','random','roll.sd')
+
+#stocks=intersect(dimnames(pt.new)[[3]],dimnames(array.all.vvs)[[2]])
+stocks=intersect(dimnames(pt.new)[[3]],market.set[,Stock])
+ baseline.rankings <- baseline.rankings.f(pt.new[1:43,,stocks],1)
+ stock.vvs <- vvs.combine(stocks,broker.vvs,array.all.vvs,t=dim(pt.new)[1])
+#
+ system.time(pred.r<- predict.ranking.sript.f(methods,stock.vvs,pt.new[1:43,,stocks],rank.parameters))
+# #dimnames(pred.r)[[2]] <- dimnames(pt.new)[[1]][4:43]
+ all.rankings <- abind(baseline.rankings[3:42,,,],aperm(pred.r,c(2,1,3,4)),along=4)
[…]

### 2015-02-14 src/paper.predict.R

@@ -1,0 +1,263 @@
+### tried to implement the ranking with data.table, too complicated. For rankings, see the array based approach (trading.R). Close this development.
+
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+#source('lib/BL-functions.APS.R')
+source('lib/BL-functions.R')
+#source('lib/ranking.scripts.APS.R')
+#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+core.dt <- setkey(na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],Stock)[stocks]
+
+ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
+cache('ranked.pt.dt')
+
+percentile <- 0.05
+
+pt.trunk.brok.tper <- setkey(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)],q.id,Stock,Broker)
+
+pt.exp.tmp <- pt.trunk.brok.tper[,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(true,seq_len(length(true)),mean,na.rm=T),by=.(Broker,Stock)]
+
[…]

### 2015-02-14 src/paper.predict.array.R

@@ -1,0 +1,250 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+delta<-1
+tau=1/50
+rank.parameters <- c(n=100,diff.lag=1,sd.lag=8,roll.p=20)
+baselines <- c('true','naive','default')
+methods<-c('raw','1diff','random','roll.sd')
+confid.id <- c('cons','last','ma')
+percentile <- 0.05
+
+system.time(source('munge/predicting.R'))
+
+
+stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+core.dt <- na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)]
+
+
+
+pt.trunk.brok.tper <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,':='(naive=c(NA,head(true,-1)),default=rollapplyr(true,seq_len(length(true)),mean,na.rm=T,partial=T),raw=true,'1diff'=true,roll.sd=true,random=true),by=.(Broker,Stock)]
+
+pt.exp.ret <- setkey(melt(pt.trunk.brok.tper,id.vars = c('q.id','Stock','Broker'),measure.vars = c(baselines,methods),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
+
+
+ranked.pt.dt <- setkey(setnames(data.table(reshape2::melt(all.rankings)),c('q.id','Broker','Stock','Method','rank'))[,q.id:=as.yearqtr(q.id)],q.id,Stock,Broker,Method)
[…]

### 2015-02-14 src/paper.trading.APS.R

@@ -1,0 +1,123 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+
+#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+
+brok.tper <- acast(unique(core.dt,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var=c('b.view'))
+
+
+
+##core rankings
+pt.new <- acast(unique(core.dt,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='rank')
+pt.stocks=intersect(dimnames(brok.tper)[[3]],market.set[,Stock])
+
+
+#pt.stocks=intersect(dimnames(pt.new)[[3]],market.set[,Stock])
+pt.baseline.rankings <- baseline.rankings.f(pt.new[,,pt.stocks],1)
+pt.all.s <- findIntersect(pt.baseline.rankings,brok.tper,3)
+pt.all.b <- findIntersect(pt.baseline.rankings,brok.tper,2)
+percentile <- 0.05
+pt.trunk.brok.tper <- truncate.f(brok.tper[,,pt.all.s],percentile)
+
+
+pt.list.rank <- alply(bl.script.f(pt.all.s,pt.baseline.rankings[3:42,pt.all.b,pt.all.s,],pt.trunk.brok.tper,t=dim(pt.baseline.rankings[3:42,,,])[1]),3,.dims=T)
+
+pt.rank.views <- setnames(data.table(reshape2::melt(pt.list.rank)),c('q.num','Stock','View','Method'))[,q.id:=dimnames(pt.baseline.rankings)[[1]][3:42],by=list(Stock,Method)][,year:=format(as.yearqtr(q.id),'%Y')]
+cache('pt.rank.views')
+
+load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
+
+eps.new <- acast(unique(complete.dt,by=c('Broker','calQ','Stock'),fromLast = T),calQ~Broker~Stock,value.var='rank')
+
[…]

### 2015-02-14 src/paper.trading.APS.true.R

@@ -1,0 +1,220 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+#source('lib/BL-functions.APS.R')
+source('lib/BL-functions.R')
+#source('lib/ranking.scripts.APS.R')
+#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+core.dt <- setkey(na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],Stock)[stocks]
+
+ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
+cache('ranked.pt.dt')
+
+percentile <- 0.05
+
+pt.trunk.brok.tper <- setkey(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)],q.id,Stock,Broker)
+
+pt.exp.tmp <- pt.trunk.brok.tper[,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(true,seq_len(length(true)),mean,na.rm=T),by=.(Broker,Stock)]
+
+pt.exp.ret <- setkey(melt(pt.exp.tmp,id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
+
+
+
+
[…]

### 2015-02-14 src/paper.trading.R

@@ -1,0 +1,113 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+
+#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+
+brok.tper <- acast(unique(core.dt,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+#pt.stocks=intersect(dimnames(pt.new)[[3]],market.set[,Stock])
+#pt.trunk.brok.tper <- truncate.f(brok.tper[,pt.all.b,pt.all.s],percentile)
+
+
+##core rankings
+pt.new <- acast(unique(core.dt,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='rank')
+pt.stocks=intersect(dimnames(pt.new)[[3]],market.set[,Stock])
+pt.baseline.rankings <- baseline.rankings.f(pt.new[1:43,,pt.stocks],1)
+pt.all.s <- findIntersect(pt.baseline.rankings,brok.tper,3)
+pt.all.b <- findIntersect(pt.baseline.rankings,brok.tper,2)
+percentile <- 0.05
+pt.trunk.brok.tper <- truncate.f(brok.tper[,pt.all.b,pt.all.s],percentile)
+
+pt.list.rank <- alply(bl.script.f(pt.all.s,pt.baseline.rankings[3:42,pt.all.b,pt.all.s,],pt.trunk.brok.tper,t=dim(pt.baseline.rankings[3:42,,,])[1]),3,.dims=T)
+
+pt.rank.views <- setnames(data.table(reshape2::melt(pt.list.rank)),c('q.num','Stock','View','Method'))[,q.id:=dimnames(pt.baseline.rankings)[[1]][3:42],by=list(Stock,Method)][,year:=format(as.yearqtr(q.id),'%Y')]
+cache('pt.rank.views')
+
+load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
+
[…]

### 2015-02-14 src/paper.trading.dt.R

@@ -1,0 +1,162 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+#source('lib/BL-functions.APS.R')
+source('lib/BL-functions.R')
+#source('lib/ranking.scripts.APS.R')
+#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
+
+stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+core.dt <- na.omit(setkey(setkey(q.data,q.id)[setkey(quarters,q.id)][,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],Stock)[stocks])
+
+#quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])
+
+
+ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
+
+percentile <- 0.05
+
+pt.trunk.brok.tper <- setkey(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)],q.id,Stock,Broker)
+
+pt.exp.tmp <- pt.trunk.brok.tper[,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)]
+
+pt.exp.ret <- setkey(melt(pt.exp.tmp,id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
+
+cache('ranked.pt.dt')
+
+
[…]

### 2015-02-14 src/pt.eps.trading.R

@@ -1,0 +1,139 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+
+delta<-2.5
+system.time(source('munge/01-data.pre.process.R'))
+system.time(source('munge/02-variables.R'))
+###Ranking periods:
+###true=1999 Q3 till 2010 Q1, naive: 1999 Q2 till 2009 Q4
+
+###subset of core stocks/broker: min. 3 broker in quarter and min. 12 quarters of coverage
+# setkey(market.set,q.num)
+
+core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+
+#core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper','rank')]
+#ggplot(melt(core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper')],id.vars=c('q.id','V1'))[V1=='mean'],aes(x=as.Date(q.id),y=value,color=variable,fill=variable))+geom_bar(stat='identity')+facet_grid(variable~.)+theme_bw()
+
+##core rankings
+pt.new <- acast(core.dt,q.id~Broker~Stock,value.var='rank')
+### Ranking algorithm ~ 13 min----
+rank.parameters <- c(n=10,diff.lag=1,sd.lag=8)
+methods<-c('raw','1diff','random','roll.sd')
+
+#stocks=intersect(dimnames(pt.new)[[3]],dimnames(array.all.vvs)[[2]])
+stocks=intersect(dimnames(pt.new)[[3]],market.set[,Stock])
+ baseline.rankings <- baseline.rankings.f(pt.new[1:43,,stocks],1)
+ stock.vvs <- vvs.combine(stocks,broker.vvs,array.all.vvs,t=dim(pt.new)[1])
+#
+ system.time(pred.r<- predict.ranking.sript.f(methods,stock.vvs,pt.new[1:43,,stocks],rank.parameters))
+# #dimnames(pred.r)[[2]] <- dimnames(pt.new)[[1]][4:43]
+ all.rankings <- abind(baseline.rankings[3:42,,,],aperm(pred.r,c(2,1,3,4)),along=4)
[…]

### 2015-02-14 src/script.predict.trade.R

@@ -1,0 +1,30 @@
+rm(list=ls())
+setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+
+library(ProjectTemplate)
+load.project()
+delta<-1L;tau=1/50;baselines <- c('true','naive','default');methods<-c('raw','1diff','random','roll.sd');confid.id <- c('cons','last','ma');percentile <- 0.05;rank.parameters <- c(n=100L,diff.lag=1L,sd.lag=8L,roll.p=15L)
+##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
+require(labelRank)
+### market data: ~ 113 sec (mcapply: ~ 52 sec)
+system.time(source('munge/01-data.q.ret.R'))
+### State var. data: ~118 sec
+system.time(source('munge/02-state-variables.R'))
+### Analysts ranking data: ~ 280 sec
+#system.time(source('munge/03-analysts.process.R'))
+### Predicting ~ 347 sec
+system.time(source('src/predicting.R'))
+
+pt.accu[,mean(value),by=.(variable)]
+
+ggplot(pt.accu[,mean(value),by=.(q.id,variable)],aes(x=as.Date(q.id),y=V1,group=variable,color=variable))+geom_line(size=0.5,alpha=0.7)+geom_smooth(method='loess',se=F,size=1L)+theme_bw()
+
+### trading: ~ 322 sec
+system.time(source('src/trading.R'))
+
+ggplot(res.accu[,mean(value,na.rm=T),by=.(q.id,variable,conf)],aes(x=as.Date(q.id),y=V1,color=variable,group=variable))+geom_line()+facet_grid(conf~.,scale='free_y')+theme_bw()
+
+
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Method,color=Method))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))+geom_hline(yintercept=100L)+facet_grid(~confAgg,scale='free_x')
+
[…]

### 2015-02-14 src/tr-prediction.R

@@ -1,0 +1,77 @@
+source('/Users/aiguzhinov/Documents/Dropbox/workspace/MetaRanks/my.paths.R')
+prediction <- function(sel.stocks,forecasts,actuals,rank.m,rank.parameters){
+  ###forecast dim(q,b,s)
+  
+    start.q <- switch(rank.m,'pt'=43,'eps'=43,'pt.new'=43)
+    forecast.p <- (dim(forecasts)[1]-start.q+1):dim(forecasts)[1]
+  if(rank.m=='pt.new'){tr <- pt.new[,,sel.stocks];broker.vvs <- broker.vvs}else{
+    tr<- target.ranking(sel.stocks,forecasts[forecast.p,,sel.stocks],actuals[forecast.p,sel.stocks],coverage=12,min.brokers=3)
+  broker.vvs <- broker.vvs.f(forecasts=forecasts[forecast.p,dimnames(tr)[[2]],dimnames(tr)[[3]]],actual=actuals[forecast.p,dimnames(tr)[[3]]])
+  }
+baseline.rankings <- replicate(1,baseline.rankings.f(tr,1))
+sectors<-c('Consumer Discretionary',
+  'Consumer Staples',
+  'Energy',
+  'Financials',
+  'Health Care',
+  'Industrials',
+  'IT',
+  'Materials',
+  'Telecom Services',
+  'Utilities')
+source(project.dir('/NBr/generic-nbr.R'))
+methods<-c('raw','1diff','random','roll.sd')
+load(analysts.dir('/Sectors/All Sectors/all.stocks.list.RData'))
+names(all.stocks.list) <- sectors
+colnames(sector.ret) <- sectors
+
+stock.vvs <- vvs.combine(stocks=dimnames(tr)[[3]],sectors.stock=all.stocks.list,broker=broker.vvs,ret.vol=ret.vol.sp.pt,sector.ret=sector.ret,t=dim(tr)[[1]])
+pred.r<- predirank.f(methods,stock.vvs,macro.vvs,tr,rank.parameters)
+pred.r <- replicate(1,pred.r)
+all.rankings <- abind(baseline.rankings,aperm(pred.r,c(2,1,3,4,5)),along=4,new.names=list(NULL,NULL,NULL,NULL,rank.m))
+accuracy <- apply(all.rankings,c(1,3,5),function(s){apply(s,2,evaluation.simple,s[,'true'],'s','p' ) })
[…]

### 2015-02-14 tests/1.R

@@ -1,0 +1,3 @@
+# Example Unit Testing Script
+system.time(source('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/src/trading.R'))
+

### 2015-02-14 tests/generic-nbr-dt-test.R

@@ -1,0 +1,172 @@
+### Lable Ranking prediciton function----
+pred.cont <- function(rank.data, model, test.data) {
+    prod <- -log(model$priors) + sapply(1:length(rank.data), function(r) {
+        cond <- sapply(1:length(test.data), function(i) {
+            pnorm(test.data[i], mean = model$cond$mean[r, i], 
+                sd = model$cond$sdev[r, i], lower.tail = F)
+        })
+        # cond[is.infinite(cond)]<-NA cond<-round(cond,5)
+        # cond[which(cond==0)]<-NA cond
+        sum(-log(cond), na.rm = T)
+    })
+    rank.data[which.min(prod), ]
+#   prod <-model$priors*
+#   sapply(1:length(rank.data), function(r) {
+#     cond <- sapply(1:length(test.data), function(i) {
+#       pnorm(test.data[i], mean = model$cond$mean[r, i], 
+#         sd = model$cond$sdev[r, i])
+#     })
+#     cond[is.infinite(cond)]<-NA 
+#     cond<-round(cond,5)
+#     cond[which(cond==0)]<-NA 
+#     cond
+#     prod(cond, na.rm = T)
+#   })
+#     rank.data[which.max(prod), ]
+  
+}
+
+### Function to create NB model----
+lr.model <- function(correlations, data, weights) {
+    priors <- sapply(1:length(correlations), function(r) {
+        weighted.mean(correlations[r, ], weights, na.rm = T)
+    })
+    
+    attributes <- 1:length(data)
+    mu <- weights * t(sapply(1:length(correlations), function(r) {
+        sapply(attributes, function(x) {
+            sum(data[, x] * correlations[r, ], na.rm = T)/sum(correlations[r, 
+                ], na.rm = T)
+        })
+    }))
+    sigma <- weights * t(sapply(1:length(correlations), function(r) {
+        sapply(attributes, function(x) {
+            sqrt(sum(correlations[r, ] * (data[, x] - mu[r, x])^2, 
+                na.rm = T)/sum(correlations[r, ], na.rm = T))
+        })
+        
+    }))
+    conditionals <- list(mean = mu, sdev = sigma)
+    list(priors = priors, cond = conditionals)
+}
+
+evaluation.simple <- function(tr, pr, method = "spearman", use = "p") {
+    cor(tr, pr, method = method, use = use)
+}
+
+### Function wrap model and predictions-----
[…]

### 2015-02-14 munge/01-data.pre.process.R
cleanining files and change of project path

@@ -1,317 +1,0 @@
-###This script for data.table excercise
-# getStockData <- function(index,tmp,skip,ref.m,val.name,date.format){
-#   data <- tmp[-skip,.SD,.SDcols=c(1,index)]
-# setnames(data,c('Date',ref.m))
-# data[,Date:=as.Date(Date,format=date.format)]
-# melt(data,id.vars='Date',variable.name='Stock',value.name=val.name)
-# }
-data.collect<- function(data.id,n)
-{
-  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
-    id=strsplit(i,split = '\\.');
-    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
-      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
-    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
-}
-
-af.data.collect<- function(data.id,n)
-{
-  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
-    id=strsplit(i,split = '\\.');
-    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
-      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
[…]

### 2015-02-14 munge/01-data.q.ret.R

@@ -15,10 +15,10 @@
 
 stock.ref <- setkey(unique(rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/names/',pattern='name.ds.*.csv'),function(i){fread(paste('~/Dropbox/Datastream/AllStocks/names/',i,sep=''),header=T,na.strings = '')})),by='DSCD')[,Stock:=WC05601],DSCD,Stock)
 
-load('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/ref.matrix.RData')
+load('~/Dropbox/workspace/Projects/BL-strategies/data/ref.matrix.RData')
 #make DT of it
 ref.dt <- setkey(data.table(Stock=ref.matrix[,1],DSCD=rownames(ref.matrix)),DSCD)
-sp.id <- setkey(setnames(fread('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
+sp.id <- setkey(setnames(fread('~/Dropbox/workspace/Projects/BL-strategies/data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
 miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
 miss.dt <- data.table(Stock=miss.tkt,DSCD=ref.dt[sp.id][which(is.na(Stock))][,DSCD])
 ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],DSCD,Stock)
@@ -121,7 +121,7 @@ set(s.ex.ret, i=which(is.na(s.ex.ret[[6]])), 6L, value=0)
 ###quarterly SP500 index, value and market weights
 quarters <- seq(as.Date('1999-04-01'),as.Date('2010-01-01'),by='3 month')-1
 
[…]

### 2015-02-14 munge/02-state-variables.R

@@ -42,10 +42,10 @@ dt[,unique(colnames(dt)),with=F][,Sector:=sec]
 
 stock.ref <- setkey(unique(rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/names/',pattern='name.ds.*.csv'),function(i){fread(paste('~/Dropbox/Datastream/AllStocks/names/',i,sep=''),header=T,na.strings = '')})),by='DSCD')[,Stock:=WC05601],DSCD,Stock)
 
-load('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/ref.matrix.RData')
+load('~/Dropbox/workspace/Projects/BL-strategies/data/ref.matrix.RData')
 #make DT of it
 ref.dt <- setnames(setkey(data.table(Stock=ref.matrix[,1],s.id=rownames(ref.matrix)),s.id),1:2,c('Stock','DSCD'))
-sp.id <- setkey(setnames(fread('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
+sp.id <- setkey(setnames(fread('~/Dropbox/workspace/Projects/BL-strategies/data/sp.ids.new.csv',header=F),'DSCD'),DSCD)
 miss.tkt <- c('AMP','ANV','ATCH','ACS','ASND','BT','HPH','MEYR','MWI','MII','RN','UCC')
 miss.dt <- data.table(Stock=miss.tkt,DSCD=ref.dt[sp.id][which(is.na(Stock))][,DSCD])
 ref.dt <- setkey(rbind(ref.dt,miss.dt)[,Stock:=as.character(Stock)][which(duplicated(rbind(ref.dt,miss.dt)[,Stock])),Stock:=paste(Stock,'1',sep='.')],DSCD,Stock)

### 2015-02-14 munge/02-variables.R

@@ -1,946 +1,0 @@
-# TODO: Add comment
-#
-# Author: aiguzhinov
-##########################
-
-#####################################################
-### A new rewrite of the script with base on data.table package
-### 27/06/14
-
-### Variables:
-### btm=btm,
-### debt.to.eq=,
-### size=
-### accruals=
-### ret.vol =
-data.collect<- function(data.id,n)
-{
-  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
-    id=strsplit(i,split = '\\.');
-    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
-      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
-    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
-}
-total.accruals<-function(cur.assets,cash,cur.liab,debt,tax,depr,tot.assets)
-{
-  variables<-cbind(
-    cur.assets,
-    cash,
-    cur.liab,
-    debt,
-    tax,
-    tot.assets)
-  variables[is.na(variables)]<-0
-  variables.diff<-diff(variables,1)
-  num<-variables.diff[,1]-variables.diff[,2]-
-    (variables.diff[,3]-variables.diff[,4])-
-    variables.diff[,5]-depr
-
-  denom<-diff(variables[,6],lag=4)/2
-  ta<-num/denom
-}
-broker.vvs.f <- function(forecasts, actual)
-{
-  sq.error <- (mean(actual) - mean(forecasts))^2
-  dispersion <- var(forecasts)
-  num.forcst <- length(forecasts)
-  sq.error[is.na(sq.error)] <- 0
-  uncertainty <- sq.error+dispersion
[…]

### 2015-02-14 munge/03-analysts.process.R

@@ -1,6 +1,6 @@
 ###This script for data.table excercise
 
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
+setwd('~/Dropbox/workspace/Projects/BL-strategies')
 source("lib/my.paths.R")
 
 lapply(list('xts','reshape2','data.table','plyr','stringr'),function(X) {do.call("require", list(X)) })

### 2015-02-14 munge/03-bl.pre.process.R

@@ -1,13 +1,0 @@
-
-views.Qs <- aaply(all.rankings,5,bl.script.f,ret=data,baselines=baselines,t=dim(all.rankings)[1],.drop=F)
-###Adding Qs from tper-based method
-both.s <- intersect(findIntersect(meanTper,norm.conf,2),dimnames(views.Qs)[[3]])
-all.Qs <- abind(views.Qs[1,drop=F,,both.s,],non.rank=aperm(replicate(1,replicate(7,meanTper[1:dim(views.Qs)[2],both.s,drop=F])),c(4,1,2,3)),along=1)
-views.omegas <- aaply(accuracy,4,buildOmega,.drop=F)
-tper.all.conf <- buildOmega(aperm(replicate(1,norm.conf),c(3,1,2)))
-
-all.conf <- abind(views.omegas[,,,both.s,],aperm(replicate(7,tper.all.conf[1:dim(views.Qs)[2],,drop=F,both.s,]),c(2,1,5,3,4)),along=1)
-dimnames(all.conf)[[1]] <- dimnames(all.Qs)[[1]]
-
-bl.period <- 4:dim(all.Qs)[2]
-m.period <-(length(market.inputs)-length(bl.period)+1) : length(market.inputs)

### 2015-02-14 munge/predicting.R

@@ -1,186 +1,0 @@
-#rm(list=ls())
-#setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
-
-#library(ProjectTemplate)
-#load.project()
-
-
-#system.time(source('munge/01-data.pre.process.R'))
-#system.time(source('munge/02-variables.R'))
-#system.time(source('munge/state-variables.R'))
-###Ranking periods:
-###true=1999 Q3 till 2010 Q1, naive: 1999 Q2 till 2009 Q4
-
-###subset of core stocks/broker: min. 3 broker in quarter and min. 12 quarters of coverage
-# setkey(market.set,q.num)
-
-###Core.dt: 1. Brokers, that follow a stock for 12 qtrs
-###2.Stocks with more than 3 brokers
-###3.Stocks with more then 8 quarters of history
-core.dt <- q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)]
-
-broker.vvs <- acast(melt(unique(core.dt[,broker.vvs.f(PT,priceAdj),by=list(q.id,Stock)],by=c('q.id','Stock')),id.vars = c('q.id','Stock'),measure.vars = c('uncertainty','assym','dispersion')),q.id~Stock~variable)
-
-quarters <- data.table(q.id=sort(unique(core.dt[,q.id])))
-
-#core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper','rank')]
-#ggplot(melt(core.dt[,descriptive.f(.SD,basic=F),by=q.id,.SDcols=c('b.view','meanTper')],id.vars=c('q.id','V1'))[V1=='mean'],aes(x=as.Date(q.id),y=value,color=variable,fill=variable))+geom_bar(stat='identity')+facet_grid(variable~.)+theme_bw()
-
-##core rankings
-
-baselines.dt<- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
-
[…]

### 2015-02-14 munge/state-variables.R

@@ -1,957 +1,0 @@
-# TODO: Add comment
-#
-# Author: aiguzhinov
-##########################
-
-#####################################################
-### A new rewrite of the script with base on data.table package
-### 27/06/14
-
-### Variables:
-### btm=btm,
-### debt.to.eq=,
-### size=
-### accruals=
-### ret.vol =
-data.collect<- function(data.id,n)
-{
-  rbindlist(lapply(list.files('~/Dropbox/Datastream/AllStocks/it3/',pattern=paste('^',data.id,'.*.csv',sep='')),function(i){
-    id=strsplit(i,split = '\\.');
-    names.tmp <- sapply(read.csv2(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),nrow=1,sep=',',na.strings='#ERROR',header=F,skip=1)
-      ,function(i){strsplit(as.character(i),split = '[[:punct:]]')[[1]][n]})
-    melt(setnames(fread(paste('~/Dropbox/Datastream/AllStocks/it3/',i,sep=''),sep=',',na.strings='')[,V1:=as.Date(V1,format = "%m/%d/%Y")],c('Date',names.tmp[2:length(names.tmp)])),id.vars = 'Date',variable.name = 'DSCD',value.name = id[[1]][1],na.rm=T)}))
-}
-total.accruals<-function(cur.assets,cash,cur.liab,debt,tax,depr,tot.assets)
-{
-  variables<-cbind(
-    cur.assets,
-    cash,
-    cur.liab,
-    debt,
-    tax,
-    tot.assets)
-  variables[is.na(variables)]<-0
-  variables.diff<-diff(variables,1)
-  num<-variables.diff[,1]-variables.diff[,2]-
-    (variables.diff[,3]-variables.diff[,4])-
-    variables.diff[,5]-depr
-
-  denom<-diff(variables[,6],lag=4)/2
-  ta<-num/denom
-}
-broker.vvs.f <- function(forecasts, actual)
-{
-  sq.error <- (mean(actual) - mean(forecasts))^2
-  dispersion <- var(forecasts)
-  num.forcst <- length(forecasts)
-  sq.error[is.na(sq.error)] <- 0
[…]

### 2015-02-14 munge/trading.R

@@ -1,58 +1,0 @@
-
-source('lib/BL-functions.R')
-stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
-quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
-
-core.dt <- na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)]
-
-
-
-pt.trunk.brok.tper <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1))][,':='(default=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T,partial=T),raw=naive,'1diff'=naive,roll.sd=naive,random=naive),by=.(Broker,Stock)]
-
-pt.exp.ret <- setkey(melt(pt.trunk.brok.tper,id.vars = c('q.id','Stock','Broker'),measure.vars = c(baselines,methods),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
-
-
-
-
-pt.ret <-pt.exp.ret[ranked.pt.dt][,rank.exp.ret.f(rank,exp.ret),by=.(q.id,Stock,Method)][V1!=0,]
-
-pt.list.rank <- acast(pt.ret,q.id~Stock~Method,value.var='V1')
-
-#pt.list.rank <- dlply(pt.ret,'Method',acast,q.id~Stock,value.var='V1')
-
-#ggplot(pt.ret,aes(x=as.Date(q.id),y=V1,group=as.Date(q.id)))+geom_boxplot()+facet_grid(Method~.,scales='free_x')+theme_bw()
-#pt.pred.rank.views <- setnames(pt.ret[,year:=format(as.yearqtr(q.id),'%Y')],'V1','View')
-
-
-require(scales)
-
-
[…]

### 2015-02-14 src/script.predict.trade.R

@@ -1,5 +1,5 @@
 rm(list=ls())
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
+setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 
 library(ProjectTemplate)
 load.project()

### 2015-02-16 src/paper.trading.APS.true.R
Code for first paper

@@ -1,35 +1,16 @@
-rm(list=ls())
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/')
 
-library(ProjectTemplate)
-load.project()
-#source('lib/BL-functions.APS.R')
-source('lib/BL-functions.R')
-#source('lib/ranking.scripts.APS.R')
-#brok.tper <- acast(unique(q.data,by=c('Broker','q.id','Stock'),fromLast = T),q.id~Broker~Stock,value.var='b.view')
 
 stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
 quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
 
-core.dt <- setkey(na.omit(setkey(na.omit(q.data),q.id)[setkey(quarters,q.id)])[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)],Stock)[stocks]
-
-ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
-cache('ranked.pt.dt')
-
-percentile <- 0.05
-
-pt.trunk.brok.tper <- setkey(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)],q.id,Stock,Broker)
-
-pt.exp.tmp <- pt.trunk.brok.tper[,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(true,seq_len(length(true)),mean,na.rm=T),by=.(Broker,Stock)]
-
-pt.exp.ret <- setkey(melt(pt.exp.tmp,id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
[…]

### 2015-02-16 src/bl.process.R
naive for 'default' calculations; results are good: TP is best for naive and true, EPS is good for default

@@ -1,110 +1,0 @@
-opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
-  #list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
-  list.conf <- c(alply(case.2.non.r.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
-  #list.conf <- alply(non.r.conf[,,,agg],2,.dims=T)
-  rbindlist(lapply(names(list.views),function(type){
-    rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))[,Aggregation:=agg]
-  }))
-}))
-
-
-
-opt.w.f <- function(agg.names,rank.views,nr.views,rank.conf,nr.conf,case='1',tau,delta){
-  
-  rbindlist(lapply(agg.names,function(agg){
-    list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(nr.conf[,,,agg],2,.dims=T))
-    switch(case,
-      '1'=rbindlist(lapply(names(nr.views),function(type){
-        rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],nr.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]
-      })),
-      
-      '2'=rbind(rbindlist(lapply(names(rank.views),function(type){
-        rbindlist(script.weights.env.f(type,market.list[m.period],rank.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]})),
-        rbindlist(lapply(names(nr.views),function(type){
-          rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],nr.views[[type]][bl.period,],list.conf[[type]][bl.period,],tau,delta))[,Aggregation:=agg]})))
-    )}))
-}
-
-
-# ####run script from here----
-# require(scales)
-# portf.perform <- abind(lapply(dimnames(all.Qs)[[1]],function(rank){ abind(lapply(baselines,function (method){
-#   sapply(dimnames(all.conf)[[5]],function(meth){
[…]

### 2015-02-16 src/bl.process.mix.R

@@ -1,104 +1,0 @@
-opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
-  list.conf <- c(alply(case.3.rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
-  
-  rbindlist(lapply(names(list.views),function(type){
-    rbindlist(
-      switch(type,
-        'true'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'naive'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'default'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'raw'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        '1diff'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'roll.sd'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'random'=script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'true.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'naive.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5),
-        'default.nr'=non.rank.script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))
-      )[,Aggregation:=agg]
-  }))
-}))
-
-
-
-# ####run script from here----
-# require(scales)
[…]

### 2015-02-16 src/bl.process.rank.R
naive for 'default' calculations

@@ -1,117 +1,0 @@
-opt.w<- rbindlist(lapply(c('last','ma','w.ma'),function(agg){
-  list.conf <- c(alply(rank.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
-  #list.conf <- c(alply(case.2.non.r.conf[,,,agg],2,.dims=T),alply(non.r.conf[,,,agg],2,.dims=T))
-  #list.conf <- alply(rank.conf[,,,agg],2,.dims=T)
-  rbindlist(lapply(names(list.views),function(type){
-    rbindlist(script.weights.env.f(type,market.list[m.period],list.views[[type]][bl.period,],list.conf[[type]][bl.period,],0.02,2.5))[,Aggregation:=agg]
-  }))
-}))
-
-
-
-bl.results <- unique(opt.w,by=c('q.id','Method','Aggregation'))[,list(Quarters=as.yearqtr(Quarters),Method,Aggregation,port.ret,n.views,q.id)]
-  
-setkey(market.set,Quarters)
-market.info <- unique(market.set[,':='(port.ret=sum(mw*ex.ret),Method='Market',n.views=.N),by=Quarters])[m.period,list(Quarters=as.yearqtr(Quarters),Method,port.ret,n.views)][,q.id:=.I]
-
-bl.results <- rbind(bl.results,bl.results[,as.list(market.info),by=Aggregation],use.names=T)
-
-bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views),by=list(Method,Aggregation)][,ann.sr:=ann.ret/ann.sd]
-setkey(bl.results,Method,Aggregation)
-bl.results[,c('cum.ret','ann.ret','ann.sd','meanViews'):=cum.ret.f(port.ret,n.views),by=list(Method,Aggregation)][,ann.sr:=ann.ret/ann.sd]
-setkey(bl.results,Method,Aggregation)
-to.bl <- rbindlist(lapply(2:length(bl.period),function(b){
-  beg <- setkey(opt.w[q.id==b,list(Stock,opt.w),by=list(Method,Aggregation)],Stock,Method,Aggregation)
-  end <- setkey(opt.w[q.id==b-1,list(Stock,opt.w),by=list(Method,Aggregation)],Stock,Method,Aggregation)
[…]

### 2015-02-16 src/paper.trading.APS.true.R

@@ -6,10 +6,10 @@ quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(
 core.dt <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)[stocks]
 
 
-pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(true,seq_len(length(true)),mean,na.rm=T),by=.(Broker,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
+pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
 
 
[…]

### 2015-02-16 doc/paper/paper-knitr-APS.Rnw
Complete code for the first paper

@@
 strategies <- c('true','recent','all-time')
-setwd('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies')
+setwd('~/Dropbox/workspace/Projects/BL-strategies')
 library(reshape2)

### 2015-02-16 doc/paper/paper-knitr-APS.tex
Complete code for the first paper

@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(eps.rank.views[View != 0, list(mean = mean(View), median = median(View), : object 'eps.rank.views' not found}}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in rbind(stat.nr, stat.pt.view, stat.eps.view): object 'stat.eps.view' not found}}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in na.omit(dt): object 'ranked.pt.dt' not found}}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in melt(stat.full, id.vars = c("{}year"{}, "{}Method"{}, "{}Strategy"{})): object 'stat.full' not found}}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in match(x, table, nomatch = 0L): object 'test' not found}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in na.omit(dt): object 'ranked.eps.dt' not found}}\end{kframe}
 \end{knitrout}
+
+\title{Are rankings of financial analysts useful to investors?}
+ \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
+ \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
+ \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+
+\affil[1]{FEP \& CEF.UP, University of Porto}
+\affil[2]{INESC TEC}
+\affil[4]{FEUP, University of Porto}
+
+\maketitle
+% You need this here, or else the first page won't have a header.
+\thispagestyle{fancy}
+
+\begin{abstract}
+Some institutions issue rankings of financial analysts.
+Given that these rankings are \textit{ex-post} they may not be able useful to investors.
+In this paper  we show that trading strategies based on past rankings outperform a passive strategy.
+In addition, we report that analysts issuing accurate price targets are more favorable to the investors  to follow rather than analysts issuing accurate EPS forecasts.
+In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
+%Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
+\end{abstract}
+
+\section{Introduction}
+\label{sec:intro}
+
+% citations  full for aurtors
+The idea that financial analysts play an important role in financial markets is rather consensual \citep{cowles1933csm,obrien1990}.
+Yet there is some debate on whether following the advice of analysts brings value to investors after transaction costs \citep{womack1996,mikhail2004sae,li2005persistence}.
+Related to this is the difficulty in identifying the analysts with superior stock picking skills.
+In this paper, we show that the rankings of financial analysts are useful to investors because strategies based upon these rankings yield positive abnormal returns.
+
+In recent years, some institutions have been very active in publishing and  selling  rankings of financial analysts.
+Some rankings  are based on privately held surveys of  buy-side analysts (e.g., the Institutional Investor's rankings of the All-America Research Teams\footnote{\url{http://www.institutionalinvestor.com/Research/4560/First-Team.html}} and Bloomberg's America's Best Stock Analysts\footnote{\sloppy \url{http://www.bloomberg.com/news/2013-08-14/jpmorgan-top-stock-picker-with-equities-out-of-lockstep.html}}); others are based on the performance of sell-side analysts (ThomsonReuters' top StarMine analysts\footnote{\url{http://excellence.thomsonreuters.com/award/starmine}}).
+In any of these cases, the rankings aim at identifying the top analysts.
+However, aside from personal acknowledgment among peers, it is still arguable whether these are useful \citep{desai2000ass} or are merely ``popularity contests" \citep{emery2009}.
+%In this paper, we support the argument that the top-ranked analysts, indeed, have stock picking skills.
+
+We show that the top ranked analysts have stock picking skills.
+The contributions of our research is fourfold.
+First, we develop a trading strategy that transforms the rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}.
+Second, we show that annualized cumulative returns generated by some trading strategies  based upon analysts' rankings outperform the passive strategy (e.g., buy-and-hold the general stock market index).
+Third, we show that the strategy based upon the perfect foresight of rankings yields the highest cumulative annualized return.
+Fourth, we find that investors  are better off following analysts that issue the most accurate target prices, rather than those that issue the most accurate EPS forecasts.
+
+The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines our proposed  trading strategies; section \ref{sec:rankings} describes the sample and presents some preliminary results; section \ref{sec:results} presents and discusses the results; and section \ref{sec:conclusion} concludes.
+
+\section{Industry Rankings of Financial Analysts}
+\label{sec:ranking}
+
+In the financial literature there has been a long debate on whether financial analysts produce valuable  advice.
+Some argue that following the advice of financial analysts,  translated as recommendations of buying, holding, or selling a particular stock, does not yield  abnormal returns, i.e.,  returns that are above the required return to compensate for risk.
+The Efficient Market Hypothesis \citep{fama1970ecm} states that financial markets are efficient and that any public available information  regarding a stock would be immediately reflected in prices; hence, it would be  impossible to generate abnormal returns based upon past information.
+
+Yet, several authors have since stressed that  there are information-gathering costs and information is not immediately reflected on prices  \citep{grossman1980iie}.
+As such, prices may not  reflect all the available information at all time because if this were the case, those who spent resources to collect and analyze   information would not have an incentive to do it because there would not get any compensation for it.
+
+%Many trading strategies try to forecast the price movements relying on the historical prices or estimate the intrinsic value of a company.
+Obviously, this type of research is associated with significant amount of up-front costs to acquire databases, software, etc.
+On the other hand, financial analysts have these tools and, presumably, skills to identify  stocks that worth be invested.
+Thus, for an investor, it is cheaper to follow the recommendations of financial analysts rather than perform a proper stock market analysis.
+
+Some authors show that that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
+\cite{barber2001} finds that over the period of 1986-1996 a portfolio of stocks with the most (least) favorable consensus analyst recommendations yields an average abnormal return of 4.13 (-4.91)\%.}.
+Assuming that some analysts produce valuable advice it make sense to rank analysts based on the accuracy of their recommendations.
+
+StarMine rankings are based on financial analysts accuracy either on price target or EPS forecasts.
+To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES).
+This score measures ``...
+[a] relative accuracy; that is, analysts are compared against their peers.
+An analyst's SES can range from 0 to 100, with 50 representing the average analyst.
+To get a score higher than 50, an analyst must make estimates that are both significantly different from and more accurate than other analysts' estimates"\footnote{\url{http://excellence.thomsonreuters.com/award/starmine?award=Analyst+Awards&award_group=Overall+Analyst+Awards}}.
+
+As for target price ranking, StarMine's methodology compares the portfolios based on analysts recommendations.
+Portfolios are constructed as follows.
+For each ``Buy'' recommendation, the portfolio is one unit long the stock and simultaneously one unit short the benchmark.
+``Strong buy'' gets a larger investment of two units long the stock and two units short the benchmark.
+``Hold'' invests one unit in the benchmark (i.e., an excess return of zero).
+``Sell" recommendations work in the reverse way.
+StarMine re-balances its calculations at the end of each month to adjust for analysts revisions (adding, dropping or altering a rating), and when a stock enters or exits an industry grouping.
+
+Recent evidence suggests that top ranked financial analyst affect market participants: prices seem to react more to the recommendations issued by the top-ranked analysts \citep{emery2009}.
+As such, StarMine ranking based models can be used to identify such analysts and generate superior estimates (e.g., SmartEstimates\footnote{\url{http://www.starmine.com/index.phtml?page_set=sm_products&sub_page_set=sm_professional&topic=analytical&section=accurate_estimates}}).
+%Evidence shows that market response to analysts' recommendations is stronger when analysts issue them with a good forecasting tracking record \citep{park2000analyst,loh2006aef}.
+Thus, it seems to be the case that only a subset of analysts influences the stock prices and, as such, only that subset of analysts deserves to be followed \citep{loh2011}.
+
+The goal of our study is to evaluate if and how rankings  add value to investors.
+With this purpose, we develop several sets of active trading strategies, selecting the stocks most favored by analysts.
+The first strategy is based on the consensus estimate (giving equal weights to analysts' recommendations).
+The second set of strategies takes in consideration the analysts' target price and EPS accuracy ranks to form ``smart estimates".
+For the latter set of strategies, we analyse different time information sets of the accuracy of the analysts.
+
+We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy).
+By doing this, we address the ongoing debate in the literature on whether analysts, when issue the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
+For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices.
+Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.
+
+A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period<U+2019>s EPS invested at the cost of equity.}.
+In short, this model justifies a price earnings ratio for companies where next period<U+2019>s earnings are expected to grow over and above the normal rate.
+
+% and it is, in a sense, an upper bound of all trading strategies.
+
+%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \tr{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.
+
+%We claim that the ranking strategies outperform the consensus ones as well as the passive strategy.
+
+%we investigate the problem with two ranking  methods that are used further as the inputs for the trading strategy.
+The first is the \naive{} rankings and this is simply the last known analysts' actual rankings.
+The second method is taken from the Machine Learning literature \citep{aiguzhinov2010} and it is so-called the \default{} ranking.
+It is the average rank of an analyst since the beginning of the sample period and it encompasses the average analyst's relative performance.
+We formalize these methods in the appropriate section of the paper.
+
+\section{Trading Strategies}
+%- BL model
+%- Information sets
+\label{sec:trading}
+Our trading strategy use the framework for  active portfolio management proposed by \cite{black1992}.
+The model incorporates ``views" in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting.
+``Views" are expectations on individual stocks future performance by investors/analysts.
+
+While in the CAPM model expected returns are a function of systematic risk, in the BL model some stocks can be over- or under-priced and, therefore, their alphas are non-zero.
+The model blends the subjective views of investors about future performance of a stock with the market implicit returns given by CAPM.
+
+\cite{da2011bl} apply the BL model and use the consensus expected returns as a proxy for views.
+They report that the resulting strategy outperforms a passive buy-and-hold strategy.
+Our approach is similar to theirs but we define views not only based on consensus estimates but also on smart estimates that account for previous analysts' TP and EPS accuracy.
+
+Here below we kept the notation in \cite{black1992}.
+$Q$ is the vector of  expected returns for the eligible stocks; $\Omega$ matrix is the confidence of $Q$.
+Altogether these two reflect the views of a particular analyst or a set of analysts.
+
+To proxy expected returns we compare the analysts' 12-month target prices (TP) with today's stock price.
+Confidence $\Omega$ for stock is based on variation  across analysts which is similar to the measure of dispersion in analysts' opinions outlined in \cite{diether2002}.
+
+We define a trading strategy as follows (figure \ref{fig:bl}):
+\begin{enumerate}
+\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
+
+\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix across stocks;
+
+\item We apply the BL model to get  optimal portfolio weights on the basis of combining views and implicit returns.
+We  buy or sell stocks accordingly.
+At the beginning of $t+1$, based on the new views, we set the new portfolio weights following  steps 1--3.
+\end{enumerate}
+
+\subsection{Defining $Q$}
+\label{def-q}
+
+For the consensus strategy, we use median of expected returns for a particular stock $s$:
+\begin{equation}
+\label{consq}
+Q_{cons,s}= \median \left\{r_{j,s}\right\}
+%\frac{1}{N} \sum_{j=1}^{N} r_{j,s}
+\end{equation}
+%$N$ is the number of analysts with a valid TP report and
+where $r_{j,s}=TP_{j,s}/P_{s}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,s}$ and stock price $P_{s}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
+
+For the strategies that weight the analysts' estimates of expected return, we use analysts' rankings and the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
+
+\begin{equation}
+\label{eq:weight}
+w_{j,s}=1-\frac{rank_{j,s}-\min{ \{rank \} }}{\max{\{rank \}}}
+\end{equation}
+
+The expected rank-weighted return is thus:
+\begin{equation}
+\label{rankq}
+Q_{rank,s}=\frac{\sum_{j=1}^{N} (w_{j,s} \times r_{j,s})}{\sum_{j=1}^{N} w_{j,s}}
+\end{equation}
+$N$ is the number of analysts.
+
+As described above, we use target price and EPS rankings.
+
+\subsubsection{Target Price ranking}
+
+Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}.
+First,  we define the forecast daily error  $FE_{i,j}$ as the absolute value of the difference between analysts' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
+
+\begin{equation}
+\label{dfe}
+FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
+\end{equation}
+The PMAFE is given as:
+\begin{equation}
+\label{tp:pmafe}
+PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
+\end{equation}
+where $\overline{{FE}_{t,s}^{TP}}$ is the average over quarter forecasting error. The target price is fixed over the quarter unless it gets revised.
+
+The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
+\begin{equation}
+\overline{PMAFE_{j,s}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,s}^{TP}
+\end{equation}
+
+\begin{equation}
+\label{tp:rank}
+rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
+\end{equation}
+where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.
+
+\subsubsection{EPS ranking} 
+To compute the EPS rankings, we apply the same procedure as above:
+\begin{equation}
+FE_{j,s}^{EPS}=|{ACT_{s}-PRED_{j,s}}|
+\end{equation}
+\begin{equation}
+PMAFE_{j,s}^{EPS}= \frac{FE_{j,s}^{EPS}}{\overline{FE_{s}^{EPS}}}
+\end{equation}
+\begin{equation}
+\label{eps:rank}
+rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\} 
+\end{equation}
+where $ACT_{s}$ and $PRED_{j,s}$ are the actual and  analyst $j$ forecast EPS respectively for each stock $s$.
+
+\subsection{Defining the confidence of expected returns $\Omega$}
+\label{def-omega}
+The confidence of $Q$ are given by the coefficient of variation of forecasting errors:
+
+\begin{equation}
+CV = \frac{\sigma (FE)}{\overline{FE}}
+\end{equation}
+where $\sigma$ and $\overline{FE}$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS.
+A low value of $CV$ reflects consensual estimates of either future prices or EPS.
+
+\subsection{Information sets to define the views}
+
+To proceed with the trading strategy, we need to establish which information we going to use to build the rankings that will be used to compute the weighted return estimates.
+Different analysts' ranks are obtained  if we select different time horizons.
+If use only recent information, we focus on recent performance of the analysts.
+This, of course, is more sensitive to unique episodes (e.g., a quarter, which has been surprisingly good or bad).
+If, alternatively, we opt to incorporate all analyst performance, the ranking is less affected by such events, yet, it may not reflect the current abilities of the analyst.
+In this paper, we use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
+We call the former the \naive{} set and the latter the \default{} set.
+
+In addition to these sets,  we also create a hypothetical scenario that assumes we know the future information about the analyst' accuracy performance which would only be available at the end of $t$.
+In this setting, we are assuming that we could  perfectly predict the true analysts' ranking in advance.
+This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies.
+We call this approach as the \tr{} set.
+
+We formalize these sets as follows. 
+\begin{itemize}
+\item  the \tr{} %-- a perfect foresight information:
+\begin{equation}
+\label{q:true}
+\widehat{Q_{.,t}}=Q_{.,t}
+\end{equation}
+
+\item  the \naive{} % -- $t-$ information:
+\begin{equation}
+\label{q:naive}
+\widehat{Q_{.,t}}=Q_{.,t-1}
+\end{equation}
+
+\item  the \default{} %-- the entire history of analysts performance:
+%\begin{itemize}
+%\item ranking based views:
+\begin{equation}
+\label{q:default}
+\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
+\end{equation}
+%\item consensus based views:
+%\begin{equation}
+%\label{default.cons}
+%\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
+%\end{equation}
+%\end{itemize}
+\end{itemize}
+where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).
+
+\section{Data and preliminary results}
+\label{sec:rankings}
+
+\subsection{Database and sample}
+We focus on the  S\&P500 stocks.
+We extract the target price information and the EPS forecasts from ThomsonReuters  I/B/E/S detailed history database.
+The  S\&P500 constituents' list and the stock daily prices are from ThomsonReuters DataStream.
+
+The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 361, covering 504 S\&P500 stocks.
+Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+After one year we assume that TP recommendation expires.
+
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and at the 95\textsuperscript{th} percentile (values above 0.791).
+This is done due to occurrence of the extreme values.
+Most of these extreme values are driven by misalignment errors found on I/B/E/S data\footnote{We found some differences between the  DataStream and I/B/E/S the databases.
+In some cases the stock-splits and the dividends were not properly adjusted.}.
+After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 145 630 to 131 068.
+
+The initial file of quarterly EPS forecast consists of  560 brokers covering 3517 stocks.
+To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
+In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
+Our final sample of EPS forecasts consist of  155 brokers covering 402 stocks.
+The total number of observation is 79 539.
+
+Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data.
+Panel A shows the number of quarterly target prices per stock.
+For the sample period (1999-2009), we report 13 672 stock-quarter observations.
+Each stock had on average of 6.42 quarterly target price reports.
+Panel B  presents similar statistics of the number of EPS forecasts.
+In total, the EPS forecast sample has 12 084 stock-quarter observations.
+The average number of quarterly forecasts is 6.58.
+
+We apply the ranking procedure outline in section \ref{def-q} on two datasets.
+For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq.
+\ref{tp:pmafe}).
+
+Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
+Four analysts had valid target price for Amazon for second quarter of 1999.
+We plot the daily Amazon price against the brokers' target prices.
+Table \ref{tab:example} shows the resulting TP and EPS ranking.
+On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate.
+For the EPS case (panel B), PACCREST is the most accurate in EPS forecasting and RBRTSON is the least.
+
+%The daily frequency allows us to capture the analysts' performance with better precision.
+Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices.
+As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock.
+At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts.
+Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices.
+The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4).
+In this example, LEGG is the most accurate in forecasting the AMZN stock and DLJ is the least.
+\subsection{Ranking contingency results}
+We consider  three terciles (\textit{top}, \textit{medium}, \textit{bottom}).
+In one particular quarter ($t$), we place  analysts at one of these bins which corresponds to a tercile.
+We, then,  check analysts position at the immediate next quarter ($t+1$) and after one year ($t+4$).
+
+We convert the rankings into scores as follows:
+\begin{equation}
+\label{eq:score}
+score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
+\end{equation}
+
+To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,s}$
+\begin{equation}
+\label{eq:mean-score}
+score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
+\end{equation}
+where $k$ is number of stocks for which an analyst $j$ had rank.
+
+Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
+%Chi square statistics include/ expected frequiency test
+%Journ. of Fin economics 
+Panel A shows the dynamics of each tercile for rankings based on the accuracy in target prices.
+We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter and even after one year.
+The case of EPS ranking shows similar results (panel B).
+This analysis confirms recent finding of \cite{hilary2013} on analyst forecast consistency.
+
+%the next quarter  $top_{t+1}$ group is as follows: round(pt.cont.tab[[1]][1,1],3)*100\%  of analysts stay at the same ranking category from the $top_{t-1}$; round(pt.cont.tab[[1]][2,1],3)*100\% move from the $middle_{t-1}$; round(pt.cont.tab[[1]][3,1],3)*100\% from the $bottom_{t-1}$.
+It is clear to observe that the $top_{t}$ category, on the average, mostly consists of brokers from the past quarter \emph{middle} rank.
+%Observe that for the $noRank_{t}$ category, most of the contribution comes from the same category of the past quarter (round(cont.tab[[1]][4,4],3)*100\%).
+This suggests that analysts are not frequent in issuing target price reports.
+
+%This also represents ... variation to justify the effor of  trying to update the ranking every quarter in order to 
+%An interesting observation is for the \emph{noRank} category:  round(cont.tab[[2]][4,1],3)*100\% of the analysts who did not have rankings in the current quarter once issued a target price report move to the \emph{top} in the following quarter.
+
+%Panel B depicts the similar analysis for the EPS forecast rankings.
+For this case, we observe that the composition of the $top_{t}$ is quite similar to the  one we see in target price case: the most contributive group for $top_{t}$ is the \emph{middle} ranks from $t-1$.
+%However, one interesting observation is that $noRank_{t-1}$ shows significant contribution for each of the ranking groups in $t$: for the \emph{top} ranking it contributes round(eps.cont.tab[[1]][4,1],3)*100\%, for the \emph{middle} --- round(eps.cont.tab[[1]][4,2],3)*100\%, and for the \emph{bottom} --- round(eps.cont.tab[[1]][4,3],3)*100\%.
+This suggests that analysts, probably, issue the EPS forecasts after the availability of firm's management EPS forecast as that could entail new information about a firm \citep{hassel1986}.
+
+\subsection{$Q$ descriptive statistics}
+
+Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
+The expected returns  are computed comparing TP estimates with actual price.
+To inform the strategies we obtain rank-weighted estimates where weights are given either by the TP or the EPS ranks.
+
+\cite{bradshaw2002} reports that analysts' average expected returns for the period of 2000--2009 of 206 brokers 24\%, in \cite{da2011} these average expected return post 40\% for the period of 1996--2004, \cite{zhou2013} find on average  96\% for the sample period of 2000--2009 reports.
+The figures suggest that analyst overly optimistic.
+%these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns.
+\cite{bodie2009} show that arithimatic average rate of return for the U.S.
+large stocks (S\&P 500) for the period of 1926--2005 is 10.17\% and the average rate of excess return is 8.39\% with the risk premium estimated 6--8\%.
+While it is not the best idea to extrapolate the historical values, still, we can say that the expected stocks return should be around 14--16\%.
+Clearly, the values presented in the literature shows that analysts are very optimistic in issuing target price reports.
+
+Panel A show the statistics for the consensus expectations as defined in eq.
+(\ref{consq}).
+The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are 18.6\%, 18.6\%, and 21.7\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (15.7\%, 15.7\%, and 18.8\%).
+Panel C shows the EPS based weighted expected returns averages (14.9\%, 14.9\%, and 19.4\%).
+
+Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic.
+The \default{} information set shows higher values of expected returns considering that it includes the whole history of analysts' performance.
+
+%obtained from the rankings based on the target price accuracy.
+We observe a reduction in average per stock expected return with the mean of  round(rank.views.full.period['true','mean'],3)*100\%.
+The case of rankings based on EPS forecasts (panel C) shows even more moderate average stock expected return of  round(pt.eps.rank.views.full.period['true','mean'],3)*100\%.
+Overall, compared to the consensus, both ranking-based methods exhibit less optimistic expected returns and are pretty close to the historical averages.
+
+%put in to the different section
+
+\section{Empirical Results}
+\label{sec:results}
+
+We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
+
+\subsection{Passive strategy}
+Panel A shows  the performance of the passive strategy \textit{Market}.
+The strategy resulted in an annualized cumulative return of \ensuremath{-3.03}\% and the Sharpe Ratio  of \ensuremath{-0.182}.
+The average number of stocks used per quarter is 499.98 and the turnover ratio of strategy is 0.053, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+
+\subsection{Perfect foresight strategy}
+\label{sec:perfect}
+Panel B presents the results for the case of \tr{} information set.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.89\%, 5.12\%, 1.86\%.
+All the strategies outperform the benchmark (\ensuremath{-3.03}\%).
+The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
+In any case, the results suggest that the advice of analysts are valuable.
+%Yet, the top analyst
+
+%The result confirms that these strategies set an upper bound for the cumulative return yield.
+It follows, that we setup a boundary for the results of the feasible strategies: the upper bound is the perfect foresight strategy and the lower bound is the market benchmark.
+
+The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
+Its Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
+In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
+Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
+Panel A of the table corresponds to the perfect foresight information set.
+The TP strategy wins over the others in every period.
+
+While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
+One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
+For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
+
+\subsection{Feasible strategies}
+Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
+As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\ensuremath{-3.03}\%)  and gain positive cumulative annualized returns: 0.28\%,  0.13\%, \ensuremath{-0.32}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
+
+As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
+The Sharpe Ratio for this strategy is 0.018 which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
+The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
+
+The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.01}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\ensuremath{-0.07}\% and 0.44\% respectively).
+The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+
+The feasible information sets demonstrate interesting results.
+It seems to be the case that the information about stock<U+2019>s expected return based on rankings create more value than the same information but based on analysts<U+2019> consensus.
+Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
+Thus, rankings are useful for investors.
+
+%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
+Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.
+
+%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
+In addition, the results show that keeping all available information about analysts' performance does not create any value.
+As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.
+
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
+Yet, it is not the case for EPS ranking.
+This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
+EPS are not good predictors of future returns, at least for short-term horizon.
+
+Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
+The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at January of 2000 and ending at December of 2009.
+Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+
+\section{Conclusions}
+\label{sec:conclusion}
+
+Some institutions, such as StarMine, rank financial analysts based on their accuracy.
+These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
+Therefore, there is a growing interest in understanding the relative performance of analysts.
+
+We show that rankings do bring value to investors as they identify the top analysts.
+By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
+We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
+The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
+%The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.
+
+For the future work we would like to develop the new methods to be able to get closer to the upper bound.
+
+\bibliographystyle{ecta}
+%\bibliographystyle{newapa}
+\bibliography{rank}
+\appendix
+
+%\section{Tables and Figures}
+
+%Descriptive  table
+\begin{table}[hp]
+  \caption{Sample Statistics}
+  \label{tab:ret-stat}
+\ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+    \toprule
+Year & Min& Mean & Median &Max& Std.dev\\
+\midrule
+%Panel A: TP&&&&&\\
+\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
+\midrule
+%Year & Min& Mean & Median &Max& Std.dev\\
+ 1999 & 3.00 & 4.25 & 4 &  10 & 1.59 \\ 
+  2000 & 3.00 & 4.76 & 4 &  14 & 1.88 \\ 
+  2001 & 3.00 & 5.25 & 5 &  15 & 2.32 \\ 
+  2002 & 3.00 & 6.04 & 5 &  19 & 2.95 \\ 
+  2003 & 3.00 & 6.67 & 6 &  21 & 3.43 \\ 
+  2004 & 3.00 & 7.12 & 6 &  21 & 3.62 \\ 
+  2005 & 3.00 & 7.35 & 7 &  21 & 3.59 \\ 
+  2006 & 3.00 & 7.41 & 7 &  20 & 3.42 \\ 
+  2007 & 3.00 & 7.05 & 6 &  20 & 3.33 \\ 
+  2008 & 3.00 & 6.37 & 6 &  18 & 2.88 \\ 
+  2009 & 3.00 & 5.15 & 5 &  18 & 2.19 \\ 
+  Total & 3.00 & 6.42 & 6 &  21 & 3.21 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\midrule
+\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
+\midrule
+ 1999 & 3.00 & 5.73 & 5 &  17 & 3.01 \\ 
+  2000 & 3.00 & 5.43 & 5 &  17 & 2.77 \\ 
+  2001 & 3.00 & 6.02 & 5 &  18 & 2.97 \\ 
+  2002 & 3.00 & 6.34 & 5 &  21 & 3.26 \\ 
+  2003 & 3.00 & 6.52 & 6 &  24 & 3.43 \\ 
+  2004 & 3.00 & 6.95 & 6 &  22 & 3.75 \\ 
+  2005 & 3.00 & 7.21 & 6 &  24 & 3.77 \\ 
+  2006 & 3.00 & 7.49 & 7 &  26 & 3.84 \\ 
+  2007 & 3.00 & 7.13 & 6 &  21 & 3.53 \\ 
+  2008 & 3.00 & 6.38 & 6 &  22 & 3.06 \\ 
+  2009 & 3.00 & 5.81 & 5 &  20 & 2.78 \\ 
+  Total & 3.00 & 6.58 & 6 &  26 & 3.43 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Example of ranking}
+  \label{tab:example}
+\ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999.
+We apply (\ref{tp:rank}) to obtain the ranks of the brokers.
+\emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error.
+For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts.
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+    \toprule
+    \multicolumn{4}{c}{\textbf{Panel A: TP}} \\
+Broker/Analyst & \emph{TP} & $\overline{PMAFE}^{TP}$ & $rank^{TP}$ \\ 
+  \midrule 
+LEGG & 58.50 & 0.05 &   1 \\ 
+  MONTSEC & 87.50 & 0.46 &   2 \\ 
+  KAUFBRO & 125.00 & 1.65 &   3 \\ 
+  DLJ & 140.00 & 1.97 &   4 \\ 
+   \midrule
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+    \multicolumn{4}{c}{\textbf{Panel B: EPS}} \\
+Broker/Analyst & $PRED$ & $PMAFE^{EPS}$ & $rank^{EPS}$ \\ 
+  \midrule 
+MONTSEC & -0.120 & 0.027 &    1 \\ 
+  BEAR & -0.130 & 0.080 &    2 \\ 
+  PACCREST & -0.130 & 0.080 &    2 \\ 
+  BACHE & -0.135 & 0.107 &    4 \\ 
+  RBRTSON & -0.140 & 0.133 &    5 \\ 
+  FBOSTON & -0.145 & 0.160 &    6 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}

### 2015-02-16 src/eda.R

@@ -260,3 +260,93 @@ mean.pt.dt[order(pt.ratio,decreasing=T)]
 #
 # new.p[Stock=='AAPL',':='(Price=Price*7,new.dsPT=new.dsPT*7)]
 
+###EDA of trading stratgies
+###
+
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+facet_wrap(~ Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))+geom_hline(yintercept=100)
+
+
+
+ggplot(final.bl,aes(x=as.Date(Quarters),y=port.ret,group=Views,color=Views))+geom_line(size=0.5)+facet_wrap(~ Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
+
+
+
+final.bl[,chart.CumReturns(xts(port.ret,order.by=as.Date(Quarters))),by=.(Method,Aggregation,Views)]
+
+test <- acast(final.bl,Quarters~Method~Views,value.var = 'port.ret')
+
+require(Quandl)
+requre(quantmod)
+Quandl.auth("X5ws5JEoYdP6VFefbPmQ")
+prices = getSymbols("^GSPC", from = "1999-01-01", to = "2009-12-31")
+tbil <- unique(data.table(Quandl('FRED/DTB3',start_date = '1999-01-01',end_date = '2009-12-31',sort='asc'))[,Quarters:=as.yearqtr(Date)][,rf:=mean(Value)/100/4,by=Quarters],by='Quarters')[3:44,.(Quarters,rf)]
+sp.ind <- (quarterlyReturn(get(prices)[,6]))[3:44,]-tbil[,rf]
+
+
+test.xts <- cbind(xts(test[,'true',],order.by=as.Date(as.yearqtr(dimnames(test)[[1]]))),coredata(sp.ind))
+
[…]

### 2015-02-16 src/paper.trading.APS.true.R

@@ -55,7 +55,7 @@ cache('eps.rank.views')
 
 
 
-meanTper <- na.omit(melt(unique(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,true:=median(true,na.rm=T),by=list(q.id,Stock)],by=c('q.id','Stock'))[,.(q.id,Stock,true)][,':='(naive=c(NA,head(true,-1)),default=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T)),by=Stock],id.vars = c('q.id','Stock'),measure.vars = c('true','naive','default'),variable.name = 'Method')[q.id!='1999 Q2',])
+meanTper <- na.omit(melt(unique(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,true:=median(true,na.rm=T),by=list(q.id,Stock)],by=c('q.id','Stock'))[,.(q.id,Stock,true)][,naive:=c(NA,head(true,-1)),by=Stock][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=Stock],id.vars = c('q.id','Stock'),measure.vars = c('true','naive','default'),variable.name = 'Method')[q.id!='1999 Q2',])
 
 #meanTper <- pt.exp.ret[,median(exp.ret,na.rm=T),by=.(q.id,Stock,Method)]
 
@@ -68,7 +68,7 @@ cons.list.rank <- acast(unique(meanTper,by=c('q.id','Stock','Method')),q.id~Stoc
 require(scales)
 
 
-conf.dt <- melt(unique(core.dt,by=c('q.id','Stock'),fromLast = T)[,.(q.id,Stock,s.coefVar)][,true:=0][,naive:=c(NA,head(s.coefVar,-1)),by=Stock][,default:=rollapplyr(s.coefVar,seq_len(length(s.coefVar)),mean,na.rm=T,partial=T),by=Stock],id.vars = c('q.id','Stock'),measure.vars = c('true','naive','default'))[q.id!='1999 Q2',]
[…]

### 2015-02-16 src/script.predict.trade.R

@@ -8,6 +8,10 @@ delta<-1L;tau=1/50;baselines <- c('true','naive','default');methods<-c('raw','1d
 require(labelRank)
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)
 system.time(source('munge/01-data.q.ret.R'))
+
+### data for first paper
+system.time(source('src/paper.trading.APS.true.R'))
+
 ### State var. data: ~118 sec
 system.time(source('munge/02-state-variables.R'))
 ### Analysts ranking data: ~ 280 sec

### 2015-02-16 doc/paper/paper-knitr-APS.tex
Fixed contingency table funciton, now uses stocks with minimum 4 brokers per quarter. Paper generated

@@
-\documentclass{article}
+\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{fancyhdr}
@@
 %-------------------------------------------------------------------------
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in na.omit(dt): object 'ranked.pt.dt' not found}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in na.omit(dt): object 'ranked.eps.dt' not found}}\end{kframe}
-\end{knitrout}
 
@@
 
-A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period<U+2019>s EPS invested at the cost of equity.}.
-In short, this model justifies a price earnings ratio for companies where next period<U+2019>s earnings are expected to grow over and above the normal rate.
+A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period’s EPS invested at the cost of equity.}.
+In short, this model justifies a price earnings ratio for companies where next period’s earnings are expected to grow over and above the normal rate.
 
@@
 The feasible information sets demonstrate interesting results.
-It seems to be the case that the information about stock<U+2019>s expected return based on rankings create more value than the same information but based on analysts<U+2019> consensus.
+It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus.
 Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
@@
 \end{table}
+
+ % Descritive rankings
+ \begin{table}[hp]
+  \caption{Analysts' accuracy consistency}
+  \label{tab:rank-stat}
+
+\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins.
+Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+    \toprule
+\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+
+ &$top$ & 68.1 & 21.5 & 10.5 & 100.2 \\ 
+  &$middle$ & 29.9 & 49.0 & 21.1 & 100.1 \\ 
+  &$bottom$ & 14.0 & 16.4 & 69.6 & 100.0 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 46.7 & 27.4 & 25.9 & 100.0 \\ 
+  &$middle$ & 41.0 & 28.6 & 30.4 & 100.0 \\ 
+  &$bottom$ & 33.6 & 26.6 & 39.7 & 100.0 \\
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\midrule
+\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+ &$top$ & 48.0 & 25.7 & 28.3 & 101.9 \\ 
+  &$middle$ & 47.1 & 26.5 & 27.1 & 100.7 \\ 
+  &$bottom$ & 44.9 & 26.1 & 29.7 & 100.8 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 47.7 & 28.1 & 26.3 & 102.1 \\ 
+  &$middle$ & 42.3 & 30.0 & 29.6 & 101.8 \\ 
+  &$bottom$ & 44.0 & 26.2 & 31.6 & 101.7 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
+  \label{tab:view-stat}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 & 219 & 0.28 & 0.27 & 0.12 \\ 
+  2000 & 295 & 0.28 & 0.27 & 0.12 \\ 
+  2001 & 341 & 0.25 & 0.24 & 0.13 \\ 
+  2002 & 374 & 0.22 & 0.20 & 0.12 \\ 
+  2003 & 390 & 0.20 & 0.18 & 0.12 \\ 
+  2004 & 399 & 0.15 & 0.14 & 0.09 \\ 
+  2005 & 414 & 0.14 & 0.14 & 0.10 \\ 
+  2006 & 421 & 0.15 & 0.14 & 0.10 \\ 
+  2007 & 426 & 0.14 & 0.13 & 0.09 \\ 
+  2008 & 420 & 0.16 & 0.15 & 0.10 \\ 
+  2009 & 365 & 0.22 & 0.20 & 0.13 \\ 
+  Total & 442 & 0.19 & 0.17 & 0.12 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 219 & 0.24 & 0.24 & 0.10 \\ 
+  2000 & 295 & 0.24 & 0.23 & 0.10 \\ 
+  2001 & 341 & 0.21 & 0.21 & 0.10 \\ 
+  2002 & 374 & 0.18 & 0.17 & 0.10 \\ 
+  2003 & 390 & 0.16 & 0.15 & 0.09 \\ 
+  2004 & 399 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 414 & 0.12 & 0.12 & 0.08 \\ 
+  2006 & 421 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 426 & 0.12 & 0.12 & 0.08 \\ 
+  2008 & 420 & 0.13 & 0.12 & 0.09 \\ 
+  2009 & 365 & 0.18 & 0.17 & 0.10 \\ 
+  Total & 442 & 0.16 & 0.14 & 0.10 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 & 144 & 0.17 & 0.14 & 0.12 \\ 
+  2000 & 211 & 0.19 & 0.17 & 0.12 \\ 
+  2001 & 257 & 0.18 & 0.17 & 0.11 \\ 
+  2002 & 299 & 0.18 & 0.16 & 0.11 \\ 
+  2003 & 311 & 0.16 & 0.15 & 0.10 \\ 
+  2004 & 331 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 343 & 0.13 & 0.12 & 0.09 \\ 
+  2006 & 344 & 0.13 & 0.11 & 0.09 \\ 
+  2007 & 357 & 0.12 & 0.11 & 0.09 \\ 
+  2008 & 339 & 0.14 & 0.13 & 0.10 \\ 
+  2009 & 300 & 0.18 & 0.17 & 0.12 \\ 
+  Total & 376 & 0.15 & 0.13 & 0.10 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
+  \label{tab:view-stat-naive}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 &  73 & 0.27 & 0.26 & 0.13 \\ 
+  2000 & 257 & 0.28 & 0.27 & 0.12 \\ 
+  2001 & 310 & 0.26 & 0.25 & 0.13 \\ 
+  2002 & 362 & 0.22 & 0.20 & 0.13 \\ 
+  2003 & 374 & 0.21 & 0.20 & 0.12 \\ 
+  2004 & 385 & 0.15 & 0.14 & 0.10 \\ 
+  2005 & 401 & 0.14 & 0.14 & 0.09 \\ 
+  2006 & 415 & 0.15 & 0.14 & 0.10 \\ 
+  2007 & 421 & 0.14 & 0.13 & 0.10 \\ 
+  2008 & 422 & 0.14 & 0.14 & 0.09 \\ 
+  2009 & 405 & 0.23 & 0.21 & 0.14 \\ 
+  Total & 442 & 0.19 & 0.17 & 0.12 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  73 & 0.24 & 0.23 & 0.11 \\ 
+  2000 & 257 & 0.24 & 0.24 & 0.10 \\ 
+  2001 & 310 & 0.22 & 0.22 & 0.10 \\ 
+  2002 & 362 & 0.19 & 0.17 & 0.10 \\ 
+  2003 & 374 & 0.17 & 0.17 & 0.09 \\ 
+  2004 & 385 & 0.13 & 0.12 & 0.08 \\ 
+  2005 & 401 & 0.12 & 0.11 & 0.08 \\ 
+  2006 & 415 & 0.13 & 0.12 & 0.08 \\ 
+  2007 & 421 & 0.12 & 0.12 & 0.08 \\ 
+  2008 & 422 & 0.12 & 0.11 & 0.08 \\ 
+  2009 & 405 & 0.19 & 0.18 & 0.11 \\ 
+  Total & 442 & 0.16 & 0.14 & 0.10 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  44 & 0.12 & 0.12 & 0.10 \\ 
+  2000 & 185 & 0.18 & 0.16 & 0.12 \\ 
+  2001 & 247 & 0.18 & 0.17 & 0.11 \\ 
+  2002 & 288 & 0.18 & 0.16 & 0.11 \\ 
+  2003 & 307 & 0.18 & 0.17 & 0.11 \\ 
+  2004 & 318 & 0.13 & 0.12 & 0.09 \\ 
+  2005 & 337 & 0.13 & 0.12 & 0.09 \\ 
+  2006 & 343 & 0.13 & 0.12 & 0.09 \\ 
+  2007 & 352 & 0.12 & 0.11 & 0.09 \\ 
+  2008 & 349 & 0.13 & 0.12 & 0.09 \\ 
+  2009 & 321 & 0.19 & 0.17 & 0.12 \\ 
+  Total & 376 & 0.15 & 0.13 & 0.10 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
+  \label{tab:view-stat-default}
+  \small\addtolength{\tabcolsep}{-2pt}
+
+\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+    \toprule
+Year &Stocks& Mean & Median &Std.dev\\
+\midrule
+  \multicolumn{5}{c}{\textbf{Panel A: Consensus views (\ref{consq})}} \\ \midrule 
+1999 &  73 & 0.27 & 0.26 & 0.13 \\ 
+  2000 & 257 & 0.28 & 0.27 & 0.12 \\ 
+  2001 & 314 & 0.27 & 0.26 & 0.11 \\ 
+  2002 & 368 & 0.25 & 0.24 & 0.11 \\ 
+  2003 & 383 & 0.24 & 0.23 & 0.10 \\ 
+  2004 & 396 & 0.22 & 0.22 & 0.10 \\ 
+  2005 & 414 & 0.21 & 0.20 & 0.09 \\ 
+  2006 & 429 & 0.20 & 0.19 & 0.09 \\ 
+  2007 & 438 & 0.19 & 0.18 & 0.09 \\ 
+  2008 & 440 & 0.18 & 0.18 & 0.08 \\ 
+  2009 & 442 & 0.19 & 0.18 & 0.08 \\ 
+  Total & 442 & 0.22 & 0.20 & 0.10 \\
+
+  \midrule
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel B: TP ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  73 & 0.24 & 0.23 & 0.11 \\ 
+  2000 & 257 & 0.24 & 0.24 & 0.10 \\ 
+  2001 & 314 & 0.24 & 0.23 & 0.09 \\ 
+  2002 & 368 & 0.22 & 0.21 & 0.09 \\ 
+  2003 & 383 & 0.21 & 0.20 & 0.09 \\ 
+  2004 & 396 & 0.19 & 0.19 & 0.08 \\ 
+  2005 & 414 & 0.17 & 0.17 & 0.08 \\ 
+  2006 & 429 & 0.17 & 0.16 & 0.08 \\ 
+  2007 & 438 & 0.16 & 0.16 & 0.07 \\ 
+  2008 & 440 & 0.16 & 0.15 & 0.07 \\ 
+  2009 & 442 & 0.16 & 0.16 & 0.07 \\ 
+  Total & 442 & 0.19 & 0.18 & 0.09 \\ 
+   \midrule
+
+  \end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \midrule
+  \multicolumn{5}{c}{\textbf{Panel C: EPS ranking views (\ref{rankq})}} \\ \midrule 
+1999 &  54 & 0.12 & 0.11 & 0.09 \\ 
+  2000 & 205 & 0.18 & 0.15 & 0.12 \\ 
+  2001 & 264 & 0.20 & 0.19 & 0.11 \\ 
+  2002 & 308 & 0.22 & 0.21 & 0.10 \\ 
+  2003 & 326 & 0.22 & 0.21 & 0.09 \\ 
+  2004 & 339 & 0.21 & 0.20 & 0.08 \\ 
+  2005 & 357 & 0.19 & 0.19 & 0.08 \\ 
+  2006 & 365 & 0.19 & 0.18 & 0.08 \\ 
+  2007 & 371 & 0.18 & 0.18 & 0.08 \\ 
+  2008 & 375 & 0.18 & 0.18 & 0.07 \\ 
+  2009 & 378 & 0.18 & 0.18 & 0.07 \\ 
+  Total & 378 & 0.19 & 0.19 & 0.09 \\
+
+\bottomrule
+  \end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Trading strategy performance}
+  \label{tab:strategy}
+  \ This table shows the performance statistics of the different trading strategies.
+Panel A presents the results for the passive strategy.
+Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}).
+Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average.
+The trading period spreads from 2000Q1 until 2009Q4.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \toprule
+  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
+Strategy&Annualized cum. return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
+\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
+  \midrule
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
+ \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
+  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
+  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
+   \midrule
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
+  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
+  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
+   \midrule
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
+  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
+  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Trading strategy performance: Sharpe ratio}
+  \label{tab:substrategy}
+  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the recent and the all history analysts' performance.
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\toprule
+  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
+Period&\textit{Market}&\textit{CONS}&\textit{TP}&\textit{EPS} \\  \multicolumn{5}{l}{\textbf{Panel A: \tr{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.287 & 0.447 & 0.232 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.261 & 0.477 & 0.311 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.485 & 0.794 & 0.540 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.201 & 1.844 & 1.299 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.233 & 0.136 & -0.173 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.042 & 0.242 & 0.011 \\ 
+  All period & -0.182 & 0.125 & 0.351 & 0.123 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel B: \naive{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.168 & 0.169 & 0.072 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.171 & 0.215 & 0.167 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.448 & 0.492 & 0.453 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.105 & 1.246 & 1.152 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.344 & -0.306 & -0.332 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.146 & -0.126 & -0.106 \\ 
+  All period & -0.182 & 0.008 & 0.018 & -0.020 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.247 & 0.233 & 0.276 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.230 & 0.252 & 0.283 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.430 & 0.469 & 0.490 \\ 
+  2003Q1/2007Q4 & 0.925 & 0.876 & 0.962 & 0.970 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.439 & -0.415 & -0.403 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.235 & -0.210 & -0.193 \\ 
+  All period & -0.182 & -0.004 & -0.000 & 0.028 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{figure}[hp]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/Black-litterman}
+\end{center}
+\caption{Trading strategy timeline}
+\label{fig:bl}
+\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
+\end{figure}
+
+\begin{figure}[hp]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/example-fig-1}
+\end{center}
+\caption{Daily stock price Amazon and brokers target prices}
+\label{fig:example}
+\ Target price and actual prices for Amazon  the second quarter of 1999.
+\end{figure}
+
+\begin{figure}[hp]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/bl-results-fig-1}
+\end{center}
+\caption{Performance of the BL model}
+\label{fig:bl-results}
+\ Quarterly performance of the cumulative portfolio wealth for all strategies.
+Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$.
+\textit{TP} is the strategy with rankings based on the accuracy in target prices, \textit{CONS} is the strategy based on the consensus among the analysts regarding a stock's expected return.
+\textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
+The trading period ranges from 2000Q1 until 2009Q4
+\end{figure}
+
+\end{document}

### 2015-02-16 src/paper.trading.APS.true.R

@@ -8,8 +8,12 @@ core.dt <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:
 
 pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
 
+### Need ranked dt for contigency analysis
+ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)]
 
-pt.new <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','true')][,.(q.id,Broker,Stock,true)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,mean.rank:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)][,default:=rank(mean.rank,na.last = 'keep'),by=.(q.id,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'rank',variable.name = 'Method'),q.id,Stock,Broker,Method)
+cache('ranked.pt.dt')
+
[…]

### 2015-02-16 lib/aux.functions.R
Fixed contingency table funciton, now uses stocks with minimum 4 brokers per quarter. Paper generated

@@ -99,7 +99,7 @@ cont.tab.f <- function(dt,t,n.b)
         rank.split <- na.omit(dt)[,valid.b:=.N>n.b,by=.(q.id,Stock)][(valid.b)][,valid:=.N>4,by=.(Broker,Stock)][(valid)][,next.per:=terciles.rank.f(true,n),by=list(q.id,Stock)][,next.q:=c(rep(NA,t),as.numeric(diff(q.id,t))==t/4),by=.(Broker,Stock)][,cur.per:=c(rep(NA,t),head(next.per,-t)),by=list(Broker,Stock)][,cur.per:=ifelse(is.na(cur.per),NA,ifelse(next.q==TRUE,cur.per,NA))]
         
         require(descr)
-        pt.cont.dt <- na.omit(rank.split)[,valid.s:=length(unique(next.per))>=3,by=.(Stock)][(valid.s)][,as.data.table(crosstab(cur.per,next.per,prop.r=T,prop.c=F,prop.t=F,prop.chisq = F,plot=F,missing.include=F,chisq=F)[2]),by=Stock][,value:=letters[1:9],by=Stock][,mean(prop.row),by=value]
+        pt.cont.dt <- na.omit(rank.split)[,valid.s:=.N>n,by=.(Stock)][(valid.s)][,as.data.table(crosstab(cur.per,next.per,prop.r=T,prop.c=F,prop.t=F,prop.chisq = F,plot=F,missing.include=F,chisq=F)[2]),by=Stock][,value:=letters[1:9],by=Stock][,mean(prop.row),by=value]
         
         matrix(pt.cont.dt[,V1],nrow=3,ncol=3)[c(3,2,1),c(3,2,1)]
 }

### 2015-02-16 src/script.predict.trade.R

@@ -15,7 +15,7 @@ system.time(source('src/paper.trading.APS.true.R'))
 ### State var. data: ~118 sec
 system.time(source('munge/02-state-variables.R'))
 ### Analysts ranking data: ~ 280 sec
-#system.time(source('munge/03-analysts.process.R'))
+system.time(source('munge/03-analysts.process.R'))
 ### Predicting ~ 347 sec
 system.time(source('src/predicting.R'))
 

### 2015-02-16 doc/paper/paper-knitr-APS.Rnw
Knitr from command line in R now

@@
 library(xtable)
-library("PerformanceAnalytics")
+library(PerformanceAnalytics)
 load('cache/q.data.RData')

### 2015-02-16 src/paper.trading.APS.true.R

@@ -118,6 +118,8 @@ final.bl$Method <- factor(final.bl$Method,levels=unique(final.bl$Method)[c(3,2,1
 final.bl$Views <- factor(final.bl$Views,levels=unique(final.bl$Views)[c(4,1,2,3)])
 cache('final.bl')
 #require("knitr")
-#knit('doc/paper/paper-knitr-APS.Rnw',output = 'doc/paper/')
-colourCount = length(unique(final.bl$Views))
-getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
+setwd('~/Dropbox/workspace/Projects/BL-strategies/doc/paper/')
+knit2pdf('paper-knitr-APS.Rnw',quiet=T)
+
+#colourCount = length(unique(final.bl$Views))
+#getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))

### 2015-03-11 doc/paper/chapter-1.Rnw
clean workspace for the true, naive, default cases. Predictions are in Black-Lit

@@
-% \documentclass{article}
-% \usepackage{fancyhdr}
-% \usepackage{time}
-% \usepackage{authblk}
-% \usepackage{amsmath, amssymb}
-% \usepackage{caption}
-% \captionsetup[table]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
-% \captionsetup[figure]{textfont={large},labelfont={normalsize},labelsep=newline,justification=justified,singlelinecheck=true, skip=0pt}
-% %\usepackage{fullpage}
-% %\usepackage{rotating}
-% %\usepackage{xcolor}
-% \usepackage[hyphens]{url}
-% \usepackage[colorlinks=true,urlcolor=blue,citecolor=black]{hyperref}
-% %\usepackage{breakurl}
-% \usepackage{times}
-% \usepackage{setspace}
-% \usepackage{graphicx}
-% \usepackage{array}
-% \usepackage{tabularx}
-% \usepackage{booktabs}
-% \usepackage{multirow}
-% %\onehalfspacing
-% \doublespace
-% \usepackage[longnamesfirst]{natbib}
-% %\usepackage[natbibapa,longnamesfist]{apacite}
-% 
-% \DeclareMathOperator*{\argmax}{arg\,max}
-% %\newcommand{\r}{\Sexpr{}}
-% \DeclareMathOperator{\rank}{rank}
-% \DeclareMathOperator*{\median}{median}
-% %\newcommand{\theHalgorithm}{\arabic{algorithm}}
-% \newcommand{\tr}{\textit{true}}
-% \newcommand{\naive}{\textit{recent}}
-% \newcommand{\default}{\textit{all-time}}
-% \newcommand{\market}{\textit{market}}
-% \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
-% %\newcommand{\raw}{\textit{raw}}
-% %\newcommand{\diff}{\textit{diff}}
-% %\newcommand{\random}{\textit{random}}
-% %\newcommand{\rollsd}{\textit{roll.sd}}
-% 
-% 
-% \newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-% 
-% %-------------------------------------------------------------------------
-% % take the % away on next line to produce the final camera-ready version
-% % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
-% %\pagestyle{empty}
-% \pagestyle{fancy}
-%  
-% \newcommand\myTime{\now}
-% \fancyhead{}
-% \fancyhead[CO, CE]{\texttt{-Draft-}}
-% \fancyhead[RO, RE]{\texttt{\today, \myTime}}
-% \setlength{\headheight}{2\baselineskip}
-% \renewcommand{\headrulewidth}{0pt}
-% %-------------------------------------------------------------------------
-% 
-% 
-% \begin{document}
-
 <<include=FALSE>>=
@@
 library(xtable)
-library("PerformanceAnalytics")
+library(PerformanceAnalytics)
+library(abind)
 load('cache/q.data.RData')
@@
 
-brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
+full.stat.call <- quote(list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)))
+
+brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,eval(full.stat.call),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,eval(full.stat.call)]),1,'year'))
 
 #Views stat
+my.call=quote(list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))))
 
-stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']
+stat.nr <- rbind(na.omit(nr.views)[,eval(my.call),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,eval(my.call),by=.(Method)]),1,'year'))[,Strategy:='CONS']
 
-stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']
+stat.pt.view <- rbind(pt.rank.views[View!=0,eval(my.call),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,eval(my.call),by=.(Method)]),1,'year'))[,Strategy:='PT']
 
-stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']
+stat.eps.view <- rbind(eps.rank.views[View!=0,eval(my.call),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,eval(my.call),by=.(Method)]),1,'year'))[,Strategy:='EPS']
 
@@
 
-brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
+brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,eval(full.stat.call),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,eval(full.stat.call)]),1,'year'))
 
@@
 
-% \title{Are rankings of financial analysts useful to investors?}
-%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
-%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
-%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-% 
-% \affil[1]{FEP \& CEF.UP, University of Porto}
-% \affil[2]{INESC TEC}
-% \affil[4]{FEUP, University of Porto}
-% 
-% 
-% \maketitle
-% % You need this here, or else the first page won't have a header.
-% \thispagestyle{fancy}
-% 
-% \begin{abstract}
-% Some institutions issue rankings of financial analysts.
-Given that these rankings are \textit{ex-post} they may not be able useful to investors.
-In this paper  we show that trading strategies based on past rankings outperform a passive strategy.
-In addition, we report that analysts issuing accurate price targets are more favorable to the investors  to follow rather than analysts issuing accurate EPS forecasts.
-In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
-% %Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
-% \end{abstract}
-
 \chapter{Are rankings of financial analysts useful to investors?}
 \section{Introduction}
-\label{sec:intro}
+\label{ch1-sec:intro}
 
@@
 
-The paper is organized as follows: section \ref{sec:ranking} provides motivation to use rankings of financial analysts; section \ref{sec:trading} outlines our proposed  trading strategies; section \ref{sec:rankings} describes the sample and presents some preliminary results; section \ref{sec:results} presents and discusses the results; and section \ref{sec:conclusion} concludes.
+The paper is organized as follows: section \ref{ch1-sec:ranking} provides motivation to use rankings of financial analysts; section \ref{ch1-sec:trading} outlines our proposed  trading strategies; section \ref{ch1-sec:rankings} describes the sample and presents some preliminary results; section \ref{ch1-sec:results} presents and discusses the results; and section \ref{ch1-sec:conclusion} concludes.
 
 \section{Industry Rankings of Financial Analysts}
-\label{sec:ranking}
+\label{ch1-sec:ranking}
 
@@
 
-%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \tr{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.
+%In addition, for each strategy, we have three timing scenarios of when we know the analysts' information: we use the \true{} timing for the case when the information is known at time $t$ (a hypothetical case); we use the \naive{} timing for the $t-1$ case, and we use the \default{} timing \citep{aiguzhinov2010} for the $t=1 \ldots t-1$ case.
 
@@
 %- Information sets
-\label{sec:trading}
+\label{ch1-sec:trading}
 Our trading strategy use the framework for  active portfolio management proposed by \cite{black1992}.
@@
 
-We define a trading strategy as follows (figure \ref{fig:bl}):
+We define a trading strategy as follows (figure \ref{ch1-fig:bl}):
 \begin{enumerate}
-\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
+\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{ch1-def-q} and \ref{ch1-def-omega} below);
 
@@
 \subsection{Defining $Q$}
-\label{def-q}
+\label{ch1-def-q}
 
@@
 \begin{equation}
-\label{consq}
+\label{ch1-consq}
 Q_{cons,s}= \median \left\{r_{j,s}\right\}
@@
 \begin{equation}
-\label{eq:weight}
+\label{ch1-eq:weight}
 w_{j,s}=1-\frac{rank_{j,s}-\min{ \{rank \} }}{\max{\{rank \}}}
@@
 \begin{equation}
-\label{rankq}
+\label{ch1-rankq}
 Q_{rank,s}=\frac{\sum_{j=1}^{N} (w_{j,s} \times r_{j,s})}{\sum_{j=1}^{N} w_{j,s}}
@@
 \begin{equation}
-\label{dfe}
+\label{ch1-dfe}
 FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
@@
 \begin{equation}
-\label{tp:pmafe}
+\label{ch1-tp:pmafe}
 PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
@@
 
-The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
+The rank  that enters equation (\ref{ch1-eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
 \begin{equation}
@@
 \begin{equation}
-\label{tp:rank}
+\label{ch1-tp:rank}
 rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
 \end{equation}
-where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.
+where $T$ is the number of trading days in a quarter. Figure \ref{ch1-fig:example} shows an example.
 
@@
 \begin{equation}
-\label{eps:rank}
+\label{ch1-eps:rank}
 rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\}
@@
 \subsection{Defining the confidence of expected returns $\Omega$}
-\label{def-omega}
+\label{ch1-def-omega}
 The confidence of $Q$ are given by the coefficient of variation of forecasting errors:
@@
 \begin{equation}
+\label{ch1-omega}
 CV = \frac{\sigma (FE)}{\overline{FE}}
@@
 This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies.
-We call this approach as the \tr{} set.
+We call this approach as the \true{} set.
 
@@
 \begin{itemize}
-\item  the \tr{} %-- a perfect foresight information:
+\item  the \true{} %-- a perfect foresight information:
 \begin{equation}
-\label{q:true}
+\label{ch1-q:true}
 \widehat{Q_{.,t}}=Q_{.,t}
@@
 \begin{equation}
-\label{q:naive}
+\label{ch1-q:naive}
 \widehat{Q_{.,t}}=Q_{.,t-1}
@@
 \begin{equation}
-\label{q:default}
+\label{ch1-q:default}
 \widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
@@
 %\begin{equation}
-%\label{default.cons}
+%\label{ch1-default.cons}
 %\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).
+where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{ch1-consq}) or $Q_{rank,s}$ (eq. \ref{ch1-rankq}).
 
 \section{Data and preliminary results}
-\label{sec:rankings}
+\label{ch1-sec:rankings}
 
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
+After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{q.data[,.N]} to \Sexpr{q.data[!is.na(trunk.view),.N]}.
 
@@
 Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+The total number of observation is \Sexpr{complete.dt[,.N]}.
 
-Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data.
+Table (\ref{ch1-tab:ret-stat}) shows the distribution of the final sample of target price and EPS data.
 Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
+For the sample period (1999-2009), we report \Sexpr{core.dt[,.N,by=list(Stock,q.id)][,.N]} stock-quarter observations.
 Each stock had on average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
+In total, the EPS forecast sample has \Sexpr{complete.dt[,.N,by=list(Stock,q.id)][,.N]} stock-quarter observations.
 The average number of quarterly forecasts is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.
 
-We apply the ranking procedure outline in section \ref{def-q} on two datasets.
+We apply the ranking procedure outline in section \ref{ch1-def-q} on two datasets.
 For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq.
-\ref{tp:pmafe}).
+\ref{ch1-tp:pmafe}).
 
-Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
+Table \ref{ch1-tab:example} and figure \ref{ch1-fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
 Four analysts had valid target price for Amazon for second quarter of 1999.
 We plot the daily Amazon price against the brokers' target prices.
-Table \ref{tab:example} shows the resulting TP and EPS ranking.
+Table \ref{ch1-tab:example} shows the resulting TP and EPS ranking.
 On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate.
@@
 %The daily frequency allows us to capture the analysts' performance with better precision.
-Panel A of table (\ref{tab:example}) shows an example of rankings based on target prices.
+Panel A of table (\ref{ch1-tab:example}) shows an example of rankings based on target prices.
 As we observe, during the second quarter of 1999, four analysts have valid target prices for Amazon (AMZN) stock.
-At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{tp:pmafe}) and (\ref{tp:rank}) to obtain the ranks of each of the analysts.
-Figure (\ref{fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices.
+At the end of the quarter, we calculate the average daily error for each of the analysts and apply equations (\ref{ch1-tp:pmafe}) and (\ref{ch1-tp:rank}) to obtain the ranks of each of the analysts.
+Figure (\ref{ch1-fig:example}) demonstrates the daily AMZN stock price and the levels of the analysts' target prices.
 The model gives to brokers the follow ranking: LEGG(1), MONTSEC(2), KAUFBRO(3), DLJ(4).
@@
 \begin{equation}
-\label{eq:score}
+\label{ch1-eq:score}
 score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
@@
 \begin{equation}
-\label{eq:mean-score}
+\label{ch1-eq:mean-score}
 score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
@@
 
-Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
+Table (\ref{ch1-tab:rank-stat}) shows a contingency analysis of the ranks.
 %Chi square statistics include/ expected frequiency test
@@
 
-Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
+Tables \ref{ch1-tab:view-stat} -- \ref{ch1-tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
 The expected returns  are computed comparing TP estimates with actual price.
@@
 Panel A show the statistics for the consensus expectations as defined in eq.
-(\ref{consq}).
-The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively.
+(\ref{ch1-consq}).
+The average consensus among the analysts about stock expected return for \true{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively.
 Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{ round(stat.pt.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.pt.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.pt.view[year=='Total'&Method=='default',mean],3)*100}\%).
@@
 \section{Empirical Results}
-\label{sec:results}
+\label{ch1-sec:results}
 
-We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
+We report results from trading strategies in table (\ref{ch1-tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
 
@@
 Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results[4,1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results[4,1,'ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results[4,1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results[4,1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}.
+The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
 
 \subsection{Perfect foresight strategy}
-\label{sec:perfect}
-Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results[1,1,1],2)}\%, \Sexpr{round(bl.results[2,1,1],2)}\%, \Sexpr{round(bl.results[3,1,1],2)}\%.
-All the strategies outperform the benchmark (\Sexpr{round(bl.results[4,1,1],2)}\%).
+\label{ch1-sec:perfect}
+Panel B presents the results for the case of \true{} information set.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results['CONS',1,1],2)}\%, \Sexpr{round(bl.results['TP',1,1],2)}\%, \Sexpr{round(bl.results['EPS',1,1],2)}\%.
+All the strategies outperform the benchmark (\Sexpr{round(bl.results['Market',1,1],2)}\%).
 The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
@@
 In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
-Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
+Table \ref{ch1-tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
 Panel A of the table corresponds to the perfect foresight information set.
@@
 \subsection{Feasible strategies}
-Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
-As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
+Panels C of table (\ref{ch1-tab:strategy}) show the performance of the \naive{} information sets.
+As in case of \true{} information set (\ref{ch1-sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
 
-As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
+As in case of the \true{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
 The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
-The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
+The sub-period analysis (panel B of table \ref{ch1-tab:substrategy}) show that this strategy outperforms the others.
 
-The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively).
-The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+The case of the \default{} (panel D table \ref{ch1-tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively).
+The panel C of table \ref{ch1-tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
 
@@
 
-Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
+Figure \ref{ch1-fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
 The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
-Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+Observe that strategies under the \true{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
 
 \section{Conclusions}
-\label{sec:conclusion}
+\label{ch1-sec:conclusion}
 
@@
 By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
-We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
+We report that under the \true{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
 The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
@@
 For the future work we would like to develop the new methods to be able to get closer to the upper bound.
-
-% 
-% \bibliographystyle{ecta}
-% %\bibliographystyle{newapa}
-% \bibliography{rank}
-% \appendix
 
@@
   \caption{Sample Statistics}
-  \label{tab:ret-stat}
+  \label{ch1-tab:ret-stat}
 \ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
@@
   \caption{Example of ranking}
-  \label{tab:example}
+  \label{ch1-tab:example}
 \ This table shows target prices (panel A) and EPS forecasts (panel B) rankings for Amazon (AMZN) for the second quarter of 1999.
-We apply (\ref{tp:rank}) to obtain the ranks of the brokers.
+We apply (\ref{ch1-tp:rank}) to obtain the ranks of the brokers.
 \emph{TP} are target prices; $\overline{PMAFE}^{TP}$ is the daily average proportional mean adjusted TP error.
@@
   \caption{Analysts' accuracy consistency}
-  \label{tab:rank-stat}
+  \label{ch1-tab:rank-stat}
 
@@
 \begin{table}[hp]
-  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
-  \label{tab:view-stat}
+  \caption{Descriptive statistics of views: \true{}}
+  \label{ch1-tab:view-stat}
   \small\addtolength{\tabcolsep}{-2pt}
 
-\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the \true{} (\ref{ch1-q:true}) consensus (median) among the analysts (panel A); \true{} target price rankings (panel B); and \true{} EPS forecasts rankings (panel C).
 
@@
 
-print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{ch1-consq})}} \\\\','\\midrule \n')))
 @
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n','\\midrule \n')))
 @
@@
 
-print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n')))
 @
@@
 \begin{table}[hp]
-  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
-  \label{tab:view-stat-naive}
+  \caption{Descriptive statistics of views: \naive{}}
+  \label{ch1-tab:view-stat-naive}
   \small\addtolength{\tabcolsep}{-2pt}
 
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+\ This table shows descriptive statistics of views (expected returns) based on: the \naive{} )(\ref{ch1-q:naive}) consensus among the analysts (panel A), the \naive{} target price rankings (panel B), and the \naive{} EPS forecasts rankings (panel C) per stock per quarter.
 
@@
 
-print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{ch1-consq})}} \\\\','\\midrule \n')))
 @
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n','\\midrule \n')))
 @
@@
 
-print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n')))
 @
@@
 \begin{table}[hp]
-  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
-  \label{tab:view-stat-default}
+  \caption{Descriptive statistics of views: \default{}}
+  \label{ch1-tab:view-stat-default}
   \small\addtolength{\tabcolsep}{-2pt}
 
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+\ This table shows descriptive statistics of views (expected returns) based on: the \default{} ((\ref{ch1-q:default})) consensus among the analysts (panel A), the \default{} target price rankings (panel B), and the \default{} EPS forecasts rankings (panel C) per stock per quarter.
 
@@
 
-print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{ch1-consq})}} \\\\','\\midrule \n')))
 @
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n','\\midrule \n')))
 @
@@
 
-print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{ch1-rankq})}} \\\\','\\midrule \n')))
 @
@@
   \caption{Trading strategy performance}
-  \label{tab:strategy}
+  \label{ch1-tab:strategy}
   \ This table shows the performance statistics of the different trading strategies.
 Panel A presents the results for the passive strategy.
-Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}).
+Panels B,C, and D show the results for the perfect foresight scenario (\true{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}).
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average.
@@
 \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
+  \multicolumn{5}{l}{\textbf{Panel B: \true{} }} \\
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results.tab[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
   \caption{Trading strategy performance: Sharpe ratio}
-  \label{tab:substrategy}
+  \label{ch1-tab:substrategy}
   \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
@@
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
-cat('\\midrule \n')
+print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\true{}}} \\\\\n')))
 @
+\midrule
 \end{tabularx}
@@
 print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
-cat('\\midrule \n')
 @
-%\midrule
+\midrule
 \end{tabularx}
@@
 \caption{Trading strategy timeline}
-\label{fig:bl}
+\label{ch1-fig:bl}
 \ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
@@
 \caption{Daily stock price Amazon and brokers target prices}
-\label{fig:example}
+\label{ch1-fig:example}
 \ Target price and actual prices for Amazon  the second quarter of 1999.
@@
 \caption{Performance of the BL model}
-\label{fig:bl-results}
+\label{ch1-fig:bl-results}
 \ Quarterly performance of the cumulative portfolio wealth for all strategies.
-Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$.
+Panel \true{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$.
 \textit{TP} is the strategy with rankings based on the accuracy in target prices, \textit{CONS} is the strategy based on the consensus among the analysts regarding a stock's expected return.
@@
 \end{figure}
-
-%\end{document}

### 2015-03-11 munge/02-state-variables.R

@@ -1,924 +1,0 @@
-# TODO: Add comment
-#
-# Author: aiguzhinov
-##########################
-
-#####################################################
-### A new rewrite of the script with base on data.table package
-### 27/06/14
-
-### Variables:
-### btm=btm,
-### debt.to.eq=,
-### size=
-### accruals=
-### ret.vol =
-
-
-#source('~/Dropbox/workspace/Projects/Black-Litterman/BL-strategies/lib/my.paths.R')
-sectors<-c('Consumer Discretionary','Consumer Staples','Energy','Financials','Health Care','Industrials','IT','Materials','Telecom Services','Utilities')
-
-vvs.data <- setkey(rbindlist(mclapply(sectors,function(sec){
-  vvs <- list.files(paste(data.stock.dir(sec),'Acc.Variables',sep='/'),pattern='*.csv')
-  dt <- do.call(cbind,lapply(vvs,function(i){
-    vvs.dt <- data.table(read.csv2(paste(data.stock.dir(sec),'Acc.Variables',i,sep='/'),sep=';',nrow=84))[,q.id:=as.yearqtr(seq.Date(as.Date('1989-04-01'),as.Date('2010-01-01'),by = '3 month')-1)]
-  setkey(melt(vvs.dt,id.vars='q.id',variable.name = 'Stock',value.name = strsplit(i,'.csv')[[1]]),q.id,Stock)
-    }))
-dt[,unique(colnames(dt)),with=F][,Sector:=sec]
-},mc.cores=4))[,':='(btm=(tot.assets-tot.liab)/as.numeric(market.cap),size=log(as.numeric(market.cap)),debt.to.eq=st.debt/(tot.assets-tot.liab),accruals=total.accruals(curr.assets,cash,curr.liab,st.debt,taxes,depr,tot.assets)),by=list(Stock,Sector)],q.id,Stock)
-
-
-###Broker specific variables load q.data from cache. To be calculated immediately before the ranking process
-# load('cache/q.data.RData')
[…]

### 2015-03-11 src/paper.trading.APS.true.R
furhter remove traces of predicting part. This is  only baseline experiments; no NB

@@ -117,7 +117,7 @@ final.bl <- setkey(unique(bl.results.f(opt.w),by=c('Method','q.id','Views')),Met
 final.bl$Method <- factor(final.bl$Method,levels=unique(final.bl$Method)[c(3,2,1)])
 final.bl$Views <- factor(final.bl$Views,levels=unique(final.bl$Views)[c(4,1,2,3)])
 cache('final.bl')
-#require("knitr")
+require("knitr")
 setwd('~/Dropbox/workspace/Projects/BL-strategies/doc/paper/')
 knit2pdf('paper-knitr-APS.Rnw',quiet=T)
 

### 2015-03-11 src/script.predict.trade.R

@@ -3,9 +3,9 @@ setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 
 library(ProjectTemplate)
 load.project()
-delta<-1L;tau=1/50;baselines <- c('true','naive','default');methods<-c('raw','1diff','random','roll.sd');confid.id <- c('cons','last','ma');percentile <- 0.05;rank.parameters <- c(n=100L,diff.lag=1L,sd.lag=8L,roll.p=15L)
+delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
-require(labelRank)
+
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)
 system.time(source('munge/01-data.q.ret.R'))
 
@@ -13,22 +13,19 @@ system.time(source('munge/01-data.q.ret.R'))
 system.time(source('src/paper.trading.APS.true.R'))
 
 ### State var. data: ~118 sec
-system.time(source('munge/02-state-variables.R'))
+#system.time(source('munge/02-state-variables.R'))
 ### Analysts ranking data: ~ 280 sec
 system.time(source('munge/03-analysts.process.R'))
 ### Predicting ~ 347 sec
-system.time(source('src/predicting.R'))
+#system.time(source('src/predicting.R'))
 
-pt.accu[,mean(value),by=.(variable)]
+#pt.accu[,mean(value),by=.(variable)]
 
-ggplot(pt.accu[,mean(value),by=.(q.id,variable)],aes(x=as.Date(q.id),y=V1,group=variable,color=variable))+geom_line(size=0.5,alpha=0.7)+geom_smooth(method='loess',se=F,size=1L)+theme_bw()
+#ggplot(pt.accu[,mean(value),by=.(q.id,variable)],aes(x=as.Date(q.id),y=V1,group=variable,color=variable))+geom_line(size=0.5,alpha=0.7)+geom_smooth(method='loess',se=F,size=1L)+theme_bw()
 
 ### trading: ~ 322 sec
-system.time(source('src/trading.R'))
+#system.time(source('src/trading.R'))
 
-ggplot(res.accu[,mean(value,na.rm=T),by=.(q.id,variable,conf)],aes(x=as.Date(q.id),y=V1,color=variable,group=variable))+geom_line()+facet_grid(conf~.,scale='free_y')+theme_bw()
[…]

### 2015-03-11 src/script.predict.trade.R
Cores in mc.cores is an option; cached market.list and market.set

@@ -3,7 +3,7 @@ setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 
 library(ProjectTemplate)
 load.project()
-delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05
+delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05;cores=4L
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
 
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)
@@ -15,7 +15,7 @@ system.time(source('src/paper.trading.APS.true.R'))
 ### State var. data: ~118 sec
 #system.time(source('munge/02-state-variables.R'))
 ### Analysts ranking data: ~ 280 sec
-system.time(source('munge/03-analysts.process.R'))
+#system.time(source('munge/03-analysts.process.R'))
 ### Predicting ~ 347 sec
 #system.time(source('src/predicting.R'))
 

### 2015-03-11 lib/BL-functions.R
add core parameter to all libs

@@ -371,7 +371,7 @@ opt.w.f <- function(views,conf,tau){
                 #list.conf <- alply(conf[,,,agg],2,.dims=T)
                 rbindlist(mclapply(dimnames(views)[[3]],function(type){
                         rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],views[bl.period,,type],conf[bl.period,,type],tau))
-                },mc.cores=4)
+                },mc.cores=cores)
                 )
                 #}))
 }

### 2015-03-11 lib/ranking.scripts.R

@@ -196,7 +196,7 @@ predict.ranking.script.f <- function(methods, stock.names, stock,  tr, r.paramet
       #analyst.prediction.f(tr[, , s], mod.vvs[,,meth], n)
       #roll.analyst.prediction.f(tr[, , s], mod.vvs[,,meth], n,x)
     }), along = 3)
-  },mc.cores=4), along = 4, new.names = list(dimnames(tr)[[2]],NULL, methods,stock.names))
+  },mc.cores=cores), along = 4, new.names = list(dimnames(tr)[[2]],NULL, methods,stock.names))
 }
 
 roll.ranking.f <- function(methods, stock.names, stock,  tr, r.parameters) {
@@ -212,7 +212,7 @@ roll.ranking.f <- function(methods, stock.names, stock,  tr, r.parameters) {
                 abind(lapply(methods , function(meth) {
                         roll.analyst.prediction.f(tr[, , s], mod.vvs[,,meth], n,x)
                 }), along = 3)
-        },mc.cores=4), along = 4, new.names = list(dimnames(tr)[[2]],NULL, methods,stock.names))
+        },mc.cores=cores), along = 4, new.names = list(dimnames(tr)[[2]],NULL, methods,stock.names))
 }
 ### Good results script
 # predict.ranking.script.f <- function(methods, stock.names, stock, tr, r.parameters) {
@@ -231,7 +231,7 @@ roll.ranking.f <- function(methods, stock.names, stock,  tr, r.parameters) {
 #
 #                         rankings.time.corrected.gw.cont(tr[, , s], mod.vvs, n)
 #                 }), along = 3)
-#         },mc.cores=4), along = 4, new.names = list(dimnames(tr)[[2]],NULL, dimnames(tr)[[3]], methods))
+#         },mc.cores=cores), along = 4, new.names = list(dimnames(tr)[[2]],NULL, dimnames(tr)[[3]], methods))
 # }
 
 analyst.prediction.f <- function(rank,features,n){
@@ -284,7 +284,7 @@ roll.baselines.f <- function(y,x){
                 default <- apply(apply(y[train, drop = F, , ], c(2,3), mean, na.rm = T),2,rank,na.last = "keep")
                 true <- y[pred.t[t],,]
                 abind(true,naive,default,along=3)
-        },mc.cores=4),along=4)
+        },mc.cores=cores),along=4)
 }
 
 

### 2015-03-11 src/script.predict.trade.R

@@ -3,7 +3,7 @@ setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 
 library(ProjectTemplate)
 load.project()
-delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05;cores=4L
+delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05; cores=2L
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
 
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)

### 2015-03-11 src/script.predict.trade.R
some changes

@@ -3,7 +3,7 @@ setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 
 library(ProjectTemplate)
 load.project()
-delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05; cores=2L
+delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons','last','ma');percentile <- 0.05; cores=4L
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
 
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)

### 2015-03-11 doc/paper/paper-knitr-APS.Rnw
edited paper to master

@@
 opts_chunk$set(concordance=TRUE)
+options(digits = 3)
 @
@@
 \begin{abstract}
-Some institutions issue rankings of financial analysts.
+Several institutions issue rankings based on the accuracy of price and EPS forecasts.
 Given that these rankings are \textit{ex-post} they may not be able useful to investors.
-In this paper  we show that trading strategies based on past rankings outperform a passive strategy.
-In addition, we report that analysts issuing accurate price targets are more favorable to the investors  to follow rather than analysts issuing accurate EPS forecasts.
-In addition, we report that the performance of trade strategies based upon price target accuracy is superior one  based upon EPS forecast accuracy
+In this paper  we show that trading strategies based on perfect foresight and past rankings outperform a passive strategy.
+In addition, we report that investors are better off following analysts that issue  accurate price targets rather that those with accurate EPS forecasts.
 %Finally, we show that a strategy based on the perfect foresight of analysts' performance gains the highest cumulative return.
@@
 In any of these cases, the rankings aim at identifying the top analysts.
-However, aside from personal acknowledgment among peers, it is still arguable whether these are useful \citep{desai2000ass} or are merely ``popularity contests" \citep{emery2009}.
+However, aside from personal acknowledgment among peers, it is still arguable whether these are useful to investors \citep{desai2000ass} or are merely ``popularity contests" \citep{emery2009}.
 %In this paper, we support the argument that the top-ranked analysts, indeed, have stock picking skills.
@@
 First, we develop a trading strategy that transforms the rankings of financial analysts into inputs for the Black-Litterman model \citep{black1992}.
-Second, we show that annualized cumulative returns generated by some trading strategies  based upon analysts' rankings outperform the passive strategy (e.g., buy-and-hold the general stock market index).
+Second, we show that annualized cumulative returns generated by some trading strategies  based upon analysts' rankings outperform a passive strategy (e.g., buy-and-hold the general stock market index).
 Third, we show that the strategy based upon the perfect foresight of rankings yields the highest cumulative annualized return.
@@
 Yet, several authors have since stressed that  there are information-gathering costs and information is not immediately reflected on prices  \citep{grossman1980iie}.
-As such, prices may not  reflect all the available information at all time because if this were the case, those who spent resources to collect and analyze   information would not have an incentive to do it because there would not get any compensation for it.
+As such, prices may not  reflect all the available information at all time because if this were the case, those who spent resources to collect and analyze   information would not have an incentive to do it, because there would not get any compensation for it.
 
@@
 
-Some authors show that that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
+Some authors show that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
 \cite{barber2001} finds that over the period of 1986-1996 a portfolio of stocks with the most (least) favorable consensus analyst recommendations yields an average abnormal return of 4.13 (-4.91)\%.}.
-Assuming that some analysts produce valuable advice it make sense to rank analysts based on the accuracy of their recommendations.
-
-StarMine rankings are based on financial analysts accuracy either on price target or EPS forecasts.
+Assuming that some analysts produce valuable advice it makes sense to rank analysts based on the accuracy of their recommendations.
+
+StarMine rankings are based on financial analysts' accuracy either on TP or EPS forecasts.
 To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES).
@@
 The second set of strategies takes in consideration the analysts' target price and EPS accuracy ranks to form ``smart estimates".
-For the latter set of strategies, we analyse different time information sets of the accuracy of the analysts.
+For the latter set of strategies, we analyse different time information sets to define the accuracy of the analysts.
 
 We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy).
-By doing this, we address the ongoing debate in the literature on whether analysts, when issue the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
+By doing this, we indirectly address the ongoing debate in the literature on whether analysts, when issuing the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
 For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices.
 Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.
-
-A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period’s EPS invested at the cost of equity.}.
-In short, this model justifies a price earnings ratio for companies where next period’s earnings are expected to grow over and above the normal rate.
+\footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}
 
@@
 \label{sec:trading}
-Our trading strategy use the framework for  active portfolio management proposed by \cite{black1992}.
+Our trading strategy uses the framework for  active portfolio management proposed by \cite{black1992}.
 The model incorporates ``views" in a CAPM framework, forming optimal portfolios in a mean-variance optimization setting.
-``Views" are expectations on individual stocks future performance by investors/analysts.
+``Views" are expectations on individual stocks' future performance.
 
@@
 
-To proxy expected returns we compare the analysts' 12-month target prices (TP) with today's stock price.
-Confidence $\Omega$ for stock is based on variation  across analysts which is similar to the measure of dispersion in analysts' opinions outlined in \cite{diether2002}.
+To proxy expected returns we compare the analyst' 12-month target price (TP) with today's stock price.
+Confidence $\Omega$ for stock is based on variation  of forecasts across analysts which is similar to the measure of dispersion in analysts' opinions outlined in \cite{diether2002}.
 
@@
 
-\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix across stocks;
+\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix;
 
@@
 
-For the strategies that weight the analysts' estimates of expected return, we use analysts' rankings and the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
+For the strategies that weight the analysts' estimates of expected return the weight of each analsyt $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
 
@@
 
-As described above, we use target price and EPS rankings.
+As mentioned above, we use both target price and EPS accuracy rankings.
 
 \subsubsection{Target Price ranking} 
-
+%%% change s to i for stock
 Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}.
-First,  we define the forecast daily error  $FE_{i,j}$ as the absolute value of the difference between analysts' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
+First,  we define the forecast daily error  $FE_{j,s}$ as the absolute value of the difference between analyst' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
 
@@
 \label{dfe}
-FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
+FE_{j,s}^{TP}=|{P_{s}-TP_{j,s}}|
 \end{equation}
@@
 \label{tp:pmafe}
-PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
-\end{equation}
-where $\overline{{FE}_{t,s}^{TP}}$ is the average over quarter forecasting error. The target price is fixed over the quarter unless it gets revised.
-
-The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
+PMAFE_{j,s}^{TP}=\frac{FE_{j,s}^{TP}}{\overline{FE_{s}^{TP}}}
+\end{equation}
+where $\overline{{FE}_{s}^{TP}}$ is the average forecasting error accros analysts. The target price is fixed over the quarter unless it gets revised.
+
+The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ over a particular quarter:
 \begin{equation}
@@
 \end{equation}
-where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.
+where $T$ are the number of trading days in a quarter and $N$ is the number of brokers with a valid TP.  Figure \ref{fig:example} shows an example.
 
@@
 \end{equation}
-where $ACT_{s}$ and $PRED_{j,s}$ are the actual and  analyst $j$ forecast EPS respectively for each stock $s$.
+where $ACT_{s}$ and $PRED_{j,s}$ are the actual quarterly EPS and  analyst $j$'s EPS forecast for stock $s$.
 
@@
 \label{def-omega}
-The confidence of $Q$ are given by the coefficient of variation of forecasting errors:
-
-\begin{equation}
-CV = \frac{\sigma (FE)}{\overline{FE}}
-\end{equation}
-where $\sigma$ and $\overline{FE}$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS.
+The confidence of $Q$ is given by the coefficient of variation (CV) of forecasting errors. For each stock $s$ is given by:
+
+\begin{equation}
+CV_{s} = \frac{\sigma (FE)_s}{\overline{FE}_s}
+\end{equation}
+where $\sigma_s$ and $\overline{FE}_s$ are the standard deviation and the mean of the forecast errors across analsyts for either TP or EPS.
 A low value of $CV$ reflects consensual estimates of either future prices or EPS.
@@
 
-To proceed with the trading strategy, we need to establish which information we going to use to build the rankings that will be used to compute the weighted return estimates.
+To proceed with the trading strategy, we need to establish which information we  will be using to build the rankings.
+These rankgins will be the inputs to compute the weighted return estimates (``smart estimates").
 Different analysts' ranks are obtained  if we select different time horizons.
-If use only recent information, we focus on recent performance of the analysts.
-This, of course, is more sensitive to unique episodes (e.g., a quarter, which has been surprisingly good or bad).
-If, alternatively, we opt to incorporate all analyst performance, the ranking is less affected by such events, yet, it may not reflect the current abilities of the analyst.
-In this paper, we use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
+If we use only the most  recent information, we will capture the recent performance of the analysts.
+This, of course, is more sensitive to unique episodes (e.g., a quarter which has been surprisingly good or bad).
+If, alternatively, we opt to incorporate the entire analyst performance, the ranking is less affected by such events, yet it may not reflect the current analyst ability.
+We use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
 We call the former the \naive{} set and the latter the \default{} set.
 
-In addition to these sets,  we also create a hypothetical scenario that assumes we know the future information about the analyst' accuracy performance which would only be available at the end of $t$.
-In this setting, we are assuming that we could  perfectly predict the true analysts' ranking in advance.
-This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies.
-We call this approach as the \tr{} set.
-
-We formalize these sets as follows. 
+In addition to these sets,  we also create a hypothetical scenario that assumes we antecipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.
+This represents the perfect foresight strategy.
+Therefore, it serves a performance reference point to evaluate the other trading strategies.
+We call this the \tr{} set.
+
+Formalizing information sets considerd are: 
 \begin{itemize}
-\item  the \tr{} %-- a perfect foresight information:
+\item  the \tr{} set%-- a perfect foresight information:
 \begin{equation}
@@
 
-\item  the \naive{} % -- $t-$ information:
+\item  the \naive{} set % -- $t-$ information:
 \begin{equation}
@@
 
-\item  the \default{} %-- the entire history of analysts performance:
+\item  the \default{}  set%-- the entire history of analysts performance:
 %\begin{itemize}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).
+where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
 
@@
 
-The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
+Given the fact that financial analysts commonly issue TP with the one year horizion \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
 After one year we assume that TP recommendation expires.
 
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{round(q.data[,min(trunk.view,na.rm=T)],3)}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
 This is done due to occurrence of the extreme values.
@@
 For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-Each stock had on average of \Sexpr{round(core.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)} quarterly target price reports.
+Each stock had on average of \Sexpr{core.dt[,.N,by=list(Stock,q.id)][,mean(N)]} quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
 In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-The average number of quarterly forecasts is \Sexpr{round(complete.dt[,.N,by=list(Stock,q.id)][,mean(N)],2)}.
-
-We apply the ranking procedure outline in section \ref{def-q} on two datasets.
-For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq.
+The average number of quarterly forecasts is \Sexpr{complete.dt[,.N,by=list(Stock,q.id)][,mean(N)]}.
+
+We apply the ranking procedure outline in section \ref{def-q} to the two datasets.
+For target price rankings, we use the average daily errors within one quarter as the measure of analysts' forecasting ability (eq.
 \ref{tp:pmafe}).
 
-Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
-Four analysts had valid target price for Amazon for second quarter of 1999.
+Table \ref{tab:example} and figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}.
+Four analysts had valid target prices for Amazon for second quarter of 1999.
 We plot the daily Amazon price against the brokers' target prices.
-Table \ref{tab:example} shows the resulting TP and EPS ranking.
+Table \ref{tab:example} shows the resulting TP and EPS rankings.
 On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate.
@@
 
-We convert the rankings into scores as follows:
+Beforend, we convert the rankings into scores as follows:
 \begin{equation}
 \label{eq:score}
-score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
+score_{j,s}=\frac{rank_{j,s}}{\max{rank_s}}
 \end{equation}
@@
 \label{eq:mean-score}
-score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
-\end{equation}
-where $k$ is number of stocks for which an analyst $j$ had rank.
+\overline{score_{j}}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
+\end{equation}
+where $k$ is number of stocks followed by a particular analyst $j$.
 
@@
 %Journ. of Fin economics 
-Panel A shows the dynamics of each tercile for rankings based on the accuracy in target prices.
-We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter and even after one year.
-The case of EPS ranking shows similar results (panel B).
-This analysis confirms recent finding of \cite{hilary2013} on analyst forecast consistency.
+Panel A shows the dynamics of each tercile for rankings based on target price  accuracy.
+We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 68\% (69\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 47 and 49\% for the top and bottom terciles.
+
+In the case of EPS ranking  (panel B) 52 and 57 (42 and 40) of the analsyts  remained in the top and bottom terciles after one quarter (year)  respectively.
+
+These results are consistent with the recent findings of \cite{hilary2013} on analyst forecast consistency.
 
@@
 
-\subsection{$Q$ descriptive statistics}
-
-Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
-The expected returns  are computed comparing TP estimates with actual price.
-To inform the strategies we obtain rank-weighted estimates where weights are given either by the TP or the EPS ranks.
-
-\cite{bradshaw2002} reports that analysts' average expected returns for the period of 2000--2009 of 206 brokers 24\%, in \cite{da2011} these average expected return post 40\% for the period of 1996--2004, \cite{zhou2013} find on average  96\% for the sample period of 2000--2009 reports.
-The figures suggest that analyst overly optimistic.
+\subsection{Views: descriptive statistics}
+
+Tables \ref{tab:view-stat} to \ref{tab:view-stat-default} present the descriptive statistics of the analysts' expected returns conditional on the different information sets.
+Table 4 shows the \tr{}, table 5 shows the \naive{} and table 6 \defaul{}.
+
+The expected returns  are computed comparing TP estimates with actual prices. To form the smart strategies we compute rank-weighted estimates where weights are given either by the TP or the EPS ranks.
+
+\cite{bradshaw2002} reports analyst average expected returns for the period of 2000--2009 and 206 brokers of 24\%.
+\cite{da2011} report an average expected return of 40\% for the period of 1996--2004.
+\cite{zhou2013} finds an average expected return of 96\% for the sample period of 2000--2009.
+These figures suggest that analysts are overly optimistic.
 %these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns.
@@
 (\ref{consq}).
-The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are \Sexpr{round(stat.nr[year=='Total'&Method=='true',mean],3)*100 }\%, \Sexpr{round(stat.nr[year=='Total'&Method=='naive',mean],3)*100 }\%, and \Sexpr{round(stat.nr[year=='Total'&Method=='default',mean],3)*100 }\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{ round(stat.pt.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.pt.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.pt.view[year=='Total'&Method=='default',mean],3)*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{ round(stat.eps.view[year=='Total'&Method=='true',mean],3)*100}\%, \Sexpr{ round(stat.eps.view[year=='Total'&Method=='naive',mean],3)*100}\%, and \Sexpr{ round(stat.eps.view[year=='Total'&Method=='default',mean],3)*100}\%).
-
-Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic.
-The \default{} information set shows higher values of expected returns considering that it includes the whole history of analysts' performance.
-
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{stat.nr[year=='Total'&Method=='true',mean]*100 }\%, \Sexpr{stat.nr[year=='Total'&Method=='naive',mean]*100 }\%, and \Sexpr{stat.nr[year=='Total'&Method=='default',mean]*100 }\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{stat.pt.view[year=='Total'&Method=='true',mean]*100}\%, \Sexpr{stat.pt.view[year=='Total'&Method=='naive',mean]*100}\%, and \Sexpr{stat.pt.view[year=='Total'&Method=='default',mean]*100}\%).
+Panel C shows the EPS based weighted expected returns averages (\Sexpr{stat.eps.view[year=='Total'&Method=='true',mean]*100}\%, \Sexpr{stat.eps.view[year=='Total'&Method=='naive',mean]*100}\%, and \Sexpr{stat.eps.view[year=='Total'&Method=='default',mean]*100}\%).
+
+Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns.
 %obtained from the rankings based on the target price accuracy.
@@
 
-We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
+We report the results from different trading strategies in table (\ref{tab:strategy}).
+We split the table into four panels.
+Panel A shows  the performance for  the passive (market) strategy \textit{Market}.
+Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategis for each of the information availability sets.
 
 \subsection{Passive strategy}
-Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \Sexpr{round(bl.results['Market',1,1],2)}\% and the Sharpe Ratio  of \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}.
-The average number of stocks used per quarter is \Sexpr{ round(bl.results['Market',1,'meanViews'],2)} and the turnover ratio of strategy is \Sexpr{ round(bl.results['Market',1,'Ave.TO'],3)}, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+
+The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1]}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr']} over the period 1999-2001.
+The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
 
@@
 \label{sec:perfect}
-Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{round(bl.results['CONS',1,1],2)}\%, \Sexpr{round(bl.results['TP',1,1],2)}\%, \Sexpr{round(bl.results['EPS',1,1],2)}\%.
-All the strategies outperform the benchmark (\Sexpr{round(bl.results['Market',1,1],2)}\%).
-The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
-In any case, the results suggest that the advice of analysts are valuable.
+Panel B presents the results for the case of the \tr{} information set.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1]}\%, \Sexpr{bl.results['TP',1,1]}\%, \Sexpr{bl.results['EPS',1,1]}\%.
+All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1]}\%).
+The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
+In any case, the results suggest that the advice of analysts, as a group, is valuable.
 %Yet, the top analyst
@@
 
-The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
-Its Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
-In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
+The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
+The Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
 Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-Panel A of the table corresponds to the perfect foresight information set.
-The TP strategy wins over the others in every period.
-
-While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
-One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
+The \textit{TP} strategy wins over the others in every period as expected.
+
+While this is an hypothetical setting, given that it is not possible to know in advance which analyst will rank first, it suggests that if we can predict the rankings with some accuracy this will be a useful investment trading tool.
+One of the possibilities is using methods developed in the Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
 For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
@@
 \subsection{Feasible strategies}
-Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
-As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\Sexpr{round(bl.results['Market',2,1],2)}\%)  and gain positive cumulative annualized returns: \Sexpr{round(bl.results['TP',2,1],2)}\%,  \Sexpr{round(bl.results['CONS',2,1],2)}\%, \Sexpr{round(bl.results['EPS',2,1],2)}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
-
-As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
-The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
-The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
-
-The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\Sexpr{round(bl.results['TP',3,1],2)}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\Sexpr{round(bl.results['CONS',3,1],2)}\% and \Sexpr{round(bl.results['EPS',3,1],2)}\% respectively).
-The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
-
-The feasible information sets demonstrate interesting results.
-It seems to be the case that the information about stock’s expected return based on rankings create more value than the same information but based on analysts’ consensus.
-Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-Thus, rankings are useful for investors.
+Panel C of table (\ref{tab:strategy}) shows the performance of the different smart startegies in the \naive{} information set.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1]}\%,  \Sexpr{bl.results['CONS',2,1]}\%, \Sexpr{bl.results['EPS',2,1]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+Similarly, the TP strategy dominates when we consider the risk-adjusted returns.
+The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
+The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
+
+Panel D of table \ref{tab:strategy} confirm the outperformance of the TP smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1]}\% and \Sexpr{bl.results['EPS',3,1]}\% respectively).
+The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+
+Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for  the passive and smart strategies in all the information sets.
+The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
+Figures show that strategies under the \tr{} panel outperform the \emph{Market} and that final value  of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+
+In sum the results of  feasible information sets outlined above suggest that  it is worth to follow the top analysts and are supportive of \cite{desai2000ass} in that rankings are useful for investors.
 
@@
 
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
-Yet, it is not the case for EPS ranking.
-This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
-EPS are not good predictors of future returns, at least for short-term horizon.
-
-Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
-Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those taht good at forecasting EPS.
+This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not based upon the simple valuation models.
 
@@
 
-Some institutions, such as StarMine, rank financial analysts based on their accuracy.
+Some institutions, such as StarMine, rank financial analysts based on EPS and target price accuracy.
 These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
-Therefore, there is a growing interest in understanding the relative performance of analysts.
-
-We show that rankings do bring value to investors as they identify the top analysts.
-By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
-We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
+Therefore, there is a growing interest in understanding the relative performance of strategies based upon analysts forecasts.
+
+By applying the Black-Litterman model, we developed simulations of trading strategies using  different information sets.
+The perfect foresight scenario (using the information know at time $t$) sets the upper bound of the trading strategies in terms of the maximum yield any such strategies could achieve.
+If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accuarte TP forecast analsyts.
+
+%We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, .
 The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
@@
 
-For the future work we would like to develop the new methods to be able to get closer to the upper bound.
+For the future work we will developed new methods to forecast analsyts rankings so us to get closer to the upper bound.
 
@@
 \begin{table}[hp]
-  \caption{Trading strategy performance}
+  \caption{Trading strategies performance: entire preriod}
   \label{tab:strategy}
@@
 Panel A presents the results for the passive strategy.
-Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent ranking (\naive{}); and  all the ranking history of analysts to weight the TP/EPS estimates (\default{}).
-Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon the EPS accuracy ranking weighted average.
-The trading period spreads from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
+Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}); and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates .
+Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
+The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
 
@@
 results.final <- bl.results[4,1,]
-cat(paste(c('Strategy','Annualized cum. return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
+cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
@@
 \begin{table}[hp]
-  \caption{Trading strategy performance: Sharpe ratio}
+  \caption{Trading strategies performance: sub-periods}
   \label{tab:substrategy}
   \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
-Panel A represents the perfect foresight information set; panels B and C show, respectively, the recent and the all history analysts' performance.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the resulsts of the strategies using the most recent and all history analysts' performance.
 \begin{tabularx}{\linewidth}{r*{5}{Y}}

### 2015-03-11 src/script.predict.trade.R
add ggplot and knitr2pdf to front script

@@ -12,20 +12,12 @@ system.time(source('munge/01-data.q.ret.R'))
 ### data for first paper
 system.time(source('src/paper.trading.APS.true.R'))
 
-### State var. data: ~118 sec
-#system.time(source('munge/02-state-variables.R'))
-### Analysts ranking data: ~ 280 sec
-#system.time(source('munge/03-analysts.process.R'))
-### Predicting ~ 347 sec
-#system.time(source('src/predicting.R'))
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
 
-#pt.accu[,mean(value),by=.(variable)]
+ggplot(unique(melt(final.bl[,list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw(base_family='Avenir')+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3L)*100L),angle=90L,size=3L,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
 
-#ggplot(pt.accu[,mean(value),by=.(q.id,variable)],aes(x=as.Date(q.id),y=V1,group=variable,color=variable))+geom_line(size=0.5,alpha=0.7)+geom_smooth(method='loess',se=F,size=1L)+theme_bw()
-
-### trading: ~ 322 sec
-#system.time(source('src/trading.R'))
-
[…]

### 2015-03-12 doc/paper/paper-knitr-APS.Rnw
more tables of stocks and total of views

@@
 \begin{enumerate}
-\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
-
-\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix;
+\item  At the beginning of quarter $t$ for each stock $i$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
+
+\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $i$,  and the variance/co-variance matrix;
 
@@
 
-For the consensus strategy, we use median of expected returns for a particular stock $s$:
+For the consensus strategy, we use median of expected returns for a particular stock $i$:
 \begin{equation}
 \label{consq}
-Q_{cons,s}= \median \left\{r_{j,s}\right\}
-%\frac{1}{N} \sum_{j=1}^{N} r_{j,s}
+Q_{cons,i}= \median \left\{r_{j,i}\right\}
+%\frac{1}{N} \sum_{j=1}^{N} r_{j,i}
 \end{equation}
 %$N$ is the number of analysts with a valid TP report and
-where $r_{j,s}=TP_{j,s}/P_{s}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,s}$ and stock price $P_{s}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
 This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
 
-For the strategies that weight the analysts' estimates of expected return the weight of each analsyt $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
+For the strategies that weight the analysts' estimates of expected return the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
 
@@
 \label{eq:weight}
-w_{j,s}=1-\frac{rank_{j,s}-\min{ \{rank \} }}{\max{\{rank \}}}
+w_{j,i}=1-\frac{rank_{j,i}-\min_i{ \{rank \} }}{\max_i{\{rank \}}}
 \end{equation}
@@
 \label{rankq}
-Q_{rank,s}=\frac{\sum_{j=1}^{N} (w_{j,s} \times r_{j,s})}{\sum_{j=1}^{N} w_{j,s}}
+Q_{rank,i}=\frac{\sum_{j=1}^{N} (w_{j,i} \times r_{j,i})}{\sum_{j=1}^{N} w_{j,i}}
 \end{equation}
@@
 Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}.
-First,  we define the forecast daily error  $FE_{j,s}$ as the absolute value of the difference between analyst' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
+First,  we define the forecast daily error  $FE_{j,i}$ as the absolute value of the difference between analyst' target price $TP_{j}$ and the daily stock price $P$ for each stock $i$:
 
@@
 \label{dfe}
-FE_{j,s}^{TP}=|{P_{s}-TP_{j,s}}|
+FE_{j,i}^{TP}=|{P_{i}-TP_{j,i}}|
 \end{equation}
@@
 \label{tp:pmafe}
-PMAFE_{j,s}^{TP}=\frac{FE_{j,s}^{TP}}{\overline{FE_{s}^{TP}}}
-\end{equation}
-where $\overline{{FE}_{s}^{TP}}$ is the average forecasting error accros analysts. The target price is fixed over the quarter unless it gets revised.
+PMAFE_{j,i}^{TP}=\frac{FE_{j,i}^{TP}}{\overline{FE_{i}^{TP}}}
+\end{equation}
+where $\overline{{FE}_{i}^{TP}}$ is the average forecasting error across analysts. The target price is fixed over the quarter unless it gets revised.
 
@@
 \begin{equation}
-\overline{PMAFE_{j,s}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,s}^{TP}
+\overline{PMAFE_{j,i}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,i}^{TP}
 \end{equation}
@@
 \label{tp:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
+rank_{j,i}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,i}^{TP}} \right\}
 \end{equation}
@@
 \begin{equation}
-FE_{j,s}^{EPS}=|{ACT_{s}-PRED_{j,s}}|
-\end{equation}
-\begin{equation}
-PMAFE_{j,s}^{EPS}= \frac{FE_{j,s}^{EPS}}{\overline{FE_{s}^{EPS}}}
+FE_{j,i}^{EPS}=|{ACT_{i}-PRED_{j,i}}|
+\end{equation}
+\begin{equation}
+PMAFE_{j,i}^{EPS}= \frac{FE_{j,i}^{EPS}}{\overline{FE_{i}^{EPS}}}
 \end{equation}
@@
 \label{eps:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\} 
-\end{equation}
-where $ACT_{s}$ and $PRED_{j,s}$ are the actual quarterly EPS and  analyst $j$'s EPS forecast for stock $s$.
+rank_{j,i}=\rank_{j=1}^{N} \left\{ PMAFE_{j,i}^{EPS} \right\} 
+\end{equation}
+where $ACT_{i}$ and $PRED_{j,i}$ are the actual quarterly EPS and  analyst $j$'s EPS forecast for stock $i$.
 
@@
 \label{def-omega}
-The confidence of $Q$ is given by the coefficient of variation (CV) of forecasting errors. For each stock $s$ is given by:
-
-\begin{equation}
-CV_{s} = \frac{\sigma (FE)_s}{\overline{FE}_s}
-\end{equation}
-where $\sigma_s$ and $\overline{FE}_s$ are the standard deviation and the mean of the forecast errors across analsyts for either TP or EPS.
+The confidence of $Q$ is given by the coefficient of variation (CV) of forecasting errors. For each stock $i$ is given by:
+
+\begin{equation}
+CV_{i} = \frac{\sigma_i (FE_{i})}{\overline{FE}_{i}}
+\end{equation}
+where $\sigma_i$ and $\overline{FE}_i$ are the standard deviation and the mean of the forecast errors across analysts for either TP or EPS.
 A low value of $CV$ reflects consensual estimates of either future prices or EPS.
@@
 To proceed with the trading strategy, we need to establish which information we  will be using to build the rankings.
-These rankgins will be the inputs to compute the weighted return estimates (``smart estimates").
+These rankings will be the inputs to compute the weighted return estimates (``smart estimates").
 Different analysts' ranks are obtained  if we select different time horizons.
@@
 
-In addition to these sets,  we also create a hypothetical scenario that assumes we antecipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.
+In addition to these sets,  we also create a hypothetical scenario that assumes we anticipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.
 This represents the perfect foresight strategy.
@@
 
-Formalizing information sets considerd are: 
+Formalizing information sets considered are: 
 \begin{itemize}
@@
 %\label{default.cons}
-%\widehat{consQ_{t,s}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,s}
+%\widehat{consQ_{t,i}} = \frac{1}{T} \sum_{T=1}^{T-1} consQ_{t,i}
 %\end{equation}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
+where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
 
@@
 Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP with the one year horizion \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
 After one year we assume that TP recommendation expires.
@@
 
-Beforend, we convert the rankings into scores as follows:
+Beforehand, we convert the rankings into scores as follows:
 \begin{equation}
 \label{eq:score}
-score_{j,s}=\frac{rank_{j,s}}{\max{rank_s}}
-\end{equation}
-
-To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,s}$
+score_{j,i}=\frac{rank_{j,i}}{\max{rank_s}}
+\end{equation}
+
+To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,i}$
 \begin{equation}
 \label{eq:mean-score}
-\overline{score_{j}}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
+\overline{score_{j}}= \frac{1}{k} \sum_{s=1}^{k} score_{j,i}
 \end{equation}
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 68\% (69\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 47 and 49\% for the top and bottom terciles.
-
-In the case of EPS ranking  (panel B) 52 and 57 (42 and 40) of the analsyts  remained in the top and bottom terciles after one quarter (year)  respectively.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[[1]][1,1]*100}\% (\Sexpr{pt.cont.tab[[1]][3,3]*100}\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[[2]][1,1]*100}\% and \Sexpr{pt.cont.tab[[2]][3,3]*100}\% for the top and bottom terciles.
+
+In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[[1]][1,1]*100}\% and  \Sexpr{eps.cont.tab[[1]][3,3]*100}\% ( \Sexpr{eps.cont.tab[[2]][1,1]*100}\% and  \Sexpr{eps.cont.tab[[2]][3,3]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
 
@@
 
-Tables \ref{tab:view-stat} to \ref{tab:view-stat-default} present the descriptive statistics of the analysts' expected returns conditional on the different information sets.
-Table 4 shows the \tr{}, table 5 shows the \naive{} and table 6 \defaul{}.
+Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
+%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).
 
@@
 Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns.
+
+Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) conditional on considered information sets.
 %obtained from the rankings based on the target price accuracy.
@@
 Panel A shows  the performance for  the passive (market) strategy \textit{Market}.
-Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategis for each of the information availability sets.
+Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategies for each of the information availability sets.
 
@@
 \subsection{Feasible strategies}
-Panel C of table (\ref{tab:strategy}) shows the performance of the different smart startegies in the \naive{} information set.
+Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
 As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1]}\%,  \Sexpr{bl.results['CONS',2,1]}\%, \Sexpr{bl.results['EPS',2,1]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the TP strategy dominates when we consider the risk-adjusted returns.
+Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
 The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the TP smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1]}\% and \Sexpr{bl.results['EPS',3,1]}\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1]}\% and \Sexpr{bl.results['EPS',3,1]}\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those taht good at forecasting EPS.
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that good at forecasting EPS.
 This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not based upon the simple valuation models.
@@
 The perfect foresight scenario (using the information know at time $t$) sets the upper bound of the trading strategies in terms of the maximum yield any such strategies could achieve.
-If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accuarte TP forecast analsyts.
+If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts.
 
@@
 
-For the future work we will developed new methods to forecast analsyts rankings so us to get closer to the upper bound.
+For the future work we will developed new methods to forecast analysts rankings so us to get closer to the upper bound.
 
@@
 \bibliography{rank}
-\appendix
 
@@
 
+\newpage
 %Descriptive  table
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
-@
-\midrule
+print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
+@
 \end{tabularx}
@@
 <<desc-eps,echo=F,results='asis'>>=
-print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."))
+print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
 @
@@
 \begin{table}[hp]
-  \caption{Descriptive statistics of views: \tr{} (\ref{q:true})}
+  \caption{Descriptive statistics of views}
   \label{tab:view-stat}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\ This table shows the descriptive statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-Year &Stocks& Mean & Median &Std.dev\\
+& Mean (in \%) & Median (in \%) &Std.dev\\
 \midrule
-<<desc-nr.views,echo=F,results='asis'>>=
-
-print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
+<<desc-q-cons,echo=F,results='asis'>>=
+test.a[,,,1:2] <- test.a[,,,1:2]*100
+dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
+print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,1],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{4}{Y}}
   \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views,echo=F,results='asis'>>=
+<<desc-q-naive,echo=F,results='asis'>>=
 #data.to.display <- c('nbr.val','mean', 'median','std.dev')
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views,echo=F,results='asis'>>=
+print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,2],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+  \end{tabularx}
+  \begin{tabularx}{\linewidth}{r*{4}{Y}}
+<<desc-q-eps,echo=F,results='asis'>>=
 #data.to.display <- c('nbr.val','mean', 'median','std.dev')
 
-print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+#cat(rep('&',ncol(results.final)),'\\\\')
+print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,3],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 \begin{table}[hp]
-  \caption{Descriptive statistics of views: \naive{} (\ref{q:naive})}
-  \label{tab:view-stat-naive}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \caption{Number of active stocks}
+  \label{tab:stocks}
+\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-naive,echo=F,results='asis'>>=
-
-print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-naive,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
+<<stocks-true,echo=F,results='asis'>>=
+print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,1],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+<<stocks-naive,echo=F,results='asis'>>=
+print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,2],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+<<stocks-def,echo=F,results='asis'>>=
+print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,3],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{table}[hp]
-  \caption{Descriptive statistics of views: \default{} (\ref{q:default})}
-  \label{tab:view-stat-default}
-  \small\addtolength{\tabcolsep}{-2pt}
-
-\ This table shows descriptive statistics of views (expected returns) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-    \toprule
-Year &Stocks& Mean & Median &Std.dev\\
-\midrule
-<<desc-nr.views-default,echo=F,results='asis'>>=
-
-print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-@
-  \midrule
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-r.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-@
-  \end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \midrule
-<<desc-eps.views-default,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-@
-\bottomrule
-  \end{tabularx}
-\end{table}
+%'   \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \tr{}}
+%'   \label{tab:view-stat}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) for the \tr{} (\ref{q:true}) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%'   
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
+%' 
+%' 
+%' \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \naive{}}
+%'   \label{tab:view-stat-naive}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows descriptive statistics of views (expected returns) for the \naive{} (\ref{q:naive}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views-naive,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views-naive,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views-naive,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
+%' 
+%' \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \default{}}
+%'   \label{tab:view-stat-default}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows descriptive statistics of views (expected returns) for the \default{} (\ref{q:default}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views-default,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views-default,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views-default,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
 
@@
 #p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
 #+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
@@
 
-require(gridExtra)
 #grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
@@
 \begin{table}[hp]
-  \caption{Trading strategies performance: entire preriod}
+  \caption{Trading strategies performance: entire period}
   \label{tab:strategy}
@@
   \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
-Panel A represents the perfect foresight information set; panels B and C show, respectively, the resulsts of the strategies using the most recent and all history analysts' performance.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
 \begin{tabularx}{\linewidth}{r*{5}{Y}}
@@
 
-\begin{figure}[hp]
+\begin{figure}[h]
 \begin{center}

### 2015-03-12 doc/paper/paper-knitr-APS.tex
furhter remove traces of predicting part. This is  only baseline experiments; no NB
more tables of stocks and total of views

--- 2015-02-16 doc/paper/paper-knitr-APS.tex
@@
 
-Some authors show that that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
+Some authors show that financial analysts' recommendations create value to investors \citep{womack1996,barber2001}\footnote{\cite{womack1996} finds that  post-recommendation excess returns are not mean-reverting, but are significant and in the direction forecast by the analysts.
 \cite{barber2001} finds that over the period of 1986-1996 a portfolio of stocks with the most (least) favorable consensus analyst recommendations yields an average abnormal return of 4.13 (-4.91)\%.}.
-Assuming that some analysts produce valuable advice it make sense to rank analysts based on the accuracy of their recommendations.
+Assuming that some analysts produce valuable advice it makes sense to rank analysts based on the accuracy of their recommendations.
 
-StarMine rankings are based on financial analysts accuracy either on price target or EPS forecasts.
+StarMine rankings are based on financial analysts' accuracy either on TP or EPS forecasts.
 To rank analysts based on EPS forecasts, StarMine developed a proprietary metric called a Single-stock Estimating Score (SES).
@@
 The second set of strategies takes in consideration the analysts' target price and EPS accuracy ranks to form ``smart estimates".
-For the latter set of strategies, we analyse different time information sets of the accuracy of the analysts.
+For the latter set of strategies, we analyse different time information sets to define the accuracy of the analysts.
 
 We compare the performance of the strategies based upon two types of rankings (target price and EPS forecast accuracy).
-By doing this, we address the ongoing debate in the literature on whether analysts, when issue the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
+By doing this, we indirectly address the ongoing debate in the literature on whether analysts, when issuing the target price reports, rely on simple growth-based models or use more complex models (such as the residual income model of \cite{ohlson1995}).
 For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices.
 Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.
-
-A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share\footnote{In words, abnormal growth in EPS is assumed to be the difference between expected EPS for the period less last period<U+2019>s EPS invested at the cost of equity.}.
-In short, this model justifies a price earnings ratio for companies where next period<U+2019>s earnings are expected to grow over and above the normal rate.
+\footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}
 
@@
 \begin{enumerate}
-\item  At the beginning of quarter $t$ for each stock $s$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
+\item  At the beginning of quarter $t$ for each stock $i$,   we define $Q$ and $\Omega$ (see \ref{def-q} and \ref{def-omega} below);
 
-\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $s$,  and the variance/co-variance matrix across stocks;
+\item Using the market price information available at the last day of quarter $t-1$, we obtain the market implicit returns for each stock $i$,  and the variance/co-variance matrix;
 
@@
 
-For the consensus strategy, we use median of expected returns for a particular stock $s$:
+For the consensus strategy, we use median of expected returns for a particular stock $i$:
 \begin{equation}
 \label{consq}
-Q_{cons,s}= \median \left\{r_{j,s}\right\}
-%\frac{1}{N} \sum_{j=1}^{N} r_{j,s}
+Q_{cons,i}= \median \left\{r_{j,i}\right\}
+%\frac{1}{N} \sum_{j=1}^{N} r_{j,i}
 \end{equation}
 %$N$ is the number of analysts with a valid TP report and
-where $r_{j,s}=TP_{j,s}/P_{s}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,s}$ and stock price $P_{s}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
 This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
 
-For the strategies that weight the analysts' estimates of expected return, we use analysts' rankings and the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
+For the strategies that weight the analysts' estimates of expected return the weight of each analyst $j$ is based on his/her rank such that the top analyst has the weight of 1 and then the weights diminish as the rank increases.
 
@@
 
-As described above, we use target price and EPS rankings.
+As mentioned above, we use both target price and EPS accuracy rankings.
 
 \subsubsection{Target Price ranking} 
-
+%%% change s to i for stock
 Analysts are ranked on the basis of Proportional Mean Absolute Forecast Error (PMAFE) that measures the accuracy of a forecast  \citep{clement1999,brown2001,ertimur2007}.
-First,  we define the forecast daily error  $FE_{i,j}$ as the absolute value of the difference between analysts' target price $TP_{j}$ and the daily stock price $P$ for each stock $s$:
+First,  we define the forecast daily error  $FE_{j,i}$ as the absolute value of the difference between analyst' target price $TP_{j}$ and the daily stock price $P$ for each stock $i$:
 
@@
 \label{dfe}
-FE_{i,s}^{TP}=|{P_{s}-TP_{j,s}}|
+FE_{j,i}^{TP}=|{P_{i}-TP_{j,i}}|
 \end{equation}
@@
 \label{tp:pmafe}
-PMAFE_{j,s}^{TP}=\frac{FE_{i,s}^{TP}}{\overline{FE_{s}^{TP}}}
+PMAFE_{j,i}^{TP}=\frac{FE_{j,i}^{TP}}{\overline{FE_{i}^{TP}}}
 \end{equation}
-where $\overline{{FE}_{t,s}^{TP}}$ is the average over quarter forecasting error. The target price is fixed over the quarter unless it gets revised.
+where $\overline{{FE}_{i}^{TP}}$ is the average forecasting error across analysts. The target price is fixed over the quarter unless it gets revised.
 
-The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ per quarter:
+The rank  that enters equation (\ref{eq:weight}) is average analyst's $PMAFE^{TP}$ over a particular quarter:
 \begin{equation}
-\overline{PMAFE_{j,s}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,s}^{TP}
+\overline{PMAFE_{j,i}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,i}^{TP}
 \end{equation}
@@
 \label{tp:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,s}^{TP}} \right\}
+rank_{j,i}=\rank_{j=1}^{N} \left\{ \overline{PMAFE_{j,i}^{TP}} \right\}
 \end{equation}
-where $T$ is the number of trading days in a quarter. Figure \ref{fig:example} shows an example.
+where $T$ are the number of trading days in a quarter and $N$ is the number of brokers with a valid TP.  Figure \ref{fig:example} shows an example.
 
@@
 \begin{equation}
-FE_{j,s}^{EPS}=|{ACT_{s}-PRED_{j,s}}|
+FE_{j,i}^{EPS}=|{ACT_{i}-PRED_{j,i}}|
 \end{equation}
 \begin{equation}
-PMAFE_{j,s}^{EPS}= \frac{FE_{j,s}^{EPS}}{\overline{FE_{s}^{EPS}}}
+PMAFE_{j,i}^{EPS}= \frac{FE_{j,i}^{EPS}}{\overline{FE_{i}^{EPS}}}
 \end{equation}
@@
 \label{eps:rank}
-rank_{j,s}=\rank_{j=1}^{N} \left\{ PMAFE_{j,s}^{EPS} \right\} 
+rank_{j,i}=\rank_{j=1}^{N} \left\{ PMAFE_{j,i}^{EPS} \right\} 
 \end{equation}
-where $ACT_{s}$ and $PRED_{j,s}$ are the actual and  analyst $j$ forecast EPS respectively for each stock $s$.
+where $ACT_{i}$ and $PRED_{j,i}$ are the actual quarterly EPS and  analyst $j$'s EPS forecast for stock $i$.
 
@@
 \label{def-omega}
-The confidence of $Q$ are given by the coefficient of variation of forecasting errors:
+The confidence of $Q$ is given by the coefficient of variation (CV) of forecasting errors. For each stock $i$ is given by:
 
 \begin{equation}
-CV = \frac{\sigma (FE)}{\overline{FE}}
+CV_{i} = \frac{\sigma_i (FE_{i})}{\overline{FE}_{i}}
 \end{equation}
-where $\sigma$ and $\overline{FE}$ are the standard deviation and the mean of the analysts' forecasting error for either TP or EPS.
+where $\sigma_i$ and $\overline{FE}_i$ are the standard deviation and the mean of the forecast errors across analysts for either TP or EPS.
 A low value of $CV$ reflects consensual estimates of either future prices or EPS.
@@
 
-To proceed with the trading strategy, we need to establish which information we going to use to build the rankings that will be used to compute the weighted return estimates.
+To proceed with the trading strategy, we need to establish which information we  will be using to build the rankings.
+These rankings will be the inputs to compute the weighted return estimates (``smart estimates").
 Different analysts' ranks are obtained  if we select different time horizons.
-If use only recent information, we focus on recent performance of the analysts.
-This, of course, is more sensitive to unique episodes (e.g., a quarter, which has been surprisingly good or bad).
-If, alternatively, we opt to incorporate all analyst performance, the ranking is less affected by such events, yet, it may not reflect the current abilities of the analyst.
-In this paper, we use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
+If we use only the most  recent information, we will capture the recent performance of the analysts.
+This, of course, is more sensitive to unique episodes (e.g., a quarter which has been surprisingly good or bad).
+If, alternatively, we opt to incorporate the entire analyst performance, the ranking is less affected by such events, yet it may not reflect the current analyst ability.
+We use two information sets: the first uses only the  information about the analyst' performance in period $t-1$; the second, uses all the available  information for that particular analyst.
 We call the former the \naive{} set and the latter the \default{} set.
 
-In addition to these sets,  we also create a hypothetical scenario that assumes we know the future information about the analyst' accuracy performance which would only be available at the end of $t$.
-In this setting, we are assuming that we could  perfectly predict the true analysts' ranking in advance.
-This represents the perfect foresight strategy; therefore, it serves as a reference point to the other trading strategies.
-We call this approach as the \tr{} set.
+In addition to these sets,  we also create a hypothetical scenario that assumes we anticipate perfectly the future analyst accuracy performance  that would only be available at the end of $t$.
+This represents the perfect foresight strategy.
+Therefore, it serves a performance reference point to evaluate the other trading strategies.
+We call this the \tr{} set.
 
-We formalize these sets as follows. 
+Formalizing information sets considered are: 
 \begin{itemize}
-\item  the \tr{} %-- a perfect foresight information:
+\item  the \tr{} set%-- a perfect foresight information:
 \begin{equation}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,s}$ (eq. \ref{consq}) or $Q_{rank,s}$ (eq. \ref{rankq}).
+where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
 
@@
 
-The total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 361, covering 504 S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP on annual basis\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 361, covering 504 S\&P500 stocks.
+Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
 After one year we assume that TP recommendation expires.
@@
 For the sample period (1999-2009), we report 13 672 stock-quarter observations.
-Each stock had on average of 6.42 quarterly target price reports.
+Each stock had on average of 6.421 quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
 In total, the EPS forecast sample has 12 084 stock-quarter observations.
-The average number of quarterly forecasts is 6.58.
+The average number of quarterly forecasts is 6.582.
 
-We apply the ranking procedure outline in section \ref{def-q} on two datasets.
-For target price rankings, we use the average per quarter daily errors within one quarter as the measure of analysts' forecasting ability (eq.
+We apply the ranking procedure outline in section \ref{def-q} to the two datasets.
+For target price rankings, we use the average daily errors within one quarter as the measure of analysts' forecasting ability (eq.
 \ref{tp:pmafe}).
 
-Table \ref{tab:example} and figure \ref{fig:example} illustrate an example of how we estimate the \textit{PMAFE}.
-Four analysts had valid target price for Amazon for second quarter of 1999.
+Table \ref{tab:example} and figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}.
+Four analysts had valid target prices for Amazon for second quarter of 1999.
 We plot the daily Amazon price against the brokers' target prices.
-Table \ref{tab:example} shows the resulting TP and EPS ranking.
+Table \ref{tab:example} shows the resulting TP and EPS rankings.
 On the bases of the average daily errors, LEGG is the most accurate in forecasting stock price and  DLJ is the least accurate.
@@
 
-We convert the rankings into scores as follows:
+Beforehand, we convert the rankings into scores as follows:
 \begin{equation}
 \label{eq:score}
-score_{j,s}=\frac{rank_{j,s}}{\max{rank}}
+score_{j,i}=\frac{rank_{j,i}}{\max{rank_s}}
 \end{equation}
 
-To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,s}$
+To get the cross-sectional values of scores across different stocks, we take the average of $score_{j,i}$
 \begin{equation}
 \label{eq:mean-score}
-score_{j}= \frac{1}{k} \sum_{s=1}^{k} score_{j,s}
+\overline{score_{j}}= \frac{1}{k} \sum_{s=1}^{k} score_{j,i}
 \end{equation}
-where $k$ is number of stocks for which an analyst $j$ had rank.
+where $k$ is number of stocks followed by a particular analyst $j$.
 
@@
 %Journ. of Fin economics 
-Panel A shows the dynamics of each tercile for rankings based on the accuracy in target prices.
-We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter and even after one year.
-The case of EPS ranking shows similar results (panel B).
-This analysis confirms recent finding of \cite{hilary2013} on analyst forecast consistency.
+Panel A shows the dynamics of each tercile for rankings based on target price  accuracy.
+We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.593\% (69.401\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 46.424\% and 40.681\% for the top and bottom terciles.
+
+In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
+
+These results are consistent with the recent findings of \cite{hilary2013} on analyst forecast consistency.
 
@@
 
-\subsection{$Q$ descriptive statistics}
+\subsection{Views: descriptive statistics}
 
-Tables \ref{tab:view-stat} -- \ref{tab:view-stat-default} present the descriptive statistics of analysts' expected returns conditional on the information sets.
-The expected returns  are computed comparing TP estimates with actual price.
-To inform the strategies we obtain rank-weighted estimates where weights are given either by the TP or the EPS ranks.
+Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
+%Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).
 
-\cite{bradshaw2002} reports that analysts' average expected returns for the period of 2000--2009 of 206 brokers 24\%, in \cite{da2011} these average expected return post 40\% for the period of 1996--2004, \cite{zhou2013} find on average  96\% for the sample period of 2000--2009 reports.
-The figures suggest that analyst overly optimistic.
+The expected returns  are computed comparing TP estimates with actual prices. To form the smart strategies we compute rank-weighted estimates where weights are given either by the TP or the EPS ranks.
+
+\cite{bradshaw2002} reports analyst average expected returns for the period of 2000--2009 and 206 brokers of 24\%.
+\cite{da2011} report an average expected return of 40\% for the period of 1996--2004.
+\cite{zhou2013} finds an average expected return of 96\% for the sample period of 2000--2009.
+These figures suggest that analysts are overly optimistic.
 %these values from the historical perspective, i.e., how the values of expected stock returns go inline with historical stock returns.
@@
 (\ref{consq}).
-The average consensus among the analysts about stock expected return for \tr{}, \naive{} and \default{} information sets are 18.6\%, 18.6\%, and 21.7\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (15.7\%, 15.7\%, and 18.8\%).
-Panel C shows the EPS based weighted expected returns averages (14.9\%, 14.9\%, and 19.4\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.729\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%).
+Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).
 
-Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic.
-The \default{} information set shows higher values of expected returns considering that it includes the whole history of analysts' performance.
+Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns.
 
+Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS},\textit{TP},\textit{EPS}) conditional on considered information sets.
 %obtained from the rankings based on the target price accuracy.
@@
 
-We report results from trading strategies in table (\ref{tab:strategy}). We split the table into four panels: one for the passive strategy and three for each of the information availability sets.
+We report the results from different trading strategies in table (\ref{tab:strategy}).
+We split the table into four panels.
+Panel A shows  the performance for  the passive (market) strategy \textit{Market}.
+Panels B to D compare the consensus , the TP rank weighted and the EPS rank weighted trading strategies for each of the information availability sets.
 
 \subsection{Passive strategy}
-Panel A shows  the performance of the passive strategy \textit{Market}.
-The strategy resulted in an annualized cumulative return of \ensuremath{-3.03}\% and the Sharpe Ratio  of \ensuremath{-0.182}.
-The average number of stocks used per quarter is 499.98 and the turnover ratio of strategy is 0.053, which reflects solely the ins/outs of the S\&P 500 constituents' list.
+
+The passive strategy generates an annualized cumulative return of \ensuremath{-3.032}\% with a Sharpe Ratio  of \ensuremath{-0.182} over the period 1999-2001.
+The average number of stocks held per quarter was 499.975 and the turnover ratio was 0.053, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
 
@@
 \label{sec:perfect}
-Panel B presents the results for the case of \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.89\%, 5.12\%, 1.86\%.
-All the strategies outperform the benchmark (\ensuremath{-3.03}\%).
-The results show, as expected, that  we would better of if we knew in advance that the top analysts are those of TP accuracy.
-In any case, the results suggest that the advice of analysts are valuable.
+Panel B presents the results for the case of the \tr{} information set.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.893\%, 5.116\%, 1.86\%.
+All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
+The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
+In any case, the results suggest that the advice of analysts, as a group, is valuable.
 %Yet, the top analyst
@@
 
-The \textit{TP} rankings strategy dominates also in the risk-adjusted setting.
-Its Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for \textit{CONS}, \textit{EPS}, and \textit{Market} strategies.
-In addition, the TP strategy prevail over the others if we consider the smaller trading periods (5 years).
+The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
+The Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
 Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-Panel A of the table corresponds to the perfect foresight information set.
-The TP strategy wins over the others in every period.
+The \textit{TP} strategy wins over the others in every period as expected.
 
-While this is a hypothetical setting in that it is not possible to know in advance, which analysts will rank first, it is possible to predict the ranking.
-One of the possibilities is using methods developed in Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
+While this is an hypothetical setting, given that it is not possible to know in advance which analyst will rank first, it suggests that if we can predict the rankings with some accuracy this will be a useful investment trading tool.
+One of the possibilities is using methods developed in the Machine Learning literature (e.g., \cite{aiguzhinov2010,brazdil2003}), where this type of problem (referred as a label ranking problem) has been broadly studied.
 For example, \cite{aiguzhinov2010} propose a label ranking algorithm using Bayesian approach to predict the rankings.
@@
 \subsection{Feasible strategies}
-Panels C of table (\ref{tab:strategy}) show the performance of the \naive{} information sets.
-As in case of \tr{} information set (\ref{sec:perfect}), all the active strategies outperform the \textit{Market} (\ensuremath{-3.03}\%)  and gain positive cumulative annualized returns: 0.28\%,  0.13\%, \ensuremath{-0.32}\% respectively for \textit{TP}, \textit{CONS}, and \textit{EPS} strategies.
+Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
+The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
+The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-As in case of the \tr{}, there is a risk-adjusted dominance of the \textit{TP} strategy.
-The Sharpe Ratio for this strategy is 0.018 which is higher that almost equal Sharpe Ratios of \textit{CONS} and \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
-The sub-period analysis (panel B of table \ref{tab:substrategy}) show that this strategy outperforms the others.
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.069}\% and 0.441\% respectively).
+The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
 
-The case of the \default{} (panel D table \ref{tab:strategy}), demonstrates the that \textit{TP} strategy is the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.01}\%) whereas both  \textit{CONS} and \textit{EPS} show negative returns (\ensuremath{-0.07}\% and 0.44\% respectively).
-The panel C of table \ref{tab:substrategy} show that the Sharpe Ratio of \textit{TP} strategy was lower then that of \textit{EPS} strategy for only first 2 periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for  the passive and smart strategies in all the information sets.
+The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at January of 2000 and ending at December of 2009.
+Figures show that strategies under the \tr{} panel outperform the \emph{Market} and that final value  of the portfolio of the TP strategy considerably outruns the other alternative strategies.
 
-The feasible information sets demonstrate interesting results.
-It seems to be the case that the information about stock<U+2019>s expected return based on rankings create more value than the same information but based on analysts<U+2019> consensus.
-Thus, rankings do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-Thus, rankings are useful for investors.
+In sum the results of  feasible information sets outlined above suggest that  it is worth to follow the top analysts and are supportive of \cite{desai2000ass} in that rankings are useful for investors.
 
@@
 
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is valuable.
-Yet, it is not the case for EPS ranking.
-This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not correlated with the growth-based heuristics (such as EPS forecasts).
-EPS are not good predictors of future returns, at least for short-term horizon.
-
-Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for all of the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at January of 2000 and ending at December of 2009.
-Observe that strategies under the \tr{} panel out-perform the \emph{Market} and that value of the portfolio of the TP strategy considerably outruns the other alternative strategies.
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that good at forecasting EPS.
+This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not based upon the simple valuation models.
 
@@
 
-Some institutions, such as StarMine, rank financial analysts based on their accuracy.
+Some institutions, such as StarMine, rank financial analysts based on EPS and target price accuracy.
 These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
-Therefore, there is a growing interest in understanding the relative performance of analysts.
+Therefore, there is a growing interest in understanding the relative performance of strategies based upon analysts forecasts.
 
-We show that rankings do bring value to investors as they identify the top analysts.
-By applying the Black-Litterman model, we developed the simulations of trading with different information availability sets.
-We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, that is the maximum yield any strategy can achieve.
+By applying the Black-Litterman model, we developed simulations of trading strategies using  different information sets.
+The perfect foresight scenario (using the information know at time $t$) sets the upper bound of the trading strategies in terms of the maximum yield any such strategies could achieve.
+If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts.
+
+%We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, .
 The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
@@
 
-For the future work we would like to develop the new methods to be able to get closer to the upper bound.
+For the future work we will developed new methods to forecast analysts rankings so us to get closer to the upper bound.
 
@@
   2009 & 3.00 & 5.15 & 5 &  18 & 2.19 \\ 
+   \midrule 
 Total & 3.00 & 6.42 & 6 &  21 & 3.21 \\
 
-\midrule
 \end{tabularx}
@@
   2009 & 3.00 & 5.81 & 5 &  20 & 2.78 \\ 
+   \midrule 
 Total & 3.00 & 6.58 & 6 &  26 & 3.43 \\
@@
 \end{table}
+
+ % Descritive rankings
+ \begin{table}[hp]
+  \caption{Analysts' accuracy consistency}
+  \label{tab:rank-stat}
+
+\ This contingency table shows changes in analysts'  \textit{top}, \textit{middle}, \textit{bottom} ranking bins.
+Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+    \toprule
+\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+
+ &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
+  &$middle$ & 30.7 & 47.6 & 21.7 & 100.0 \\ 
+  &$bottom$ & 13.6 & 17.0 & 69.4 & 100.0 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 46.4 & 27.7 & 25.9 & 100.0 \\ 
+  &$middle$ & 39.1 & 29.1 & 31.8 & 100.0 \\ 
+  &$bottom$ & 32.7 & 26.7 & 40.7 & 100.0 \\
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\midrule
+\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
+&&$top$&$middle$&$bottom$&Sum\\
+ &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
+  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
+  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
+    &&\multicolumn{4}{c}{$t+4$}\\ 
+&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
+  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
+  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Descriptive statistics of views}
+  \label{tab:view-stat}
+\ This table shows the descriptive statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\toprule
+Secnario& Mean (in \%) & Median (in \%) &Std.dev\\
+\midrule
+  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
+ \midrule 
+\tr{} & 18.577 & 16.861 & 0.119 \\ 
+  \naive{} & 18.615 & 16.866 & 0.120 \\ 
+  \default{} & 21.729 & 20.478 & 0.102 \\
+
+\end{tabularx}
+
+  \begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \midrule
+  \multicolumn{4}{l}{\textbf{Panel B: TP}} \\ 
+ \midrule 
+\tr{} & 14.893 & 13.407 & 0.102 \\ 
+  \naive{} & 14.895 & 13.393 & 0.103 \\ 
+  \default{} & 19.394 & 18.602 & 0.088 \\
+
+  \end{tabularx}
+  \begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
+ \midrule 
+\tr{} & 15.719 & 14.303 & 0.098 \\ 
+  \naive{} & 15.738 & 14.304 & 0.098 \\ 
+  \default{} & 18.836 & 17.795 & 0.086 \\
+
+\bottomrule
+\end{tabularx}
+  \end{table}
+
+\begin{table}[hp]
+  \caption{Number of active stocks}
+  \label{tab:stocks}
+\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C). 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\toprule
+Year& $CONS$& $PT$ &$EPS$\\
+\midrule
+  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
+ \midrule 
+1999 &  219 &  219 &  144 \\ 
+  2000 &  295 &  295 &  211 \\ 
+  2001 &  341 &  341 &  257 \\ 
+  2002 &  374 &  374 &  299 \\ 
+  2003 &  390 &  390 &  311 \\ 
+  2004 &  399 &  399 &  331 \\ 
+  2005 &  414 &  414 &  343 \\ 
+  2006 &  421 &  421 &  344 \\ 
+  2007 &  426 &  426 &  357 \\ 
+  2008 &  420 &  420 &  339 \\ 
+  2009 &  365 &  365 &  300 \\ 
+   \midrule 
+Total &  442 &  442 &  376 \\
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
+ \midrule 
+1999 &   73 &   73 &   44 \\ 
+  2000 &  257 &  257 &  185 \\ 
+  2001 &  310 &  310 &  247 \\ 
+  2002 &  362 &  362 &  288 \\ 
+  2003 &  374 &  374 &  307 \\ 
+  2004 &  385 &  385 &  318 \\ 
+  2005 &  401 &  401 &  337 \\ 
+  2006 &  415 &  415 &  343 \\ 
+  2007 &  421 &  421 &  352 \\ 
+  2008 &  422 &  422 &  349 \\ 
+  2009 &  405 &  405 &  321 \\ 
+   \midrule 
+Total &  442 &  442 &  376 \\
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
+ \midrule 
+1999 &   73 &   73 &   54 \\ 
+  2000 &  257 &  257 &  205 \\ 
+  2001 &  314 &  314 &  264 \\ 
+  2002 &  368 &  368 &  308 \\ 
+  2003 &  383 &  383 &  326 \\ 
+  2004 &  396 &  396 &  339 \\ 
+  2005 &  414 &  414 &  357 \\ 
+  2006 &  429 &  429 &  365 \\ 
+  2007 &  438 &  438 &  371 \\ 
+  2008 &  440 &  440 &  375 \\ 
+  2009 &  442 &  442 &  378 \\ 
+   \midrule 
+Total &  442 &  442 &  378 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+%'   \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \tr{}}
+%'   \label{tab:view-stat}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) for the \tr{} (\ref{q:true}) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%'   
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
+%' 
+%' 
+%' \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \naive{}}
+%'   \label{tab:view-stat-naive}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows descriptive statistics of views (expected returns) for the \naive{} (\ref{q:naive}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views-naive,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views-naive,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views-naive,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
+%' 
+%' \begin{table}[hp]
+%'   \caption{Descriptive statistics of views: \default{}}
+%'   \label{tab:view-stat-default}
+%'   \small\addtolength{\tabcolsep}{-2pt}
+%'   
+%' \ This table shows descriptive statistics of views (expected returns) for the \default{} (\ref{q:default}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
+%'   
+%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'     \toprule
+%' Year &Stocks& Mean & Median &Std.dev\\
+%' \midrule
+%' <<desc-nr.views-default,echo=F,results='asis'>>=
+%' 
+%' print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \midrule
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-r.views-default,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' #cat(rep('&',ncol(results.final)),'\\\\')
+%' print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
+%' @
+%'   \end{tabularx}
+%' 
+%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
+%'   \midrule
+%' <<desc-eps.views-default,echo=F,results='asis'>>=
+%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
+%' 
+%' print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
+%' @
+%' \bottomrule
+%'   \end{tabularx}
+%' \end{table}
+
+\begin{table}[hp]
+  \caption{Trading strategies performance: entire period}
+  \label{tab:strategy}
+  \ This table shows the performance statistics of the different trading strategies.
+Panel A presents the results for the passive strategy.
+Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}); and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates .
+Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
+The trading period goes from 2000Q1 until 2009Q4.
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \toprule
+  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
+Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
+\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
+  \midrule
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
+ \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
+  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
+  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
+   \midrule
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
+  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
+  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
+   \midrule
+
+\end{tabularx}
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
+  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
+  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{table}[hp]
+  \caption{Trading strategies performance: sub-periods}
+  \label{tab:substrategy}
+  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\toprule
+  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
+Period&\textit{Market}&\textit{CONS}&\textit{TP}&\textit{EPS} \\  \multicolumn{5}{l}{\textbf{Panel A: \tr{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.287 & 0.447 & 0.232 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.261 & 0.477 & 0.311 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.485 & 0.794 & 0.540 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.201 & 1.844 & 1.299 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.233 & 0.136 & -0.173 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.042 & 0.242 & 0.011 \\ 
+  All period & -0.182 & 0.125 & 0.351 & 0.123 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel B: \naive{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.168 & 0.169 & 0.072 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.171 & 0.215 & 0.167 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.448 & 0.492 & 0.453 \\ 
+  2003Q1/2007Q4 & 0.925 & 1.105 & 1.246 & 1.152 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.344 & -0.306 & -0.332 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.146 & -0.126 & -0.106 \\ 
+  All period & -0.182 & 0.008 & 0.018 & -0.020 \\
+
+\midrule
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
+2000Q1/2004Q4 & -0.201 & 0.247 & 0.233 & 0.276 \\ 
+  2001Q1/2005Q4 & -0.093 & 0.230 & 0.252 & 0.283 \\ 
+  2002Q1/2006Q4 & 0.196 & 0.430 & 0.469 & 0.490 \\ 
+  2003Q1/2007Q4 & 0.925 & 0.876 & 0.962 & 0.970 \\ 
+  2004Q1/2008Q4 & -0.435 & -0.439 & -0.415 & -0.403 \\ 
+  2005Q1/2009Q4 & -0.158 & -0.235 & -0.210 & -0.193 \\ 
+  All period & -0.182 & -0.004 & -0.000 & 0.028 \\
+
+\bottomrule
+\end{tabularx}
+\end{table}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/Black-litterman}
+\end{center}
+\caption{Trading strategy timeline}
+\label{fig:bl}
+\ Black-Litterman model inputs are at the beginning of $t$ we apply the BL model and form the active portfolio. At the end of $t$, we evaluate performance.
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/example-fig-1}
+\end{center}
+\caption{Daily stock price Amazon and brokers target prices}
+\label{fig:example}
+\ Target price and actual prices for Amazon  the second quarter of 1999.
+\end{figure}
+
+\begin{figure}[h]
+\begin{center}
+\includegraphics[width=\linewidth]{figure/bl-results-fig-1}
+\end{center}
+\caption{Performance of the BL model}
+\label{fig:bl-results}
+\ Quarterly performance of the cumulative portfolio wealth for all strategies.
+Panel \tr{} shows the case of the known future information; \naive{} is the case of ranking information know at $t-1$, and the \default{} is the case of using all ranking information for up to $t-1$.
+\textit{TP} is the strategy with rankings based on the accuracy in target prices, \textit{CONS} is the strategy based on the consensus among the analysts regarding a stock's expected return.
+\textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
+The trading period ranges from 2000Q1 until 2009Q4
+\end{figure}
+
+\end{document}

### 2015-03-12 src/paper.trading.APS.true.R

@@ -117,9 +117,9 @@ final.bl <- setkey(unique(bl.results.f(opt.w),by=c('Method','q.id','Views')),Met
 final.bl$Method <- factor(final.bl$Method,levels=unique(final.bl$Method)[c(3,2,1)])
 final.bl$Views <- factor(final.bl$Views,levels=unique(final.bl$Views)[c(4,1,2,3)])
 cache('final.bl')
-require("knitr")
-setwd('~/Dropbox/workspace/Projects/BL-strategies/doc/paper/')
-knit2pdf('paper-knitr-APS.Rnw',quiet=T)
-
-#colourCount = length(unique(final.bl$Views))
+# require("knitr")
+# setwd('~/Dropbox/workspace/Projects/BL-strategies/doc/paper/')
+# knit2pdf('paper-knitr-APS.Rnw',quiet=T)
+# 
+# #colourCount = length(unique(final.bl$Views))
 #getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))

### 2015-03-12 doc/paper/paper-knitr-APS.Rnw
all tables per APS

@@
 \usepackage{multirow}
+\usepackage{adjustbox}
 %\onehalfspacing
@@
 
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ round(q.data[,max(trunk.view,na.rm=T)],3)}).
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view,na.rm=T)]}).
 This is done due to occurrence of the extreme values.
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ round(bl.results['TP',1,'ann.sr'],3)} against \Sexpr{ round(bl.results['CONS',1,'ann.sr'],3)}, \Sexpr{ round(bl.results['EPS',1,'ann.sr'],3)}, and \Sexpr{ round(bl.results['Market',1,'ann.sr'],3)}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr']} against \Sexpr{ bl.results['CONS',1,'ann.sr']}, \Sexpr{ bl.results['EPS',1,'ann.sr']}, and \Sexpr{ bl.results['Market',1,'ann.sr']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is \Sexpr{ round(bl.results['TP',2,'ann.sr'],3)} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ round(bl.results['CONS',2,'ann.sr'],3)} and \Sexpr{ round(bl.results['EPS',2,'ann.sr'],3)} respectively).
+The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr']} and \Sexpr{bl.results['EPS',2,'ann.sr']} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(brok.full.stat.pt,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
+print(xtable(brok.full.stat.pt,display=c('s','f','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
 @
@@
 <<desc-eps,echo=F,results='asis'>>=
-print(xtable(brok.full.stat.eps,display=c('s','d','f','f','f','d','f')),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
+print(xtable(brok.full.stat.eps,display=c('s','d','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
 @
@@
 Panel A presents the results for the passive strategy.
-Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}); and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates .
+Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates .
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
@@
   \label{tab:substrategy}
-  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
 Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+
+\resizebox{\textwidth}{!}{%
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+\begin{tabular}{rrrrrrrrr}
 \toprule
-  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
+Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\
+
+& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\
+
 <<sr-true,echo=F,results='asis'>>=
-
+periods.array[,,,,1] <- periods.array[,,,,1]*100
 #results.final <- bl.results['Market',1,]
-cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
+#cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
+#print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+
 @
 \midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
 <<sr-naive,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
+#print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+
 @
 \midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\end{tabular}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
 <<sr-default,echo=F,results='asis'>>=
-print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
+#print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}
@@
 \end{center}
-\caption{Daily stock price Amazon and brokers target prices}
+\caption{Amazon daily stock price and brokers target prices}
 \label{fig:example}

### 2015-03-12 doc/paper/paper-knitr-APS.tex
all tables per APS

@@
 
-Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS},\textit{TP},\textit{EPS}) conditional on considered information sets.
+Table \ref{tab:stocks} shows the number of active stocks for each of the trading strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) conditional on considered information sets.
 %obtained from the rankings based on the target price accuracy.
@@
 %Year & Min& Mean & Median &Max& Std.dev\\
- 1999 & 3.00 & 4.25 & 4 &  10 & 1.59 \\ 
-  2000 & 3.00 & 4.76 & 4 &  14 & 1.88 \\ 
-  2001 & 3.00 & 5.25 & 5 &  15 & 2.32 \\ 
-  2002 & 3.00 & 6.04 & 5 &  19 & 2.95 \\ 
-  2003 & 3.00 & 6.67 & 6 &  21 & 3.43 \\ 
-  2004 & 3.00 & 7.12 & 6 &  21 & 3.62 \\ 
-  2005 & 3.00 & 7.35 & 7 &  21 & 3.59 \\ 
-  2006 & 3.00 & 7.41 & 7 &  20 & 3.42 \\ 
-  2007 & 3.00 & 7.05 & 6 &  20 & 3.33 \\ 
-  2008 & 3.00 & 6.37 & 6 &  18 & 2.88 \\ 
-  2009 & 3.00 & 5.15 & 5 &  18 & 2.19 \\ 
-   \midrule 
-Total & 3.00 & 6.42 & 6 &  21 & 3.21 \\
+ 1999 &    3 & 4.246 & 4 &   10 & 1.588 \\ 
+  2000 &    3 & 4.756 & 4 &   14 & 1.878 \\ 
+  2001 &    3 & 5.248 & 5 &   15 & 2.323 \\ 
+  2002 &    3 & 6.043 & 5 &   19 & 2.948 \\ 
+  2003 &    3 & 6.667 & 6 &   21 & 3.427 \\ 
+  2004 &    3 & 7.120 & 6 &   21 & 3.617 \\ 
+  2005 &    3 & 7.348 & 7 &   21 & 3.592 \\ 
+  2006 &    3 & 7.408 & 7 &   20 & 3.417 \\ 
+  2007 &    3 & 7.050 & 6 &   20 & 3.334 \\ 
+  2008 &    3 & 6.370 & 6 &   18 & 2.884 \\ 
+  2009 &    3 & 5.152 & 5 &   18 & 2.191 \\ 
+   \midrule 
+Total &    3 & 6.421 & 6 &   21 & 3.210 \\
 
@@
 \midrule
- 1999 & 3.00 & 5.73 & 5 &  17 & 3.01 \\ 
-  2000 & 3.00 & 5.43 & 5 &  17 & 2.77 \\ 
-  2001 & 3.00 & 6.02 & 5 &  18 & 2.97 \\ 
-  2002 & 3.00 & 6.34 & 5 &  21 & 3.26 \\ 
-  2003 & 3.00 & 6.52 & 6 &  24 & 3.43 \\ 
-  2004 & 3.00 & 6.95 & 6 &  22 & 3.75 \\ 
-  2005 & 3.00 & 7.21 & 6 &  24 & 3.77 \\ 
-  2006 & 3.00 & 7.49 & 7 &  26 & 3.84 \\ 
-  2007 & 3.00 & 7.13 & 6 &  21 & 3.53 \\ 
-  2008 & 3.00 & 6.38 & 6 &  22 & 3.06 \\ 
-  2009 & 3.00 & 5.81 & 5 &  20 & 2.78 \\ 
-   \midrule 
-Total & 3.00 & 6.58 & 6 &  26 & 3.43 \\
+ 1999 &    3 & 5.728 & 5 &   17 & 3.007 \\ 
+  2000 &    3 & 5.433 & 5 &   17 & 2.774 \\ 
+  2001 &    3 & 6.020 & 5 &   18 & 2.972 \\ 
+  2002 &    3 & 6.338 & 5 &   21 & 3.264 \\ 
+  2003 &    3 & 6.523 & 6 &   24 & 3.430 \\ 
+  2004 &    3 & 6.947 & 6 &   22 & 3.749 \\ 
+  2005 &    3 & 7.205 & 6 &   24 & 3.774 \\ 
+  2006 &    3 & 7.494 & 7 &   26 & 3.843 \\ 
+  2007 &    3 & 7.134 & 6 &   21 & 3.532 \\ 
+  2008 &    3 & 6.378 & 6 &   22 & 3.062 \\ 
+  2009 &    3 & 5.811 & 5 &   20 & 2.783 \\ 
+   \midrule 
+Total &    3 & 6.582 & 6 &   26 & 3.426 \\
 
@@
 \toprule
-Secnario& Mean (in \%) & Median (in \%) &Std.dev\\
+& Mean (in \%) & Median (in \%) &Std.dev\\
 \midrule
@@
 \toprule
-Year& $CONS$& $PT$ &$EPS$\\
-\midrule
+Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
   \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
@@
   \label{tab:substrategy}
-  \ This table presents the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
 Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+
+\resizebox{\textwidth}{!}{%
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+\begin{tabular}{rrrrrrrrr}
 \toprule
-  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-Period&\textit{Market}&\textit{CONS}&\textit{TP}&\textit{EPS} \\  \multicolumn{5}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -0.201 & 0.287 & 0.447 & 0.232 \\ 
-  2001Q1/2005Q4 & -0.093 & 0.261 & 0.477 & 0.311 \\ 
-  2002Q1/2006Q4 & 0.196 & 0.485 & 0.794 & 0.540 \\ 
-  2003Q1/2007Q4 & 0.925 & 1.201 & 1.844 & 1.299 \\ 
-  2004Q1/2008Q4 & -0.435 & -0.233 & 0.136 & -0.173 \\ 
-  2005Q1/2009Q4 & -0.158 & -0.042 & 0.242 & 0.011 \\ 
-  All period & -0.182 & 0.125 & 0.351 & 0.123 \\
-
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel B: \naive{}}} \\
-2000Q1/2004Q4 & -0.201 & 0.168 & 0.169 & 0.072 \\ 
-  2001Q1/2005Q4 & -0.093 & 0.171 & 0.215 & 0.167 \\ 
-  2002Q1/2006Q4 & 0.196 & 0.448 & 0.492 & 0.453 \\ 
-  2003Q1/2007Q4 & 0.925 & 1.105 & 1.246 & 1.152 \\ 
-  2004Q1/2008Q4 & -0.435 & -0.344 & -0.306 & -0.332 \\ 
-  2005Q1/2009Q4 & -0.158 & -0.146 & -0.126 & -0.106 \\ 
-  All period & -0.182 & 0.008 & 0.018 & -0.020 \\
-
-\midrule
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\
+
+& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\
+
+  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\
+
+\midrule
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 2.689 & 0.168 & 2.635 & 0.169 & 1.145 & 0.072 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.686 & 0.171 & 3.280 & 0.215 & 2.599 & 0.167 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.740 & 0.448 & 6.088 & 0.492 & 5.465 & 0.453 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.542 & 1.105 & 10.065 & 1.246 & 9.312 & 1.152 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.718 & -0.344 & -4.155 & -0.306 & -4.546 & -0.332 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.373 & -0.146 & -2.019 & -0.126 & -1.759 & -0.106 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.126 & 0.008 & 0.281 & 0.018 & -0.318 & -0.020 \\
+
+\midrule
+\end{tabular}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -0.201 & 0.247 & 0.233 & 0.276 \\ 
-  2001Q1/2005Q4 & -0.093 & 0.230 & 0.252 & 0.283 \\ 
-  2002Q1/2006Q4 & 0.196 & 0.430 & 0.469 & 0.490 \\ 
-  2003Q1/2007Q4 & 0.925 & 0.876 & 0.962 & 0.970 \\ 
-  2004Q1/2008Q4 & -0.435 & -0.439 & -0.415 & -0.403 \\ 
-  2005Q1/2009Q4 & -0.158 & -0.235 & -0.210 & -0.193 \\ 
-  All period & -0.182 & -0.004 & -0.000 & 0.028 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\
 
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}

### 2015-03-12 src/script.predict.trade.R
some changes

@@ -12,6 +12,8 @@ system.time(source('munge/01-data.q.ret.R'))
 ### data for first paper
 system.time(source('src/paper.trading.APS.true.R'))
 
+colourCount = length(unique(final.bl$Views))
+getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
 ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
 
 ggplot(unique(melt(final.bl[,list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw(base_family='Avenir')+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3L)*100L),angle=90L,size=3L,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))

### 2015-03-12 doc/paper/paper-knitr-APS.tex
some changes
same number of stocks for both TP and EPS. Results change; all-time is indifferent in terms of ann.return

@@
 \label{eq:score}
-score_{j,i}=\frac{rank_{j,i}}{\max{rank_s}}
+score_{j,i}=\frac{rank_{j,i}}{\max{rank_i}}
 \end{equation}
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.593\% (69.401\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 46.424\% and 40.681\% for the top and bottom terciles.
-
-In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.769\% (69.548\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 46.199\% and 41.09\% for the top and bottom terciles.
+
+In the case of EPS ranking  (panel B) 48.417\% and  28.496\% ( 46.844\% and  32.399\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.729\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%).
-Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.944\%, 18.99\%, and 22.207\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (16.068\%, 16.095\%, and 19.343\%).
+Panel C shows the EPS based weighted expected returns averages (14.964\%, 14.967\%, and 19.511\%).
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.893\%, 5.116\%, 1.86\%.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 2.247\%, 5.4\%, 1.957\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.371 against 0.149, 0.129, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
+The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.069}\% and 0.441\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.441\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.413\% and 0.441\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 
- &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
-  &$middle$ & 30.7 & 47.6 & 21.7 & 100.0 \\ 
-  &$bottom$ & 13.6 & 17.0 & 69.4 & 100.0 \\ 
+ &$top$ & 67.8 & 22.0 & 10.2 & 100.0 \\ 
+  &$middle$ & 29.9 & 48.2 & 22.0 & 100.0 \\ 
+  &$bottom$ & 13.4 & 17.1 & 69.5 & 100.0 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.4 & 27.7 & 25.9 & 100.0 \\ 
-  &$middle$ & 39.1 & 29.1 & 31.8 & 100.0 \\ 
-  &$bottom$ & 32.7 & 26.7 & 40.7 & 100.0 \\
+&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
+  &$middle$ & 39.2 & 29.2 & 31.7 & 100.0 \\ 
+  &$bottom$ & 32.1 & 26.8 & 41.1 & 100.0 \\
 
@@
  &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
-  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
-  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
+  &$middle$ & 48.2 & 26.2 & 25.8 & 100.2 \\ 
+  &$bottom$ & 46.3 & 25.9 & 28.5 & 100.6 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
-  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
-  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\
+&$top$ & 46.8 & 28.3 & 26.0 & 101.2 \\ 
+  &$middle$ & 45.5 & 27.0 & 28.1 & 100.6 \\ 
+  &$bottom$ & 42.7 & 27.6 & 32.4 & 102.7 \\
 
@@
  \midrule 
-\tr{} & 18.577 & 16.861 & 0.119 \\ 
-  \naive{} & 18.615 & 16.866 & 0.120 \\ 
-  \default{} & 21.729 & 20.478 & 0.102 \\
+\tr{} & 18.944 & 17.156 & 0.119 \\ 
+  \naive{} & 18.990 & 17.173 & 0.119 \\ 
+  \default{} & 22.207 & 20.707 & 0.101 \\
 
@@
  \midrule 
-\tr{} & 14.893 & 13.407 & 0.102 \\ 
-  \naive{} & 14.895 & 13.393 & 0.103 \\ 
-  \default{} & 19.394 & 18.602 & 0.088 \\
+\tr{} & 14.964 & 13.449 & 0.103 \\ 
+  \naive{} & 14.967 & 13.432 & 0.103 \\ 
+  \default{} & 19.511 & 18.756 & 0.089 \\
 
@@
  \midrule 
-\tr{} & 15.719 & 14.303 & 0.098 \\ 
-  \naive{} & 15.738 & 14.304 & 0.098 \\ 
-  \default{} & 18.836 & 17.795 & 0.086 \\
+\tr{} & 16.068 & 14.522 & 0.098 \\ 
+  \naive{} & 16.095 & 14.525 & 0.098 \\ 
+  \default{} & 19.343 & 18.179 & 0.084 \\
 
@@
  \midrule 
-1999 &  219 &  219 &  144 \\ 
-  2000 &  295 &  295 &  211 \\ 
-  2001 &  341 &  341 &  257 \\ 
-  2002 &  374 &  374 &  299 \\ 
-  2003 &  390 &  390 &  311 \\ 
-  2004 &  399 &  399 &  331 \\ 
-  2005 &  414 &  414 &  343 \\ 
-  2006 &  421 &  421 &  344 \\ 
-  2007 &  426 &  426 &  357 \\ 
-  2008 &  420 &  420 &  339 \\ 
-  2009 &  365 &  365 &  300 \\ 
-   \midrule 
-Total &  442 &  442 &  376 \\
+1999 &  202 &  202 &  145 \\ 
+  2000 &  269 &  269 &  211 \\ 
+  2001 &  306 &  306 &  257 \\ 
+  2002 &  333 &  333 &  299 \\ 
+  2003 &  346 &  346 &  311 \\ 
+  2004 &  351 &  351 &  331 \\ 
+  2005 &  359 &  359 &  343 \\ 
+  2006 &  361 &  361 &  344 \\ 
+  2007 &  365 &  365 &  357 \\ 
+  2008 &  361 &  361 &  339 \\ 
+  2009 &  323 &  323 &  300 \\ 
+   \midrule 
+Total &  379 &  379 &  376 \\
 
@@
  \midrule 
-1999 &   73 &   73 &   44 \\ 
-  2000 &  257 &  257 &  185 \\ 
-  2001 &  310 &  310 &  247 \\ 
-  2002 &  362 &  362 &  288 \\ 
-  2003 &  374 &  374 &  307 \\ 
-  2004 &  385 &  385 &  318 \\ 
-  2005 &  401 &  401 &  337 \\ 
-  2006 &  415 &  415 &  343 \\ 
-  2007 &  421 &  421 &  352 \\ 
-  2008 &  422 &  422 &  349 \\ 
-  2009 &  405 &  405 &  321 \\ 
-   \midrule 
-Total &  442 &  442 &  376 \\
+1999 &   69 &   69 &   44 \\ 
+  2000 &  235 &  235 &  186 \\ 
+  2001 &  281 &  281 &  247 \\ 
+  2002 &  323 &  323 &  288 \\ 
+  2003 &  334 &  334 &  307 \\ 
+  2004 &  341 &  341 &  318 \\ 
+  2005 &  352 &  352 &  337 \\ 
+  2006 &  359 &  359 &  343 \\ 
+  2007 &  362 &  362 &  352 \\ 
+  2008 &  361 &  361 &  349 \\ 
+  2009 &  351 &  351 &  321 \\ 
+   \midrule 
+Total &  379 &  379 &  376 \\
 
@@
  \midrule 
-1999 &   73 &   73 &   54 \\ 
-  2000 &  257 &  257 &  205 \\ 
-  2001 &  314 &  314 &  264 \\ 
-  2002 &  368 &  368 &  308 \\ 
-  2003 &  383 &  383 &  326 \\ 
-  2004 &  396 &  396 &  339 \\ 
-  2005 &  414 &  414 &  357 \\ 
-  2006 &  429 &  429 &  365 \\ 
-  2007 &  438 &  438 &  371 \\ 
-  2008 &  440 &  440 &  375 \\ 
-  2009 &  442 &  442 &  378 \\ 
-   \midrule 
-Total &  442 &  442 &  378 \\
+1999 &   69 &   69 &   54 \\ 
+  2000 &  235 &  235 &  205 \\ 
+  2001 &  284 &  284 &  264 \\ 
+  2002 &  327 &  327 &  308 \\ 
+  2003 &  341 &  341 &  326 \\ 
+  2004 &  350 &  350 &  339 \\ 
+  2005 &  364 &  364 &  357 \\ 
+  2006 &  371 &  371 &  365 \\ 
+  2007 &  375 &  375 &  371 \\ 
+  2008 &  377 &  377 &  375 \\ 
+  2009 &  379 &  379 &  378 \\ 
+   \midrule 
+Total &  379 &  379 &  378 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
- \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
-  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
-  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
+ \textit{CONS} & 2.247 & 15.032 & 0.149 &  257 & 0.277 \\ 
+  \textit{TP} & 5.400 & 14.552 & 0.371 &  257 & 0.298 \\ 
+  \textit{EPS} & 1.957 & 15.145 & 0.129 &  209 & 0.501 \\ 
    \midrule
@@
   \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
-  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
-  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
+ \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
+  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
+  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
    \midrule
@@
   \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
-  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
-  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\
+ \textit{CONS} & 0.413 & 15.873 & 0.026 &  257 & 0.185 \\ 
+  \textit{TP} & 0.441 & 15.658 & 0.028 &  257 & 0.189 \\ 
+  \textit{EPS} & 0.441 & 15.702 & 0.028 &  250 & 0.198 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 5.269 & 0.343 & 7.564 & 0.509 & 3.757 & 0.245 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 4.232 & 0.280 & 7.159 & 0.496 & 4.859 & 0.335 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 6.230 & 0.504 & 9.682 & 0.816 & 6.428 & 0.537 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 10.092 & 1.180 & 14.339 & 1.817 & 10.708 & 1.296 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -3.059 & -0.245 & 1.285 & 0.103 & -2.163 & -0.174 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -0.689 & -0.046 & 3.279 & 0.225 & 0.187 & 0.012 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 2.247 & 0.149 & 5.400 & 0.371 & 1.957 & 0.129 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 2.689 & 0.168 & 2.635 & 0.169 & 1.145 & 0.072 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 2.686 & 0.171 & 3.280 & 0.215 & 2.599 & 0.167 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.740 & 0.448 & 6.088 & 0.492 & 5.465 & 0.453 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.542 & 1.105 & 10.065 & 1.246 & 9.312 & 1.152 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.718 & -0.344 & -4.155 & -0.306 & -4.546 & -0.332 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.373 & -0.146 & -2.019 & -0.126 & -1.759 & -0.106 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & 0.126 & 0.008 & 0.281 & 0.018 & -0.318 & -0.020 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 4.702 & 0.305 & 4.367 & 0.291 & 4.204 & 0.277 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.873 & 0.253 & 4.112 & 0.278 & 4.294 & 0.286 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.774 & 0.455 & 6.045 & 0.494 & 5.997 & 0.491 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 8.344 & 0.881 & 8.584 & 0.964 & 8.604 & 0.972 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -6.018 & -0.432 & -5.686 & -0.412 & -5.537 & -0.402 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -3.700 & -0.225 & -3.337 & -0.203 & -3.186 & -0.194 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.413 & 0.026 & 0.441 & 0.028 & 0.441 & 0.028 \\
 

### 2015-03-12 src/paper.trading.APS.true.R

@@ -1,9 +1,15 @@
 
 
-stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+m.stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+
+load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
+
 quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
 
+stocks <- sort(intersect(intersect(m.stocks,q.data$Stock),complete.dt$Stock))
+
 core.dt <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)[stocks]
+
 
 
 pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
@@ -35,7 +41,7 @@ pt.rank.views <- setnames(pt.ret[,year:=format(as.yearqtr(q.id),'%Y')],'V1','Vie
 cache('pt.rank.views')
 
 ###EPS case
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
+
 
[…]

### 2015-03-12 src/script.predict.trade.R

@@ -11,7 +11,7 @@ system.time(source('munge/01-data.q.ret.R'))
 
 ### data for first paper
 system.time(source('src/paper.trading.APS.true.R'))
-
+require(ggplot2)
 colourCount = length(unique(final.bl$Views))
 getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
 ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
@@ -22,4 +22,10 @@ require("knitr")
 setwd('~/Dropbox/workspace/Projects/BL-strategies/doc/paper/')
 knit2pdf('paper-knitr-APS.Rnw',quiet=T)
 setwd('~/Dropbox/workspace/Projects/BL-strategies/')
+
+
+ggplot(unique(final.bl[Views!='Market'],by=c('Quarters','n.views','Method','Views')),aes(x=as.Date(Quarters),y=n.views,group=Method,color=Method))+geom_point()+geom_line()+facet_grid(Views~.,scale='free_x')+theme_bw()
+
+
+
 

### 2015-03-16 doc/paper/paper-knitr-APS.Rnw
some changes

@@
 
-\bibliographystyle{ecta}
+\bibliographystyle{chicago}
 %\bibliographystyle{newapa}
@@
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=4,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
 cat('\\midrule \n')
@@
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @

### 2015-03-16 doc/paper/paper-knitr-APS.tex
some changes

@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.769\% (69.548\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 46.199\% and 41.09\% for the top and bottom terciles.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.739\% (69.582\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 46.189\% and 41.204\% for the top and bottom terciles.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.944\%, 18.99\%, and 22.207\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (16.068\%, 16.095\%, and 19.343\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.947\%, 18.993\%, and 22.216\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (16.071\%, 16.098\%, and 19.352\%).
 Panel C shows the EPS based weighted expected returns averages (14.964\%, 14.967\%, and 19.511\%).
@@
 
- &$top$ & 67.8 & 22.0 & 10.2 & 100.0 \\ 
-  &$middle$ & 29.9 & 48.2 & 22.0 & 100.0 \\ 
-  &$bottom$ & 13.4 & 17.1 & 69.5 & 100.0 \\ 
+ &$top$ & 67.7 & 22.1 & 10.2 & 100.0 \\ 
+  &$middle$ & 29.9 & 48.2 & 21.9 & 100.0 \\ 
+  &$bottom$ & 13.4 & 17.1 & 69.6 & 100.0 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
 &$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
-  &$middle$ & 39.2 & 29.2 & 31.7 & 100.0 \\ 
-  &$bottom$ & 32.1 & 26.8 & 41.1 & 100.0 \\
+  &$middle$ & 39.2 & 29.2 & 31.6 & 100.0 \\ 
+  &$bottom$ & 32.1 & 26.7 & 41.2 & 100.0 \\
 
@@
  \midrule 
-\tr{} & 18.944 & 17.156 & 0.119 \\ 
-  \naive{} & 18.990 & 17.173 & 0.119 \\ 
-  \default{} & 22.207 & 20.707 & 0.101 \\
+\tr{} & 18.947 & 17.156 & 0.119 \\ 
+  \naive{} & 18.993 & 17.173 & 0.119 \\ 
+  \default{} & 22.216 & 20.715 & 0.101 \\
 
@@
  \midrule 
-\tr{} & 16.068 & 14.522 & 0.098 \\ 
-  \naive{} & 16.095 & 14.525 & 0.098 \\ 
-  \default{} & 19.343 & 18.179 & 0.084 \\
+\tr{} & 16.071 & 14.525 & 0.098 \\ 
+  \naive{} & 16.098 & 14.528 & 0.098 \\ 
+  \default{} & 19.352 & 18.195 & 0.084 \\
 
@@
   2004 &  351 &  351 &  331 \\ 
-  2005 &  359 &  359 &  343 \\ 
-  2006 &  361 &  361 &  344 \\ 
-  2007 &  365 &  365 &  357 \\ 
-  2008 &  361 &  361 &  339 \\ 
+  2005 &  358 &  358 &  343 \\ 
+  2006 &  360 &  360 &  344 \\ 
+  2007 &  364 &  364 &  357 \\ 
+  2008 &  360 &  360 &  339 \\ 
   2009 &  323 &  323 &  300 \\ 
    \midrule 
-Total &  379 &  379 &  376 \\
+Total &  378 &  378 &  376 \\
 
@@
   2005 &  352 &  352 &  337 \\ 
-  2006 &  359 &  359 &  343 \\ 
-  2007 &  362 &  362 &  352 \\ 
-  2008 &  361 &  361 &  349 \\ 
+  2006 &  358 &  358 &  343 \\ 
+  2007 &  361 &  361 &  352 \\ 
+  2008 &  360 &  360 &  349 \\ 
   2009 &  351 &  351 &  321 \\ 
    \midrule 
-Total &  379 &  379 &  376 \\
+Total &  378 &  378 &  376 \\
 
@@
   2005 &  364 &  364 &  357 \\ 
-  2006 &  371 &  371 &  365 \\ 
-  2007 &  375 &  375 &  371 \\ 
-  2008 &  377 &  377 &  375 \\ 
-  2009 &  379 &  379 &  378 \\ 
-   \midrule 
-Total &  379 &  379 &  378 \\
+  2006 &  370 &  370 &  365 \\ 
+  2007 &  374 &  374 &  371 \\ 
+  2008 &  376 &  376 &  375 \\ 
+  2009 &  378 &  378 &  378 \\ 
+   \midrule 
+Total &  378 &  378 &  378 \\
 
@@
 Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
-\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
+\textit{Market} & -3.0323 & 16.6545 & -0.1821 &   499 & 0.0526 \\ 
   \midrule
@@
   \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
- \textit{CONS} & 2.247 & 15.032 & 0.149 &  257 & 0.277 \\ 
-  \textit{TP} & 5.400 & 14.552 & 0.371 &  257 & 0.298 \\ 
-  \textit{EPS} & 1.957 & 15.145 & 0.129 &  209 & 0.501 \\ 
+ \textit{CONS} & 2.2470 & 15.0316 & 0.1495 &   257 & 0.2774 \\ 
+  \textit{TP} & 5.3998 & 14.5525 & 0.3711 &   257 & 0.2982 \\ 
+  \textit{EPS} & 1.9567 & 15.1450 & 0.1292 &   209 & 0.5006 \\ 
    \midrule
@@
   \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
-  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
-  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
+ \textit{CONS} & 0.4491 & 15.9932 & 0.0281 &   252 & 0.2503 \\ 
+  \textit{TP} & 0.6217 & 15.6819 & 0.0396 &   252 & 0.2556 \\ 
+  \textit{EPS} & -0.3614 & 16.1002 & -0.0224 &   206 & 0.4077 \\ 
    \midrule
@@
   \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & 0.413 & 15.873 & 0.026 &  257 & 0.185 \\ 
-  \textit{TP} & 0.441 & 15.658 & 0.028 &  257 & 0.189 \\ 
-  \textit{EPS} & 0.441 & 15.702 & 0.028 &  250 & 0.198 \\
+ \textit{CONS} & 0.4128 & 15.8729 & 0.0260 &   257 & 0.1853 \\ 
+  \textit{TP} & 0.4414 & 15.6585 & 0.0282 &   257 & 0.1888 \\ 
+  \textit{EPS} & 0.4409 & 15.7018 & 0.0281 &   250 & 0.1977 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 5.269 & 0.343 & 7.564 & 0.509 & 3.757 & 0.245 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 4.232 & 0.280 & 7.159 & 0.496 & 4.859 & 0.335 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 6.230 & 0.504 & 9.682 & 0.816 & 6.428 & 0.537 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 10.092 & 1.180 & 14.339 & 1.817 & 10.708 & 1.296 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -3.059 & -0.245 & 1.285 & 0.103 & -2.163 & -0.174 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -0.689 & -0.046 & 3.279 & 0.225 & 0.187 & 0.012 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & 2.247 & 0.149 & 5.400 & 0.371 & 1.957 & 0.129 \\
+2000Q1/2004Q4 & -3.4007 & -0.2011 & 5.2694 & 0.3428 & 7.5639 & 0.5094 & 3.7574 & 0.2453 \\ 
+  2001Q1/2005Q4 & -1.5393 & -0.0926 & 4.2321 & 0.2804 & 7.1589 & 0.4958 & 4.8590 & 0.3349 \\ 
+  2002Q1/2006Q4 & 2.5665 & 0.1960 & 6.2298 & 0.5039 & 9.6824 & 0.8158 & 6.4279 & 0.5371 \\ 
+  2003Q1/2007Q4 & 7.9195 & 0.9254 & 10.0924 & 1.1796 & 14.3387 & 1.8166 & 10.7077 & 1.2962 \\ 
+  2004Q1/2008Q4 & -5.6671 & -0.4354 & -3.0593 & -0.2447 & 1.2854 & 0.1032 & -2.1627 & -0.1744 \\ 
+  2005Q1/2009Q4 & -2.6625 & -0.1582 & -0.6887 & -0.0461 & 3.2793 & 0.2252 & 0.1873 & 0.0122 \\ 
+   \midrule 
+All period & -3.0323 & -0.1821 & 2.2470 & 0.1495 & 5.3998 & 0.3711 & 1.9567 & 0.1292 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\
+2000Q1/2004Q4 & -3.4007 & -0.2011 & 3.4013 & 0.2145 & 3.3446 & 0.2169 & 1.0450 & 0.0656 \\ 
+  2001Q1/2005Q4 & -1.5393 & -0.0926 & 2.8396 & 0.1805 & 3.5380 & 0.2323 & 2.5370 & 0.1628 \\ 
+  2002Q1/2006Q4 & 2.5665 & 0.1960 & 5.8368 & 0.4684 & 6.2288 & 0.5169 & 5.4148 & 0.4477 \\ 
+  2003Q1/2007Q4 & 7.9195 & 0.9254 & 9.4104 & 1.0983 & 9.9651 & 1.2416 & 9.2980 & 1.1488 \\ 
+  2004Q1/2008Q4 & -5.6671 & -0.4354 & -4.8255 & -0.3490 & -4.2537 & -0.3109 & -4.5513 & -0.3325 \\ 
+  2005Q1/2009Q4 & -2.6625 & -0.1582 & -2.4189 & -0.1474 & -2.0293 & -0.1250 & -1.7483 & -0.1050 \\ 
+   \midrule 
+All period & -3.0323 & -0.1821 & 0.4491 & 0.0281 & 0.6217 & 0.0396 & -0.3614 & -0.0224 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 4.702 & 0.305 & 4.367 & 0.291 & 4.204 & 0.277 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.873 & 0.253 & 4.112 & 0.278 & 4.294 & 0.286 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.774 & 0.455 & 6.045 & 0.494 & 5.997 & 0.491 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 8.344 & 0.881 & 8.584 & 0.964 & 8.604 & 0.972 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -6.018 & -0.432 & -5.686 & -0.412 & -5.537 & -0.402 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -3.700 & -0.225 & -3.337 & -0.203 & -3.186 & -0.194 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & 0.413 & 0.026 & 0.441 & 0.028 & 0.441 & 0.028 \\
+2000Q1/2004Q4 & -3.4007 & -0.2011 & 4.7015 & 0.3048 & 4.3673 & 0.2913 & 4.2041 & 0.2771 \\ 
+  2001Q1/2005Q4 & -1.5393 & -0.0926 & 3.8730 & 0.2529 & 4.1116 & 0.2777 & 4.2935 & 0.2865 \\ 
+  2002Q1/2006Q4 & 2.5665 & 0.1960 & 5.7738 & 0.4555 & 6.0452 & 0.4941 & 5.9968 & 0.4914 \\ 
+  2003Q1/2007Q4 & 7.9195 & 0.9254 & 8.3443 & 0.8812 & 8.5839 & 0.9635 & 8.6038 & 0.9724 \\ 
+  2004Q1/2008Q4 & -5.6671 & -0.4354 & -6.0175 & -0.4319 & -5.6861 & -0.4116 & -5.5371 & -0.4018 \\ 
+  2005Q1/2009Q4 & -2.6625 & -0.1582 & -3.7003 & -0.2250 & -3.3367 & -0.2025 & -3.1863 & -0.1942 \\ 
+   \midrule 
+All period & -3.0323 & -0.1821 & 0.4128 & 0.0260 & 0.4414 & 0.0282 & 0.4409 & 0.0281 \\
 

### 2015-03-16 src/paper.trading.APS.true.R

@@ -1,12 +1,14 @@
 
 
-m.stocks <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+stocks.m <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
 
 load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
 
 quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
 
-stocks <- sort(intersect(intersect(m.stocks,q.data$Stock),complete.dt$Stock))
+stocks <- sort(intersect(intersect(stocks.m,setkey(q.data,q.id)[quarters]$Stock),setkey(complete.dt,q.id)[quarters]$Stock))
+
+
 
 core.dt <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)[stocks]
 
@@ -90,7 +92,8 @@ conf.dt <- melt(unique(core.dt,by=c('q.id','Stock'),fromLast = T)[,.(q.id,Stock,
 conf.coef <- acast(conf.dt,q.id~Stock~variable,value.var='value')
 
 eps.stocks <- intersect(dimnames(eps.list.rank)[[2]],dimnames(conf.coef)[[2]])
-same.stocks <- intersect(intersect(dimnames(pt.list.rank)[[2]],dimnames(conf.coef)[[2]]),dimnames(eps.list.rank)[[2]])
+
+#same.stocks <- intersect(intersect(dimnames(pt.list.rank)[[2]],dimnames(conf.coef)[[2]]),dimnames(eps.list.rank)[[2]])
 
 ##BL inputs for non-rank strategy:meanTper and s.coefVar
 #cons.rankings <- pt.baseline.rankings[3:42,pt.all.b,pt.all.s,]
@@ -110,9 +113,9 @@ tau=1/50
 
 #source('lib/BL-functions.R')
 
-pt.opt.w <- opt.w.f(pt.list.rank,conf.coef[,same.stocks,],tau)[,Views:='TP']
[…]

### 2015-03-16 src/paper.trading.APS.true.R
change to different stock sets (type column: 'all' and 'same')

@@ -10,28 +10,31 @@ stocks <- sort(intersect(intersect(stocks.m,setkey(q.data,q.id)[quarters]$Stock)
 
 
 
-core.dt <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)[stocks]
+core.dt.tmp <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)
+
+core.dt <- rbind(core.dt.tmp[stocks][,type:='same'],core.dt.tmp[stocks.m][,type:='all'])
 
 
-
-pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock),.SDcols=c('q.id','Broker','Stock','b.view')][,.(q.id,Broker,Stock,b.view)][,true:=truncate.f(b.view,percentile)][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock)],id.vars = c('q.id','Stock','Broker'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method)
[…]

### 2015-03-16 lib/BL-functions.R
working commit

@@ -369,9 +369,9 @@ opt.w.f <- function(views,conf,tau){
         
         #rbindlist(lapply(agg.names,function(agg){
                 #list.conf <- alply(conf[,,,agg],2,.dims=T)
-                rbindlist(mclapply(dimnames(views)[[3]],function(type){
+                rbindlist(lapply(dimnames(views)[[3]],function(type){
                         rbindlist(non.rank.script.weights.env.f(type,market.list[m.period],views[bl.period,,type],conf[bl.period,,type],tau))
-                },mc.cores=cores)
+                })
                 )
                 #}))
 }
@@ -434,38 +434,32 @@ cum.ret.f <- function(Return,n.views,in.value=100){
 
 bl.results.f <- function(opt.w)
 {
-bl.results <- unique(opt.w,by=c('q.id','Method','Views'))[,list(Quarters=as.yearqtr(Quarters),Views,Method,port.ret,ns.port.ret,ann.port.ret,n.views,q.id)]
-#risk.free <- setkey(rbindlist(lapply(seq_along(market.list),function(q){data.table(Quarters=as.yearqtr(market.list[[q]]$Quarters),rf=market.list[[q]]$rf)}))[m.period,],Quarters)
-##Looks like these are the dates for SP500 from=1998-10-01 to 2009-09-30; shoud be from 1999-01-01 to 2009-12-31
-#require(quantmod)
-#prices = getSymbols("^GSPC", from = "1999-01-01", to = "2009-12-31")
-
-#prices = getSymbols("SPY", from = "1999-01-01", to = "2009-12-31")
-#prices = getSymbols("^GSPC", from = "1999-01-01", to = "2009-12-31")
-#market.port.ret<- setnames(setkey(data.table(Quarters=index(quarterlyReturn(get(prices)[,6])),port.ret=coredata(quarterlyReturn(get(prices)[,6])))[,Quarters:=as.yearqtr(Quarters)],Quarters)[risk.free],2,'sp.ret')[,port.ret:=sp.ret-rf][,Views:='Market'][,n.views:=500][,ann.port.ret:=(1+port.ret)^(1/4)-1][,q.id:=.I][,.(Quarters,Views,port.ret,ann.port.ret,n.views,q.id)]
[…]

### 2015-03-16 src/paper.trading.APS.true.R

@@ -117,18 +117,18 @@ tau=1/50
 
 #source('lib/BL-functions.R')
 
-opt.w <- rbindlist(lapply(c('same','all'),function(t)
+opt.w <- rbindlist(mclapply(c('same','all'),function(t)
 {
+rbind(
+        opt.w.f(pt.list.rank[[t]],conf.coef[[t]],tau)[,Views:='TP'],
+        opt.w.f(cons.list.rank[[t]],conf.coef[[t]],tau)[,Views:='CONS'],
+        opt.w.f(eps.list.rank[[t]],conf.coef[[t]][,eps.stocks,],tau)[,Views:='EPS'])[,type:=t]
+},mc.cores=cores))
 
-rbind(opt.w.f(pt.list.rank[[t]],conf.coef[[t]],tau)[,Views:='TP'],opt.w.f(cons.list.rank[[t]],conf.coef[[t]],tau)[,Views:='CONS'],opt.w.f(eps.list.rank[[t]],conf.coef[[t]][,eps.stocks,],tau)[,Views:='EPS'])[,type:=t]
-}))
-
-
-opt.w <- rbind(pt.opt.w,cons.opt.w,eps.opt.w)
 cache('opt.w')
 
 
-final.bl <- setkey(unique(bl.results.f(opt.w),by=c('Method','q.id','Views')),Method)
+final.bl <- setkey(unique(bl.results.f(opt.w),by=c('Method','q.id','Views','type')),Method,type)
 final.bl$Method <- factor(final.bl$Method,levels=unique(final.bl$Method)[c(3,2,1)])
 final.bl$Views <- factor(final.bl$Views,levels=unique(final.bl$Views)[c(4,1,2,3)])
 cache('final.bl')

### 2015-03-17 doc/paper/paper-knitr-APS.Rnw
modify rnw for different types of stock sets

@@
 
-stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='CONS']
-
-stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='PT']
-
-stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method)]),1,'year'))[,Strategy:='EPS']
+stat.nr <- rbind(na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',na.omit(nr.views)[,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='CONS']
+
+stat.pt.view <- rbind(pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',pt.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='PT']
+
+stat.eps.view <- rbind(eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(year,Method,type)],setnames(cbind('Total',eps.rank.views[View!=0,list(mean=mean(View),median=median(View),st.dev=sd(View),Stocks=length(unique(Stock))),by=.(Method,type)]),1,'year'))[,Strategy:='EPS']
 
@@
 
-test <- melt(stat.full,id.vars = c('year','Method','Strategy'))
-test.a <- acast(test,year~Method~Strategy~variable,value.var = 'value')
+test <- melt(stat.full,id.vars = c('year','Method','Strategy','type'))
+test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
 
@@
 final.bl <- final.bl[,ann.ret:=ann.ret*100][,ann.st:=ann.sd*100]
-bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views')),Views~Method~variable,value.var = 'value')
+bl.results <- acast(unique(melt(data = final.bl,id.vars = c('Method','Views','type'),measure.vars  = c('ann.ret','ann.st','ann.sr','meanViews','Ave.TO')),by=c('Method','variable','Views','type')),Views~Method~variable~type,value.var = 'value')
 
@@
 
-periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat)][,sr:=ann.ret/ann.sd]
-
-periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat')),period~Views~Method~strat~variable,value.var = 'value')
+periods <- rbind(final.bl[,data.table(rollapplyr(port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method,type)][,strat:='yes'],final.bl[,data.table(rollapplyr(ns.port.ret,20,roll.ret.f,by=4,partial=F)),by=.(Views,Method,type)][,strat:='no'],final.bl[,data.table(roll.ret.f(port.ret)),by=.(Views,Method,type)][,strat:='yes'],final.bl[,data.table(roll.ret.f(ns.port.ret)),by=.(Views,Method,type)][,strat:='no'])[,period:=periods.id,by=.(Views,Method,strat,type)][,sr:=ann.ret/ann.sd]
+
+periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
 

### 2015-03-17 lib/aux.functions.R

@@ -96,12 +96,12 @@ summary.mean.stat <- function(dt,value){
 cont.tab.f <- function(dt,t,n.b)
 {
         
-        rank.split <- na.omit(dt)[,valid.b:=.N>n.b,by=.(q.id,Stock)][(valid.b)][,valid:=.N>4,by=.(Broker,Stock)][(valid)][,next.per:=terciles.rank.f(true,n),by=list(q.id,Stock)][,next.q:=c(rep(NA,t),as.numeric(diff(q.id,t))==t/4),by=.(Broker,Stock)][,cur.per:=c(rep(NA,t),head(next.per,-t)),by=list(Broker,Stock)][,cur.per:=ifelse(is.na(cur.per),NA,ifelse(next.q==TRUE,cur.per,NA))]
+        rank.split <- na.omit(dt)[,valid.b:=.N>n.b,by=.(q.id,Stock)][(valid.b)][,valid:=.N>4,by=.(Broker,Stock,type)][(valid)][,next.per:=terciles.rank.f(true,n),by=list(q.id,Stock,type)][,next.q:=c(rep(NA,t),as.numeric(diff(q.id,t))==t/4),by=.(Broker,Stock,type)][,cur.per:=c(rep(NA,t),head(next.per,-t)),by=list(Broker,Stock,type)][,cur.per:=ifelse(is.na(cur.per),NA,ifelse(next.q==TRUE,cur.per,NA))]
         
         require(descr)
-        pt.cont.dt <- na.omit(rank.split)[,valid.s:=.N>n,by=.(Stock)][(valid.s)][,as.data.table(crosstab(cur.per,next.per,prop.r=T,prop.c=F,prop.t=F,prop.chisq = F,plot=F,missing.include=F,chisq=F)[2]),by=Stock][,value:=letters[1:9],by=Stock][,mean(prop.row),by=value]
+        pt.cont.dt <- na.omit(rank.split)[,valid.s:=.N>n,by=.(Stock)][(valid.s)][,as.data.table(crosstab(cur.per,next.per,prop.r=T,prop.c=F,prop.t=F,prop.chisq = F,plot=F,missing.include=F,chisq=F)[2]),by=.(Stock,type)][,value:=letters[1:9],by=.(Stock,type)][,mean(prop.row),by=.(value,type)]
         
-        matrix(pt.cont.dt[,V1],nrow=3,ncol=3)[c(3,2,1),c(3,2,1)]
[…]

### 2015-03-17 src/script.predict.trade.R

@@ -7,16 +7,16 @@ delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
 
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)
-system.time(source('munge/01-data.q.ret.R'))
+#system.time(source('munge/01-data.q.ret.R'))
 
 ### data for first paper
 system.time(source('src/paper.trading.APS.true.R'))
 require(ggplot2)
 colourCount = length(unique(final.bl$Views))
 getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(type~Method,scale='free_x')
 
[…]

### 2015-03-17 doc/paper/paper-knitr-APS.Rnw
working paper but only one choice for type (either 'all' or 'same')

@@
 library(xtable)
+library(abind)
 library(PerformanceAnalytics)
@@
 #options(descr.na.replacement = "noRank")
-pt.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.pt.dt,i,n.b)})
+pt.cont.tab <- abind(lapply(c(1,4),function(i) {cont.tab.f(ranked.pt.dt,i,n.b)}),along=4,new.names=list(NULL,NULL,NULL,c('t','t+4')))
 
@@
 
-eps.cont.tab <- lapply(c(1,4),function(i) {cont.tab.f(ranked.eps.dt,i,n.b)})
+eps.cont.tab <- abind(lapply(c(1,4),function(i) {cont.tab.f(ranked.eps.dt,i,n.b)}),along=4,new.names=list(NULL,NULL,NULL,c('t','t+4')))
 
@@
 
-The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
+The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
 To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[[1]][1,1]*100}\% (\Sexpr{pt.cont.tab[[1]][3,3]*100}\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[[2]][1,1]*100}\% and \Sexpr{pt.cont.tab[[2]][3,3]*100}\% for the top and bottom terciles.
-
-In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[[1]][1,1]*100}\% and  \Sexpr{eps.cont.tab[[1]][3,3]*100}\% ( \Sexpr{eps.cont.tab[[2]][1,1]*100}\% and  \Sexpr{eps.cont.tab[[2]][3,3]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles.
+
+In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{stat.nr[year=='Total'&Method=='true',mean]*100 }\%, \Sexpr{stat.nr[year=='Total'&Method=='naive',mean]*100 }\%, and \Sexpr{stat.nr[year=='Total'&Method=='default',mean]*100 }\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{stat.pt.view[year=='Total'&Method=='true',mean]*100}\%, \Sexpr{stat.pt.view[year=='Total'&Method=='naive',mean]*100}\%, and \Sexpr{stat.pt.view[year=='Total'&Method=='default',mean]*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{stat.eps.view[year=='Total'&Method=='true',mean]*100}\%, \Sexpr{stat.eps.view[year=='Total'&Method=='naive',mean]*100}\%, and \Sexpr{stat.eps.view[year=='Total'&Method=='default',mean]*100}\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean','all'][[3]]*100}\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%).
+Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%).
 
@@
 
-The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1]}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr']} over the period 1999-2001.
-The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
+The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,'all']}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr','all']} over the period 1999-2001.
+The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews','all']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO','all']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1]}\%, \Sexpr{bl.results['TP',1,1]}\%, \Sexpr{bl.results['EPS',1,1]}\%.
-All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1]}\%).
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,'all']}\%, \Sexpr{bl.results['TP',1,1,'all']}\%, \Sexpr{bl.results['EPS',1,1,'all']}\%.
+All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
 The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr']} against \Sexpr{ bl.results['CONS',1,'ann.sr']}, \Sexpr{ bl.results['EPS',1,'ann.sr']}, and \Sexpr{ bl.results['Market',1,'ann.sr']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1]}\%,  \Sexpr{bl.results['CONS',2,1]}\%, \Sexpr{bl.results['EPS',2,1]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,'all']}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,'all']}\%,  \Sexpr{bl.results['CONS',2,1,'all']}\%, \Sexpr{bl.results['EPS',2,1,'all']}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr']} and \Sexpr{bl.results['EPS',2,'ann.sr']} respectively).
+The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr','all']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr','all']} and \Sexpr{bl.results['EPS',2,'ann.sr','all']} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1]}\% and \Sexpr{bl.results['EPS',3,1]}\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,'all']}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,'all']}\% and \Sexpr{bl.results['EPS',3,1,'all']}\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 <<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,'all','t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-tab=2
-tab.r <- round(cbind(pt.cont.tab[[tab]],Total=apply(pt.cont.tab[[tab]],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,'all','t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 <<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab=1
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,'all','t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab=2
-tab.r <- round(cbind(eps.cont.tab[[tab]],Total=apply(eps.cont.tab[[tab]],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,'all','t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 <<desc-q-cons,echo=F,results='asis'>>=
-test.a[,,,1:2] <- test.a[,,,1:2]*100
+test.a[,,,1:2,'all'] <- test.a[,,,1:2,'all']*100
 dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
-print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,1],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,1],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,2],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,2],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(aperm(test.a[12,,,1:3],c(1,3,2))[,,3],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,3],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<stocks-true,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,1],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,1],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<stocks-naive,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,2],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,2],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<stocks-def,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4],c(1,3,2))[,,3],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,3],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 #p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_wrap(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
 #+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
@@
 dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results[4,1,]
+results.final <- bl.results[4,1,,'all']
 cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
@@
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,1,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,1,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,2,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,2,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,3,],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(bl.results[1:3,3,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
@@
 <<sr-true,echo=F,results='asis'>>=
-periods.array[,,,,1] <- periods.array[,,,,1]*100
+periods.array[,,,,1,'all'] <- periods.array[,,,,1,'all']*100
 #results.final <- bl.results['Market',1,]
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4)]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @

### 2015-03-17 lib/aux.functions.R

@@ -95,13 +95,14 @@ summary.mean.stat <- function(dt,value){
 }
 cont.tab.f <- function(dt,t,n.b)
 {
-        
-        rank.split <- na.omit(dt)[,valid.b:=.N>n.b,by=.(q.id,Stock)][(valid.b)][,valid:=.N>4,by=.(Broker,Stock,type)][(valid)][,next.per:=terciles.rank.f(true,n),by=list(q.id,Stock,type)][,next.q:=c(rep(NA,t),as.numeric(diff(q.id,t))==t/4),by=.(Broker,Stock,type)][,cur.per:=c(rep(NA,t),head(next.per,-t)),by=list(Broker,Stock,type)][,cur.per:=ifelse(is.na(cur.per),NA,ifelse(next.q==TRUE,cur.per,NA))]
+        abind(lapply(c('all','same'),function(a){
+        rank.split <- na.omit(dt[type==a])[,valid.b:=.N>n.b,by=.(q.id,Stock)][(valid.b)][,valid:=.N>4,by=.(Broker,Stock,type)][(valid)][,next.per:=terciles.rank.f(true,n),by=list(q.id,Stock,type)][,next.q:=c(rep(NA,t),as.numeric(diff(q.id,t))==t/4),by=.(Broker,Stock,type)][,cur.per:=c(rep(NA,t),head(next.per,-t)),by=list(Broker,Stock,type)][,cur.per:=ifelse(is.na(cur.per),NA,ifelse(next.q==TRUE,cur.per,NA))]
         
         require(descr)
         pt.cont.dt <- na.omit(rank.split)[,valid.s:=.N>n,by=.(Stock)][(valid.s)][,as.data.table(crosstab(cur.per,next.per,prop.r=T,prop.c=F,prop.t=F,prop.chisq = F,plot=F,missing.include=F,chisq=F)[2]),by=.(Stock,type)][,value:=letters[1:9],by=.(Stock,type)][,mean(prop.row),by=.(value,type)]
         
-        ddply(pt.cont.dt,'type',function(x){matrix(x[,3],nrow=3,ncol=3)[c(3,2,1),c(3,2,1)]})
+        matrix(as.matrix(pt.cont.dt[,3,with=F]),nrow=3,ncol=3)[c(3,2,1),c(3,2,1)]
+        }),along=3,new.names=list(NULL,NULL,c('all','same')))
 }
 
 data.collect<- function(data.id,n)

### 2015-03-17 doc/paper/paper-knitr-APS.Rnw
paper with table side-by-side all and same set of stocks

@@
 \usepackage{adjustbox}
+%\usepackage{floatpag}
 %\onehalfspacing
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-& Mean (in \%) & Median (in \%) &Std.dev\\
+& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same\\
 \midrule
 <<desc-q-cons,echo=F,results='asis'>>=
-test.a[,,,1:2,'all'] <- test.a[,,,1:2,'all']*100
+test.a[,,,1:2,] <- test.a[,,,1:2,]*100
 dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
-print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,1],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{4}{Y}}
+print(xtable(acast(melt(test.a[12,,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
   \midrule
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,2],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-  \end{tabularx}
-  \begin{tabularx}{\linewidth}{r*{4}{Y}}
+print(xtable(acast(melt(test.a[12,,'PT',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+  \end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<desc-q-eps,echo=F,results='asis'>>=
-#data.to.display <- c('nbr.val','mean', 'median','std.dev')
-
-#cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(aperm(test.a[12,,,1:3,'all'],c(1,3,2))[,,3],display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,,'EPS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 \ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+
+%\resizebox{\textwidth}{!}{%
+%\begin{tabular}{rrrrrrr}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
+Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
+&all&same&all&same&all&same\\
 <<stocks-true,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,1],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<stocks-naive,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,2],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+print(xtable(acast(melt(test.a[,2,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<stocks-def,echo=F,results='asis'>>=
-print(xtable(aperm(test.a[,,c(1,3,2),4,'all'],c(1,3,2))[,,3],display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,3,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 \end{table}
-
-%'   \begin{table}[hp]
-%'   \caption{Descriptive statistics of views: \tr{}}
-%'   \label{tab:view-stat}
-%'   \small\addtolength{\tabcolsep}{-2pt}
-%'   
-%' \ This table shows the descriptive (per stock per quarter) statistics of views (expected returns) for the \tr{} (\ref{q:true}) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
-%'   
-%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'     \toprule
-%' Year &Stocks& Mean & Median &Std.dev\\
-%' \midrule
-%' <<desc-nr.views,echo=F,results='asis'>>=
-%' 
-%' print(xtable(test.a[,1,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-%' @
-%'   \midrule
-%'   \end{tabularx}
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-r.views,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' #cat(rep('&',ncol(results.final)),'\\\\')
-%' print(xtable(test.a[,1,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-%' @
-%'   \end{tabularx}
-%'   
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-eps.views,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' print(xtable(test.a[,1,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-%' @
-%' \bottomrule
-%'   \end{tabularx}
-%' \end{table}
-%' 
-%' 
-%' \begin{table}[hp]
-%'   \caption{Descriptive statistics of views: \naive{}}
-%'   \label{tab:view-stat-naive}
-%'   \small\addtolength{\tabcolsep}{-2pt}
-%'   
-%' \ This table shows descriptive statistics of views (expected returns) for the \naive{} (\ref{q:naive}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-%'   
-%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'     \toprule
-%' Year &Stocks& Mean & Median &Std.dev\\
-%' \midrule
-%' <<desc-nr.views-naive,echo=F,results='asis'>>=
-%' 
-%' print(xtable(test.a[,2,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n')))
-%' @
-%'   \midrule
-%'   \end{tabularx}
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-r.views-naive,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' #cat(rep('&',ncol(results.final)),'\\\\')
-%' print(xtable(test.a[,2,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-%' @
-%'   \end{tabularx}
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-eps.views-naive,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' print(xtable(test.a[,2,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-%' @
-%' \bottomrule
-%'   \end{tabularx}
-%' \end{table}
-%' 
-%' \begin{table}[hp]
-%'   \caption{Descriptive statistics of views: \default{}}
-%'   \label{tab:view-stat-default}
-%'   \small\addtolength{\tabcolsep}{-2pt}
-%'   
-%' \ This table shows descriptive statistics of views (expected returns) for the \default{} (\ref{q:default}) based on: the consensus among the analysts (panel A), target price rankings (panel B), and EPS forecasts rankings (panel C) per stock per quarter.
-%'   
-%' \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'     \toprule
-%' Year &Stocks& Mean & Median &Std.dev\\
-%' \midrule
-%' <<desc-nr.views-default,echo=F,results='asis'>>=
-%' 
-%' print(xtable(test.a[,3,'CONS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{5}{c}{\\textbf{Panel A: Consensus views (\\ref{consq})}} \\\\','\\midrule \n','\\midrule \n')))
-%' @
-%'   \midrule
-%'   \end{tabularx}
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-r.views-default,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' #cat(rep('&',ncol(results.final)),'\\\\')
-%' print(xtable(test.a[,3,'PT',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,nrow(test.a)),command=c('\\multicolumn{5}{c}{\\textbf{Panel B: TP ranking views (\\ref{rankq})}} \\\\','\\midrule \n','\\midrule \n')))
-%' @
-%'   \end{tabularx}
-%' 
-%'   \begin{tabularx}{\linewidth}{r*{5}{Y}}
-%'   \midrule
-%' <<desc-eps.views-default,echo=F,results='asis'>>=
-%' #data.to.display <- c('nbr.val','mean', 'median','std.dev')
-%' 
-%' print(xtable(test.a[,3,'EPS',c(4,1,2,3)],display=c('s','d','f','f','f')),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{5}{c}{\\textbf{Panel C: EPS ranking views (\\ref{rankq})}} \\\\','\\midrule \n')))
-%' @
-%' \bottomrule
-%'   \end{tabularx}
-%' \end{table}
 
@@
 ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
-#+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1))
-
-#+scale_color_manual(values=getPalette(colourCount))+
-
-#+scale_x_date(breaks='year',labels=date_format('%Y'))
-
-#p.ann.ret <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw()+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3)*100),angle=90,size=3,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
-
-#p.TO <-ggplot(unique(melt(final.bl[Aggregation=='ma',list(Views,Method,meanViews,Ave.TO)],id.vars=c('Method','Views'))),aes(x=Views,y=value,fill=Views))+theme_bw()+geom_bar(stat='identity')+facet_grid(variable~Method,scale='free_y')+ggtitle('Trading statistics conditional confidence aggregation \n (averages of number of views and turnover ratio)')+theme(legend.position='none',axis.title.x=element_blank(),plot.title = element_text(colour = "Blue"),axis.title.y=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_fill_manual(values=getPalette(colourCount))
-
-#grid.arrange(p.cum.ret,p.ann.ret,rectGrob(gp=gpar(lwd=2, fill=NA)))
-#grid.draw(grobTree(arrangeGrob(p.cum.ret,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
+#
 @
@@
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=4,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
 cat('\\midrule \n')
@@
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  &all&same&all&same&all&same&all&same&all&same \\
+
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,1,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
+print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,2,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
-@
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
+print(xtable(acast(melt(bl.results[1:3,2,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+@
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(bl.results[1:3,3,,'all'],display=c('s','f','f','f','d','f'),digits=4),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,3,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=4),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @

### 2015-03-17 doc/paper/paper-knitr-APS.tex
working paper but only one choice for type (either 'all' or 'same')
paper with table side-by-side all and same set of stocks

--- 2015-03-12 doc/paper/paper-knitr-APS.tex
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-& Mean (in \%) & Median (in \%) &Std.dev\\
-\midrule
-  \multicolumn{4}{l}{\textbf{Panel A: Consensus}} \\ 
- \midrule 
-\tr{} & 18.577 & 16.861 & 0.119 \\ 
-  \naive{} & 18.615 & 16.866 & 0.120 \\ 
-  \default{} & 21.729 & 20.478 & 0.102 \\
-
-\end{tabularx}
-
-  \begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \midrule
-  \multicolumn{4}{l}{\textbf{Panel B: TP}} \\ 
- \midrule 
-\tr{} & 14.893 & 13.407 & 0.102 \\ 
-  \naive{} & 14.895 & 13.393 & 0.103 \\ 
-  \default{} & 19.394 & 18.602 & 0.088 \\
-
-  \end{tabularx}
-  \begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{l}{\textbf{Panel C: EPS}} \\ 
- \midrule 
-\tr{} & 15.719 & 14.303 & 0.098 \\ 
-  \naive{} & 15.738 & 14.304 & 0.098 \\ 
-  \default{} & 18.836 & 17.795 & 0.086 \\
+& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same\\
+\midrule
+  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
+ \midrule 
+\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
+  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
+  \default{} & 21.729 & 22.216 & 20.478 & 20.715 & 0.102 & 0.101 \\
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \midrule
+  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
+ \midrule 
+\tr{} & 15.719 & 16.071 & 14.303 & 14.525 & 0.098 & 0.098 \\ 
+  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
+  \default{} & 18.836 & 19.352 & 17.795 & 18.195 & 0.086 & 0.084 \\
+
+  \end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
+ \midrule 
+\tr{} & 14.893 & 14.964 & 13.407 & 13.449 & 0.102 & 0.103 \\ 
+  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
+  \default{} & 19.394 & 19.511 & 18.602 & 18.756 & 0.088 & 0.089 \\
 
@@
 \ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+
+%\resizebox{\textwidth}{!}{%
+%\begin{tabular}{rrrrrrr}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-Year& \textit{CONS}& \textit{TP} & \textit{EPS}\\
-  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
- \midrule 
-1999 &  219 &  219 &  144 \\ 
-  2000 &  295 &  295 &  211 \\ 
-  2001 &  341 &  341 &  257 \\ 
-  2002 &  374 &  374 &  299 \\ 
-  2003 &  390 &  390 &  311 \\ 
-  2004 &  399 &  399 &  331 \\ 
-  2005 &  414 &  414 &  343 \\ 
-  2006 &  421 &  421 &  344 \\ 
-  2007 &  426 &  426 &  357 \\ 
-  2008 &  420 &  420 &  339 \\ 
-  2009 &  365 &  365 &  300 \\ 
-   \midrule 
-Total &  442 &  442 &  376 \\
-
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
- \midrule 
-1999 &   73 &   73 &   44 \\ 
-  2000 &  257 &  257 &  185 \\ 
-  2001 &  310 &  310 &  247 \\ 
-  2002 &  362 &  362 &  288 \\ 
-  2003 &  374 &  374 &  307 \\ 
-  2004 &  385 &  385 &  318 \\ 
-  2005 &  401 &  401 &  337 \\ 
-  2006 &  415 &  415 &  343 \\ 
-  2007 &  421 &  421 &  352 \\ 
-  2008 &  422 &  422 &  349 \\ 
-  2009 &  405 &  405 &  321 \\ 
-   \midrule 
-Total &  442 &  442 &  376 \\
-
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
- \midrule 
-1999 &   73 &   73 &   54 \\ 
-  2000 &  257 &  257 &  205 \\ 
-  2001 &  314 &  314 &  264 \\ 
-  2002 &  368 &  368 &  308 \\ 
-  2003 &  383 &  383 &  326 \\ 
-  2004 &  396 &  396 &  339 \\ 
-  2005 &  414 &  414 &  357 \\ 
-  2006 &  429 &  429 &  365 \\ 
-  2007 &  438 &  438 &  371 \\ 
-  2008 &  440 &  440 &  375 \\ 
-  2009 &  442 &  442 &  378 \\ 
-   \midrule 
-Total &  442 &  442 &  378 \\
+Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
+&all&same&all&same&all&same\\
+  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
+ \midrule 
+1999 &  219 &  202 &  219 &  202 &  144 &  145 \\ 
+  2000 &  295 &  269 &  295 &  269 &  211 &  211 \\ 
+  2001 &  341 &  306 &  341 &  306 &  257 &  257 \\ 
+  2002 &  374 &  333 &  374 &  333 &  299 &  299 \\ 
+  2003 &  390 &  346 &  390 &  346 &  311 &  311 \\ 
+  2004 &  399 &  351 &  399 &  351 &  331 &  331 \\ 
+  2005 &  414 &  358 &  414 &  358 &  343 &  343 \\ 
+  2006 &  421 &  360 &  421 &  360 &  344 &  344 \\ 
+  2007 &  426 &  364 &  426 &  364 &  357 &  357 \\ 
+  2008 &  420 &  360 &  420 &  360 &  339 &  339 \\ 
+  2009 &  365 &  323 &  365 &  323 &  300 &  300 \\ 
+   \midrule 
+Total &  442 &  378 &  442 &  378 &  376 &  376 \\
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
+ \midrule 
+1999 &   73 &   69 &   73 &   69 &   44 &   44 \\ 
+  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
+  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
+  2002 &  362 &  323 &  362 &  323 &  288 &  288 \\ 
+  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
+  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
+  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
+  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
+  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
+  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
+  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
+   \midrule 
+Total &  442 &  378 &  442 &  378 &  376 &  376 \\
+
+\end{tabularx}
+
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
+ \midrule 
+1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
+  2000 &  257 &  235 &  257 &  235 &  205 &  205 \\ 
+  2001 &  314 &  284 &  314 &  284 &  264 &  264 \\ 
+  2002 &  368 &  327 &  368 &  327 &  308 &  308 \\ 
+  2003 &  383 &  341 &  383 &  341 &  326 &  326 \\ 
+  2004 &  396 &  350 &  396 &  350 &  339 &  339 \\ 
+  2005 &  414 &  364 &  414 &  364 &  357 &  357 \\ 
+  2006 &  429 &  370 &  429 &  370 &  365 &  365 \\ 
+  2007 &  438 &  374 &  438 &  374 &  371 &  371 \\ 
+  2008 &  440 &  376 &  440 &  376 &  375 &  375 \\ 
+  2009 &  442 &  378 &  442 &  378 &  378 &  378 \\ 
+   \midrule 
+Total &  442 &  378 &  442 &  378 &  378 &  378 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel B: \tr{} }} \\
- \textit{CONS} & 1.893 & 15.147 & 0.125 &  291 & 0.291 \\ 
-  \textit{TP} & 5.116 & 14.593 & 0.351 &  291 & 0.314 \\ 
-  \textit{EPS} & 1.860 & 15.172 & 0.123 &  209 & 0.503 \\ 
-   \midrule
-
-\end{tabularx}
-
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
-  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
-  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
-   \midrule
-
-\end{tabularx}
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
-  \multicolumn{5}{l}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & -0.069 & 15.817 & -0.004 &  290 & 0.188 \\ 
-  \textit{TP} & -0.005 & 15.633 & -0.000 &  290 & 0.192 \\ 
-  \textit{EPS} & 0.441 & 15.673 & 0.028 &  250 & 0.198 \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  &all&same&all&same&all&same&all&same&all&same \\
+
+ \textit{CONS} & 1.893 & 2.247 & 15.147 & 15.032 & 0.125 & 0.149 &  291 &  257 & 0.291 & 0.277 \\ 
+  \textit{TP} & 5.116 & 5.400 & 14.593 & 14.552 & 0.351 & 0.371 &  291 &  257 & 0.314 & 0.298 \\ 
+  \textit{EPS} & 1.860 & 1.957 & 15.172 & 15.145 & 0.123 & 0.129 &  209 &  209 & 0.503 & 0.501 \\ 
+   \midrule
+
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.126 & 0.449 & 15.947 & 15.993 & 0.008 & 0.028 &  284 &  252 & 0.256 & 0.250 \\ 
+  \textit{TP} & 0.281 & 0.622 & 15.661 & 15.682 & 0.018 & 0.040 &  284 &  252 & 0.264 & 0.256 \\ 
+  \textit{EPS} & -0.318 & -0.361 & 16.094 & 16.100 & -0.020 & -0.022 &  206 &  206 & 0.409 & 0.408 \\ 
+   \midrule
+
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & -0.069 & 0.413 & 15.817 & 15.873 & -0.004 & 0.026 &  290 &  257 & 0.188 & 0.185 \\ 
+  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
+  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\
 
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}

### 2015-03-18 doc/paper/paper-knitr-APS.Rnw
all time for CONS is the median instead of mean

@@
 Panel A presents the results for the passive strategy.
-Panels B,C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates .
+Panels B, C, and D show the results for the perfect foresight scenario (\tr{}), and, respectively, the scenarios for which we use the most recent  (\naive{}) and  all ranking history of analysts (\default{}) to weight the TP/EPS estimates.
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.

### 2015-03-18 doc/paper/paper-knitr-APS.tex
all time for CONS is the median instead of mean

@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.729\% respectively.
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.218\% respectively.
 Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.069}\% and 0.441\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.032}\% and 0.441\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
   \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
-  \default{} & 21.729 & 22.216 & 20.478 & 20.715 & 0.102 & 0.101 \\
+  \default{} & 21.218 & 21.729 & 19.742 & 20.014 & 0.107 & 0.106 \\
 
@@
   \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & -0.069 & 0.413 & 15.817 & 15.873 & -0.004 & 0.026 &  290 &  257 & 0.188 & 0.185 \\ 
+ \textit{CONS} & -0.032 & 0.478 & 15.827 & 15.860 & -0.002 & 0.030 &  290 &  257 & 0.189 & 0.187 \\ 
   \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.836 & 0.247 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.516 & 0.230 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.565 & 0.430 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 8.238 & 0.876 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -6.058 & -0.439 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -3.827 & -0.235 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.891 & 0.251 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.581 & 0.234 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.604 & 0.431 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 8.217 & 0.865 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -5.999 & -0.435 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -3.806 & -0.233 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
    \midrule 
-All period & -3.032 & -0.182 & -0.069 & -0.004 & -0.005 & -0.000 & 0.441 & 0.028 \\
+All period & -3.032 & -0.182 & -0.032 & -0.002 & -0.005 & -0.000 & 0.441 & 0.028 \\
 

### 2015-03-18 src/paper.trading.APS.true.R

@@ -75,7 +75,10 @@ cache('eps.rank.views')
 
 
 
-meanTper <- na.omit(melt(unique(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock,type),.SDcols=c('q.id','Broker','Stock','b.view','type')][,.(q.id,Broker,Stock,b.view,type)][,true:=truncate.f(b.view,percentile),by=type][,true:=median(true,na.rm=T),by=list(q.id,Stock,type)],by=c('q.id','Stock','type'))[,.(q.id,Stock,true,type)][,naive:=c(NA,head(true,-1)),by=.(Stock,type)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Stock,type)],id.vars = c('q.id','Stock','type'),measure.vars = c('true','naive','default'),variable.name = 'Method')[q.id!='1999 Q2',])
+meanTper <- na.omit(melt(unique(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock,type),.SDcols=c('q.id','Broker','Stock','b.view','type')][,.(q.id,Broker,Stock,b.view,type)][,true:=truncate.f(b.view,percentile),by=type][,true:=median(true,na.rm=T),by=list(q.id,Stock,type)],by=c('q.id','Stock','type'))[,.(q.id,Stock,true,type)][,naive:=c(NA,head(true,-1)),by=.(Stock,type)][,default:=rollapplyr(naive,seq_len(length(naive)),median,na.rm=T),by=.(Stock,type)],id.vars = c('q.id','Stock','type'),measure.vars = c('true','naive','default'),variable.name = 'Method')[q.id!='1999 Q2',])
+
[…]

### 2015-03-19 doc/paper/paper-knitr-APS.Rnw
add APS comment on having the recent TPER for all rankings (true,naive,default)

@@
 test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
+test.a[,'true','CONS',,] <- NA
 
@@
 
+bl.results['CONS','true',,] <- NA
+
 quarters <- unique(final.bl[,Quarters])
@@
 periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
+periods.array[,'CONS','true',,,] <- NA
 
@@
 dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
-print(xtable(acast(melt(test.a[12,,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<stocks-true,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 

### 2015-03-19 doc/paper/paper-knitr-APS.tex
add APS comment on having the recent TPER for all rankings (true,naive,default)

@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, 18.577\%, 18.615\%, and 21.218\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (15.719\%, 15.738\%, and 18.836\%).
-Panel C shows the EPS based weighted expected returns averages (14.893\%, 14.895\%, and 19.394\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.615\%, and 18.615\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%).
+Panel C shows the EPS based weighted expected returns averages (14.696\%, 14.895\%, and 12.857\%).
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, 1.893\%, 5.116\%, 1.86\%.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.288\%, 0.565\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.351 against 0.125, 0.123, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.292 against NA, 0.036, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\ensuremath{-0.005}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\ensuremath{-0.032}\% and 0.441\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.681\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.323\% and 0.738\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
  \midrule 
-\tr{} & 18.577 & 18.947 & 16.861 & 17.156 & 0.119 & 0.119 \\ 
+\tr{} & - & - & - & - & - & - \\ 
   \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
-  \default{} & 21.218 & 21.729 & 19.742 & 20.014 & 0.107 & 0.106 \\
+  \default{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\
 
@@
  \midrule 
-\tr{} & 15.719 & 16.071 & 14.303 & 14.525 & 0.098 & 0.098 \\ 
+\tr{} & 14.876 & 15.191 & 13.369 & 13.595 & 0.096 & 0.096 \\ 
   \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
-  \default{} & 18.836 & 19.352 & 17.795 & 18.195 & 0.086 & 0.084 \\
+  \default{} & 12.461 & 12.718 & 10.588 & 10.789 & 0.088 & 0.089 \\
 
@@
  \midrule 
-\tr{} & 14.893 & 14.964 & 13.407 & 13.449 & 0.102 & 0.103 \\ 
+\tr{} & 14.696 & 14.774 & 13.233 & 13.269 & 0.101 & 0.102 \\ 
   \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
-  \default{} & 19.394 & 19.511 & 18.602 & 18.756 & 0.088 & 0.089 \\
+  \default{} & 12.857 & 12.928 & 11.410 & 11.440 & 0.089 & 0.089 \\
 
@@
  \midrule 
-1999 &  219 &  202 &  219 &  202 &  144 &  145 \\ 
-  2000 &  295 &  269 &  295 &  269 &  211 &  211 \\ 
-  2001 &  341 &  306 &  341 &  306 &  257 &  257 \\ 
-  2002 &  374 &  333 &  374 &  333 &  299 &  299 \\ 
-  2003 &  390 &  346 &  390 &  346 &  311 &  311 \\ 
-  2004 &  399 &  351 &  399 &  351 &  331 &  331 \\ 
-  2005 &  414 &  358 &  414 &  358 &  343 &  343 \\ 
-  2006 &  421 &  360 &  421 &  360 &  344 &  344 \\ 
-  2007 &  426 &  364 &  426 &  364 &  357 &  357 \\ 
-  2008 &  420 &  360 &  420 &  360 &  339 &  339 \\ 
-  2009 &  365 &  323 &  365 &  323 &  300 &  300 \\ 
+1999 & - & - &   73 &   69 &   44 &   44 \\ 
+  2000 & - & - &  253 &  232 &  191 &  191 \\ 
+  2001 & - & - &  302 &  273 &  244 &  244 \\ 
+  2002 & - & - &  354 &  317 &  290 &  290 \\ 
+  2003 & - & - &  369 &  330 &  299 &  299 \\ 
+  2004 & - & - &  375 &  331 &  318 &  318 \\ 
+  2005 & - & - &  395 &  347 &  337 &  337 \\ 
+  2006 & - & - &  403 &  351 &  337 &  337 \\ 
+  2007 & - & - &  418 &  359 &  351 &  351 \\ 
+  2008 & - & - &  414 &  354 &  339 &  339 \\ 
+  2009 & - & - &  346 &  306 &  306 &  306 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  376 &  376 \\
+Total & - & - &  442 &  378 &  375 &  375 \\
 
@@
 1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
-  2000 &  257 &  235 &  257 &  235 &  205 &  205 \\ 
-  2001 &  314 &  284 &  314 &  284 &  264 &  264 \\ 
-  2002 &  368 &  327 &  368 &  327 &  308 &  308 \\ 
-  2003 &  383 &  341 &  383 &  341 &  326 &  326 \\ 
-  2004 &  396 &  350 &  396 &  350 &  339 &  339 \\ 
-  2005 &  414 &  364 &  414 &  364 &  357 &  357 \\ 
-  2006 &  429 &  370 &  429 &  370 &  365 &  365 \\ 
-  2007 &  438 &  374 &  438 &  374 &  371 &  371 \\ 
-  2008 &  440 &  376 &  440 &  376 &  375 &  375 \\ 
-  2009 &  442 &  378 &  442 &  378 &  378 &  378 \\ 
+  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
+  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
+  2002 &  362 &  323 &  362 &  323 &  304 &  304 \\ 
+  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
+  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
+  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
+  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
+  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
+  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
+  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  378 &  378 \\
+Total &  442 &  378 &  442 &  378 &  377 &  377 \\
 
@@
 
- \textit{CONS} & 1.893 & 2.247 & 15.147 & 15.032 & 0.125 & 0.149 &  291 &  257 & 0.291 & 0.277 \\ 
-  \textit{TP} & 5.116 & 5.400 & 14.593 & 14.552 & 0.351 & 0.371 &  291 &  257 & 0.314 & 0.298 \\ 
-  \textit{EPS} & 1.860 & 1.957 & 15.172 & 15.145 & 0.123 & 0.129 &  209 &  209 & 0.503 & 0.501 \\ 
+ \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
+  \textit{TP} & 4.288 & 4.512 & 14.695 & 14.792 & 0.292 & 0.305 &  284 &  251 & 0.344 & 0.326 \\ 
+  \textit{EPS} & 0.565 & 0.718 & 15.541 & 15.509 & 0.036 & 0.046 &  205 &  205 & 0.495 & 0.493 \\ 
    \midrule
@@
   \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & -0.032 & 0.478 & 15.827 & 15.860 & -0.002 & 0.030 &  290 &  257 & 0.189 & 0.187 \\ 
-  \textit{TP} & -0.005 & 0.441 & 15.633 & 15.658 & -0.000 & 0.028 &  290 &  257 & 0.192 & 0.189 \\ 
-  \textit{EPS} & 0.441 & 0.441 & 15.673 & 15.702 & 0.028 & 0.028 &  250 &  250 & 0.198 & 0.198 \\
+ \textit{CONS} & 0.323 & 0.702 & 15.771 & 15.820 & 0.020 & 0.044 &  284 &  252 & 0.228 & 0.223 \\ 
+  \textit{TP} & 0.681 & 1.043 & 15.553 & 15.476 & 0.044 & 0.067 &  284 &  252 & 0.256 & 0.248 \\ 
+  \textit{EPS} & 0.738 & 0.711 & 15.446 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.255 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 4.476 & 0.287 & 6.780 & 0.447 & 3.577 & 0.232 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.948 & 0.261 & 6.937 & 0.477 & 4.558 & 0.311 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 6.201 & 0.485 & 9.785 & 0.794 & 6.455 & 0.540 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 10.432 & 1.201 & 14.850 & 1.844 & 10.713 & 1.299 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -2.931 & -0.233 & 1.676 & 0.136 & -2.132 & -0.173 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -0.627 & -0.042 & 3.477 & 0.242 & 0.171 & 0.011 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.783 & 0.391 & 1.855 & 0.121 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.081 & 0.422 & 3.861 & 0.263 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.116 & 0.757 & 5.872 & 0.490 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.705 & 1.913 & 10.700 & 1.367 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.905 & 0.069 & -3.106 & -0.231 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.814 & 0.188 & -0.709 & -0.044 \\ 
    \midrule 
-All period & -3.032 & -0.182 & 1.893 & 0.125 & 5.116 & 0.351 & 1.860 & 0.123 \\
+All period & -3.032 & -0.182 & - & - & 4.288 & 0.292 & 0.565 & 0.036 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.891 & 0.251 & 3.537 & 0.233 & 4.177 & 0.276 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.581 & 0.234 & 3.738 & 0.252 & 4.232 & 0.283 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.604 & 0.431 & 5.863 & 0.469 & 5.969 & 0.490 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 8.217 & 0.865 & 8.554 & 0.962 & 8.572 & 0.970 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -5.999 & -0.435 & -5.690 & -0.415 & -5.561 & -0.403 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -3.806 & -0.233 & -3.427 & -0.210 & -3.161 & -0.193 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.128 & 0.199 & 3.127 & 0.204 & 3.501 & 0.232 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.040 & 0.196 & 3.725 & 0.249 & 3.917 & 0.261 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.417 & 0.418 & 5.794 & 0.464 & 5.711 & 0.468 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.069 & 10.329 & 1.244 & 9.981 & 1.198 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.873 & -0.359 & -3.945 & -0.289 & -4.237 & -0.310 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.405 & -0.149 & -1.708 & -0.106 & -1.951 & -0.122 \\ 
    \midrule 
-All period & -3.032 & -0.182 & -0.032 & -0.002 & -0.005 & -0.000 & 0.441 & 0.028 \\
+All period & -3.032 & -0.182 & 0.323 & 0.020 & 0.681 & 0.044 & 0.738 & 0.048 \\
 

### 2015-03-19 src/paper.trading.APS.true.R

@@ -15,7 +15,7 @@ core.dt.tmp <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,t
 core.dt <- rbind(core.dt.tmp[stocks][,type:='same'],core.dt.tmp[stocks.m][,type:='all'])
 
 
-pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock,type),.SDcols=c('q.id','Broker','Stock','b.view','type')][,.(q.id,Broker,Stock,b.view,type)][,true:=truncate.f(b.view,percentile),by=type][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock,type)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T),by=.(Broker,Stock,type)],id.vars = c('q.id','Stock','Broker','type'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method,type)
+pt.exp.ret <- setkey(melt(core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock,type),.SDcols=c('q.id','Broker','Stock','b.view','type')][,.(q.id,Broker,Stock,b.view,type)][,true:=truncate.f(b.view,percentile),by=type][,naive:=c(NA,head(true,-1)),by=.(Broker,Stock,type)][,':='(true=naive,default=naive),by=.(Broker,Stock,type)],id.vars = c('q.id','Stock','Broker','type'),measure.vars = c('true','naive','default'),value.name = 'exp.ret',variable.name = 'Method'),q.id,Stock,Broker,Method,type)
 
 ### Need ranked dt for contigency analysis
 ranked.pt.dt <- core.dt[,merge(setkey(quarters,q.id),.SD,all=T),by=list(Broker,Stock,type),.SDcols=c('q.id','Broker','Stock','true','type')][,.(q.id,Broker,Stock,true,type)]
@@ -75,13 +75,7 @@ cache('eps.rank.views')
 
 
 
[…]

### 2015-03-25 doc/paper/paper-knitr-APS.Rnw
Tabels show one type of stocks: all or same

--- 2015-03-18 doc/paper/paper-knitr-APS.Rnw
@@
 periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
+
+sel.s <- 'same'
+
+test.a[,'true','CONS',,] <- NA
+bl.results['CONS','true',,] <- NA
+periods.array[,'CONS','true',,,] <- NA
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean','all'][[3]]*100}\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean',sel.s][[3]]*100}\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean',sel.s][[3]]*100}\%).
+Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean',sel.s][[3]]*100}\%).
 
@@
 
-The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,'all']}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr','all']} over the period 1999-2001.
-The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews','all']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO','all']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
+The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,sel.s]}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr',sel.s]} over the period 1999-2001.
+The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews',sel.s]} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO',sel.s]}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,'all']}\%, \Sexpr{bl.results['TP',1,1,'all']}\%, \Sexpr{bl.results['EPS',1,1,'all']}\%.
-All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,sel.s]}\%, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
+All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,sel.s]}\%).
 The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['CONS',1,'ann.sr',sel.s]}, \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]}, and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,'all']}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,'all']}\%,  \Sexpr{bl.results['CONS',2,1,'all']}\%, \Sexpr{bl.results['EPS',2,1,'all']}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,sel.s]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,sel.s]}\%,  \Sexpr{bl.results['CONS',2,1,sel.s]}\%, \Sexpr{bl.results['EPS',2,1,sel.s]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr','all']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr','all']} and \Sexpr{bl.results['EPS',2,'ann.sr','all']} respectively).
+The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr',sel.s]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr',sel.s]} and \Sexpr{bl.results['EPS',2,'ann.sr',sel.s]} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,'all']}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,'all']}\% and \Sexpr{bl.results['EPS',3,1,'all']}\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,sel.s]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,sel.s]}\% and \Sexpr{bl.results['EPS',3,1,sel.s]}\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 <<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(pt.cont.tab[,,'all','t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-tab.r <- round(cbind(pt.cont.tab[,,'all','t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 <<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(eps.cont.tab[,,'all','t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab.r <- round(cbind(eps.cont.tab[,,'all','t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
-&all&same&all&same&all&same\\
+& Mean (in \%)&Median (in \%)&Std.dev\\
+%&all&same&all&same&all&same\\
 \midrule
 <<desc-q-cons,echo=F,results='asis'>>=
-test.a[,,,1:2,] <- test.a[,,,1:2,]*100
+test.a[,,,1:2,sel.s] <- test.a[,,,1:2,sel.s]*100
 dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
-print(xtable(acast(melt(test.a[12,,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
   \midrule
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(acast(melt(test.a[12,,'PT',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,,'PT',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 <<desc-q-eps,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[12,,'EPS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,,'EPS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 %\begin{tabular}{rrrrrrr}
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
-&all&same&all&same&all&same\\
+Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
+%&all&same&all&same&all&same\\
 <<stocks-true,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,1,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 <<stocks-naive,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,2,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,2,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 <<stocks-def,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,3,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,3,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 #p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+ggplot(final.bl[type==sel.s],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
 #
@@
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
   \toprule
@@
 dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results[4,1,,'all']
+results.final <- bl.results[4,1,,sel.s]
 cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{6}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
 cat('\\midrule \n')
@@
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
-  &all&same&all&same&all&same&all&same&all&same \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\
 
   <<bl-nr,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,1,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,NA.string='-',include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,sel.s])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,2,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,2,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,sel.s])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,3,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,3,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
 \bottomrule
-\end{tabular}}
+\end{tabularx}
 \end{table}
@@
 <<sr-true,echo=F,results='asis'>>=
-periods.array[,,,,1,'all'] <- periods.array[,,,,1,'all']*100
+periods.array[,,,,1,sel.s] <- periods.array[,,,,1,sel.s]*100
 #results.final <- bl.results['Market',1,]
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @

### 2015-03-25 doc/paper/paper-knitr-APS.tex

@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.615\%, and 18.615\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%).
-Panel C shows the EPS based weighted expected returns averages (14.696\%, 14.895\%, and 12.857\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.993\%, and 18.993\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (15.191\%, 16.098\%, and 12.718\%).
+Panel C shows the EPS based weighted expected returns averages (14.774\%, 14.967\%, and 12.928\%).
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.288\%, 0.565\%.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.512\%, 0.718\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.292 against NA, 0.036, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.305 against NA, 0.046, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
+The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.681\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.323\% and 0.738\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (1.043\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.702\% and 0.711\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 
- &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
-  &$middle$ & 30.7 & 47.6 & 21.7 & 100.0 \\ 
-  &$bottom$ & 13.6 & 17.0 & 69.4 & 100.0 \\ 
+ &$top$ & 67.7 & 22.1 & 10.2 & 100.0 \\ 
+  &$middle$ & 29.9 & 48.2 & 21.9 & 100.0 \\ 
+  &$bottom$ & 13.4 & 17.1 & 69.6 & 100.0 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.4 & 27.7 & 25.9 & 100.0 \\ 
-  &$middle$ & 39.1 & 29.1 & 31.8 & 100.0 \\ 
-  &$bottom$ & 32.7 & 26.7 & 40.7 & 100.0 \\
+&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
+  &$middle$ & 39.2 & 29.2 & 31.6 & 100.0 \\ 
+  &$bottom$ & 32.1 & 26.7 & 41.2 & 100.0 \\
 
@@
  &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
-  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
-  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
+  &$middle$ & 48.2 & 26.2 & 25.8 & 100.4 \\ 
+  &$bottom$ & 46.3 & 25.9 & 28.5 & 100.8 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
-  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
-  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\
+&$top$ & 46.8 & 28.3 & 26.0 & 101.1 \\ 
+  &$middle$ & 45.5 & 27.0 & 28.1 & 100.6 \\ 
+  &$bottom$ & 42.7 & 27.6 & 32.4 & 102.7 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
-&all&same&all&same&all&same\\
+& Mean (in \%)&Median (in \%)&Std.dev\\
+%&all&same&all&same&all&same\\
 \midrule
-  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
+  \multicolumn{4}{c}{\textbf{Panel A: Consensus}} \\ 
  \midrule 
-\tr{} & - & - & - & - & - & - \\ 
-  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
-  \default{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\
+\tr{} & - & - & - \\ 
+  \naive{} & 18.993 & 17.173 & 0.119 \\ 
+  \default{} & 18.993 & 17.173 & 0.119 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
   \midrule
-  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
+  \multicolumn{4}{c}{\textbf{Panel B: TP}} \\ 
  \midrule 
-\tr{} & 14.876 & 15.191 & 13.369 & 13.595 & 0.096 & 0.096 \\ 
-  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
-  \default{} & 12.461 & 12.718 & 10.588 & 10.789 & 0.088 & 0.089 \\
+\tr{} & 15.191 & 13.595 & 0.096 \\ 
+  \naive{} & 16.098 & 14.528 & 0.098 \\ 
+  \default{} & 12.718 & 10.789 & 0.089 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{c}{\textbf{Panel C: EPS}} \\ 
  \midrule 
-\tr{} & 14.696 & 14.774 & 13.233 & 13.269 & 0.101 & 0.102 \\ 
-  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
-  \default{} & 12.857 & 12.928 & 11.410 & 11.440 & 0.089 & 0.089 \\
+\tr{} & 14.774 & 13.269 & 0.102 \\ 
+  \naive{} & 14.967 & 13.432 & 0.103 \\ 
+  \default{} & 12.928 & 11.440 & 0.089 \\
 
@@
 %\begin{tabular}{rrrrrrr}
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
-&all&same&all&same&all&same\\
-  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
+Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
+%&all&same&all&same&all&same\\
+  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
  \midrule 
-1999 & - & - &   73 &   69 &   44 &   44 \\ 
-  2000 & - & - &  253 &  232 &  191 &  191 \\ 
-  2001 & - & - &  302 &  273 &  244 &  244 \\ 
-  2002 & - & - &  354 &  317 &  290 &  290 \\ 
-  2003 & - & - &  369 &  330 &  299 &  299 \\ 
-  2004 & - & - &  375 &  331 &  318 &  318 \\ 
-  2005 & - & - &  395 &  347 &  337 &  337 \\ 
-  2006 & - & - &  403 &  351 &  337 &  337 \\ 
-  2007 & - & - &  418 &  359 &  351 &  351 \\ 
-  2008 & - & - &  414 &  354 &  339 &  339 \\ 
-  2009 & - & - &  346 &  306 &  306 &  306 \\ 
+1999 & - &   69 &   44 \\ 
+  2000 & - &  232 &  191 \\ 
+  2001 & - &  273 &  244 \\ 
+  2002 & - &  317 &  290 \\ 
+  2003 & - &  330 &  299 \\ 
+  2004 & - &  331 &  318 \\ 
+  2005 & - &  347 &  337 \\ 
+  2006 & - &  351 &  337 \\ 
+  2007 & - &  359 &  351 \\ 
+  2008 & - &  354 &  339 \\ 
+  2009 & - &  306 &  306 \\ 
    \midrule 
-Total & - & - &  442 &  378 &  375 &  375 \\
+Total & - &  378 &  375 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
  \midrule 
-1999 &   73 &   69 &   73 &   69 &   44 &   44 \\ 
-  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
-  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
-  2002 &  362 &  323 &  362 &  323 &  288 &  288 \\ 
-  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
-  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
-  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
-  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
-  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
-  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
-  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
+1999 &   69 &   69 &   44 \\ 
+  2000 &  235 &  235 &  186 \\ 
+  2001 &  281 &  281 &  247 \\ 
+  2002 &  323 &  323 &  288 \\ 
+  2003 &  334 &  334 &  307 \\ 
+  2004 &  341 &  341 &  318 \\ 
+  2005 &  352 &  352 &  337 \\ 
+  2006 &  358 &  358 &  343 \\ 
+  2007 &  361 &  361 &  352 \\ 
+  2008 &  360 &  360 &  349 \\ 
+  2009 &  351 &  351 &  321 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  376 &  376 \\
+Total &  378 &  378 &  376 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
  \midrule 
-1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
-  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
-  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
-  2002 &  362 &  323 &  362 &  323 &  304 &  304 \\ 
-  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
-  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
-  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
-  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
-  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
-  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
-  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
+1999 &   69 &   69 &   54 \\ 
+  2000 &  235 &  235 &  204 \\ 
+  2001 &  281 &  281 &  261 \\ 
+  2002 &  323 &  323 &  304 \\ 
+  2003 &  334 &  334 &  317 \\ 
+  2004 &  341 &  341 &  332 \\ 
+  2005 &  352 &  352 &  344 \\ 
+  2006 &  358 &  358 &  353 \\ 
+  2007 &  361 &  361 &  358 \\ 
+  2008 &  360 &  360 &  359 \\ 
+  2009 &  351 &  351 &  350 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  377 &  377 \\
+Total &  378 &  378 &  377 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
   \toprule
   %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
+Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{6}{l}{\textbf{Panel A}} \\ 
 \textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
@@
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
-  &all&same&all&same&all&same&all&same&all&same \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\
 
- \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
-  \textit{TP} & 4.288 & 4.512 & 14.695 & 14.792 & 0.292 & 0.305 &  284 &  251 & 0.344 & 0.326 \\ 
-  \textit{EPS} & 0.565 & 0.718 & 15.541 & 15.509 & 0.036 & 0.046 &  205 &  205 & 0.495 & 0.493 \\ 
+ \textit{CONS} & - & - & - & - & - \\ 
+  \textit{TP} & 4.512 & 14.792 & 0.305 &  251 & 0.326 \\ 
+  \textit{EPS} & 0.718 & 15.509 & 0.046 &  205 & 0.493 \\ 
    \midrule
 
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.126 & 0.449 & 15.947 & 15.993 & 0.008 & 0.028 &  284 &  252 & 0.256 & 0.250 \\ 
-  \textit{TP} & 0.281 & 0.622 & 15.661 & 15.682 & 0.018 & 0.040 &  284 &  252 & 0.264 & 0.256 \\ 
-  \textit{EPS} & -0.318 & -0.361 & 16.094 & 16.100 & -0.020 & -0.022 &  206 &  206 & 0.409 & 0.408 \\ 
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
+  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
+  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
    \midrule
 
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & 0.323 & 0.702 & 15.771 & 15.820 & 0.020 & 0.044 &  284 &  252 & 0.228 & 0.223 \\ 
-  \textit{TP} & 0.681 & 1.043 & 15.553 & 15.476 & 0.044 & 0.067 &  284 &  252 & 0.256 & 0.248 \\ 
-  \textit{EPS} & 0.738 & 0.711 & 15.446 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.255 \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & 0.702 & 15.820 & 0.044 &  252 & 0.223 \\ 
+  \textit{TP} & 1.043 & 15.476 & 0.067 &  252 & 0.248 \\ 
+  \textit{EPS} & 0.711 & 15.481 & 0.046 &  245 & 0.255 \\
 
 \bottomrule
-\end{tabular}}
+\end{tabularx}
 \end{table}
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.783 & 0.391 & 1.855 & 0.121 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.081 & 0.422 & 3.861 & 0.263 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.116 & 0.757 & 5.872 & 0.490 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.705 & 1.913 & 10.700 & 1.367 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.905 & 0.069 & -3.106 & -0.231 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.814 & 0.188 & -0.709 & -0.044 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 6.545 & 0.447 & 2.080 & 0.137 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.185 & 0.429 & 4.076 & 0.279 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 8.985 & 0.768 & 5.822 & 0.485 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.236 & 1.889 & 10.690 & 1.365 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.399 & 0.030 & -3.083 & -0.229 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.518 & 0.165 & -0.625 & -0.039 \\ 
    \midrule 
-All period & -3.032 & -0.182 & - & - & 4.288 & 0.292 & 0.565 & 0.036 \\
+All period & -3.032 & -0.182 & - & - & 4.512 & 0.305 & 0.718 & 0.046 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 2.689 & 0.168 & 2.635 & 0.169 & 1.145 & 0.072 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 2.686 & 0.171 & 3.280 & 0.215 & 2.599 & 0.167 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.740 & 0.448 & 6.088 & 0.492 & 5.465 & 0.453 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.542 & 1.105 & 10.065 & 1.246 & 9.312 & 1.152 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.718 & -0.344 & -4.155 & -0.306 & -4.546 & -0.332 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.373 & -0.146 & -2.019 & -0.126 & -1.759 & -0.106 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
    \midrule 
-All period & -3.032 & -0.182 & 0.126 & 0.008 & 0.281 & 0.018 & -0.318 & -0.020 \\
+All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.128 & 0.199 & 3.127 & 0.204 & 3.501 & 0.232 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.040 & 0.196 & 3.725 & 0.249 & 3.917 & 0.261 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.417 & 0.418 & 5.794 & 0.464 & 5.711 & 0.468 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.069 & 10.329 & 1.244 & 9.981 & 1.198 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.873 & -0.359 & -3.945 & -0.289 & -4.237 & -0.310 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.405 & -0.149 & -1.708 & -0.106 & -1.951 & -0.122 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.934 & 0.252 & 3.833 & 0.256 & 3.470 & 0.229 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.278 & 0.211 & 4.000 & 0.270 & 3.883 & 0.259 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.464 & 0.433 & 5.907 & 0.487 & 5.686 & 0.465 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.285 & 1.066 & 10.185 & 1.252 & 9.964 & 1.195 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.979 & -0.364 & -4.093 & -0.299 & -4.251 & -0.311 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.429 & -0.149 & -1.671 & -0.103 & -1.974 & -0.122 \\ 
    \midrule 
-All period & -3.032 & -0.182 & 0.323 & 0.020 & 0.681 & 0.044 & 0.738 & 0.048 \\
+All period & -3.032 & -0.182 & 0.702 & 0.044 & 1.043 & 0.067 & 0.711 & 0.046 \\
 

### 2015-03-26 doc/paper/paper-knitr-APS.Rnw
remove mention of CONS/true from paper

@@
 %$N$ is the number of analysts with a valid TP report and
-where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+where $r_{j,i}=TP_{j,i}/P_{i}-1$  is the last known analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
 This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
@@
 \label{q:true}
-\widehat{Q_{.,t}}=Q_{.,t}
+\widehat{Q_{rank,i,t}}=Q_{rank,i,t}
 \end{equation}
-
+% 
 \item  the \naive{} set % -- $t-$ information:
@@
 \label{q:naive}
-\widehat{Q_{.,t}}=Q_{.,t-1}
+\widehat{Q_{rank,i,t}}=Q_{rank,i,t-1}
 \end{equation}
-
+% 
 \item  the \default{}  set%-- the entire history of analysts performance:
@@
 \label{q:default}
-\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
+\widehat{Q_{rank,i,t}} = \frac{1}{T-1} \sum_{t=1}^{T-1} Q_{rank,i,t}
 \end{equation}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
+where  $Q_{rank,i,.}$ is the smart estimate for stock $i$ (eq.
+\ref{rankq}).
+For the case of consensus based expected returns ($Q_{cons,i}), the \tr{} information set is not applicable as analysts have equal weights.
 
@@
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
+Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.
+The total number of stocks in our sample, thus, is \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} stocks.
+
+%The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
 
@@
 
-Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
+Table \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
 %Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean',sel.s][[3]]*100}\% respectively.
+The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean',sel.s][[3]]*100}\% respectively.
 Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean',sel.s][[3]]*100}\%).
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,sel.s]}\%, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
 All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,sel.s]}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['CONS',1,'ann.sr',sel.s]}, \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]}, and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]} and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{EPS}and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).

### 2015-03-26 src/script.predict.trade.R

@@ -7,16 +7,16 @@ delta<-1L;tau=1/50;baselines <- c('true','naive','default');confid.id <- c('cons
 ##rolling rankings: 20 qtrs - no winning; 16 qtrs - win roll.sd (last); 12
 
 ### market data: ~ 113 sec (mcapply: ~ 52 sec)
-#system.time(source('munge/01-data.q.ret.R'))
+system.time(source('munge/01-data.q.ret.R'))
 
 ### data for first paper
 system.time(source('src/paper.trading.APS.true.R'))
 require(ggplot2)
 colourCount = length(unique(final.bl$Views))
 getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(type~Method,scale='free_x')
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
 
[…]

### 2015-03-27 doc/paper/paper-knitr-APS.Rnw
change paper to blinded version (no authors)

@@
 % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
-%\pagestyle{empty}
-\pagestyle{fancy}
+\pagestyle{empty}
+%\pagestyle{fancy}
 
@@
 \title{Are rankings of financial analysts useful to investors?}
- \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
- \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
- \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-
-\affil[1]{FEP \& CEF.UP, University of Porto}
-\affil[2]{INESC TEC}
-\affil[4]{FEUP, University of Porto}
+%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
+%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
+%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+% 
+% \affil[1]{FEP \& CEF.UP, University of Porto}
+% \affil[2]{INESC TEC}
+% \affil[4]{FEUP, University of Porto}
 
@@
 % You need this here, or else the first page won't have a header.
-\thispagestyle{fancy}
+%\thispagestyle{fancy}
 
@@
 \ref{rankq}).
-For the case of consensus based expected returns ($Q_{cons,i}), the \tr{} information set is not applicable as analysts have equal weights.
+For the case of consensus based expected returns ($Q_{cons,i}$), the \tr{} information set is not applicable as analysts have equal weights.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, \Sexpr{bl.results['TP',1,1,sel.s]}\% and \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
 All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,sel.s]}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]} and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{EPS}and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]} and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively, for the \textit{EPS} and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,sel.s]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,sel.s]}\%,  \Sexpr{bl.results['CONS',2,1,sel.s]}\%, \Sexpr{bl.results['EPS',2,1,sel.s]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,sel.s]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,sel.s]}\% and  \Sexpr{bl.results['CONS',2,1,sel.s]}\% respectively.
+The active strategy based on EPS forecasts, demonstrated negative annualized cumulative return of \Sexpr{bl.results['EPS',2,1,sel.s]}\%.
+
+%Moreover, comparing the smart estimate and the consensus based strategy, observe that the former outperforms the latter confirming that rankings can identify the best analsyts
+
+The \textit{TP} strategy also dominates when we consider the risk-adjusted returns.
 The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr',sel.s]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr',sel.s]} and \Sexpr{bl.results['EPS',2,'ann.sr',sel.s]} respectively).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,sel.s]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,sel.s]}\% and \Sexpr{bl.results['EPS',3,1,sel.s]}\% respectively).
-The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Panel D of table \ref{tab:strategy} further confirms the outperformance of the \textit{TP} smart strategy: under the \default{} information set it yields the highest annualized cumulative return  of \Sexpr{bl.results['TP',3,1,sel.s]}\% comparing to the \textit{CONS} and the \textit{EPS} strategies (\Sexpr{bl.results['CONS',3,1,sel.s]}\% and \Sexpr{bl.results['EPS',3,1,sel.s]}\% respectively).
+The panel C of table \ref{tab:substrategy} shows that \textit{TP} strategy is also dominant in every sub-periods.
 
@@
 In sum the results of  feasible information sets outlined above suggest that  it is worth to follow the top analysts and are supportive of \cite{desai2000ass} in that rankings are useful for investors.
-
-%The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
-Thus, an investor is better off when following the analysts who issue more accurate target price; hence, rankings are usefull for the investors.
-
-%do identify the best analysts and this findings supports the argument of \cite{desai2000ass}.
-In addition, the results show that keeping all available information about analysts' performance does not create any value.
-As we see, the \default{} strategy is the worse in term of the annualized cumulative returns.
-
+Moreover, the results also show  that when consider the all history of  analyst' performance, investors gain the best outcomes for all active  strategies.
 Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that good at forecasting EPS.
@@
 If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts.
+This also holds if the all history of analyst's performance is considered.
 

### 2015-03-27 doc/paper/paper-knitr-APS.tex
change paper to blinded version (no authors)

@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
+where  $Q_{rank,i,.}$ is the smart estimate for stock $i$ (eq.
+\ref{rankq}).
+For the case of consensus based expected returns ($Q_{cons,i}$), the \tr{} information set is not applicable as analysts have equal weights.
 
@@
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  155 brokers covering 402 stocks.
-The total number of observation is 79 539.
+Our sample of EPS forecasts consist of  155 brokers covering 402 stocks.
+Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.
+The total number of stocks in our sample, thus, is 378 stocks.
+
+%The total number of observation is prettyNum(complete.dt[,.N],big.mar=' ').
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.993\%, and 18.993\% respectively.
+The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, 18.993\%, and 18.993\% respectively.
 Panel B of the table shows the TP accuracy weighted average expected returns (15.191\%, 16.098\%, and 12.718\%).
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.512\%, 0.718\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, 4.512\% and 0.718\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.305 against NA, 0.046, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.305 against 0.046 and \ensuremath{-0.182}, respectively, for the \textit{EPS} and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\% and  0.449\% respectively.
+The active strategy based on EPS forecasts, demonstrated negative annualized cumulative return of \ensuremath{-0.361}\%.
+
+%Moreover, comparing the smart estimate and the consensus based strategy, observe that the former outperforms the latter confirming that rankings can identify the best analsyts
+
+The \textit{TP} strategy also dominates when we consider the risk-adjusted returns.
 The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (1.043\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.702\% and 0.711\% respectively).
-The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Panel D of table \ref{tab:strategy} further confirms the outperformance of the \textit{TP} smart strategy: under the \default{} information set it yields the highest annualized cumulative return  of 1.043\% comparing to the \textit{CONS} and the \textit{EPS} strategies (0.702\% and 0.711\% respectively).
+The panel C of table \ref{tab:substrategy} shows that \textit{TP} strategy is also dominant in every sub-periods.
 

### 2015-03-30 src/script.predict.trade.R
small changes

@@ -14,9 +14,9 @@ system.time(source('src/paper.trading.APS.true.R'))
 require(ggplot2)
 colourCount = length(unique(final.bl$Views))
 getPalette = colorRampPalette(RColorBrewer::brewer.pal(colourCount, "Set1"))
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
+ggplot(final.bl[type=='same'],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views))+geom_line(size=0.5)+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw(base_family='Avenir')+theme(plot.title = element_text(colour = "Blue"),legend.position='top')+scale_color_manual(values=getPalette(colourCount))+guides(color=guide_legend(nrow=1L))+geom_hline(yintercept=100L)+facet_grid(~Method,scale='free_x')
 
-ggplot(unique(melt(final.bl[,list(Views,Method,ann.ret,ann.sd,ann.sr)],id.vars=c('Method','Views'))),aes(x=Views,y=value))+geom_bar(aes(fill=Views),stat='identity',alpha=0.7)+facet_grid(variable~Method,scale='free_y')+theme_bw(base_family='Avenir')+ggtitle('Annualized portfolio measures (return, st.dev, and the Sharpe ratio) \n conditional on confidence aggregation')+theme(plot.title = element_text(colour = "Blue"),legend.position='top',axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+scale_y_continuous(labels=percent)+ylab('Percent')+geom_text(aes(label=round(value,3L)*100L),angle=90L,size=3L,hjust=1.2)+scale_fill_manual(values=getPalette(colourCount))
[…]

### 2015-04-01 doc/paper/paper-knitr-APS.Rnw
switched to 'all' selected stocks.

@@
 % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
-\pagestyle{empty}
-%\pagestyle{fancy}
+%\pagestyle{empty}
+\pagestyle{fancy}
 
@@
 
-sel.s <- 'same'
+sel.s <- 'all'
 
@@
 \title{Are rankings of financial analysts useful to investors?}
-%  \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
-%  \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
-%  \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-% 
-% \affil[1]{FEP \& CEF.UP, University of Porto}
-% \affil[2]{INESC TEC}
-% \affil[4]{FEUP, University of Porto}
+ \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
+ \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
+ \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+
+\affil[1]{FEP \& CEF.UP, University of Porto}
+\affil[2]{INESC TEC}
+\affil[4]{FEUP, University of Porto}
 
@@
 % You need this here, or else the first page won't have a header.
-%\thispagestyle{fancy}
+\thispagestyle{fancy}
 
@@
 
-Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
+Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} S\&P500 stocks.
 Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
+We also require that a stock had at least three brokers per quarter.
+In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
+After all necessary data requirements, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(pt.rank.views[,.N],big.mark=' ')}.
 
 The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
-To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
-In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
+We apply the same data requirements as in case of TP dataset (minimum 3 brokers per stock and 12 quarters of coverage).
+Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{eps.rank.views[,.N,by=Stock][,.N]} stocks
+
 Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.
-The total number of stocks in our sample, thus, is \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} stocks.
 

### 2015-04-01 doc/paper/paper-knitr-APS.tex
switched to 'all' selected stocks.

--- 2015-03-19 doc/paper/paper-knitr-APS.tex
@@
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  155 brokers covering 402 stocks.
-The total number of observation is 79 539.
+Our sample of EPS forecasts consist of  155 brokers covering 402 stocks.
+Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.
+The total number of stocks in our sample, thus, is 442 stocks.
+
+%The total number of observation is prettyNum(complete.dt[,.N],big.mar=' ').
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.615\%, and 18.615\% respectively.
+The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, 18.615\%, and 18.615\% respectively.
 Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.738\%, and 12.461\%).
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.288\%, 0.565\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, 4.288\% and 0.565\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.292 against NA, 0.036, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.292 against 0.036 and \ensuremath{-0.182}, respectively, for the \textit{EPS} and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\%,  0.126\%, \ensuremath{-0.318}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.281\% and  0.126\% respectively.
+The active strategy based on EPS forecasts, demonstrated negative annualized cumulative return of \ensuremath{-0.318}\%.
+
+%Moreover, comparing the smart estimate and the consensus based strategy, observe that the former outperforms the latter confirming that rankings can identify the best analsyts
+
+The \textit{TP} strategy also dominates when we consider the risk-adjusted returns.
 The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.008 and \ensuremath{-0.02} respectively).
@@
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.681\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.323\% and 0.738\% respectively).
-The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Panel D of table \ref{tab:strategy} further confirms the outperformance of the \textit{TP} smart strategy: under the \default{} information set it yields the highest annualized cumulative return  of 0.681\% comparing to the \textit{CONS} and the \textit{EPS} strategies (0.323\% and 0.738\% respectively).
+The panel C of table \ref{tab:substrategy} shows that \textit{TP} strategy is also dominant in every sub-periods.
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
-&all&same&all&same&all&same\\
+& Mean (in \%)&Median (in \%)&Std.dev\\
+%&all&same&all&same&all&same\\
 \midrule
-  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
+  \multicolumn{4}{c}{\textbf{Panel A: Consensus}} \\ 
  \midrule 
-\tr{} & - & - & - & - & - & - \\ 
-  \naive{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\ 
-  \default{} & 18.615 & 18.993 & 16.866 & 17.173 & 0.120 & 0.119 \\
+\tr{} & - & - & - \\ 
+  \naive{} & 18.615 & 16.866 & 0.120 \\ 
+  \default{} & 18.615 & 16.866 & 0.120 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
   \midrule
-  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
+  \multicolumn{4}{c}{\textbf{Panel B: TP}} \\ 
  \midrule 
-\tr{} & 14.876 & 15.191 & 13.369 & 13.595 & 0.096 & 0.096 \\ 
-  \naive{} & 15.738 & 16.098 & 14.304 & 14.528 & 0.098 & 0.098 \\ 
-  \default{} & 12.461 & 12.718 & 10.588 & 10.789 & 0.088 & 0.089 \\
+\tr{} & 14.876 & 13.369 & 0.096 \\ 
+  \naive{} & 15.738 & 14.304 & 0.098 \\ 
+  \default{} & 12.461 & 10.588 & 0.088 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{c}{\textbf{Panel C: EPS}} \\ 
  \midrule 
-\tr{} & 14.696 & 14.774 & 13.233 & 13.269 & 0.101 & 0.102 \\ 
-  \naive{} & 14.895 & 14.967 & 13.393 & 13.432 & 0.103 & 0.103 \\ 
-  \default{} & 12.857 & 12.928 & 11.410 & 11.440 & 0.089 & 0.089 \\
+\tr{} & 14.696 & 13.233 & 0.101 \\ 
+  \naive{} & 14.895 & 13.393 & 0.103 \\ 
+  \default{} & 12.857 & 11.410 & 0.089 \\
 
@@
 %\begin{tabular}{rrrrrrr}
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
 \toprule
-Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
-&all&same&all&same&all&same\\
-  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
+Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
+%&all&same&all&same&all&same\\
+  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
  \midrule 
-1999 & - & - &   73 &   69 &   44 &   44 \\ 
-  2000 & - & - &  253 &  232 &  191 &  191 \\ 
-  2001 & - & - &  302 &  273 &  244 &  244 \\ 
-  2002 & - & - &  354 &  317 &  290 &  290 \\ 
-  2003 & - & - &  369 &  330 &  299 &  299 \\ 
-  2004 & - & - &  375 &  331 &  318 &  318 \\ 
-  2005 & - & - &  395 &  347 &  337 &  337 \\ 
-  2006 & - & - &  403 &  351 &  337 &  337 \\ 
-  2007 & - & - &  418 &  359 &  351 &  351 \\ 
-  2008 & - & - &  414 &  354 &  339 &  339 \\ 
-  2009 & - & - &  346 &  306 &  306 &  306 \\ 
+1999 & - &   73 &   44 \\ 
+  2000 & - &  253 &  191 \\ 
+  2001 & - &  302 &  244 \\ 
+  2002 & - &  354 &  290 \\ 
+  2003 & - &  369 &  299 \\ 
+  2004 & - &  375 &  318 \\ 
+  2005 & - &  395 &  337 \\ 
+  2006 & - &  403 &  337 \\ 
+  2007 & - &  418 &  351 \\ 
+  2008 & - &  414 &  339 \\ 
+  2009 & - &  346 &  306 \\ 
    \midrule 
-Total & - & - &  442 &  378 &  375 &  375 \\
+Total & - &  442 &  375 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
  \midrule 
-1999 &   73 &   69 &   73 &   69 &   44 &   44 \\ 
-  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
-  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
-  2002 &  362 &  323 &  362 &  323 &  288 &  288 \\ 
-  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
-  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
-  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
-  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
-  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
-  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
-  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
+1999 &   73 &   73 &   44 \\ 
+  2000 &  257 &  257 &  185 \\ 
+  2001 &  310 &  310 &  247 \\ 
+  2002 &  362 &  362 &  288 \\ 
+  2003 &  374 &  374 &  307 \\ 
+  2004 &  385 &  385 &  318 \\ 
+  2005 &  401 &  401 &  337 \\ 
+  2006 &  415 &  415 &  343 \\ 
+  2007 &  421 &  421 &  352 \\ 
+  2008 &  422 &  422 &  349 \\ 
+  2009 &  405 &  405 &  321 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  376 &  376 \\
+Total &  442 &  442 &  376 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{7}{Y}}
-  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{4}{Y}}
+  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
  \midrule 
-1999 &   73 &   69 &   73 &   69 &   54 &   54 \\ 
-  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
-  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
-  2002 &  362 &  323 &  362 &  323 &  304 &  304 \\ 
-  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
-  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
-  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
-  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
-  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
-  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
-  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
+1999 &   73 &   73 &   54 \\ 
+  2000 &  257 &  257 &  204 \\ 
+  2001 &  310 &  310 &  261 \\ 
+  2002 &  362 &  362 &  304 \\ 
+  2003 &  374 &  374 &  317 \\ 
+  2004 &  385 &  385 &  332 \\ 
+  2005 &  401 &  401 &  344 \\ 
+  2006 &  415 &  415 &  353 \\ 
+  2007 &  421 &  421 &  358 \\ 
+  2008 &  422 &  422 &  359 \\ 
+  2009 &  405 &  405 &  350 \\ 
    \midrule 
-Total &  442 &  378 &  442 &  378 &  377 &  377 \\
+Total &  442 &  442 &  377 \\
 
@@
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
-  &all&same&all&same&all&same&all&same&all&same \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\
 
- \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
-  \textit{TP} & 4.288 & 4.512 & 14.695 & 14.792 & 0.292 & 0.305 &  284 &  251 & 0.344 & 0.326 \\ 
-  \textit{EPS} & 0.565 & 0.718 & 15.541 & 15.509 & 0.036 & 0.046 &  205 &  205 & 0.495 & 0.493 \\ 
+ \textit{CONS} & - & - & - & - & - \\ 
+  \textit{TP} & 4.288 & 14.695 & 0.292 &  284 & 0.344 \\ 
+  \textit{EPS} & 0.565 & 15.541 & 0.036 &  205 & 0.495 \\ 
    \midrule
 
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.126 & 0.449 & 15.947 & 15.993 & 0.008 & 0.028 &  284 &  252 & 0.256 & 0.250 \\ 
-  \textit{TP} & 0.281 & 0.622 & 15.661 & 15.682 & 0.018 & 0.040 &  284 &  252 & 0.264 & 0.256 \\ 
-  \textit{EPS} & -0.318 & -0.361 & 16.094 & 16.100 & -0.020 & -0.022 &  206 &  206 & 0.409 & 0.408 \\ 
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.126 & 15.947 & 0.008 &  284 & 0.256 \\ 
+  \textit{TP} & 0.281 & 15.661 & 0.018 &  284 & 0.264 \\ 
+  \textit{EPS} & -0.318 & 16.094 & -0.020 &  206 & 0.409 \\ 
    \midrule
 
-\end{tabular}}
+\end{tabularx}
 
-\resizebox{\textwidth}{!}{%
-\begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & 0.323 & 0.702 & 15.771 & 15.820 & 0.020 & 0.044 &  284 &  252 & 0.228 & 0.223 \\ 
-  \textit{TP} & 0.681 & 1.043 & 15.553 & 15.476 & 0.044 & 0.067 &  284 &  252 & 0.256 & 0.248 \\ 
-  \textit{EPS} & 0.738 & 0.711 & 15.446 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.255 \\
+\begin{tabularx}{\linewidth}{r*{6}{Y}}
+  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & 0.323 & 15.771 & 0.020 &  284 & 0.228 \\ 
+  \textit{TP} & 0.681 & 15.553 & 0.044 &  284 & 0.256 \\ 
+  \textit{EPS} & 0.738 & 15.446 & 0.048 &  245 & 0.256 \\
 
 \bottomrule
-\end{tabular}}
+\end{tabularx}
 \end{table}

### 2015-04-01 src/script.predict.trade.R

@@ -27,5 +27,15 @@ setwd('~/Dropbox/workspace/Projects/BL-strategies/')
 ggplot(unique(final.bl[Views!='Market'&type=='same'],by=c('Quarters','n.views','Method','Views')),aes(x=as.Date(Quarters),y=n.views,group=Method,color=Method))+geom_point()+geom_line()+facet_grid(Views~.,scale='free_x')+theme_bw()
 
 
+# 
+# con <- file("E: \\sales.txt", "r")
+# result=read.table(con,nrows=100000,sep="\t",header=TRUE)
+# result<-aggregate(result[,4],list(result[,2]),sum)
+# while(nrow(databatch<-read.table(con,header=FALSE,nrows=100000,sep="\t",col.names=c("ORDERID","Group.1","SELLERID","x","ORDERDATE")))!=0) {
+#         databatch<-databatch[,c(2,4)]
+#         result<-rbind(result,databatch)
+#         result<-aggregate(result[,2],list(result[,1]),sum)
+# }
+# close(con)
 
 

### 2015-04-01 doc/paper/paper-knitr-APS.Rnw
Include both sets in the paper

--- 2015-03-26 doc/paper/paper-knitr-APS.Rnw
@@
 load('cache/q.data.RData')
+load('cache/core.dt.RData')
 load('cache/final.bl.RData')
@@
 
-core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
+#core.dt <- na.omit(q.data)[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,rank:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)]
 
+#core.dt <- core.dt[,year:=format(q.id,'%Y')]
 #pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
@@
 
-brok.full.stat.pt <- rbind(setkey(na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(core.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
+brok.full.stat.pt <- rbind(setkey(core.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=.(year,type)],year),setnames(cbind('Total',(core.dt)[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=type]),1,'year'))
 
@@
 periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
-
-sel.s <- 'same'
-
-test.a[,'true','CONS',,] <- NA
-bl.results['CONS','true',,] <- NA
 periods.array[,'CONS','true',,,] <- NA
@@
 %$N$ is the number of analysts with a valid TP report and
-where $r_{j,i}=TP_{j,i}/P_{i}-1$  is the last known analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
 This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
@@
 \label{q:true}
-\widehat{Q_{rank,i,t}}=Q_{rank,i,t}
+\widehat{Q_{.,t}}=Q_{.,t}
 \end{equation}
-% 
+
 \item  the \naive{} set % -- $t-$ information:
@@
 \label{q:naive}
-\widehat{Q_{rank,i,t}}=Q_{rank,i,t-1}
+\widehat{Q_{.,t}}=Q_{.,t-1}
 \end{equation}
-% 
+
 \item  the \default{}  set%-- the entire history of analysts performance:
@@
 \label{q:default}
-\widehat{Q_{rank,i,t}} = \frac{1}{T-1} \sum_{t=1}^{T-1} Q_{rank,i,t}
+\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
 \end{equation}
@@
 \end{itemize}
-where  $Q_{rank,i,.}$ is the smart estimate for stock $i$ (eq.
-\ref{rankq}).
-For the case of consensus based expected returns ($Q_{cons,i}), the \tr{} information set is not applicable as analysts have equal weights.
+where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
 
@@
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-Finally, we consider stocks that have both EPS and TP forecasts in a given quarter.
-The total number of stocks in our sample, thus, is \Sexpr{pt.rank.views[,.N,by=.(type,Stock)][type==sel.s,.N,by=type][,N]} stocks.
-
-%The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
+The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
 
@@
 
-Table \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
+Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
 %Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean',sel.s][[3]]*100}\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean',sel.s][[3]]*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean',sel.s][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean',sel.s][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean',sel.s][[3]]*100}\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean','all'][[3]]*100}\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%).
+Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%).
 
@@
 
-The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,sel.s]}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr',sel.s]} over the period 1999-2001.
-The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews',sel.s]} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO',sel.s]}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
+The passive strategy generates an annualized cumulative return of \Sexpr{bl.results['Market',1,1,'all']}\% with a Sharpe Ratio  of \Sexpr{bl.results['Market',1,'ann.sr','all']} over the period 1999-2001.
+The average number of stocks held per quarter was \Sexpr{bl.results['Market',1,'meanViews','all']} and the turnover ratio was \Sexpr{bl.results['Market',1,'Ave.TO','all']}, which reflects solely the inclusion and deletions  of the S\&P 500 constituent list.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['TP',1,1,sel.s]}\%, \Sexpr{bl.results['EPS',1,1,sel.s]}\%.
-All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,sel.s]}\%).
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,'all']}\%, \Sexpr{bl.results['TP',1,1,'all']}\%, \Sexpr{bl.results['EPS',1,1,'all']}\%.
+All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
 The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr',sel.s]} against \Sexpr{ bl.results['EPS',1,'ann.sr',sel.s]} and \Sexpr{ bl.results['Market',1,'ann.sr',sel.s]}, respectively for the \textit{EPS}and the \textit{Market} strategies.
+The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,sel.s]}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,sel.s]}\%,  \Sexpr{bl.results['CONS',2,1,sel.s]}\%, \Sexpr{bl.results['EPS',2,1,sel.s]}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,'all']}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,'all']}\%,  \Sexpr{bl.results['CONS',2,1,'all']}\%, \Sexpr{bl.results['EPS',2,1,'all']}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr',sel.s]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr',sel.s]} and \Sexpr{bl.results['EPS',2,'ann.sr',sel.s]} respectively).
+The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr','all']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr','all']} and \Sexpr{bl.results['EPS',2,'ann.sr','all']} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,sel.s]}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,sel.s]}\% and \Sexpr{bl.results['EPS',3,1,sel.s]}\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,'all']}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,'all']}\% and \Sexpr{bl.results['EPS',3,1,'all']}\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 <<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,'all','t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-tab.r <- round(cbind(pt.cont.tab[,,sel.s,'t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- round(cbind(pt.cont.tab[,,'all','t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 <<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,'all','t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab.r <- round(cbind(eps.cont.tab[,,sel.s,'t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- round(cbind(eps.cont.tab[,,'all','t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-& Mean (in \%)&Median (in \%)&Std.dev\\
-%&all&same&all&same&all&same\\
+& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same\\
 \midrule
 <<desc-q-cons,echo=F,results='asis'>>=
-test.a[,,,1:2,sel.s] <- test.a[,,,1:2,sel.s]*100
+test.a[,,,1:2,] <- test.a[,,,1:2,]*100
 dimnames(test.a)[[2]] <- c('\\tr{}','\\naive{}','\\default{}')
-print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,1:3,'CONS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel A: Consensus}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
   \midrule
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(acast(melt(test.a[12,,'PT',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,,'PT',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel B: TP}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<desc-q-eps,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[12,,'EPS',1:3,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{4}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[12,,'EPS',1:3,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0),command=c('\\multicolumn{7}{c}{\\textbf{Panel C: EPS}} \\\\ \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 %\begin{tabular}{rrrrrrr}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
-%&all&same&all&same&all&same\\
+Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
+&all&same&all&same&all&same\\
 <<stocks-true,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,1,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,1,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,NA.string='-',hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel A: \\tr{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<stocks-naive,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,2,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,2,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel B: \\naive{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 <<stocks-def,echo=F,results='asis'>>=
-print(xtable(acast(melt(test.a[,3,c(1,3,2),4,sel.s]),Var1~Var2,value.var='value'),display=c('s','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{4}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(test.a[,3,c(1,3,2),4,]),Var1~Var2+Var3,value.var='value'),display=c('s','d','d','d','d','d','d'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,0,11),command=c('\\multicolumn{7}{l}{\\textbf{Panel C: \\default{}}} \\\\ \n','\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 #p.cum.ret <-
-ggplot(final.bl[type==sel.s],aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
 #
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
   \toprule
@@
 dimnames(bl.results)[[1]] <- c('\\textit{CONS}','\\textit{TP}','\\textit{EPS}','\\textit{Market}')
-results.final <- bl.results[4,1,,sel.s]
+results.final <- bl.results[4,1,,'all']
 cat(paste(c('Strategy','Annualized return (in \\%)','Annualized Std. dev (in \\%)','Sharpe ratio' ,'Average num. stock','Average turnover rate'), collapse = "&"),'\\\\')
 #cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
-print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{6}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(t(data.table('\\textit{Market}'=results.final)),display=c('s','f','f','f','d','f'),digits=3,align=c('r',rep('c',length(results.final)))),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A}} \\\\ \n')),sanitize.text.function = function(x) x)
 cat('\\midrule \n')
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  &all&same&all&same&all&same&all&same&all&same \\
 
 <<bl-nr,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,1,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,NA.string='-',include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,sel.s])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,1,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(nrow(bl.results[1:3,1,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
-\end{tabularx}
+\end{tabular}}
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
 <<bl-pt,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,2,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,sel.s])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,2,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),,add.to.row=list(pos=list(nrow(bl.results[1:3,2,,'all'])),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
-\end{tabularx}
+\end{tabular}}
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 <<bl-eps,echo=F,results='asis'>>=
-print(xtable(acast(melt(bl.results[1:3,3,,sel.s]),Var1~Var2,value.var='value'),display=c('s','f','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
+print(xtable(acast(melt(bl.results[1:3,3,,]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),sanitize.text.function = function(x) x)
 @
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}
@@
 <<sr-true,echo=F,results='asis'>>=
-periods.array[,,,,1,sel.s] <- periods.array[,,,,1,sel.s]*100
+periods.array[,,,,1,'all'] <- periods.array[,,,,1,'all']*100
 #results.final <- bl.results['Market',1,]
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
 
@@
 
-print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),sel.s]),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'all']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
 @

### 2015-04-01 doc/paper/paper-knitr-APS.tex
Include both sets in the paper

--- 2015-03-25 doc/paper/paper-knitr-APS.tex
@@
 Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report 13 672 stock-quarter observations.
-Each stock had on average of 6.421 quarterly target price reports.
+For the sample period (1999-2009), we report 15 048 stock-quarter observations.
+Each stock had on average of 12.823 quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.593\% (69.401\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 46.424\% and 40.681\% for the top and bottom terciles.
+Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.58\% (69.37\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.993\%, and 18.993\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (15.191\%, 16.098\%, and 12.718\%).
-Panel C shows the EPS based weighted expected returns averages (14.774\%, 14.967\%, and 12.928\%).
+The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.61\%, and 18.61\% respectively.
+Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.742\%, and 12.459\%).
+Panel C shows the EPS based weighted expected returns averages (14.689\%, 14.884\%, and 12.843\%).
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.512\%, 0.718\%.
+The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.325\%, 0.574\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.305 against NA, 0.046, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio is 0.294 against NA, 0.037, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
+As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.282\%,  0.116\%, \ensuremath{-0.303}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
 Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively).
+The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.007 and \ensuremath{-0.019} respectively).
 The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
 
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (1.043\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.702\% and 0.711\% respectively).
+Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.689\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.314\% and 0.746\% respectively).
 The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
@@
 %Year & Min& Mean & Median &Max& Std.dev\\
- 1999 &    3 & 4.246 & 4 &   10 & 1.588 \\ 
-  2000 &    3 & 4.756 & 4 &   14 & 1.878 \\ 
-  2001 &    3 & 5.248 & 5 &   15 & 2.323 \\ 
-  2002 &    3 & 6.043 & 5 &   19 & 2.948 \\ 
-  2003 &    3 & 6.667 & 6 &   21 & 3.427 \\ 
-  2004 &    3 & 7.120 & 6 &   21 & 3.617 \\ 
-  2005 &    3 & 7.348 & 7 &   21 & 3.592 \\ 
-  2006 &    3 & 7.408 & 7 &   20 & 3.417 \\ 
-  2007 &    3 & 7.050 & 6 &   20 & 3.334 \\ 
-  2008 &    3 & 6.370 & 6 &   18 & 2.884 \\ 
-  2009 &    3 & 5.152 & 5 &   18 & 2.191 \\ 
-   \midrule 
-Total &    3 & 6.421 & 6 &   21 & 3.210 \\
+\begin{kframe}
 
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `display<-.xtable`(`*tmp*`, value = c("{}s"{}, "{}f"{}, "{}d"{}, "{}f"{}, "{}f"{}, : "{}display"{} must have length equal to 8 ( ncol(x) + 1 )}}\end{kframe}
 \end{tabularx}
@@
 
- &$top$ & 67.7 & 22.1 & 10.2 & 100.0 \\ 
-  &$middle$ & 29.9 & 48.2 & 21.9 & 100.0 \\ 
-  &$bottom$ & 13.4 & 17.1 & 69.6 & 100.0 \\ 
+ &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
+  &$middle$ & 30.5 & 47.8 & 21.7 & 100.0 \\ 
+  &$bottom$ & 13.7 & 16.9 & 69.4 & 100.0 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
-  &$middle$ & 39.2 & 29.2 & 31.6 & 100.0 \\ 
-  &$bottom$ & 32.1 & 26.7 & 41.2 & 100.0 \\
+&$top$ & 46.6 & 27.9 & 25.6 & 100.0 \\ 
+  &$middle$ & 39.0 & 29.1 & 31.9 & 100.0 \\ 
+  &$bottom$ & 32.7 & 26.4 & 40.9 & 100.0 \\
 
@@
  &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
-  &$middle$ & 48.2 & 26.2 & 25.8 & 100.4 \\ 
-  &$bottom$ & 46.3 & 25.9 & 28.5 & 100.8 \\ 
+  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
+  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
     &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.8 & 28.3 & 26.0 & 101.1 \\ 
-  &$middle$ & 45.5 & 27.0 & 28.1 & 100.6 \\ 
-  &$bottom$ & 42.7 & 27.6 & 32.4 & 102.7 \\
+&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
+  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
+  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-& Mean (in \%)&Median (in \%)&Std.dev\\
-%&all&same&all&same&all&same\\
+& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same\\
 \midrule
-  \multicolumn{4}{c}{\textbf{Panel A: Consensus}} \\ 
+  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
  \midrule 
-\tr{} & - & - & - \\ 
-  \naive{} & 18.993 & 17.173 & 0.119 \\ 
-  \default{} & 18.993 & 17.173 & 0.119 \\
+\tr{} & - & - & - & - & - & - \\ 
+  \naive{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\ 
+  \default{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
   \midrule
-  \multicolumn{4}{c}{\textbf{Panel B: TP}} \\ 
+  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
  \midrule 
-\tr{} & 15.191 & 13.595 & 0.096 \\ 
-  \naive{} & 16.098 & 14.528 & 0.098 \\ 
-  \default{} & 12.718 & 10.789 & 0.089 \\
+\tr{} & 14.876 & 15.191 & 13.380 & 13.604 & 0.096 & 0.096 \\ 
+  \naive{} & 15.742 & 16.102 & 14.314 & 14.541 & 0.098 & 0.098 \\ 
+  \default{} & 12.459 & 12.714 & 10.591 & 10.798 & 0.089 & 0.089 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{c}{\textbf{Panel C: EPS}} \\ 
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
  \midrule 
-\tr{} & 14.774 & 13.269 & 0.102 \\ 
-  \naive{} & 14.967 & 13.432 & 0.103 \\ 
-  \default{} & 12.928 & 11.440 & 0.089 \\
+\tr{} & 14.689 & 14.769 & 13.214 & 13.252 & 0.101 & 0.102 \\ 
+  \naive{} & 14.884 & 14.959 & 13.392 & 13.420 & 0.103 & 0.103 \\ 
+  \default{} & 12.843 & 12.916 & 11.410 & 11.439 & 0.089 & 0.089 \\
 
@@
 %\begin{tabular}{rrrrrrr}
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
 \toprule
-Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
-%&all&same&all&same&all&same\\
-  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
+Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
+&all&same&all&same&all&same\\
+  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
  \midrule 
-1999 & - &   69 &   44 \\ 
-  2000 & - &  232 &  191 \\ 
-  2001 & - &  273 &  244 \\ 
-  2002 & - &  317 &  290 \\ 
-  2003 & - &  330 &  299 \\ 
-  2004 & - &  331 &  318 \\ 
-  2005 & - &  347 &  337 \\ 
-  2006 & - &  351 &  337 \\ 
-  2007 & - &  359 &  351 \\ 
-  2008 & - &  354 &  339 \\ 
-  2009 & - &  306 &  306 \\ 
+1999 & - & - &   71 &   67 &   42 &   42 \\ 
+  2000 & - & - &  253 &  232 &  191 &  191 \\ 
+  2001 & - & - &  302 &  273 &  244 &  244 \\ 
+  2002 & - & - &  353 &  316 &  289 &  289 \\ 
+  2003 & - & - &  369 &  330 &  299 &  299 \\ 
+  2004 & - & - &  375 &  331 &  318 &  318 \\ 
+  2005 & - & - &  395 &  347 &  337 &  337 \\ 
+  2006 & - & - &  403 &  351 &  337 &  337 \\ 
+  2007 & - & - &  418 &  359 &  351 &  351 \\ 
+  2008 & - & - &  413 &  353 &  339 &  339 \\ 
+  2009 & - & - &  346 &  306 &  306 &  306 \\ 
    \midrule 
-Total & - &  378 &  375 \\
+Total & - & - &  442 &  378 &  375 &  375 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
  \midrule 
-1999 &   69 &   69 &   44 \\ 
-  2000 &  235 &  235 &  186 \\ 
-  2001 &  281 &  281 &  247 \\ 
-  2002 &  323 &  323 &  288 \\ 
-  2003 &  334 &  334 &  307 \\ 
-  2004 &  341 &  341 &  318 \\ 
-  2005 &  352 &  352 &  337 \\ 
-  2006 &  358 &  358 &  343 \\ 
-  2007 &  361 &  361 &  352 \\ 
-  2008 &  360 &  360 &  349 \\ 
-  2009 &  351 &  351 &  321 \\ 
+1999 &   71 &   67 &   71 &   67 &   41 &   41 \\ 
+  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
+  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
+  2002 &  360 &  321 &  360 &  321 &  287 &  287 \\ 
+  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
+  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
+  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
+  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
+  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
+  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
+  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
    \midrule 
-Total &  378 &  378 &  376 \\
+Total &  442 &  378 &  442 &  378 &  376 &  376 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{4}{Y}}
-  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
+\begin{tabularx}{\linewidth}{r*{7}{Y}}
+  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
  \midrule 
-1999 &   69 &   69 &   54 \\ 
-  2000 &  235 &  235 &  204 \\ 
-  2001 &  281 &  281 &  261 \\ 
-  2002 &  323 &  323 &  304 \\ 
-  2003 &  334 &  334 &  317 \\ 
-  2004 &  341 &  341 &  332 \\ 
-  2005 &  352 &  352 &  344 \\ 
-  2006 &  358 &  358 &  353 \\ 
-  2007 &  361 &  361 &  358 \\ 
-  2008 &  360 &  360 &  359 \\ 
-  2009 &  351 &  351 &  350 \\ 
+1999 &   71 &   67 &   71 &   67 &   51 &   51 \\ 
+  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
+  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
+  2002 &  360 &  321 &  360 &  321 &  302 &  302 \\ 
+  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
+  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
+  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
+  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
+  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
+  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
+  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
    \midrule 
-Total &  378 &  378 &  377 \\
+Total &  442 &  378 &  442 &  378 &  377 &  377 \\
 
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{5}{Y}}
   \toprule
   %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
-Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{6}{l}{\textbf{Panel A}} \\ 
+Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
 \textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  &all&same&all&same&all&same&all&same&all&same \\
 
- \textit{CONS} & - & - & - & - & - \\ 
-  \textit{TP} & 4.512 & 14.792 & 0.305 &  251 & 0.326 \\ 
-  \textit{EPS} & 0.718 & 15.509 & 0.046 &  205 & 0.493 \\ 
+ \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
+  \textit{TP} & 4.325 & 4.549 & 14.697 & 14.794 & 0.294 & 0.307 &  283 &  251 & 0.345 & 0.327 \\ 
+  \textit{EPS} & 0.574 & 0.719 & 15.528 & 15.505 & 0.037 & 0.046 &  205 &  205 & 0.496 & 0.494 \\ 
    \midrule
 
-\end{tabularx}
+\end{tabular}}
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
- \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
-  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
-  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
+ \textit{CONS} & 0.116 & 0.434 & 15.948 & 15.995 & 0.007 & 0.027 &  283 &  251 & 0.256 & 0.251 \\ 
+  \textit{TP} & 0.282 & 0.621 & 15.662 & 15.682 & 0.018 & 0.040 &  284 &  251 & 0.264 & 0.256 \\ 
+  \textit{EPS} & -0.303 & -0.349 & 16.088 & 16.096 & -0.019 & -0.022 &  206 &  206 & 0.410 & 0.408 \\ 
    \midrule
 
-\end{tabularx}
+\end{tabular}}
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
-  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
- \textit{CONS} & 0.702 & 15.820 & 0.044 &  252 & 0.223 \\ 
-  \textit{TP} & 1.043 & 15.476 & 0.067 &  252 & 0.248 \\ 
-  \textit{EPS} & 0.711 & 15.481 & 0.046 &  245 & 0.255 \\
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrrrr}
+  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
+ \textit{CONS} & 0.314 & 0.686 & 15.773 & 15.825 & 0.020 & 0.043 &  283 &  251 & 0.228 & 0.223 \\ 
+  \textit{TP} & 0.689 & 1.056 & 15.565 & 15.485 & 0.044 & 0.068 &  284 &  251 & 0.256 & 0.248 \\ 
+  \textit{EPS} & 0.746 & 0.717 & 15.444 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.256 \\
 
 \bottomrule
-\end{tabularx}
+\end{tabular}}
 \end{table}
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 6.545 & 0.447 & 2.080 & 0.137 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.185 & 0.429 & 4.076 & 0.279 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 8.985 & 0.768 & 5.822 & 0.485 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.236 & 1.889 & 10.690 & 1.365 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.399 & 0.030 & -3.083 & -0.229 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.518 & 0.165 & -0.625 & -0.039 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.844 & 0.395 & 1.890 & 0.124 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.119 & 0.425 & 3.945 & 0.270 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.124 & 0.757 & 5.877 & 0.492 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.715 & 1.915 & 10.681 & 1.364 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.908 & 0.070 & -3.133 & -0.232 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.827 & 0.189 & -0.725 & -0.045 \\ 
    \midrule 
-All period & -3.032 & -0.182 & - & - & 4.512 & 0.305 & 0.718 & 0.046 \\
+All period & -3.032 & -0.182 & - & - & 4.325 & 0.294 & 0.574 & 0.037 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 2.663 & 0.167 & 2.620 & 0.168 & 1.172 & 0.074 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.669 & 0.170 & 3.266 & 0.214 & 2.659 & 0.171 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.734 & 0.447 & 6.075 & 0.490 & 5.485 & 0.455 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.548 & 1.106 & 10.068 & 1.248 & 9.337 & 1.155 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.708 & -0.343 & -4.148 & -0.305 & -4.541 & -0.332 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.367 & -0.146 & -2.003 & -0.125 & -1.757 & -0.106 \\ 
    \midrule 
-All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\
+All period & -3.032 & -0.182 & 0.116 & 0.007 & 0.282 & 0.018 & -0.303 & -0.019 \\
 
@@
   \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & 3.934 & 0.252 & 3.833 & 0.256 & 3.470 & 0.229 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & 3.278 & 0.211 & 4.000 & 0.270 & 3.883 & 0.259 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & 5.464 & 0.433 & 5.907 & 0.487 & 5.686 & 0.465 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & 9.285 & 1.066 & 10.185 & 1.252 & 9.964 & 1.195 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & -4.979 & -0.364 & -4.093 & -0.299 & -4.251 & -0.311 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & -2.429 & -0.149 & -1.671 & -0.103 & -1.974 & -0.122 \\ 
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.102 & 0.197 & 3.133 & 0.205 & 3.501 & 0.232 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.016 & 0.194 & 3.727 & 0.249 & 3.954 & 0.264 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.410 & 0.417 & 5.793 & 0.464 & 5.712 & 0.468 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.419 & 1.071 & 10.335 & 1.245 & 10.002 & 1.202 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.860 & -0.358 & -3.941 & -0.289 & -4.223 & -0.309 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.398 & -0.149 & -1.697 & -0.105 & -1.936 & -0.121 \\ 
    \midrule 
-All period & -3.032 & -0.182 & 0.702 & 0.044 & 1.043 & 0.067 & 0.711 & 0.046 \\
+All period & -3.032 & -0.182 & 0.314 & 0.020 & 0.689 & 0.044 & 0.746 & 0.048 \\
 

### 2015-04-01 src/paper.trading.APS.true.R

@@ -1,19 +1,28 @@
 
+q.data <- na.omit(q.data)
 
-stocks.m <- sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))
+stocks.m <- setkey(data.table(Stock.m=sort(unique(unlist(lapply(market.list,function(m){m$stock.names}))))),Stock.m)
 
 load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
 
 quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
 
-stocks <- sort(intersect(intersect(stocks.m,setkey(q.data,q.id)[quarters]$Stock),setkey(complete.dt,q.id)[quarters]$Stock))
+stocks <- setkey(data.table(Stock=sort(intersect(intersect(stocks.m$Stock.m,setkey(q.data,q.id)[quarters]$Stock),setkey(complete.dt,q.id)[quarters]$Stock))),Stock)
 
 
 
-core.dt.tmp <- setkey(q.data[,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)
+core.dt.tmp <- setkey(setkey(q.data,Stock)[stocks,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)
 
-core.dt <- rbind(core.dt.tmp[stocks][,type:='same'],core.dt.tmp[stocks.m][,type:='all'])
+load('cache/q.data.RData')
+q.data <- na.omit(q.data)
+core.dt.tmp.m <- setkey(setkey(q.data,Stock)[stocks.m,core.b:=.N>=12,by=list(Stock,Broker)][(core.b)][,true:=rank(score),by=list(q.id,Stock)][,core.s:=.N>=3,by=list(q.id,Stock)][(core.s)][,core.q:=length(unique(q.id))>=8,by=.(Stock)][(core.q)],Stock)
 
+
[…]

### 2015-04-02 doc/paper/paper-knitr-APS.Rnw
change all tables to a "all-same" format. Next is to change the text

@@
 ###ADD NAs for the case of no ranking ( if NA, no raking)
+q.data.ex <- q.data
+q.data <- na.omit(q.data)
+
+stocks.m <- setkey(data.table(Stock.m=sort(market.set[,unique(Stock)])),Stock.m)
+
+load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
+complete.dt.ex <- complete.dt
+quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
+
+stocks <- setkey(data.table(Stock=sort(intersect(intersect(stocks.m$Stock.m,setkey(q.data,q.id)[quarters]$Stock),setkey(complete.dt,q.id)[quarters]$Stock))),Stock)
+dt.1 <- setkey(q.data,Stock)[stocks]
+dt.2 <- q.data[stocks.m]
+q.data <- rbind(dt.1[,type:='same'],dt.2[,type:='all'])
+
 trunk.percent <- 0.05
-stocks <- unique(market.set[,Stock])
-#q.data[,quantile(b.view,c(trunk.percent,1-trunk.percent),na.rm=T)]
-q.data.full <- setkey(q.data[,':='(year=format(s.Date,'%Y'))],Stock)
-
-q.data <- na.omit(q.data.full[stocks])
-q.data <- q.data[,trunk.view:=truncate.f(b.view,trunk.percent)]
+q.data <- na.omit(q.data[,trunk.view:=truncate.f(b.view,trunk.percent),by=type][,year:=format(q.id,'%Y')])
 #stats.q.data <- summary.stat(q.data[!is.na(trunk.view),])
@@
 #pt.contin.dt <- unique(core.dt[,cont.rank:=.N>8,by=.(q.id,Stock)][(cont.rank)],by=c('q.id','Broker','Stock'))
-quarters <- data.table(q.id=core.dt[order(q.id)][,unique(q.id)])
 
@@
 load('cache/ranked.eps.dt.RData')
-load('~/Dropbox/workspace/Projects/EPS/cache/complete.dt.RData')
 
-complete.dt <- setkey(complete.dt,fis.q)[quarters]
-eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
-complete.dt <- setnames(na.omit(setkey(complete.dt,Stock)[eps.stocks][,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))])[,q.id:=NULL],'fis.q','q.id')
+dt.3 <- setkey(complete.dt,Stock)[stocks]
+dt.4 <- complete.dt[stocks.m]
+complete.dt <- na.omit(setkey(rbind(dt.3[,type:='same'],dt.4[,type:='all']),q.id)[quarters])
+
+#complete.dt <- setkey(complete.dt,fis.q)[quarters]
+#eps.stocks <- intersect(complete.dt$Stock,unique(market.set[,Stock]))
+
+complete.dt <- setnames(complete.dt[,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps)),by=type],'fis.q','q.id')
 
@@
 
-brok.full.stat.pt <- rbind(setkey(core.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=.(year,type)],year),setnames(cbind('Total',(core.dt)[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=type]),1,'year'))
+brok.full.stat.pt <- rbind(setkey(core.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.numeric(median(N)),max=max(N),st.dev=sd(N)),by=.(year,type)],year),setnames(cbind('Total',(core.dt)[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.numeric(median(N)),max=max(N),st.dev=sd(N)),by=type]),1,'year'))
+
+brok.full.stat.eps <- rbind(setkey(complete.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.numeric(median(N)),max=max(N),st.dev=sd(N)),by=.(year,type)],year),setnames(cbind('Total',complete.dt[,.N,by=.(Stock,q.id,year,type)][,list(min=min(N),mean=mean(N),median=as.numeric(median(N)),max=max(N),st.dev=sd(N)),by=type]),1,'year'))
 
@@
 test.a[,'true','CONS',,] <- NA
-
-brok.full.stat.eps <- rbind(setkey(na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N)),by=year],year),setnames(cbind('Total',na.omit(complete.dt)[,.N,by=.(Stock,q.id,year)][,list(min=min(N),mean=mean(N),median=as.character(median(N)),max=max(N),st.dev=sd(N))]),1,'year'))
 
@@
 end.year <- format(as.Date(final.bl[,tail(Quarters,1)]),'%Y')
+
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{11}{Y}}
 \toprule
-Year & Min& Mean & Median &Max& Std.dev\\
+    & \multicolumn{2}{c}{Min}&\multicolumn{2}{c}{Mean}& \multicolumn{2}{c}{Median}& \multicolumn{2}{c}{Max}&\multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same&all&same&all&same\\
 \midrule
 %Panel A: TP&&&&&\\
-\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
+\multicolumn{11}{l}{\textbf{Panel A: TP}} \\
 \midrule
 %Year & Min& Mean & Median &Max& Std.dev\\
-<<desc-pt,echo=F,results='asis'>>=
-
-#data.to.display <- c('min','mean', 'median','max','std.dev')
-#results.final <- rbind(brok.full.stat.pt[,data.to.display],'Total period'=setkey(pt.full.period,Statistics)[data.to.display][,value])
+<<desc-pt,echo=F,results='asis',warning=FALSE>>=
 
@@
 #cat(rep('&',ncol(results.final)),'\\\\')
-print(xtable(brok.full.stat.pt,display=c('s','f','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
+print(xtable(acast(melt(brok.full.stat.pt,id.vars=c('year','type')),year~type+variable,value.var='value')[,c(1,6,2,7,3,8,4,9,5,10)],display=c('s','d','d','f','f','d','d','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=T,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
 @
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{11}{Y}}
 \midrule
-\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
+\multicolumn{11}{l}{\textbf{Panel B: EPS}} \\
 \midrule
-<<desc-eps,echo=F,results='asis'>>=
-print(xtable(brok.full.stat.eps,display=c('s','d','d','f','f','d','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=FALSE,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
+<<desc-eps,echo=F,results='asis',warning=FALSE>>=
+print(xtable(acast(melt(brok.full.stat.eps,id.vars=c('year','type')),year~type+variable,value.var='value')[,c(1,6,2,7,3,8,4,9,5,10)],display=c('s','d','d','f','f','d','d','d','d','f','f'),digits=3),only.contents=T,include.colnames=FALSE,include.rownames=T,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(11),command=c('\\midrule \n')))
 @
@@
 <<example-table,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(q.data[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'\\emph{TP}'=PT,'$\\overline{PMAFE}^{TP}$'=round(score,3))][,rank:=c(4,3,1,2)][order(rank)],4,'$rank^{TP}$'),display=c('s','d','f','f','d')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0,4),command=c('\\midrule \n','\\midrule \n')),sanitize.text.function = function(x) x)
+print(xtable(setnames(q.data.ex[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'\\emph{TP}'=PT,'$\\overline{PMAFE}^{TP}$'=round(score,3),rank=rank(score))][order(rank)],4,'$rank^{TP}$'),display=c('s','d','f','f','f')),include.rownames=F,only.contents = T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
+\midrule
 \end{tabularx}
@@
 <<example-table-eps,echo=FALSE,warning=FALSE,message=FALSE,results='asis'>>=
-print(xtable(setnames(complete.dt[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'$PRED$'=Est,'$PMAFE^{EPS}$'=eps.pmafe,rank)][order(rank)],4,'$rank^{EPS}$'),display=c('s','d','f','f','d'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
+
+ex.eps <- setnames(complete.dt.ex[,eps.pmafe:=abs(Est-act.eps)/mean(abs(Est-act.eps))],'fis.q','q.id')
+
+print(xtable(setnames(ex.eps[Stock=='AMZN'&q.id=='1999 Q2'][,list('Broker/Analyst'=Broker,'$PRED$'=Est,'$PMAFE^{EPS}$'=eps.pmafe,rank)][order(rank)],4,'$rank^{EPS}$'),display=c('s','d','f','f','f'),digits=3),include.rownames=F,only.contents=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('\\midrule \n')),sanitize.text.function = function(x) x)
 @
@@
 <<example-fig,echo=F,include=FALSE,results='hide',fig.width=10.7,fig.height=8.3>>=
-require(gridExtra)
+
 example.dt$Broker <- factor(example.dt$Broker,levels=unique(example.dt$Broker))
@@
 
-#ggplot(setnames(rbind(example.dt[,.(s.Date,PT,Broker)],setnames(example.dt[,.(s.Date,priceAdj)][,Broker:='AMZN'],2,'PT')),'Broker','Stock Price'),aes(x=s.Date,y=PT,group=`Stock Price`,color=`Stock Price`,shape=`Stock Price`))+geom_line(size=1)+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
-
-#ggplot(example.dt,aes(x=s.Date,y=PT,group=Broker,color=Broker,shape=Broker))+geom_line(size=1)+geom_line(aes(y=priceAdj),color='black')+geom_point()+theme_bw()+ylab('Dollars')+xlab('1999Q2')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices')+scale_color_grey()
-
 ggplot(test,aes(x=s.Date,y=PT,group=Series,color=Series,shape=Series))+theme_bw()+ylab('Dollars')+ggtitle('Daily stock price (AMZN) compared to broker\'s target prices \n over the period of the second calendar quarter of 1999')+geom_line()+geom_point(size=2)+scale_color_grey()+theme(axis.title.x=element_blank(),text=element_text(size=20,family='Times'),legend.title=element_blank())
-
-#+geom_line(aes(y=priceAdj),color='black')+theme(plot.title = element_text(colour = "Black"),legend.position='top')
-#grid.draw(grobTree(arrangeGrob(p,ncol=1),rectGrob(gp=gpar(lwd=2, fill=NA))))
 @
@@
 Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{10}{Y}}
     \toprule
-\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
+&&\multicolumn{2}{c}{$top$}&\multicolumn{2}{c}{$middle$}&\multicolumn{2}{c}{$bottom$}&\multicolumn{2}{c}{$Sum$}\\
+&&all&same&all&same&all&same&all&same\\
+\midrule
+\multirow{10}{*}{$t$}&\multicolumn{2}{l}{\textbf{Panel A: TP}}&\multicolumn{6}{c}{$t+1$} \\
 
 <<desc-rank-pt-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(pt.cont.tab[,,'all','t'],Total=apply(pt.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- acast(rbind(melt(pt.cont.tab[,,,'t']),data.table(melt(aperm(apply(pt.cont.tab,c(1,3,4),sum),c(1,3,2))))[Var2=='t']),Var1~Var2+Var3,value.var='value')*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 
-tab.r <- round(cbind(pt.cont.tab[,,'all','t+4'],Total=apply(pt.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- acast(rbind(melt(pt.cont.tab[,,,'t+4']),data.table(melt(aperm(apply(pt.cont.tab,c(1,3,4),sum),c(1,3,2))))[Var2=='t+4']),Var1~Var2+Var3,value.var='value')*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
 #colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{8}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
 @
 \end{tabularx}
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{10}{Y}}
 \midrule
-\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
+\multirow{10}{*}{$t$}&\multicolumn{2}{l}{\textbf{Panel B: EPS}}&\multicolumn{6}{c}{$t+1$} \\
+%&&$top$&$middle$&$bottom$&Sum\\
 <<desc-rank-eps-t1,echo=F,results='asis'>>=
-tab.r <- round(cbind(eps.cont.tab[,,'all','t'],Total=apply(eps.cont.tab[,,1,1],1,sum)),3)*100
+tab.r <- acast(rbind(melt(eps.cont.tab[,,,'t']),data.table(melt(aperm(apply(eps.cont.tab,c(1,3,4),sum),c(1,3,2))))[Var2=='t']),Var1~Var2+Var3,value.var='value')*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
@@
 print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,sanitize.text.function = function(x) x)
-tab.r <- round(cbind(eps.cont.tab[,,'all','t+4'],Total=apply(eps.cont.tab[,,1,2],1,sum)),3)*100
+tab.r <- acast(rbind(melt(eps.cont.tab[,,,'t+4']),data.table(melt(aperm(apply(eps.cont.tab,c(1,3,4),sum),c(1,3,2))))[Var2=='t+4']),Var1~Var2+Var3,value.var='value')*100
 rownames(tab.r) <- c('&$top$','&$middle$','&$bottom$')
 #colnames(tab.r) <- c('$top$','$middle$','$bottom$','Sum')
-print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{4}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
+print(xtable(tab.r,hline = F,digits=1),only.contents=T,include.colnames=F,include.rownames=T,hline.after=NULL,add.to.row=list(pos=list(0),command=c('&&\\multicolumn{8}{c}{$t+4$}\\\\ \n')),sanitize.text.function = function(x) x)
 @
@@
 #p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)+scale_x_date(breaks=date_breaks('2 years'),labels=date_format('%Y'))
 #

### 2015-04-02 doc/paper/paper-knitr-APS.tex
change all tables to a "all-same" format. Next is to change the text

@@
 
-Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 361, covering 504 S\&P500 stocks.
+Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 351, covering 498 S\&P500 stocks.
 Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
@@
 
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and at the 95\textsuperscript{th} percentile (values above 0.791).
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the 5\textsuperscript{th} percentile (values below \ensuremath{-0.114}) and at the 95\textsuperscript{th} percentile (values above 0.805).
 This is done due to occurrence of the extreme values.
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 145 630 to 131 068.
+After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 247 163 to 247 163.
 
@@
 In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  155 brokers covering 402 stocks.
-The total number of observation is 79 539.
+Our final sample of EPS forecasts consist of  157 brokers covering 402 stocks.
+The total number of observation is 158 029.
 
@@
 Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has 12 084 stock-quarter observations.
-The average number of quarterly forecasts is 6.582.
+In total, the EPS forecast sample has 12 203 stock-quarter observations.
+The average number of quarterly forecasts is 12.95.
 
@@
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{11}{Y}}
 \toprule
-Year & Min& Mean & Median &Max& Std.dev\\
+    & \multicolumn{2}{c}{Min}&\multicolumn{2}{c}{Mean}& \multicolumn{2}{c}{Median}& \multicolumn{2}{c}{Max}&\multicolumn{2}{c}{Std.dev}\\
+&all&same&all&same&all&same&all&same&all&same\\
 \midrule
 %Panel A: TP&&&&&\\
-\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
+\multicolumn{11}{l}{\textbf{Panel A: TP}} \\
 \midrule
 %Year & Min& Mean & Median &Max& Std.dev\\
-\begin{kframe}
+ 1999 &    3 &    3 & 4.286 & 4.326 &    4 &    4 &   11 &   11 & 1.657 & 1.668 \\ 
+  2000 &    3 &    3 & 4.873 & 4.944 &    4 &    4 &   14 &   14 & 2.009 & 2.017 \\ 
+  2001 &    3 &    3 & 5.537 & 5.691 &    5 &    5 &   16 &   16 & 2.453 & 2.481 \\ 
+  2002 &    3 &    3 & 6.411 & 6.611 &    6 &    6 &   19 &   19 & 3.108 & 3.145 \\ 
+  2003 &    3 &    3 & 7.021 & 7.252 &    6 &    6 &   21 &   21 & 3.524 & 3.573 \\ 
+  2004 &    3 &    3 & 7.477 & 7.728 &    7 &    7 &   22 &   22 & 3.671 & 3.726 \\ 
+  2005 &    3 &    3 & 7.667 & 7.946 &    7 &    7 &   24 &   24 & 3.736 & 3.744 \\ 
+  2006 &    3 &    3 & 7.754 & 8.037 &    7 &    7 &   22 &   22 & 3.561 & 3.532 \\ 
+  2007 &    3 &    3 & 7.394 & 7.691 &    7 &    7 &   22 &   22 & 3.494 & 3.429 \\ 
+  2008 &    3 &    3 & 6.708 & 6.973 &    6 &    6 &   18 &   18 & 3.023 & 2.964 \\ 
+  2009 &    3 &    3 & 5.510 & 5.627 &    5 &    5 &   19 &   19 & 2.412 & 2.433 \\ 
+   \midrule 
+Total &    3 &    3 & 6.710 & 6.915 &    6 &    6 &   24 &   24 & 3.336 & 3.356 \\
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `display<-.xtable`(`*tmp*`, value = c("{}s"{}, "{}f"{}, "{}d"{}, "{}f"{}, "{}f"{}, : "{}display"{} must have length equal to 8 ( ncol(x) + 1 )}}\end{kframe}
 \end{tabularx}
 
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{11}{Y}}
 \midrule
-\multicolumn{6}{c}{\textbf{Panel B: EPS}} \\
+\multicolumn{11}{l}{\textbf{Panel B: EPS}} \\
 \midrule
- 1999 &    3 & 5.728 & 5 &   17 & 3.007 \\ 
-  2000 &    3 & 5.433 & 5 &   17 & 2.774 \\ 
-  2001 &    3 & 6.020 & 5 &   18 & 2.972 \\ 
-  2002 &    3 & 6.338 & 5 &   21 & 3.264 \\ 
-  2003 &    3 & 6.523 & 6 &   24 & 3.430 \\ 
-  2004 &    3 & 6.947 & 6 &   22 & 3.749 \\ 
-  2005 &    3 & 7.205 & 6 &   24 & 3.774 \\ 
-  2006 &    3 & 7.494 & 7 &   26 & 3.843 \\ 
-  2007 &    3 & 7.134 & 6 &   21 & 3.532 \\ 
-  2008 &    3 & 6.378 & 6 &   22 & 3.062 \\ 
-  2009 &    3 & 5.811 & 5 &   20 & 2.783 \\ 
+ 1999 &    3 &    3 & 5.673 & 5.643 &    5 &    5 &   17 &   17 & 2.991 & 2.936 \\ 
+  2000 &    3 &    3 & 5.433 & 5.426 &    5 &    5 &   17 &   17 & 2.774 & 2.733 \\ 
+  2001 &    3 &    3 & 6.020 & 6.048 &    5 &    5 &   18 &   18 & 2.972 & 2.987 \\ 
+  2002 &    3 &    3 & 6.338 & 6.357 &    5 &    5 &   21 &   21 & 3.264 & 3.274 \\ 
+  2003 &    3 &    3 & 6.523 & 6.532 &    6 &    6 &   24 &   24 & 3.430 & 3.443 \\ 
+  2004 &    3 &    3 & 6.947 & 6.978 &    6 &    6 &   22 &   22 & 3.749 & 3.771 \\ 
+  2005 &    3 &    3 & 7.205 & 7.216 &    6 &    6 &   24 &   24 & 3.774 & 3.777 \\ 
+  2006 &    3 &    3 & 7.494 & 7.467 &    7 &    7 &   26 &   26 & 3.843 & 3.820 \\ 
+  2007 &    3 &    3 & 7.134 & 7.091 &    6 &    6 &   21 &   21 & 3.532 & 3.489 \\ 
+  2008 &    3 &    3 & 6.378 & 6.353 &    6 &    6 &   22 &   22 & 3.062 & 3.039 \\ 
+  2009 &    3 &    3 & 5.811 & 5.773 &    5 &    5 &   20 &   20 & 2.783 & 2.753 \\ 
    \midrule 
-Total &    3 & 6.582 & 6 &   26 & 3.426 \\
+Total &    3 &    3 & 6.571 & 6.563 &    6 &    6 &   26 &   26 & 3.423 & 3.412 \\
 
@@
   \midrule 
-LEGG & 58.50 & 0.05 &   1 \\ 
-  MONTSEC & 87.50 & 0.46 &   2 \\ 
-  KAUFBRO & 125.00 & 1.65 &   3 \\ 
-  DLJ & 140.00 & 1.97 &   4 \\ 
+LEGG & 58.50 & 0.05 & 1.00 \\ 
+  MONTSEC & 87.50 & 0.46 & 2.00 \\ 
+  KAUFBRO & 125.00 & 1.65 & 3.00 \\ 
+  DLJ & 140.00 & 1.97 & 4.00 \\
+
 \midrule
-
 \end{tabularx}
@@
   \midrule 
-MONTSEC & -0.120 & 0.027 &    1 \\ 
-  BEAR & -0.130 & 0.080 &    2 \\ 
-  PACCREST & -0.130 & 0.080 &    2 \\ 
-  BACHE & -0.135 & 0.107 &    4 \\ 
-  RBRTSON & -0.140 & 0.133 &    5 \\ 
-  FBOSTON & -0.145 & 0.160 &    6 \\
+MONTSEC & -0.120 & 0.023 & 1.000 \\ 
+  BEAR & -0.130 & 0.068 & 2.500 \\ 
+  PACCREST & -0.130 & 0.068 & 2.500 \\ 
+  BACHE & -0.135 & 0.091 & 4.000 \\ 
+  RBRTSON & -0.140 & 0.114 & 5.000 \\ 
+  FBOSTON & -0.145 & 0.137 & 6.000 \\
 
@@
 Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{10}{Y}}
     \toprule
-\multirow{10}{*}{$t$}&\textbf{Panel A: TP}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
+&&\multicolumn{2}{c}{$top$}&\multicolumn{2}{c}{$middle$}&\multicolumn{2}{c}{$bottom$}&\multicolumn{2}{c}{$Sum$}\\
+&&all&same&all&same&all&same&all&same\\
+\midrule
+\multirow{10}{*}{$t$}&\multicolumn{2}{l}{\textbf{Panel A: TP}}&\multicolumn{6}{c}{$t+1$} \\
 
- &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
-  &$middle$ & 30.5 & 47.8 & 21.7 & 100.0 \\ 
-  &$bottom$ & 13.7 & 16.9 & 69.4 & 100.0 \\ 
-    &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.6 & 27.9 & 25.6 & 100.0 \\ 
-  &$middle$ & 39.0 & 29.1 & 31.9 & 100.0 \\ 
-  &$bottom$ & 32.7 & 26.4 & 40.9 & 100.0 \\
+ &$top$ & 67.6 & 67.7 & 22.2 & 22.0 & 10.3 & 10.2 & 100.0 & 100.0 \\ 
+  &$middle$ & 30.5 & 29.7 & 47.8 & 48.4 & 21.7 & 21.9 & 100.0 & 100.0 \\ 
+  &$bottom$ & 13.7 & 13.4 & 16.9 & 17.0 & 69.4 & 69.6 & 100.0 & 100.0 \\ 
+    &&\multicolumn{8}{c}{$t+4$}\\ 
+&$top$ & 46.6 & 46.3 & 27.9 & 28.2 & 25.6 & 25.5 & 100.0 & 100.0 \\ 
+  &$middle$ & 39.0 & 39.1 & 29.1 & 29.1 & 31.9 & 31.7 & 100.0 & 100.0 \\ 
+  &$bottom$ & 32.7 & 32.1 & 26.4 & 26.5 & 40.9 & 41.4 & 100.0 & 100.0 \\
 
 \end{tabularx}
-\begin{tabularx}{\linewidth}{r*{6}{Y}}
+\begin{tabularx}{\linewidth}{r*{10}{Y}}
 \midrule
-\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
-&&$top$&$middle$&$bottom$&Sum\\
- &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
-  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
-  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
-    &&\multicolumn{4}{c}{$t+4$}\\ 
-&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
-  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
-  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\
+\multirow{10}{*}{$t$}&\multicolumn{2}{l}{\textbf{Panel B: EPS}}&\multicolumn{6}{c}{$t+1$} \\
+%&&$top$&$middle$&$bottom$&Sum\\
+ &$top$ & 48.4 & 48.4 & 26.1 & 26.1 & 26.0 & 26.0 & 100.5 & 100.5 \\ 
+  &$middle$ & 48.1 & 48.2 & 26.3 & 26.2 & 25.9 & 25.8 & 100.4 & 100.2 \\ 
+  &$bottom$ & 46.5 & 46.3 & 25.7 & 25.9 & 28.6 & 28.5 & 100.8 & 100.6 \\ 
+    &&\multicolumn{8}{c}{$t+4$}\\ 
+&$top$ & 46.7 & 46.8 & 28.4 & 28.3 & 26.1 & 26.0 & 101.1 & 101.2 \\ 
+  &$middle$ & 45.4 & 45.5 & 27.1 & 27.0 & 28.1 & 28.1 & 100.6 & 100.6 \\ 
+  &$bottom$ & 42.8 & 42.7 & 27.7 & 27.6 & 32.3 & 32.4 & 102.7 & 102.7 \\
 

### 2015-04-08 doc/paper/paper-knitr-APS.Rnw
change text to include two stock sets (same and all). Send to APS

@@
 \documentclass{article}
+\usepackage[printfigures]{figcaps}
 \usepackage{fancyhdr}
@@
 %\onehalfspacing
-\doublespace
+%\doublespace
 \usepackage[longnamesfirst]{natbib}
@@
 \newcommand{\tr}{\textit{true}}
+\newcommand{\true}{\textit{true}}
 \newcommand{\naive}{\textit{recent}}
@@
 \newcommand{\market}{\textit{market}}
+
+\newcommand{\same}{\textit{same}}
+\newcommand{\all}{\textit{all}}
 \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}% raggedleft column X
@@
 strategies <- c('true','recent','all-time')
+sets <- c('all','same')
 setwd('~/Dropbox/workspace/Projects/BL-strategies')
@@
 complete.dt.ex <- complete.dt
+
 quarters <- setnames(unique(market.set[,.(Quarters)]),'q.id')[,q.id:=as.yearqtr(q.id)]
@@
 dt.2 <- q.data[stocks.m]
-q.data <- rbind(dt.1[,type:='same'],dt.2[,type:='all'])
+q.data <- rbind(dt.1[,type:=sets[2]],dt.2[,type:=sets[1]])
 
@@
 dt.4 <- complete.dt[stocks.m]
-complete.dt <- na.omit(setkey(rbind(dt.3[,type:='same'],dt.4[,type:='all']),q.id)[quarters])
+complete.dt <- na.omit(setkey(rbind(dt.3[,type:=sets[2]],dt.4[,type:=sets[1]]),q.id)[quarters])
 
@@
 %$N$ is the number of analysts with a valid TP report and
-where $r_{j,i}=TP_{j,i}/P_{i}-1$  is analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
+where $r_{j,i}=TP_{j,i}/P_{i}-1$  is last known analyst's $j$ expected return computed using the analyst price target $TP_{j,i}$ and stock price $P_{i}$\footnote{Consistent with the literature, we use stock price 3 days \emph{ex-ante} the TP announcement.
 This is done to avoid any information leakage around new TP announcement day \citep{bonini2010}}.
@@
 \begin{equation}
-\overline{PMAFE_{j,i}^{TP}}=\frac{1}{T} \sum_{t=1}^{T} PMAFE_{j,t,i}^{TP}
+\overline{PMAFE_{j,i}^{TP}}=\frac{1}{D} \sum_{t=1}^{D} PMAFE_{j,t,i}^{TP}
 \end{equation}
@@
 \end{equation}
-where $T$ are the number of trading days in a quarter and $N$ is the number of brokers with a valid TP.  Figure \ref{fig:example} shows an example.
+where $D$ are the number of trading days in a quarter and $N$ is the number of brokers with a valid TP.  Figure \ref{fig:example} shows an example.
 
@@
 \begin{equation}
+\label{eq-cv}
 CV_{i} = \frac{\sigma_i (FE_{i})}{\overline{FE}_{i}}
@@
 \subsection{Information sets to define the views}
-
+\label{inf-set}
 To proceed with the trading strategy, we need to establish which information we  will be using to build the rankings.
@@
 \label{q:true}
-\widehat{Q_{.,t}}=Q_{.,t}
+\widehat{Q_{t}}=Q_{t}
 \end{equation}
@@
 \label{q:naive}
-\widehat{Q_{.,t}}=Q_{.,t-1}
+\widehat{Q_{t}}=Q_{t-1}
 \end{equation}
@@
 \label{q:default}
-\widehat{Q_{.,t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{.,t}
+\widehat{Q_{t}} = \frac{1}{T} \sum_{t=1}^{T} Q_{t}
 \end{equation}
@@
 \end{itemize}
-where the $.$ subscript corresponds to either $Q_{cons,i}$ (eq. \ref{consq}) or $Q_{rank,i}$ (eq. \ref{rankq}), i.e. this is consensus or smart estimate.
+where $Q_{t}$ is the analysts' expected rank-weighted stock return (eq.
+\ref{rankq})\footnote{The  consensus returns ($Q_{cons}$) have equal weights among the analysts, and, thus, are not included information sets.
+However, since views also include the confidence (\ref{eq-cv}), which is based on analysts performance, we include the consensus returns to \naive{} and \default{} information sets.}.
 
@@
 
-Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[!is.na(b.view),.N,by=Broker][,.N]}, covering \Sexpr{q.data[!is.na(b.view),.N,by=Stock][,.N]} S\&P500 stocks.
+Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[,.N,by=.(Broker,type)][,.N,by=type][,N][2]}, covering \Sexpr{q.data[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks.
 Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
@@
 
-Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view,na.rm=T)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view,na.rm=T)]}).
+Consistent with other studies on analysts' expected returns that work with price targets  \citep{bradshaw2002,brav2003,da2011}, we truncate the sample of $TP/P-1$ at the \Sexpr{ trunk.percent *100}\textsuperscript{th} percentile (values below \Sexpr{q.data[,min(trunk.view)]}) and at the \Sexpr{(1-trunk.percent)*100}\textsuperscript{th} percentile (values above \Sexpr{ q.data[,max(trunk.view)]}).
 This is done due to occurrence of the extreme values.
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N], big.mark=' ')} to \Sexpr{ prettyNum(q.data[!is.na(trunk.view),.N],big.mark=' ')}.
-
-The initial file of quarterly EPS forecast consists of  \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
-To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
-In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=Broker][,.N]} brokers covering \Sexpr{complete.dt[,.N,by=Stock][,.N]} stocks.
-The total number of observation is \Sexpr{prettyNum(complete.dt[,.N],big.mar=' ')}.
+To implement ranking, we require that a stock had at least three brokers per quarter and that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
+After all the  data requirements, our final sample number of brokers issued target prices is \Sexpr{core.dt[,.N,by=.(Broker,type)][,.N,by=type][,N][2]} covering \Sexpr{core.dt[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks.
+Overall, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from \Sexpr{ prettyNum(q.data[,.N,by=type][,N][2], big.mark=' ')} (initial) to \Sexpr{ prettyNum(core.dt[,.N,by=type][,N][2],big.mark=' ')} (filtered).
+
+In the case of EPS forecasts, the initial file of quarterly EPS forecast consists of \Sexpr{eps.dt[,.N,by=.(Broker)][,.N]} brokers covering \Sexpr{eps.dt[,.N,by=Stock][,.N]} stocks.
+Considering the ranking data requirement, our final sample of EPS forecasts consist of  \Sexpr{complete.dt[,.N,by=.(Broker,type)][,.N,by=type][,N][2]} brokers covering \Sexpr{complete.dt[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks.
+The total number of observation is \Sexpr{prettyNum(complete.dt[,.N,by=type][,N][2],big.mar=' ')}.
+
+Given that we have two different ranking datasets (based on TP and EPS), we, further, consider S\&P500 stocks that are part of both datasets.
+We call this subset of stocks as the \same{} and the full set of S\&P500 stocks as the \all{}.
 
@@
 Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report \Sexpr{prettyNum(core.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-Each stock had on average of \Sexpr{core.dt[,.N,by=list(Stock,q.id)][,mean(N)]} quarterly target price reports.
+For the sample period (1999-2009), we report that each stock in the \same{} and the \all{} stock sets had on average of \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{core.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively, quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has \Sexpr{prettyNum(complete.dt[,.N,by=list(Stock,q.id)][,.N],big.mark=' ')} stock-quarter observations.
-The average number of quarterly forecasts is \Sexpr{complete.dt[,.N,by=list(Stock,q.id)][,mean(N)]}.
+The average number of quarterly forecasts for the  \same{} and the \all{} is \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][1]} and \Sexpr{complete.dt[,.N,by=list(Stock,q.id,type)][,mean(N),by=type][,V1][2]}, respectively.
 
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles.
-
-In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
+For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles\footnote{For the case of the \same{} stock set, the results of ranking consistency are similar to that of the \all{} stock set.}.
+
+In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year) in the \all{} stock set respectively.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, \Sexpr{test.a['Total',,'CONS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'CONS','mean','all'][[3]]*100}\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%).
-Panel C shows the EPS based weighted expected returns averages (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%).
-
-Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns.
+As mentioned above (sec.
+\ref{inf-set}), the consensus views have equal weights among the analysts; thus, for the case of \tr{} they are not existent and for cases of the \naive{} and the \default{}, they are equal as we use the last known $Q_{cons}$ (eq.
+\ref{consq}).
+Therefore, the average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets for the \all{} stock set is \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\% and for the \same{} stock set is \Sexpr{test.a['Total',,'CONS','mean','same'][[2]]*100 }\%
+
+Panel B of the table shows the TP accuracy weighted average expected returns for the \all{} stock sets (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%) and for the \same{} (\Sexpr{test.a['Total',,'PT','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','same'][[3]]*100}\%)
+
+Panel C shows the EPS based weighted expected returns averages for the \all{} set (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%) and for the \same{} stock set (\Sexpr{test.a['Total',,'EPS','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','same'][[3]]*100}\%)
+
+Overall compared to the consensus the ranked weighted expected returns (``smart estimates") are less optimistic.
+The \default{} information set shows the lowest values of expected returns among all information sets.
+For the different stock sets,  the \same{} set of stocks has higher values of expected returns compared to the \all{} stocks.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, \Sexpr{bl.results['CONS',1,1,'all']}\%, \Sexpr{bl.results['TP',1,1,'all']}\%, \Sexpr{bl.results['EPS',1,1,'all']}\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock set: \Sexpr{bl.results['TP',1,1,'all']}\% and  \Sexpr{bl.results['EPS',1,1,'all']}\% and, respectively, for the \same{} set of stocks: \Sexpr{bl.results['TP',1,1,'same']}\% and \Sexpr{bl.results['EPS',1,1,'same']}\%.
 All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
@@
 In any case, the results suggest that the advice of analysts, as a group, is valuable.
-%Yet, the top analyst
+%Yet the top analyst
 
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio for the \all{} (\same{}) stock set is \Sexpr{ bl.results['TP',1,'ann.sr','all']} (\Sexpr{ bl.results['TP',1,'ann.sr','same']}) against \Sexpr{ bl.results['EPS',1,'ann.sr','all']} (\Sexpr{ bl.results['EPS',1,'ann.sr','same']}), and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for  the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 \subsection{Feasible strategies}
-Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,'all']}\%)  and show positive cumulative annualized returns of \Sexpr{bl.results['TP',2,1,'all']}\%,  \Sexpr{bl.results['CONS',2,1,'all']}\%, \Sexpr{bl.results['EPS',2,1,'all']}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is \Sexpr{ bl.results['TP',2,'ann.sr','all']} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (\Sexpr{ bl.results['CONS',2,'ann.sr','all']} and \Sexpr{bl.results['EPS',2,'ann.sr','all']} respectively).
-The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
-
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (\Sexpr{bl.results['TP',3,1,'all']}\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (\Sexpr{bl.results['CONS',3,1,'all']}\% and \Sexpr{bl.results['EPS',3,1,'all']}\% respectively).
-The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,1]}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) set of stocks of \Sexpr{bl.results['TP',2,1,sets[1]]}\% (\Sexpr{bl.results['TP',2,1,sets[2]]}\%) and  \Sexpr{bl.results['CONS',2,1,sets[1]]}\% (\Sexpr{bl.results['CONS',2,1,sets[2]]}\%) respectively.
+The active strategy based on EPS forecasts, demonstrated negative annualized cumulative returns in both sets of stocks of  \Sexpr{bl.results['EPS',2,1,sets[1]]}\% and \Sexpr{bl.results['EPS',2,1,sets[2]]}\% for the \all{} and the \same{} respectively.
+
+The risk-adjusted results for this information sets shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy with Sharpe ratios for the \all{} stocks of \Sexpr{ bl.results['TP',2,'ann.sr',sets[1]]} and for the \same{} of \Sexpr{ bl.results['TP',2,'ann.sr',sets[2]]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[1]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[1]]} respectively for the \all{} set  and  of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[2]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[2]]} respectively for the \same{} set of stocks.
+The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods independent of stock sets.
+
+Panel D of table \ref{tab:strategy} demonstrates an interesting finding.
+On one hand, when consider \all{} set of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (\Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
+On the other hand, the result changes when consider \same{} set of stocks (\Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
+
+The analysis of the sub-periods performance of \textit{TP} and \textit{EPS} depicted in table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4 of \Sexpr{periods.array[1,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[1,'TP',3,2,1,1]*100}\%  in 2001Q1/2005Q4 of \Sexpr{periods.array[2,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[2,'TP',3,2,1,1]*100}\% respectively for the \textit{EPS} and \textit{TP}.
+For the rest  sup-periods, the annualized cumulative returns of the \textit{EPS} strategy have been constantly lower than that of the \textit{TP} strategy.
+This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s.
+Table \ref{tab:substrategy-same} shows the sub-period results when considered only the \same{} set of stock.
+In this setting, the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} in every sup-period.
+
+%The sub-period results analysis and the dominant out-performance of the \same{} set of stocks relative to the \all{} set can be attributed to the fact that \all{} set for the \textit{EPS} strategy included the stocks
 
@@
 
+Second, the results show that the values of the annualized cumulative return are higher in the \default{} information sets when compared with \naive{}.
+This suggests that analysts accumulate forecasting skills overtime which brings more value to investors rather than recent analyst's performance that, presumably, takes advantage of the price momentum.
+
 %The results of trading strategies suggest that the dominant trading strategy is \textit{TP} strategy which is based on the accuracy of analsyts' TP reports.
@@
 The perfect foresight scenario (using the information know at time $t$) sets the upper bound of the trading strategies in terms of the maximum yield any such strategies could achieve.
-If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts.
+If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts considering a whole history of analysts performance.
 
@@
 \ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 
@@
     & \multicolumn{2}{c}{Min}&\multicolumn{2}{c}{Mean}& \multicolumn{2}{c}{Median}& \multicolumn{2}{c}{Max}&\multicolumn{2}{c}{Std.dev}\\
-&all&same&all&same&all&same&all&same&all&same\\
+&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}\\
 \midrule
@@
 For the EPS case, $PRED$ are the EPS forecasts issued by the analysts; $PMAFE^{EPS}$ is the proportional mean-adjusted forecast error of quarterly EPS forecasts.
+
 \begin{tabularx}{\linewidth}{r*{4}{Y}}
@@
 Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+
 \begin{tabularx}{\linewidth}{r*{10}{Y}}
@@
 &&\multicolumn{2}{c}{$top$}&\multicolumn{2}{c}{$middle$}&\multicolumn{2}{c}{$bottom$}&\multicolumn{2}{c}{$Sum$}\\
-&&all&same&all&same&all&same&all&same\\
+&&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}\\
 \midrule
@@
 \ This table shows the descriptive statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 
@@
 & \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
-&all&same&all&same&all&same\\
+&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}\\
 \midrule
@@
 \ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 
@@
 Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
-&all&same&all&same&all&same\\
+&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}\\
 <<stocks-true,echo=F,results='asis'>>=
@@
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
@@
   \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
-  &all&same&all&same&all&same&all&same&all&same \\
+  &\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same {}\\
 
@@
 \begin{table}[hp]
-  \caption{Trading strategies performance: sub-periods}
+  \caption{Trading strategies performance: sub-periods for the \all{} set of stocks}
   \label{tab:substrategy}
@@
 
-\begin{figure}[h]
+\begin{table}[hp]
+  \caption{Trading strategies performance: sub-periods for the  \same{} set of stocks}
+  \label{tab:substrategy-same}
+  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies for the \same{} set of stocks: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
+
+\resizebox{\textwidth}{!}{%
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+\begin{tabular}{rrrrrrrrr}
+\toprule
+Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\
+
+& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\
+
+<<sr-true-same,echo=F,results='asis'>>=
+periods.array[,,,,1,'same'] <- periods.array[,,,,1,'same']*100
+#results.final <- bl.results['Market',1,]
+#cat(paste(c('Period','\\textit{Market}','\\textit{CONS}','\\textit{TP}','\\textit{EPS}'), collapse = "&"),'\\\\')
+#cat('\\multicolumn{5}{l}{\\textbf{Panel A: Market}} \n')
+#print(xtable(periods.array[,c(4,1,2,3),1,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),1,'yes',c(1,4),'same']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,NA.string='-',include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel A: \\tr{}}} \\\\\n', '\\midrule \n')))
+
+@
+\midrule
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+<<sr-naive-same,echo=F,results='asis'>>=
+#print(xtable(periods.array[,c(4,1,2,3),2,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),2,'yes',c(1,4),'same']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{9}{l}{\\textbf{Panel B: \\naive{}}} \\\\\n', '\\midrule \n')))
+
+@
+\midrule
+\end{tabular}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+<<sr-default-same,echo=F,results='asis'>>=
+#print(xtable(periods.array[,c(4,1,2,3),3,'yes','sr'],display=c('s','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n')))
+
+print(xtable(acast(melt(periods.array[,c(4,1,2,3),3,'yes',c(1,4),'same']),Var1~Var2+Var3,value.var='value'),display=c('s','f','f','f','f','f','f','f','f'),digits=3),only.contents=T,include.colnames=F,hline.after=NULL, format.args=list(big.mark = " ", decimal.mark = "."),add.to.row=list(pos=list(0,6),command=c('\\multicolumn{5}{l}{\\textbf{Panel C: \\default{}}} \\\\\n','\\midrule \n')))
+@
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\begin{figure}[!ht]
 \begin{center}
@@
 
-\begin{figure}[h]
+\begin{figure}[!ht]
 \begin{center}
@@
 \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}

### 2015-04-08 doc/paper/paper-knitr-APS.tex
change text to include two stock sets (same and all). Send to APS

@@
 \usepackage{alltt}
+\usepackage[printfigures]{figcaps}
 \usepackage{fancyhdr}
@@
 In some cases the stock-splits and the dividends were not properly adjusted.}.
-After trimming, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 247 163 to 247 163.
-
-The initial file of quarterly EPS forecast consists of  560 brokers covering 3517 stocks.
-To implement the EPS ranking, we require that a stock had at least three brokers per quarter.
-In addition, we require that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
-Our final sample of EPS forecasts consist of  157 brokers covering 402 stocks.
-The total number of observation is 158 029.
+To implement ranking, we require that a stock had at least three brokers per quarter and that a broker has to be active in covering a particular stock for at least 3 years (12 quarters).
+After all the  data requirements, our final sample number of brokers issued target prices is 158 covering 448 S\&P500 stocks.
+Overall, the number of observations ($\mathrm{Stock} \times \mathrm{Broker} \times  \mathrm{Quarter}$) is reduced  from 131 068 (initial) to 100 974 (filtered).
+
+In the case of EPS forecasts, the initial file of quarterly EPS forecast consists of 560 brokers covering 3517 stocks.
+Considering the ranking data requirement, our final sample of EPS forecasts consist of  157 brokers covering 402 S\&P500 stocks.
+The total number of observation is 80 185.
+
+Given that we have two different ranking datasets (based on TP and EPS), we, further, consider S\&P500 stocks that are part of both datasets.
+We call this subset of stocks as the \same{} and the full set of S\&P500 stocks as the \all{}.
 
@@
 Panel A shows the number of quarterly target prices per stock.
-For the sample period (1999-2009), we report 15 048 stock-quarter observations.
-Each stock had on average of 12.823 quarterly target price reports.
+For the sample period (1999-2009), we report that each stock in the \same{} and the \all{} stock sets had on average of 6.915 and 6.71, respectively, quarterly target price reports.
 Panel B  presents similar statistics of the number of EPS forecasts.
-In total, the EPS forecast sample has 12 203 stock-quarter observations.
-The average number of quarterly forecasts is 12.95.
+The average number of quarterly forecasts for the  \same{} and the \all{} is 6.563 and 6.571, respectively.
 
@@
 We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter.
-Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.58\% (69.37\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles.
-
-In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year)  respectively.
+For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.58\% (69.37\%) remain in that same tercile after one quarter.
+After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles\footnote{For the case of the \same{} stock set, the results of ranking consistency are similar to that of the \all{} stock set.}.
+
+In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year) in the \all{} stock set respectively.
 
@@
 (\ref{consq}).
-The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.61\%, and 18.61\% respectively.
-Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.742\%, and 12.459\%).
-Panel C shows the EPS based weighted expected returns averages (14.689\%, 14.884\%, and 12.843\%).
-
-Overall compared to the consensus the ranked weighted expected returns (smart estimates) are less optimistic. The \default{} information set shows higher values of expected returns.
+As mentioned above (sec.
+\ref{inf-set}), the consensus views have equal weights among the analysts; thus, for the case of \tr{} they are not existent and for cases of the \naive{} and the \default{}, they are equal as we use the last known $Q_{cons}$ (eq.
+\ref{consq}).
+Therefore, the average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets for the \all{} stock set is 18.61\% and for the \same{} stock set is 18.985\%
+
+Panel B of the table shows the TP accuracy weighted average expected returns for the \all{} stock sets (14.876\%, 15.742\%, and 12.459\%) and for the \same{} (15.191\%, 16.102\%, and 12.714\%)
+
+Panel C shows the EPS based weighted expected returns averages for the \all{} set (14.689\%, 14.884\%, and 12.843\%) and for the \same{} stock set (14.769\%, 14.959\%, and 12.916\%)
+
+Overall compared to the consensus the ranked weighted expected returns (``smart estimates") are less optimistic.
+The \default{} information set shows the lowest values of expected returns among all information sets.
+For the different stock sets,  the \same{} set of stocks has higher values of expected returns compared to the \all{} stocks.
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.325\%, 0.574\%.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock set: 4.325\% and  0.574\% and, respectively, for the \same{} set of stocks: 4.549\% and 0.719\%.
 All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio is 0.294 against NA, 0.037, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies.
+The Sharpe Ratio for the \all{} (\same{}) stock set is 0.294 (0.307) against 0.037 (0.046), and \ensuremath{-0.182}, respectively for  the \textit{EPS}, and the \textit{Market} strategies.
 In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
@@
 \subsection{Feasible strategies}
-Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set.
-As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.282\%,  0.116\%, \ensuremath{-0.303}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies.
-Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns.
-The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.007 and \ensuremath{-0.019} respectively).
-The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.
-
-Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.689\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.314\% and 0.746\% respectively).
-The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).
+Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) set of stocks of 0.282\% (0.621\%) and  0.116\% (0.434\%) respectively.
+The active strategy based on EPS forecasts, demonstrated negative annualized cumulative returns in both sets of stocks of  \ensuremath{-0.303}\% and \ensuremath{-0.349}\% for the \all{} and the \same{} respectively.
+
+The risk-adjusted results for this information sets shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy with Sharpe ratios for the \all{} stocks of 0.018 and for the \same{} of 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of 0.007 and \ensuremath{-0.019} respectively for the \all{} set  and  of 0.027 and \ensuremath{-0.022} respectively for the \same{} set of stocks.
+The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods independent of stock sets.
+
+Panel D of table \ref{tab:strategy} demonstrates an interesting finding.
+On one hand, when consider \all{} set of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (0.746\%, 0.689\%, 0.314\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
+On the other hand, the result changes when consider \same{} set of stocks (1.056\%, 0.717\%, 0.686\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
+
+The analysis of the sub-periods performance of \textit{TP} and \textit{EPS} depicted in table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4 of 3.501\% and 3.133\%  in 2001Q1/2005Q4 of 3.954\% and 3.727\% respectively for the \textit{EPS} and \textit{TP}.
+For the rest  sup-periods, the annualized cumulative returns of the \textit{EPS} strategy have been constantly lower than that of the \textit{TP} strategy.
+This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s.
+Table \ref{tab:substrategy-same} shows the sub-period results when considered only the \same{} set of stock.
+In this setting, the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} in every sup-period.
+
+%The sub-period results analysis and the dominant out-performance of the \same{} set of stocks relative to the \all{} set can be attributed to the fact that \all{} set for the \textit{EPS} strategy included the stocks
 
@@
 Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
-&all&same&all&same&all&same\\
+&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}\\
   \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
@@
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 The trading period goes from 2000Q1 until 2009Q4.
@@
 
-\begin{figure}[h]
+\begin{table}[hp]
+  \caption{Trading strategies performance: sub-periods for the  \same{} set of stocks}
+  \label{tab:substrategy-same}
+  \ This table presents the annualized return (in \%) and the Sharpe ratio of each of the trading strategies for the \same{} set of stocks: the passive (\textit{Market}) and the active (consensus and smart estimates) calculated for different holding periods.
+Panel A represents the perfect foresight information set; panels B and C show, respectively, the results of the strategies using the most recent and all history analysts' performance.
+
+\resizebox{\textwidth}{!}{%
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+\begin{tabular}{rrrrrrrrr}
+\toprule
+Period&\multicolumn{2}{c}{\textit{Market}}&\multicolumn{2}{c}{\textit{CONS}}&\multicolumn{2}{c}{\textit{TP}}&\multicolumn{2}{c}{\textit{EPS}} \\
+
+& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR& Ann.ret&SR\\
+
+  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
+2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 6.609 & 0.451 & 2.116 & 0.139 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.226 & 0.432 & 4.161 & 0.286 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 8.985 & 0.768 & 5.827 & 0.486 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.249 & 1.891 & 10.672 & 1.361 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.398 & 0.030 & -3.126 & -0.232 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.528 & 0.166 & -0.658 & -0.041 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & - & - & 4.549 & 0.307 & 0.719 & 0.046 \\
+
+\midrule
+\end{tabular}}
+
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.378 & 0.213 & 3.331 & 0.216 & 1.073 & 0.067 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.825 & 0.180 & 3.523 & 0.231 & 2.598 & 0.167 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.836 & 0.468 & 6.218 & 0.516 & 5.436 & 0.450 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.417 & 1.100 & 9.972 & 1.244 & 9.325 & 1.153 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.252 & -0.311 & -4.552 & -0.332 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.426 & -0.148 & -2.019 & -0.124 & -1.752 & -0.105 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.434 & 0.027 & 0.621 & 0.040 & -0.349 & -0.022 \\
+
+\midrule
+\end{tabular}}
+\resizebox{\textwidth}{!}{%
+\begin{tabular}{rrrrrrrrr}
+%\begin{tabularx}{\linewidth}{r*{9}{Y}}
+  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.909 & 0.250 & 3.852 & 0.257 & 3.470 & 0.230 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 3.254 & 0.210 & 4.014 & 0.271 & 3.919 & 0.261 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.461 & 0.433 & 5.915 & 0.488 & 5.686 & 0.465 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.297 & 1.067 & 10.199 & 1.253 & 9.988 & 1.199 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.979 & -0.364 & -4.091 & -0.299 & -4.241 & -0.310 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.437 & -0.150 & -1.665 & -0.102 & -1.963 & -0.122 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.686 & 0.043 & 1.056 & 0.068 & 0.717 & 0.046 \\
+
+\bottomrule
+\end{tabular}}
+\end{table}
+
+\begin{figure}[!ht]
 \begin{center}
@@
 \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
+Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
 The trading period ranges from 2000Q1 until 2009Q4

### 2015-04-13 doc/paper/paper-knitr-APS.Rnw
Submitted paper to APS with her comments on Apr.10th.

@@
 \documentclass{article}
-\usepackage[printfigures]{figcaps}
+%\usepackage[printfigures]{figcaps}
+\usepackage[nolists,tablesfirst,nomarkers]{endfloat}
 \usepackage{fancyhdr}
@@
 % Be sure to remove \thispagestyle{fancy} as well after the \maketitle.
-%\pagestyle{empty}
-\pagestyle{fancy}
-
-\newcommand\myTime{\now}
-\fancyhead{}
-\fancyhead[CO, CE]{\texttt{-Draft-}}
-\fancyhead[RO, RE]{\texttt{\today, \myTime}}
-\setlength{\headheight}{2\baselineskip}
-\renewcommand{\headrulewidth}{0pt}
+%%\pagestyle{empty}
+%\pagestyle{fancy}
+
+% \newcommand\myTime{\now}
+% \fancyhead{}
+% \fancyhead[CO, CE]{\texttt{-Draft-}}
+% \fancyhead[RO, RE]{\texttt{\today, \myTime}}
+% \setlength{\headheight}{2\baselineskip}
+% \renewcommand{\headrulewidth}{0pt}
 %-------------------------------------------------------------------------
@@
 test.a <- acast(test,year~Method~Strategy~variable~type,value.var = 'value')
-test.a[,'true','CONS',,] <- NA
+#test.a[,'true','CONS',,] <- NA
 
@@
 
-bl.results['CONS','true',,] <- NA
+#bl.results['CONS','true',,] <- NA
 
@@
 periods.array <- acast(melt(periods,id.vars = c('Views','Method','period','strat','type')),period~Views~Method~strat~variable~type,value.var = 'value')
-periods.array[,'CONS','true',,,] <- NA
+#periods.array[,'CONS','true',,,] <- NA
 
@@
 Several institutions issue rankings based on the accuracy of price and EPS forecasts.
-Given that these rankings are \textit{ex-post} they may not be able useful to investors.
+Given that these rankings are \textit{ex-post} they may not be useful to investors.
 In this paper  we show that trading strategies based on perfect foresight and past rankings outperform a passive strategy.
@@
 For example, \cite{bradshaw2004} suggests that analysts' EPS forecasts are consistent with their price targets and that analysts use growth models based on EPS forecasts to estimate stocks target prices.
-Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets.
-\footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}
+Differently, \cite{simon2011} argue that the most accurate analysts rely on more complex models in setting their price targets\footnote{A further major development in the theoretical accounting literature on equity valuation models is the abnormal earnings growth (AEG) model of \cite{ohlson2005}, which relates share price to the level of expected earnings per share.}.
 
@@
 
-We define a trading strategy as follows (figure \ref{fig:bl}):
+We define a trading strategy as follows (Figure \ref{fig:bl}):
 \begin{enumerate}
@@
 This represents the perfect foresight strategy.
+The perfect foresight refers to analyst rankings not stock prices.
 Therefore, it serves a performance reference point to evaluate the other trading strategies.
@@
 \end{itemize}
-where $Q_{t}$ is the analysts' expected rank-weighted stock return (eq.
-\ref{rankq})\footnote{The  consensus returns ($Q_{cons}$) have equal weights among the analysts, and, thus, are not included information sets.
-However, since views also include the confidence (\ref{eq-cv}), which is based on analysts performance, we include the consensus returns to \naive{} and \default{} information sets.}.
+where $Q_{t}$ is the analysts' expected rank-weighted stock return (eq. \ref{rankq})
 
@@
 Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is \Sexpr{q.data[,.N,by=.(Broker,type)][,.N,by=type][,N][2]}, covering \Sexpr{q.data[,.N,by=.(Stock,type)][,.N,by=type][,N][2]} S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+Given the fact that financial analysts commonly issue TP with the one year horizon\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
 After one year we assume that TP recommendation expires.
@@
 Given that we have two different ranking datasets (based on TP and EPS), we, further, consider S\&P500 stocks that are part of both datasets.
-We call this subset of stocks as the \same{} and the full set of S\&P500 stocks as the \all{}.
-
-Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data.
+We call this sample of stocks as the \same{} and the full sample of S\&P500 stocks as the \all{}.
+
+Table \ref{tab:ret-stat} shows the distribution of the final sample of target price and EPS data.
 Panel A shows the number of quarterly target prices per stock.
@@
 
-Table \ref{tab:example} and figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}.
+Table \ref{tab:example} and Figure \ref{fig:example} illustrate an example illustrate how we estimate the \textit{PMAFE}.
 Four analysts had valid target prices for Amazon for second quarter of 1999.
@@
 
-Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
+Table \ref{tab:rank-stat} shows a contingency analysis of the ranks. 
 %Chi square statistics include/ expected frequiency test
@@
 For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter \Sexpr{pt.cont.tab[1,1,1,1]*100}\% (\Sexpr{pt.cont.tab[3,3,1,1]*100}\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles\footnote{For the case of the \same{} stock set, the results of ranking consistency are similar to that of the \all{} stock set.}.
-
-In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles after one quarter (year) in the \all{} stock set respectively.
+After one year the corresponding figures are lower respectively \Sexpr{pt.cont.tab[1,1,1,2]*100}\% and \Sexpr{pt.cont.tab[3,3,1,2]*100}\% for the top and bottom terciles\footnote{For the case of the \same{} stock sample, the results of ranking consistency analysis are similar.}.
+
+In the case of EPS ranking  (panel B) \Sexpr{eps.cont.tab[1,1,1,1]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,1]*100}\% ( \Sexpr{eps.cont.tab[1,1,1,2]*100}\% and  \Sexpr{eps.cont.tab[3,3,1,2]*100}\%) of the analysts  remained in the top and bottom terciles, respectively,  after one quarter (year) in the \all{} stock samples.
 
@@
 
-Tables \ref{tab:view-stat} present the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
+Table \ref{tab:view-stat} presents the descriptive statistics of the analysts' expected returns conditional on the different information sets. 
 %Panel A shows the expected returns based on the analysts consensus and Panel B and C are based on the smart estimates (TP and EPS).
@@
 
-Panel A show the statistics for the consensus expectations as defined in eq.
+Panel A of Table \ref{tab:view-stat} show the statistics for the consensus expectations as defined in eq.
 (\ref{consq}).
 As mentioned above (sec.
-\ref{inf-set}), the consensus views have equal weights among the analysts; thus, for the case of \tr{} they are not existent and for cases of the \naive{} and the \default{}, they are equal as we use the last known $Q_{cons}$ (eq.
-\ref{consq}).
-Therefore, the average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets for the \all{} stock set is \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\% and for the \same{} stock set is \Sexpr{test.a['Total',,'CONS','mean','same'][[2]]*100 }\%
-
-Panel B of the table shows the TP accuracy weighted average expected returns for the \all{} stock sets (\Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%) and for the \same{} (\Sexpr{test.a['Total',,'PT','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','same'][[3]]*100}\%)
-
-Panel C shows the EPS based weighted expected returns averages for the \all{} set (\Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%) and for the \same{} stock set (\Sexpr{test.a['Total',,'EPS','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','same'][[3]]*100}\%)
+\ref{inf-set}), the consensus views have equal weights among the analysts, regardless of their ranks; thus, for the case of \tr{}, \naive{}, and \default{, the mean is the same regardless of knowing or not the present or past rankings ($Q_{cons}$ (eq.
+\ref{consq})).
+As such, the mean, median, and standard deviation in the \tr{}, \naive{}, and \default{} information sets are the same.
+For the sample of \all{} stocks the mean expected return is \Sexpr{test.a['Total',,'CONS','mean','all'][[2]]*100 }\%.
+However, since views also include the confidence (eq.
+\ref{eq-cv}), which is based on analysts past performance, the results of the trading strategy based on consensus expectations will be different for the \naive{} and \default{} information sets.
+
+%and for the \same{} sample of stocks the mean is \Sexpr{test.a['Total',,'CONS','mean','same'][[2]]*100 }\%.
+
+Panel B of the table shows the TP accuracy weighted average expected returns.
+For the sample of \all{} stocks the weighted average returns for \tr{}, \naive{}, and \default{} information sets are respectively \Sexpr{test.a['Total',,'PT','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','all'][[3]]*100}\%.
+
+%and for the \same{} (\Sexpr{test.a['Total',,'PT','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'PT','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'PT','mean','same'][[3]]*100}\%)
+
+Panel C shows the EPS based weighted expected return.
+The average return for the \tr{}, \naive{}, and \default{} information sets are respectively \Sexpr{test.a['Total',,'EPS','mean','all'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','all'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','all'][[3]]*100}\%.
+
+The statistics for the subsample of stocks that integrate both the TP of the EPS samples are similar.
+
+%and for the \same{} stock sample (\Sexpr{test.a['Total',,'EPS','mean','same'][[1]]*100 }\%, \Sexpr{test.a['Total',,'EPS','mean','same'][[2]]*100 }\%, and \Sexpr{test.a['Total',,'EPS','mean','same'][[3]]*100}\%)
 
@@
 The \default{} information set shows the lowest values of expected returns among all information sets.
-For the different stock sets,  the \same{} set of stocks has higher values of expected returns compared to the \all{} stocks.
+For the different stock sets,  the \same{} sample of stocks has higher values of expected returns compared to the \all{} stocks.
 
@@
 
-We report the results from different trading strategies in table (\ref{tab:strategy}).
+We report the results from different trading strategies in Table \ref{tab:strategy}.
 We split the table into four panels.
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock set: \Sexpr{bl.results['TP',1,1,'all']}\% and  \Sexpr{bl.results['EPS',1,1,'all']}\% and, respectively, for the \same{} set of stocks: \Sexpr{bl.results['TP',1,1,'same']}\% and \Sexpr{bl.results['EPS',1,1,'same']}\%.
-All the strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
-The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
-In any case, the results suggest that the advice of analysts, as a group, is valuable.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock sample: \Sexpr{bl.results['TP',1,1,'all']}\% and  \Sexpr{bl.results['EPS',1,1,'all']}\%.
+For the \same{} sample of stocks these are respectively \Sexpr{bl.results['TP',1,1,'same']}\% and \Sexpr{bl.results['EPS',1,1,'same']}\%.
+The two smart strategies outperform the passive benchmark (\Sexpr{bl.results['Market',1,1,'all']}\%).
+The consensus strategy annualized returns for the \all{} and the \same{} sample of stocks are respectively   \Sexpr{bl.results['CONS',1,1,'all']}\% and  \Sexpr{bl.results['CONS',1,1,'same']}\%
+
+The results show, as expected, that  investors would better off if they knew in advance who the top analysts in terms of TP or EPS accuracy would be.
+In any case, the results suggest that the advices of analysts, as a group, are valuable.
 %Yet the top analyst
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio for the \all{} (\same{}) stock set is \Sexpr{ bl.results['TP',1,'ann.sr','all']} (\Sexpr{ bl.results['TP',1,'ann.sr','same']}) against \Sexpr{ bl.results['EPS',1,'ann.sr','all']} (\Sexpr{ bl.results['EPS',1,'ann.sr','same']}), and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for  the \textit{EPS}, and the \textit{Market} strategies.
-In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
+The Sharpe Ratio for the \all{} (\same{}) stock sample is \Sexpr{ bl.results['TP',1,'ann.sr','all']} against \Sexpr{ bl.results['EPS',1,'ann.sr','all']}, \Sexpr{ bl.results['CONS',1,'ann.sr','all']}, and \Sexpr{ bl.results['Market',1,'ann.sr','all']}, respectively for  the \textit{EPS}, \textit{CONS} and the \textit{Market} strategies.
+In addition, the \textit{TP} strategy dominates  the others if we consider the shorter trading periods (5 years).
 Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-The \textit{TP} strategy wins over the others in every period as expected.
+The \textit{TP} strategy wins over the others in every period.
+The results for the subsample of stocks that integrate both the TP of the EPS datasets are similar.
 
@@
 \subsection{Feasible strategies}
-Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
-The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,1]}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) set of stocks of \Sexpr{bl.results['TP',2,1,sets[1]]}\% (\Sexpr{bl.results['TP',2,1,sets[2]]}\%) and  \Sexpr{bl.results['CONS',2,1,sets[1]]}\% (\Sexpr{bl.results['CONS',2,1,sets[2]]}\%) respectively.
-The active strategy based on EPS forecasts, demonstrated negative annualized cumulative returns in both sets of stocks of  \Sexpr{bl.results['EPS',2,1,sets[1]]}\% and \Sexpr{bl.results['EPS',2,1,sets[2]]}\% for the \all{} and the \same{} respectively.
-
-The risk-adjusted results for this information sets shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy with Sharpe ratios for the \all{} stocks of \Sexpr{ bl.results['TP',2,'ann.sr',sets[1]]} and for the \same{} of \Sexpr{ bl.results['TP',2,'ann.sr',sets[2]]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[1]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[1]]} respectively for the \all{} set  and  of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[2]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[2]]} respectively for the \same{} set of stocks.
-The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods independent of stock sets.
-
-Panel D of table \ref{tab:strategy} demonstrates an interesting finding.
-On one hand, when consider \all{} set of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (\Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
-On the other hand, the result changes when consider \same{} set of stocks (\Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
-
-The analysis of the sub-periods performance of \textit{TP} and \textit{EPS} depicted in table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4 of \Sexpr{periods.array[1,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[1,'TP',3,2,1,1]*100}\%  in 2001Q1/2005Q4 of \Sexpr{periods.array[2,'EPS',3,2,1,1]*100}\% and \Sexpr{periods.array[2,'TP',3,2,1,1]*100}\% respectively for the \textit{EPS} and \textit{TP}.
-For the rest  sup-periods, the annualized cumulative returns of the \textit{EPS} strategy have been constantly lower than that of the \textit{TP} strategy.
-This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s.
-Table \ref{tab:substrategy-same} shows the sub-period results when considered only the \same{} set of stock.
-In this setting, the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} in every sup-period.
+Panel C of Table \ref{tab:strategy} shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
+We report the results of forming portfolios with the available stocks within each dataset (\all{}) and the subsample of stocks that include both the TP or the EPS datasets (\same{}).
+
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\Sexpr{bl.results['Market',2,1,1]}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) sample of stocks of \Sexpr{bl.results['TP',2,1,sets[1]]}\% (\Sexpr{bl.results['TP',2,1,sets[2]]}\%) and  \Sexpr{bl.results['CONS',2,1,sets[1]]}\% (\Sexpr{bl.results['CONS',2,1,sets[2]]}\%) respectively.
+The active strategy based on EPS forecasts, has negative annualized cumulative returns of  \Sexpr{bl.results['EPS',2,1,sets[1]]}\% and \Sexpr{bl.results['EPS',2,1,sets[2]]}\% for the \all{} and the \same{} samples respectively.
+
+The risk-adjusted results for this information set shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy regardless of forming portfolios with \all{} stocks or with the \same{} subsample.
+%Sharpe ratios for the \all{} stocks of \Sexpr{ bl.results['TP',2,'ann.sr',sets[1]]} and for the \same{} of \Sexpr{ bl.results['TP',2,'ann.sr',sets[2]]} which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[1]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[1]]} respectively for the \all{} sample  and  of \Sexpr{ bl.results['CONS',2,'ann.sr',sets[2]]} and \Sexpr{bl.results['EPS',2,'ann.sr',sets[2]]} respectively for the \same{} sample of stocks.
+The results in panel B of Table \ref{tab:substrategy} show as well that this strategy outperforms the others for all of the shorter trading periods.
+
+Panel D of Table \ref{tab:strategy} shows interesting and slightly different findings.
+On one hand, when all the analyst forecast performance track record is included to set the rankings, we observe an increase in annualized cumulative returns and risk-adjusted returns for the smart strategies.
+Particularly in the case of the EPS strategy, the results suggest that strategies that weight the estimates with accuracy rankings obtained using more information show better performance: when we consider the \all{} sample of stocks, the strategy based on the accuracy of EPS forecasts outperforms the other strategies (annualized cumulative returns of \Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS}).
+The TP strategy dominates when we consider the subsample of stocks that are included in both the TP and EPS datasets (\Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\% respectively for the \textit{EPS}, \textit{TP} and \textit{CONS} strategies) but the returns and risk-adjusted improve as well when compared to the figures in Panel C.
+
+%On one hand, when consider \all{} sample of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (\Sexpr{bl.results['EPS',3,1,sets[1]]}\%, \Sexpr{bl.results['TP',3,1,sets[1]]}\%, \Sexpr{bl.results['CONS',3,1,sets[1]]}\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
+On the other hand, the result changes when consider \same{} sample of stocks (\Sexpr{bl.results['TP',3,1,sets[2]]}\%, \Sexpr{bl.results['EPS',3,1,sets[2]]}\%, \Sexpr{bl.results['CONS',3,1,sets[2]]}\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
+
+The analysis of the sub-periods performance of the \textit{TP} and \textit{EPS} -based strategies depicted in Table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4  \Sexpr{periods.array[1,'EPS',3,2,1,1]*100}\% vs.
+\Sexpr{periods.array[1,'TP',3,2,1,1]*100}\%  in 2001Q1/2005Q4 \Sexpr{periods.array[2,'EPS',3,2,1,1]*100}\%  vs.
+\Sexpr{periods.array[2,'TP',3,2,1,1]*100}\% respectively for the \textit{EPS} and the \textit{TP} strategies.
+For the all the other sup-periods, the annualized cumulative returns of the \textit{EPS} strategy are lower than those of the \textit{TP} strategy.
+%This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s. 
+Table \ref{tab:substrategy-same} shows the sub-period results when we consider only the sample of stocks that integrates the TP and EPS dataset.
+In this setting (\same{}), the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} strategies in every sub-period.
 
@@
 Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for  the passive and smart strategies in all the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} of \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)} of \Sexpr{end.year}.
-Figures show that strategies under the \tr{} panel outperform the \emph{Market} and that final value  of the portfolio of the TP strategy considerably outruns the other alternative strategies.
-
-In sum the results of  feasible information sets outlined above suggest that  it is worth to follow the top analysts and are supportive of \cite{desai2000ass} in that rankings are useful for investors.
-
-Second, the results show that the values of the annualized cumulative return are higher in the \default{} information sets when compared with \naive{}.
+The $y$-axis is the dollar value of wealth and the $x$-axis is the time starting at \Sexpr{ months(as.Date(final.bl[,head(Quarters,1)]))} \Sexpr{start.year } and ending at \Sexpr{ months(as.Date(final.bl[,tail(Quarters,1)])+91)}  \Sexpr{end.year}.
+The active investment management strategies in the \tr{} panel outperform the \emph{Market} and the final value  of the portfolio of the \textit{TP} strategy is well above those of the other alternative strategies.
+
+In sum the results of the feasible information sets outlined above suggest that  it is worthwhile to follow the analysts, particularly the top ranked analysts, and are supportive of \cite{desai2000ass} in that smart strategies based upon analyst accuracy rankings are beneficial for investors.
+
+Further the results show that the values of the annualized cumulative returns are higher in the \default{} information set when compared with those yield by the strategies that use only the most \naive{} ranking information set.
+This seems to suggest that investors should estimate analysts forecasting skills over a long period of time rather than focusing on the most recent analyst accuracy performance.
+
+%Second, the results show that the values of the annualized cumulative return are higher in the \default{} information sets when compared with \naive{}.
 This suggests that analysts accumulate forecasting skills overtime which brings more value to investors rather than recent analyst's performance that, presumably, takes advantage of the price momentum.
@@
 
-Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that good at forecasting EPS.
-This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that the stock recommendations of the most accurate analysts are not based upon the simple valuation models.
+Finally, the results suggest that, from an investor's point of view, following analysts who are accurate in setting price targets is more valuable than following those that are good at forecasting EPS.
+This result contradicts the findings of \cite{bradshaw2004} and supports the argument of \cite{simon2011} that stock recommendations of the most accurate analysts are not based upon simple valuation models.
 
@@
 
-Some institutions, such as StarMine, rank financial analysts based on EPS and target price accuracy.
-These rankings are published and are relevant: stocks favored by top-ranked analysts will probably receive more attention from investors.
-Therefore, there is a growing interest in understanding the relative performance of strategies based upon analysts forecasts.
-
-By applying the Black-Litterman model, we developed simulations of trading strategies using  different information sets.
-The perfect foresight scenario (using the information know at time $t$) sets the upper bound of the trading strategies in terms of the maximum yield any such strategies could achieve.
-If only the information known at time $t-1$ is used, investors would be better off following the strategy that weights more heavily the estimates given by the most accurate TP forecast analysts considering a whole history of analysts performance.
-
-%We report that under the \tr{} information (the information known at time $t$) about stock's expected return we get the upper bound of the trading strategies, .
-The \naive{} information (the information known at time $t-1$) create more value from the following the top-ranked analysts who set accurate stock price targets.
-%The \default{} information (the information known from the beginning up to $t-1$), because of its outdated nature, fails to show any positive outcomes and the passive strategy is the only choice for this information set.
-
-For the future work we will developed new methods to forecast analysts rankings so us to get closer to the upper bound.
+Some institutions, such as StarMine (ThomsonReuters), rank financial analysts based on EPS and target price accuracy.
+These rankings are published and are relevant: stocks favored by top ranked analysts will probably receive more attention from investors.
+Therefore, there is a growing interest in understanding the relative performance of strategies based upon analysts with different forecast accuracy.
+
+We use the Black-Litterman model.
+The views are TP or EPS rank-weighted means of analysts forecasted returns.
+We developed simulations of trading strategies using different information sets to compute the ranks.
+If we consider that only the information known prior to time $t$ is used to obtain the ranks, investors would be better off following the strategy that weights more heavily the estimates issued  by the most accurate TP forecast analysts and considering the whole performance tracking record of the of the analysts.
+
+For future work we will developed new methods to forecast analysts rankings so as to get closer to the upper bound of perfect foresight of rankings.
 
@@
 \ This table shows the average number of target prices  (panel A) and EPS forecasts (panel B) per stock per quarter.
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 
@@
 Panel A (Panel B) depicts the dynamics of the analysts' ranks  based on the accuracy in target prices (EPS forecasts).
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 
@@
 \ This table shows the descriptive statistics of views (expected returns) based on the consensus (median) among the analysts (panel A); target price rankings (panel B); and EPS forecasts rankings (panel C).
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 
@@
 \begin{table}[hp]
+\small\addtolength{\tabcolsep}{-2pt}
   \caption{Number of active stocks}
   \label{tab:stocks}
-\ This table shows number of active stocks in each of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+\ This table shows number of active stocks in each 
+of the trading strategies conditional on different information sets: \tr{} (panel A), \naive{} (panel B) and \default{} (panel C).
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 
@@
 #p.cum.ret <-
-ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Portfolio performance with $100 initial investment')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)+scale_x_date(breaks=date_breaks('2 years'),labels=date_format('%Y'))
+ggplot(final.bl,aes(x=as.Date(Quarters),y=cum.ret,group=Views,color=Views,shape=Views))+geom_line(size=0.5)+facet_grid(type~Method,scale='free_x')+ylab('Portfolio wealth (initial=$100)')+xlab('Quarters')+ggtitle('Cumulative portfolio wealth for all strategies')+theme_bw()+theme(plot.title = element_text(colour = "Black"),legend.position='top',legend.title=element_blank(),strip.text=element_text(size=20),text=element_text(size=20,family='Times'))+scale_color_grey()+geom_point()+geom_hline(yintercept=100)+scale_x_date(breaks=date_breaks('2 years'),labels=date_format('%Y'))
 #
@@
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 The trading period goes from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\begin{tabularx}{\linewidth}{c*{5}{Y}}
   \toprule
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  \multicolumn{11}{l}{\textbf{Panel B: \tr{} }} \\
   &\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same {}\\
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
+  \multicolumn{11}{l}{\textbf{Panel C: \naive{}}} \\
 <<bl-pt,echo=F,results='asis'>>=
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
+  \multicolumn{11}{l}{\textbf{Panel D: \default{}}} \\
 <<bl-eps,echo=F,results='asis'>>=
@@
 \begin{table}[hp]
-  \caption{Trading strategies performance: sub-periods for the \all{} set of stocks}
+  \caption{Trading strategies performance: sub-periods, \all{} sample}
   \label{tab:substrategy}
@@
 \begin{table}[hp]
-  \caption{Trading strategies performance: sub-periods for the  \same{} set of stocks}
+  \caption{Trading strategies performance: sub-periods, \same{} subsample}
   \label{tab:substrategy-same}
@@
 \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
-The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
+The trading period ranges from \Sexpr{gsub('[[:space:]]','',final.bl[,head(Quarters,1)])} until \Sexpr{gsub('[[:space:]]','',final.bl[,tail(Quarters,1)])}.
 \end{figure}

### 2015-04-13 doc/paper/paper-knitr-APS.tex
Submitted paper to APS with her comments on Apr.10th.

@@
 \usepackage{alltt}
-\usepackage[printfigures]{figcaps}
+%\usepackage[printfigures]{figcaps}
+\usepackage[nolists,tablesfirst,nomarkers]{endfloat}
 \usepackage{fancyhdr}
@@
 Over the sample period, the total number of brokers\footnote{We use words ``analyst" and ``broker" interchangeably.} in TP dataset is 351, covering 498 S\&P500 stocks.
-Given the fact that financial analysts commonly issue TP with the one year horizon \footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
+Given the fact that financial analysts commonly issue TP with the one year horizon\footnote{According to Wharton Research Data Services (WRDS), 92.33\% of all price targets reported in I/B/E/S have a 12-month horizon \citep{glushkov2009}.}, we assume that analysts keep their TP forecasts valid for one calendar year unless it is revised.
 After one year we assume that TP recommendation expires.
@@
 For the \all{} stocks,  of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.58\% (69.37\%) remain in that same tercile after one quarter.
-After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles\footnote{For the case of the \same{} stock set, the results of ranking consistency are similar to that of the \all{} stock set.}.
-
-In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles after one quarter (year) in the \all{} stock set respectively.
+After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles\footnote{For the case of the \same{} stock sample, the results of ranking consistency analysis are similar.}.
+
+In the case of EPS ranking  (panel B) 48.402\% and  28.63\% ( 46.687\% and  32.253\%) of the analysts  remained in the top and bottom terciles, respectively,  after one quarter (year) in the \all{} stock samples.
 
@@
 
-Panel A show the statistics for the consensus expectations as defined in eq.
+Panel A of Table \ref{tab:view-stat} show the statistics for the consensus expectations as defined in eq.
 (\ref{consq}).
 As mentioned above (sec.
-\ref{inf-set}), the consensus views have equal weights among the analysts; thus, for the case of \tr{} they are not existent and for cases of the \naive{} and the \default{}, they are equal as we use the last known $Q_{cons}$ (eq.
-\ref{consq}).
-Therefore, the average consensus among the analysts on stock expected returns in the  \naive{} and \default{} information sets for the \all{} stock set is 18.61\% and for the \same{} stock set is 18.985\%
-
-Panel B of the table shows the TP accuracy weighted average expected returns for the \all{} stock sets (14.876\%, 15.742\%, and 12.459\%) and for the \same{} (15.191\%, 16.102\%, and 12.714\%)
-
-Panel C shows the EPS based weighted expected returns averages for the \all{} set (14.689\%, 14.884\%, and 12.843\%) and for the \same{} stock set (14.769\%, 14.959\%, and 12.916\%)
+\ref{inf-set}), the consensus views have equal weights among the analysts, regardless of their ranks; thus, for the case of \tr{}, \naive{}, and \default{, the mean is the same regardless of knowing or not the present or past rankings ($Q_{cons}$ (eq.
+\ref{consq})).
+As such, the mean, median, and standard deviation in the \tr{}, \naive{}, and \default{} information sets are the same.
+For the sample of \all{} stocks the mean expected return is 18.61\%.
+However, since views also include the confidence (eq.
+\ref{eq-cv}), which is based on analysts past performance, the results of the trading strategy based on consensus expectations will be different for the \naive{} and \default{} information sets.
+
+%and for the \same{} sample of stocks the mean is test.a['Total',,'CONS','mean','same'][[2]]*100 \%.
+
+Panel B of the table shows the TP accuracy weighted average expected returns.
+For the sample of \all{} stocks the weighted average returns for \tr{}, \naive{}, and \default{} information sets are respectively 14.876\%, 15.742\%, and 12.459\%.
+
+%and for the \same{} (test.a['Total',,'PT','mean','same'][[1]]*100 \%, test.a['Total',,'PT','mean','same'][[2]]*100 \%, and test.a['Total',,'PT','mean','same'][[3]]*100\%)
+
+Panel C shows the EPS based weighted expected return. The average return for the \tr{}, \naive{}, and \default{} information sets are respectively 14.689\%, 14.884\%, and 12.843\%.
+
+The statistics for the subsample of stocks that integrate both the TP of the EPS samples are similar.
+
+%and for the \same{} stock sample (test.a['Total',,'EPS','mean','same'][[1]]*100 \%, test.a['Total',,'EPS','mean','same'][[2]]*100 \%, and test.a['Total',,'EPS','mean','same'][[3]]*100\%)
 
@@
 Panel B presents the results for the case of the \tr{} information set.
-The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock set: 4.325\% and  0.574\% and, respectively, for the \same{} set of stocks: 4.549\% and 0.719\%.
-All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
-The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be.
-In any case, the results suggest that the advice of analysts, as a group, is valuable.
+The annualized cumulative returns for each of the active strategies (\textit{TP} and \textit{EPS}) are, respectively, for the \all{} stock sample: 4.325\% and  0.574\%.
+For the \same{} sample of stocks these are respectively 4.549\% and 0.719\%.
+The two smart strategies outperform the passive benchmark (\ensuremath{-3.032}\%).
+The consensus strategy annualized returns for the \all{} and the \same{} sample of stocks are respectively   0.116\% and  0.434\%
+
+The results show, as expected, that  investors would better off if they knew in advance who the top analysts in terms of TP or EPS accuracy would be.
+In any case, the results suggest that the advices of analysts, as a group, are valuable.
 %Yet the top analyst
@@
 The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns.
-The Sharpe Ratio for the \all{} (\same{}) stock set is 0.294 (0.307) against 0.037 (0.046), and \ensuremath{-0.182}, respectively for  the \textit{EPS}, and the \textit{Market} strategies.
-In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years).
+The Sharpe Ratio for the \all{} (\same{}) stock sample is 0.294 against 0.037, 0.007, and \ensuremath{-0.182}, respectively for  the \textit{EPS}, \textit{CONS} and the \textit{Market} strategies.
+In addition, the \textit{TP} strategy dominates  the others if we consider the shorter trading periods (5 years).
 Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods.
-The \textit{TP} strategy wins over the others in every period as expected.
+The \textit{TP} strategy wins over the others in every period.
+The results for the subsample of stocks that integrate both the TP of the EPS datasets are similar.
 
@@
 \subsection{Feasible strategies}
-Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
-The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) set of stocks of 0.282\% (0.621\%) and  0.116\% (0.434\%) respectively.
-The active strategy based on EPS forecasts, demonstrated negative annualized cumulative returns in both sets of stocks of  \ensuremath{-0.303}\% and \ensuremath{-0.349}\% for the \all{} and the \same{} respectively.
-
-The risk-adjusted results for this information sets shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy with Sharpe ratios for the \all{} stocks of 0.018 and for the \same{} of 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of 0.007 and \ensuremath{-0.019} respectively for the \all{} set  and  of 0.027 and \ensuremath{-0.022} respectively for the \same{} set of stocks.
-The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods independent of stock sets.
-
-Panel D of table \ref{tab:strategy} demonstrates an interesting finding.
-On one hand, when consider \all{} set of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (0.746\%, 0.689\%, 0.314\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
-On the other hand, the result changes when consider \same{} set of stocks (1.056\%, 0.717\%, 0.686\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
-
-The analysis of the sub-periods performance of \textit{TP} and \textit{EPS} depicted in table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4 of 3.501\% and 3.133\%  in 2001Q1/2005Q4 of 3.954\% and 3.727\% respectively for the \textit{EPS} and \textit{TP}.
-For the rest  sup-periods, the annualized cumulative returns of the \textit{EPS} strategy have been constantly lower than that of the \textit{TP} strategy.
-This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s.
-Table \ref{tab:substrategy-same} shows the sub-period results when considered only the \same{} set of stock.
-In this setting, the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} in every sup-period.
+Panel C of Table \ref{tab:strategy} shows the performance of the different smart strategies and the consensus strategy in the \naive{} information set.
+We report the results of forming portfolios with the available stocks within each dataset (\all{}) and the subsample of stocks that include both the TP or the EPS datasets (\same{}).
+
+The \textit{TP} and \textit{CONS} active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns for the \all{} (\same{}) sample of stocks of 0.282\% (0.621\%) and  0.116\% (0.434\%) respectively.
+The active strategy based on EPS forecasts, has negative annualized cumulative returns of  \ensuremath{-0.303}\% and \ensuremath{-0.349}\% for the \all{} and the \same{} samples respectively.
+
+The risk-adjusted results for this information set shows that, as in the case with the \tr{}, the dominant trading strategy is the \textit{TP} strategy regardless of forming portfolios with \all{} stocks or with the \same{} subsample.
+%Sharpe ratios for the \all{} stocks of  bl.results['TP',2,'ann.sr',sets[1]] and for the \same{} of  bl.results['TP',2,'ann.sr',sets[2]] which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies of  bl.results['CONS',2,'ann.sr',sets[1]] and bl.results['EPS',2,'ann.sr',sets[1]] respectively for the \all{} sample  and  of  bl.results['CONS',2,'ann.sr',sets[2]] and bl.results['EPS',2,'ann.sr',sets[2]] respectively for the \same{} sample of stocks.
+The results in panel B of Table \ref{tab:substrategy} show as well that this strategy outperforms the others for all of the shorter trading periods.
+
+Panel D of Table \ref{tab:strategy} shows interesting and slightly different findings.
+On one hand, when all the analyst forecast performance track record is included to set the rankings, we observe an increase in annualized cumulative returns and risk-adjusted returns for the smart strategies.
+Particularly in the case of the EPS strategy, the results suggest that strategies that weight the estimates with accuracy rankings obtained using more information show better performance: when we consider the \all{} sample of stocks, the strategy based on the accuracy of EPS forecasts outperforms the other strategies (annualized cumulative returns of 0.746\%, 0.689\%, 0.314\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS}).
+The TP strategy dominates when we consider the subsample of stocks that are included in both the TP and EPS datasets (0.717\%, 1.056\%, 0.686\% respectively for the \textit{EPS}, \textit{TP} and \textit{CONS} strategies) but the returns and risk-adjusted improve as well when compared to the figures in Panel C.
+
+%On one hand, when consider \all{} sample of stocks, the  strategy based on the accuracy of EPS forecasts  outperforms the strategies based on the target prices (bl.results['EPS',3,1,sets[1]]\%, bl.results['TP',3,1,sets[1]]\%, bl.results['CONS',3,1,sets[1]]\%, respectively for the \textit{EPS}, \textit{TP}, and \textit{CONS} strategies).
+On the other hand, the result changes when consider \same{} sample of stocks (bl.results['TP',3,1,sets[2]]\%, bl.results['EPS',3,1,sets[2]]\%, bl.results['CONS',3,1,sets[2]]\%, respectively for the \textit{TP}, \textit{EPS}, and \textit{CONS} strategies).
+
+The analysis of the sub-periods performance of the \textit{TP} and \textit{EPS} -based strategies depicted in Table \ref{tab:substrategy} shows that the latter outperforms the former in terms of the annualized cumulative return only for the first two periods: in  2000Q1/2004Q4  3.501\% vs.
+3.133\%  in 2001Q1/2005Q4 3.954\%  vs.
+3.727\% respectively for the \textit{EPS} and the \textit{TP} strategies.
+For the all the other sup-periods, the annualized cumulative returns of the \textit{EPS} strategy are lower than those of the \textit{TP} strategy.
+%This can imply that the quality of EPS forecasts have changed in response to the new SEC legislation that took place in the early 2000s. 
+Table \ref{tab:substrategy-same} shows the sub-period results when we consider only the sample of stocks that integrates the TP and EPS dataset.
+In this setting (\same{}), the \textit{TP} strategy dominates the \textit{EPS} and \text{CONS} strategies in every sub-period.
 
@@
 Figure \ref{fig:bl-results} shows the graphical representation of the cumulative portfolio wealth for  the passive and smart strategies in all the information sets.
-The $y$-axis is the monetary value of wealth and $x$-axis is the time starting at January of 2000 and ending at December of 2009.
-Figures show that strategies under the \tr{} panel outperform the \emph{Market} and that final value  of the portfolio of the TP strategy considerably outruns the other alternative strategies.
-
-In sum the results of  feasible information sets outlined above suggest that  it is worth to follow the top analysts and are supportive of \cite{desai2000ass} in that rankings are useful for investors.
-
-Second, the results show that the values of the annualized cumulative return are higher in the \default{} information sets when compared with \naive{}.
+The $y$-axis is the dollar value of wealth and the $x$-axis is the time starting at January 2000 and ending at December  2009.
+The active investment management strategies in the \tr{} panel outperform the \emph{Market} and the final value  of the portfolio of the \textit{TP} strategy is well above those of the other alternative strategies.
+
+In sum the results of the feasible information sets outlined above suggest that  it is worthwhile to follow the analysts, particularly the top ranked analysts, and are supportive of \cite{desai2000ass} in that smart strategies based upon analyst accuracy rankings are beneficial for investors.
+
+Further the results show that the values of the annualized cumulative returns are higher in the \default{} information set when compared with those yield by the strategies that use only the most \naive{} ranking information set.
+This seems to suggest that investors should estimate analysts forecasting skills over a long period of time rather than focusing on the most recent analyst accuracy performance.
+
+%Second, the results show that the values of the annualized cumulative return are higher in the \default{} information sets when compared with \naive{}.
 This suggests that analysts accumulate forecasting skills overtime which brings more value to investors rather than recent analyst's performance that, presumably, takes advantage of the price momentum.
@@
  \midrule 
-\tr{} & - & - & - & - & - & - \\ 
+\tr{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\ 
   \naive{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\ 
@@
  \midrule 
-1999 & - & - &   71 &   67 &   42 &   42 \\ 
-  2000 & - & - &  253 &  232 &  191 &  191 \\ 
-  2001 & - & - &  302 &  273 &  244 &  244 \\ 
-  2002 & - & - &  353 &  316 &  289 &  289 \\ 
-  2003 & - & - &  369 &  330 &  299 &  299 \\ 
-  2004 & - & - &  375 &  331 &  318 &  318 \\ 
-  2005 & - & - &  395 &  347 &  337 &  337 \\ 
-  2006 & - & - &  403 &  351 &  337 &  337 \\ 
-  2007 & - & - &  418 &  359 &  351 &  351 \\ 
-  2008 & - & - &  413 &  353 &  339 &  339 \\ 
-  2009 & - & - &  346 &  306 &  306 &  306 \\ 
-   \midrule 
-Total & - & - &  442 &  378 &  375 &  375 \\
+1999 &   71 &   67 &   71 &   67 &   42 &   42 \\ 
+  2000 &  257 &  235 &  253 &  232 &  191 &  191 \\ 
+  2001 &  310 &  281 &  302 &  273 &  244 &  244 \\ 
+  2002 &  360 &  321 &  353 &  316 &  289 &  289 \\ 
+  2003 &  374 &  334 &  369 &  330 &  299 &  299 \\ 
+  2004 &  385 &  341 &  375 &  331 &  318 &  318 \\ 
+  2005 &  401 &  352 &  395 &  347 &  337 &  337 \\ 
+  2006 &  415 &  358 &  403 &  351 &  337 &  337 \\ 
+  2007 &  421 &  361 &  418 &  359 &  351 &  351 \\ 
+  2008 &  422 &  360 &  413 &  353 &  339 &  339 \\ 
+  2009 &  405 &  351 &  346 &  306 &  306 &  306 \\ 
+   \midrule 
+Total &  442 &  378 &  442 &  378 &  375 &  375 \\
 
@@
 Within each panel, we show the strategy results of three views regarding expected return: \textit{CONS} uses the median of the analysts estimates; \textit{TP} is based upon TP accuracy ranking; and \textit{EPS} is based upon  EPS accuracy ranking.
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
 The trading period goes from 2000Q1 until 2009Q4.
 
-\begin{tabularx}{\linewidth}{r*{5}{Y}}
+\begin{tabularx}{\linewidth}{c*{5}{Y}}
   \toprule
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
+  \multicolumn{11}{l}{\textbf{Panel B: \tr{} }} \\
   &\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same{}&\all{}&\same {}\\
 
- \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
+ \textit{CONS} & 0.116 & 0.434 & 15.948 & 15.995 & 0.007 & 0.027 &  283 &  251 & 0.256 & 0.251 \\ 
   \textit{TP} & 4.325 & 4.549 & 14.697 & 14.794 & 0.294 & 0.307 &  283 &  251 & 0.345 & 0.327 \\ 
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
+  \multicolumn{11}{l}{\textbf{Panel C: \naive{}}} \\
  \textit{CONS} & 0.116 & 0.434 & 15.948 & 15.995 & 0.007 & 0.027 &  283 &  251 & 0.256 & 0.251 \\ 
@@
 \begin{tabular}{rrrrrrrrrrr}
-  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
+  \multicolumn{11}{l}{\textbf{Panel D: \default{}}} \\
  \textit{CONS} & 0.314 & 0.686 & 15.773 & 15.825 & 0.020 & 0.043 &  283 &  251 & 0.228 & 0.223 \\ 
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.844 & 0.395 & 1.890 & 0.124 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.119 & 0.425 & 3.945 & 0.270 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.124 & 0.757 & 5.877 & 0.492 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.715 & 1.915 & 10.681 & 1.364 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.908 & 0.070 & -3.133 & -0.232 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.827 & 0.189 & -0.725 & -0.045 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & - & - & 4.325 & 0.294 & 0.574 & 0.037 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 2.663 & 0.167 & 5.844 & 0.395 & 1.890 & 0.124 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.669 & 0.170 & 6.119 & 0.425 & 3.945 & 0.270 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.734 & 0.447 & 9.124 & 0.757 & 5.877 & 0.492 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.548 & 1.106 & 14.715 & 1.915 & 10.681 & 1.364 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.708 & -0.343 & 0.908 & 0.070 & -3.133 & -0.232 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.367 & -0.146 & 2.827 & 0.189 & -0.725 & -0.045 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.116 & 0.007 & 4.325 & 0.294 & 0.574 & 0.037 \\
 
@@
   \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
-2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 6.609 & 0.451 & 2.116 & 0.139 \\ 
-  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.226 & 0.432 & 4.161 & 0.286 \\ 
-  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 8.985 & 0.768 & 5.827 & 0.486 \\ 
-  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.249 & 1.891 & 10.672 & 1.361 \\ 
-  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.398 & 0.030 & -3.126 & -0.232 \\ 
-  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.528 & 0.166 & -0.658 & -0.041 \\ 
-   \midrule 
-All period & -3.032 & -0.182 & - & - & 4.549 & 0.307 & 0.719 & 0.046 \\
+2000Q1/2004Q4 & -3.401 & -0.201 & 3.378 & 0.213 & 6.609 & 0.451 & 2.116 & 0.139 \\ 
+  2001Q1/2005Q4 & -1.539 & -0.093 & 2.825 & 0.180 & 6.226 & 0.432 & 4.161 & 0.286 \\ 
+  2002Q1/2006Q4 & 2.567 & 0.196 & 5.836 & 0.468 & 8.985 & 0.768 & 5.827 & 0.486 \\ 
+  2003Q1/2007Q4 & 7.919 & 0.925 & 9.417 & 1.100 & 14.249 & 1.891 & 10.672 & 1.361 \\ 
+  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & 0.398 & 0.030 & -3.126 & -0.232 \\ 
+  2005Q1/2009Q4 & -2.662 & -0.158 & -2.426 & -0.148 & 2.528 & 0.166 & -0.658 & -0.041 \\ 
+   \midrule 
+All period & -3.032 & -0.182 & 0.434 & 0.027 & 4.549 & 0.307 & 0.719 & 0.046 \\
 
@@
 \textit{EPS} is the strategy with rankings based on the accuracy of EPS forecasts.
-Stocks in the \all{} set are part of the S\&P 500, stocks in the \same{} set are part of both the EPS and TP datasets.
-The trading period ranges from 2000Q1 until 2009Q4
+Stocks in the \all{} sample are subsamples of the S\&P 500, stocks in the \same{} sample integrate both the EPS and TP datasets.
+The trading period ranges from 2000Q1 until 2009Q4.
 \end{figure}

### 2015-04-13 src/paper.trading.APS.true.R

@@ -96,12 +96,18 @@ require(scales)
 
 conf.dt <- melt(unique(core.dt,by=c('q.id','Stock','type'),fromLast = T)[,.(q.id,Stock,s.coefVar,type)][,true:=0][,naive:=c(NA,head(s.coefVar,-1)),by=.(Stock,type)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T,partial=T),by=.(Stock,type)],id.vars = c('q.id','Stock','type'),measure.vars = c('true','naive','default'))[q.id!='1999 Q2',]
 
+### for CONS strategy true confidnece = naive confidence
+cons.conf.dt <- melt(unique(core.dt,by=c('q.id','Stock','type'),fromLast = T)[,.(q.id,Stock,s.coefVar,type)][,true:=0][,naive:=c(NA,head(s.coefVar,-1)),by=.(Stock,type)][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T,partial=T),by=.(Stock,type)][,true:=naive],id.vars = c('q.id','Stock','type'),measure.vars = c('true','naive','default'))[q.id!='1999 Q2',]
+
 #conf.dt <- melt(conf.dt[,naive:=c(NA,head(s.coefVar,-1)),by=Stock][,default:=rollapplyr(naive,seq_len(length(naive)),mean,na.rm=T,partial=T),by=Stock],id.vars = c('q.id','Stock'),measure.vars = c('true','naive','default'))[q.id!='1999 Q2',]
 
 
 conf.coef <- dlply(conf.dt,'type',acast,q.id~Stock~variable,value.var='value')
 
+cons.conf.coef <- dlply(cons.conf.dt,'type',acast,q.id~Stock~variable,value.var='value')
+
 eps.stocks <- intersect(dimnames(eps.list.rank[[1]])[[2]],dimnames(conf.coef[[1]])[[2]])
+
 
 #same.stocks <- intersect(intersect(dimnames(pt.list.rank)[[2]],dimnames(conf.coef)[[2]]),dimnames(eps.list.rank)[[2]])
 
@@ -127,7 +133,7 @@ opt.w <- rbindlist(mclapply(c('same','all'),function(t)
 {
 rbind(
         opt.w.f(pt.list.rank[[t]],conf.coef[[t]],tau)[,Views:='TP'],
[…]

### 2015-04-16 doc/paper/paper-knitr-APS.Rnw
submitted version to FAJ

@@
 \title{Are rankings of financial analysts useful to investors?}
- \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
- \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
- \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
-
-\affil[1]{FEP \& CEF.UP, University of Porto}
-\affil[2]{INESC TEC}
-\affil[4]{FEUP, University of Porto}
+% \author[1,2]{ Artur Aiguzhinov (\href{mailto:artur.aiguzhinov@inescporto.pt}{artur.aiguzhinov@inescporto.pt})}
+% \author[1]{ Ana Paula Serra (\href{mailto:aserra@fep.up.pt}{aserra@fep.up.pt})}
+% \author[2,4]{Carlos Soares (\href{mailto:csoares@fe.up.pt}{csoares@fe.up.pt})}
+
+%\affil[1]{FEP \& CEF.UP, University of Porto}
+%\affil[2]{INESC TEC}
+%\affil[4]{FEUP, University of Porto}
 
